### 2014-03-26 ms_probaweb.tex

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{color,lineno,setspace,multirow,kpfonts}
\usepackage{graphicx}
\usepackage[top=2.4cm,left=2.4cm,top=2.4cm,bottom=2.4cm,includefoot]{geometry}
\usepackage[style=bes]{biblatex}
\usepackage{rotating}

\bibliography{library}

\begin{document}

\linenumbers 
\modulolinenumbers[1]

\textbf{Title:} A quantitative framework for network biogeography\\
% Alternative: The distribution of ecological interactions

\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Timoth\'ee Poisot$^{1,2,3}$, Neo
Martinez$^{4}$, Jennifer Dunne$^{5}$, Jason Tylianakis$^{3}$, Nicolas
Mouquet$^{6}$, Daniel Stouffer$^{3}$ \\

1: Canada Research Chair in Biogeography and community ecology. D\'epartement de
biologie, chimie et g\'eographique, Universit\'e du Qu\'ebec \`a Rimouski, 300
All\'ee des Ursulines, Qu\'ebec, Canada. G5L 3A1.\\

2: Qu\'ebec Centre for Biodiversity Sciences\\

3: \\

4: \\

5: \\

6:\\

\textbf{Keywords:} networks, spatial ecology, co-occurrence, probability of interaction\\

\textbf{Words in the abstract:}

\textbf{Words in the main text:}

\textbf{Words in the legends:}

\textbf{Figures:}

\textbf{Tables:}

\textbf{References:}

\newpage
\doublespacing

%========================================================%
\section*{Abstract}

\newpage
%========================================================%
\section*{Introduction}

\begin{itemize}
\item The community is more than a species list. Interactions are central. \\

\item Network structure do vary in space in time. \\

\item We don't know yet to what extent interactions are varying with the
environment. \\

\item No theory to explain and interpret the meaning of network variation in space.
Current interpretation fo species turnover involves the effect of the
environment and stochasticity. \\

\item Objective: Propose a theoretical framework to understand and predict the
spatial and temporal variation in network structure.\\

\end{itemize}

\newpage
%========================================================%
\section*{A probabilistic representation of ecological networks}

Interaction networks do vary in space and time because any given pairwise
interaction could either occur or not at any particular location. We seek to
represent the probability an interaction between species $i$ and $j$ occurs at
location $y$. We consequently define $L_{ijy}$ as a stochastic variable taking a
value of 1 when an interaction occurs and are thus looking at the probabilty of
this event, $P(L_{ijy})$. There are several factors that could impact the
occurrence of an interaction and we will describe them below. But ultimately,
this probability depends on the spatial and temporal scale of observation. As
long as the interaction probability is not null, the probability of observing an
interaction will tend to 1 as the scale of observation increases.

The occurrence of an interaction requires the co-occurrence of species
$i$ and $j$. This argument might seem trivial at first, but the explicit
consideration of this condition in the probabilistic representation of
ecological networks will prove fundamental to understand their variation. We
thus define $X_{iy}$ as a stochastic variable representing the occurrence of a
species $i$ at location $y$, and similarly $X_{ijy}$ the co-occurrence of species
$i$ and $j$. The quantity we seek to understand is the probability of a joint
event:

%-----------------
\begin{equation}
	P(X_{iy},X_{jy},L_{ijy},)
\end{equation}
%-----------------

Which reads as the probability of observing species $i$, species $j$ and an
interaction between them. This probability could be further decomposed in two parts using the
product rule of probabilities:
%-----------------
\begin{equation}
	P(X_{iy},X_{jy},L_{ijy})=P(L_{ijy}|X_{iy},X_{jy},E_y)P(X_{iy},X_{jy}|E_y)
\end{equation}
%-----------------
We will refer to the left term as the metaweb. It is a conditional probability,
representing the probability that an interaction occurs if species $i$ and $j$
are co-occurring. The right term is the probability of observing the two species
co-occurring at location $y$.

The metaweb concept is making its way through the network litterature even
though it has never been formally and technically defined. It is usually
conceived as a network of interactions among species that could potentially
co-occur. It is usually represented by a binary matrix and thus
deterministically. Here we define it as the matrix of interaction probabilities
between co-occurring species. It thus represents potential interactions and
should therefore include interactions between species that never co-occurred but
are susceptible to. The problem with most representations of metawebs to date is
that the effect of co-occurrence is never factored out. The traditional approach
to build a metaweb is to cumulate observations across replicated networks. The
main problem with that approach is that the co-occurrence of rare species is
extremely unlikely and thus most often appear as an absence of interactions in
the metaweb. This approach is inappropriate because the observed co-occurrence
will have a strong signature on the evaluation of interactions. A rarefaction
analysis previously shown that interactions accumulate with the addition of
networks at a slower rate than species richness. It indicates that it is harder
to have a direct evaluation of interactions from observeration than it is to
evaluate species richness. If built from the observation of interactions, then
the only way to fill a metaweb is by running cafeteria experiments between all
pairs of species. Otherwise, the metaweb should be inferred using traits and
phylogenetic information. Most of the published metawebs are therefore
incomplete because of their sensitivity to sampling heterogeneity. We will come
back to the issue of evaluating the metaweb in the sections Example and Applications

There are many variants of the metaweb representing different hypotheses about
the origin of temporal and spatial variation in network structure (see the
explicit formulations at Table 1). First, the interaction could be 
deterministic instead of probabilistic. In other words, $P(L_{ijy}) = 1$ if
$X_{ijy} = 1$, and 0 otherwise. This representation of the metaweb is the one
mostly used so far, as soon as the species are found together they are assumed
to interact. It is also the only way to represent interactions when there is not
enough information available to evaluate the interaction probability. It should be a
reasonnable approximation when the sampling and inferrence scales are large
enough and that the only variation of networks considered arises from species
distribution.

Ecological interactions could also depend on the environment.
Although it is not common to see a conditional representation of ecological
interactions, experimental studies of pairwise interactions revealing their
sensitivity to the environment are common (REF). For instance, it has been
documented that the predation risks of shorebirds do vary at the continental
scale, from the south to the north (REF). The effect of the environment on
interactions propagate up the community and influence network structure (REF).
Here the environment is considered in a very broad sense, as any factor
potentially influencing the probability of a pairwise interaction, provided that
the species co-occur. It thus includes both the biotic and the abiotic
components of environment. We note however that here the biotic environment
includes organisms that are not considered in the co-occurrence matrix.
Including a biotic component to the metaweb signifies that the pairwise
interaction is conditional on higher order interactions. An interaction modifier
occurs for instance when the predation risk by species $j$ might be impacted by
a parasite $k$ changing the behaviour of the prey $i$. We note that a
conditional probability approach could thus be used represent non-trophic
interactions into ecological networks (REF). This topic is however beyond the
scope of the current paper.

There are also variants to the co-occurrence matrix. Akin to the metaweb,
co-occurrence could be conditional or not. The simplest model relates
co-occurrence probability directly to the environment. In this situation there
is no underlying assumption about the ecological processes responsible for
co-occurrence. Alternatively, the co-occurrence probability could be a function
of the environment because of shared ecological requirements by the two species.
Species are independently distributed, but co-occur more often that expected by
chance alone because they are found on the same environments. We call this model
later neutral because species are specifically responding to the environment but
are independently distributed. Co-occurrence is then simply obtained by
multiplying the result of two independent and specific species distribution
models (SDM).

Finally, the co-occurrence probability itself could be dependent on ecological
interactions. Direct pairwise interactions such as competition, facilitation and
predation have long been studied for their impact on co-distribution. Second and
higher order interactions (e.g. trophic cascade) could also impact
co-occurrence. There is however currently no general theory on the expected
co-occurrence in complex ecological networks. For instance, we do not know how
far co-occurrence is not-random when going along the chain of indirect
interactions. Berlow(2009) shown previously that almost only first and second
order interactions do matter in food webs, but we don't know for
co-distribution. We neither know what is the sensitiviy to species richness: do
interactions tend to buffer each other? Generalizing knowledge aquired by the
study of small community modiles will require future research.

\newpage
%========================================================%
\section*{Interpretation: the integrated niche}

The niche concept is central in biogeography to understand and predict species
distribution. Several attempts have been made to refresh the concept, but its
main usage still follows Hutchinson’s idea that species interactions restrict
the fundamental niche to a realized one. Despite its intuitive
interpretation and translation into species distribution models, the 
concept has been constantly criticized (Hardin, 1960; Peters, 1991;
Chase2003; Silvertown, 2004; Soberon, 2007) and several attempts have
been made to expand and reinforce it.

Part of the problem surrounding the definition of the niche has been clarified
with the distinction between Eltonian and Grinnellian definitions (ChaseLeibold
2003). The Grinnellian dimension of the niche is the effect of the environment
on the demography of a species, while the Eltonian dimension is the effect of a
species on its environment sensu lato. The Grinnellian niche is the most
intuitive one to apply and is the conceptual backbone of species distribution
models. The Eltonian niche is well known by food web ecologists, but it is much
more difficult to formulate into distribution models. Nonetheless, the
development of the niche model of food web structure (Williams2000) and its parameterization (Williams2010; Gravel2013) made
it more operational.

While it is straigthforward to represent statistically the hyper volume where a species
occurs, it is much more challenging to account for ecological interactions.
Chase and Leibold (2003) attempted this representation in their definition:
\textit{[The niche is] the joint description of the environmental conditions
that allow a species to satisfy its minimum requirements so that the birth rate
of a local population is equal or greater than its death rate along with the set
of per capita effects of that species on these environmental conditions.} They
represented the niche graphically with zero-net growth isoclines (the Grinnelian
niche) and impact vectors (the Eltonian niche). While this representation has
been very influential in community ecology at the local scale, it remains
unpracticable at the biogeographical one. The absence of any mathematical
representation of the niche that could easily be fit to ecological data perhaps
explain why biogeographers are still struggling to develop species distribution
models taking into account ecological interactions.

The key point to integrate dimensions of the niche is to represent the Eltonian niche into a Grinnelian space. 
- We do so by considering that the Eltonian niche is the hyper volume in the trait-space allowing an interaction. \\
- Doing so, we could project both niches in a plane and find the hypervolume where an interaction should occur (Fig. 2). \\
- This visual representation is parallel to the probabilistic definition of interaction probability. \\
- We propose that the metaweb is the Eltonian dimension of the niche, while the matrix of co-occurrence is the Grinnellian dimension. \\
- Feedbacks between dimensions occur through the inclusion of co-occurrence in the metaweb, and interactions in the co-occurrence matrix. \\
- This approach radically change the representation of the niche, putting species distribution and ecological interactions at the same level. \\
- Fitting the probabilistic model allows the evaluation of link distribution and species distribution models. \\
- Moreover, the integrated niche concept facilitates the formulation of species distribution models taking into account biotic interactions (see the section Applications) \\

 % TO BE COMPLETED

\newpage
%========================================================%
\section*{Example: network structure in different habitats}

In this section we provide an analysis illustrating the framework with an
empirical dataset of host-parasitoid networks. Data come from the study of
Tylianakis(2007) on the impacts of habitat modifications to the network
structure. The data consists of 48 networks with 4090 recorded interactions. The
advantage of replicated host-parasitoid networks is that usually every
interaction is observed, not inferred from a stationary metaweb. It thus allows
to evaluate interaction probability and to factor out the effect of
co-occurrence. Five habitats were sampled along a gradient of habitat
modification: forest, abandonned coffee agroforest, coffee agroforest, pasture
and rice culture. The metaweb consists of 9 parasitoids and kleptoparasites
(Hymenoptera: Eulophidae, Ichneumonidae, Leucospidae, Megachilidae and
Chrysididae; Dyptera: Bombyliidae) of 33 species of bees and wasps (Hymenoptera:
Apidae, Megachilidae, Mutilidae, Pompilidae, Sphecidae, Vespidae). The metaweb
is illustrated at Fig. 2, along with an example of one iteration of the metaweb.

Tylianakis (2007) investigated if habitat modification affects the structure of
these networks They found a significant impact of the habitat on their
structure, despite little variation in species richness. Increasing habitat
modification led to a higher parasitoid to host species ratio and a paraistoid
were also more specialized, thus impacting considerably vulnerability. A closer
inspection of the networks revealed that intensive agricultural systems were
dominated by a strong interaction and a specialization of the most abundanc
parasitoid. Although the discussion made clear that both the turnover in species
composition and the interaction probability changed with habitat modification,
it was not possible to partition these components.

We developped a R package (REF) to fit alternative formulations of the metaweb
and the co-occurrence matrix along an environmental gradient and run it to
re-interpret the data of Tylianaks (2007). The package provides a general
interface facilitating the development of different species and link
distribution models. It is also built to facilitate the interaction iwth the
Mangal database of ecological interactions (REF). The first step consists of
fitting a probablistic model from the observation of a pairwise interaction
(binary) and the environment (could be categorical or continuous) from the
subset of the data where the two species are co-occurring. In other words, it
fits the equation $P(L_{ijy}|X_{iy},X{jy},E_y)$ to the data where $X_{iy} = 1$
and $X_{iy} = 1$. Logistic regression was used and is currently programmed, but
alternative models could be used as well. The second steps consists of fitting a
a probabilistic model for co-occurrence over the whole dataset,
$P(X_{iy},X{jy}|E_y)$, independently of the observation of an interaction. The
two probabilities are then multiplied to obtain the probability of observing an
interaction (Eq. 2). We used this probability to compute the likelihood of each
observation ($\zeta(\theta|D) = P(L_{ijy},X_{iy},X_{jy})$ if $L_{ijy}=1$ and
$\zeta(\theta|D) = 1 - P(L_{ijy},X_{iy},X_{jy})$ otherwise). We then after
compare the models by their AIC.

We considered the gradient of habitat modification as a ordered categorical
variable and compared XX models (results are summarized at Table 2). Not
surprisingly the best model takes into account the effect of the environment on
both the metaweb and co-occurrence. What is most interesting are the comparisons
to the best model. First, we find that using a constant metaweb has a dramatic
impact on the fit of the model to the data (the AIC drops from X for model 1 to
X for model 2), indicating a strong effect of the environment on pairwise
interactions. Secondly, we find that the deterministic metaweb is the worst
model (model 3, AIC = ). This result indicate that the traditional appraoch to
consider that species interact as soon as they co-occur is definitely wrong.
Thirdly, we also find that using a constant co-occurrence does have a
significant impact on the model (the AIC drops to X, model 4), indicating there
is a non-random change in community composition with habitat modification. Taken
together, these two results better explain why network structured changed with
habitat modification, even though here we only used binary information about the
network structure. Another interesting result is that considering a neutral
co-occurrence did not impact much the fit of the modeel. The AIC drops to XX
with model 6, indicating that considering indepdenent SDMs yields similar
networks over this environmental gradient. This means that for this particular
dataset, ecological interactions does not have a strong impact on species
distribution since; a strong dependence of parasitoids to the host for instance
would have a occurrence probability higher than expected by chance, while a
repulsion would have had the opposite.

An important output of this analysis is a more explicit representation of the
uncertainty in the evaluation of the metaweb. We find that among the XX pairs of
host and parasitoids, XX did not co-occur. There were therefore many forbidden
links based on co-occurrence. These might never occur in reality, but we do not
know without doing extra experiments. Therefore, any analysis of the structure
of the metaweb would be inappropriate without filling those gaps. In addition to
specific experiments, the gaps could be filled with a trait-based approach,
using phylogenies or with a null hypothesis (e.g. the interaction probability is
equal to connectance computed on the observed interactions).

It is also possible to obtain for each pairwise interaction an estimate of the
uncertainty. Not surprisingly, the confidence interval is usually very high for
the estimation of a probability with a very small sample size. The standard
error on the evaluation of the interaction probability is provided along with
the metaweb at Fig. 3. It reveals that the uncertainty is very high for most
interactions, even if 48 networks were sampled. Such an approach could be used
to detect wich pairwise interaction requires additional sampling in order to
reduce the uncertainty to a manageable level.

\newpage
%========================================================%
\section*{Applications}

\subsection*{Network descriptors}

\subsection*{Partitionning beta diversity}

\subsection*{Null model testing}

\subsection*{Species \& link distribution models}

\newpage
%========================================================%
\section*{Conclusion}

\begin{itemize}
\item New research agenda\\

\item List of new questions \\
\end{itemize}

\newpage
%========================================================%
\section*{Acknowledgements}
This is tis a contribution to the Santa Fe Institute working group \emph{Networks over
ecological gradients}. DG received financial support from NSERC and Canada
Research Chair program. TP is supported by a MELS-FQRNT post-doctoral
fellowship.
\newpage

%========================================================%
\printbibliography

\newpage
%========================================================%
\section*{Figure legends}

%------------------------
\subsection*{Figure 1}
\textbf{Non-random sampling of the metaweb}. The sampling of the metaweb is illustrated with a local interaction network from the Tylianakis et al (2007) dataset. Here the metaweb is simply the number of observed interactions over the 48 networks. Arrows points to species that are present in the local network \#34 (represented on the right).

%------------------------
\subsection*{Figure 2}
\textbf{The integrated niche}.  The Grinnellian niche is the set of environmental conditions
where the intrinsic growth rate $r$ is positive (axioms i, ii \& iii).
Contingencies (axiom iv) such as disturbances and stochastic extinctions, in
conjunction with limited dispersal (axiom v), restrict species distribution to
the conditions where the colonization rate $c$ is larger than extinction rate
$e$. The Eltonian niche on the other dimension is represented by the set of
traits allowing species to interact (axiom viii). The red species is a predator
with a trophic position $n$, feeding on species whose niche is within a certain
range around the niche optimum $c$. The integrated niche combines the effects of
the environment and ecological interactions. The central square represents the
area where the joint probability of observing interactions and co-occurrence is
positive.

%------------------------
\subsection*{Figure 3}
\textbf{Uncertainty in the evaluation of the metaweb}. The inferred metaweb for the XX environment is represented (left), along with the uncertainty in the evaluation of the interaction probability (right). Note that the standard error for probabilities is not symetric and thus only the upper bound is represented.

\newpage
%========================================================%
%------------------------
\subsection*{Figure 1}

\begin{figure}[ht!]
	\centering\includegraphics[width=0.8\textwidth]{sampling}
\end{figure}

\newpage

%------------------------
\subsection*{Figure 2}

\begin{figure}[ht!]
	\centering\includegraphics[width=0.8\textwidth]{niche}
\end{figure}

\newpage

%------------------------
\subsection*{Figure 3}

\begin{figure}[ht!]
	\centering\includegraphics[width=0.8\textwidth]{niche}
\end{figure}

\newpage

%========================================================%

%------------------------
\begin{table*}[c]
	\centering
	\begin{tabular}{p{4cm}p{4cm}p{6cm}}
	\hline
	Name & Equation & Details \\
	\hline
	\textbf{Metaweb} &   &  \\
	Constant & $P(L_{ijy}|X_{iy},X_{jy})$ & Interaction probability is invariant to the environment \\
	Conditional & $P(L_{ijy}|X_{iy},X_{jy},E_y)$ & Interaction probability is a function of the local environment \\
	Deterministic & $P(L^*_{ijy}|X_{iy},X_{jy})$ & Interaction occurs whenever both species are present \\

	\textbf{Co-occurrence} & &\\
	Constant & $P(X_{iy},X_{jy})$ & Species distribution independent of $E$ \\
	Conditional on $E$ & $P(X_{iy},X_{jy} |E_y)$ & Similar to a SDM applied to co-occurrence \\
	Neutral & $P(X_{ix}|E_y)P(X_{jy}|E_y)$ & Independent SDMs fit to both species; could be independent of $E$ \\
	Conditional on $L_y$ & $P(X_{iy},X_{jy} | L_y)$ & Could account for first and higher order interactions \\
	\hline
	\end{tabular}
	\caption{List of different models}
\end{table*}

\newpage

%------------------------

\begin{sidewaystable}[c]
	\centering
	\begin{tabular}{lllllllll}
	\hline
	\textbf{Model} & \textbf{Metaweb} & & & \textbf{Co-occurrence} & & & \textbf{$L(H|D)$} & AIC\\
	 & Constant & Cond. on $E$ & Deterministic & Constant & Cond. on $E$ & Neutral & & \\
	\hline
	1. & X & & &  & X & & 0 & 0 \\
	2. & & X & &  & X & & 0 & 0 \\
	3. & &  & X & & X & & 0 & 0 \\
	4. & & X & & X & & & 0 & 0 \\
	5. & & X & & & X & & 0 & 0 \\
	6. & & X & & & & X & 0 & 0 \\
	\hline
	\end{tabular}
	\caption{Model comparison with the host-parasitoid networks. The 48 networks were fitted to different models of interaction networks. Note that for the computation of the likelihood all null interaction probabilities, co-occurrences and the pairwise interactions without observed co-occurrences were removed.
}
\end{sidewaystable}

\newpage

\end{document}
%========================================================%

### 2014-03-26 ms_probaweb.tex
Bibtex file for Tim

@@
 
-\bibliography{library}
+\bibliography{library, tim}
 
@@
 
-The niche concept is central in biogeography to understand and predict species
-distribution. Several attempts have been made to refresh the concept, but its
-main usage still follows Hutchinson’s idea that species interactions restrict
-the fundamental niche to a realized one. Despite its intuitive
-interpretation and translation into species distribution models, the 
-concept has been constantly criticized (Hardin, 1960; Peters, 1991;
-Chase2003; Silvertown, 2004; Soberon, 2007) and several attempts have
-been made to expand and reinforce it.
+The niche concept is key to understand and predict species
+distribution. Several attempts have been made to refresh it, but its main
+usage still follows Hutchinson’s idea that species interactions restrict
+the fundamental niche to a realized one \parencite{Blonder2014}. Despite its
+intuitive interpretation and translation into species distribution models,
+the concept has been constantly criticized (Hardin, 1960; Peters, 1991;
+Chase2003; Silvertown, 2004; Soberon, 2007) and several attempts have been
+made to expand and reinforce it.
 

### 2014-03-26 ms_probaweb.tex
Some edits, first sentence of the intro

@@
 
+Most ecology textbooks define the ecological community at \quote{the pool of
+species occupying a given location at a given time, and the list of their
+interactions} (ref to Morin?). Yet we oft forget the last part of this
+definition, focusing on species and neglecting the way they interact.
+
 \begin{itemize}
-\item The community is more than a species list. Interactions are central. \\
-
 \item Network structure do vary in space in time. \\
@@
 usage still follows Hutchinson’s idea that species interactions restrict
-the fundamental niche to a realized one \parencite{Blonder2014}. Despite its
+the fundamental niche to a realized one, and ecologists haven't moved far past
+the n-dimensional hypervolume formalism \parencite{Blonder2014}. Despite its
 intuitive interpretation and translation into species distribution models,
@@
 
-Part of the problem surrounding the definition of the niche has been clarified
-with the distinction between Eltonian and Grinnellian definitions (ChaseLeibold
-2003). The Grinnellian dimension of the niche is the effect of the environment
-on the demography of a species, while the Eltonian dimension is the effect of a
-species on its environment sensu lato. The Grinnellian niche is the most
-intuitive one to apply and is the conceptual backbone of species distribution
-models. The Eltonian niche is well known by food web ecologists, but it is much
-more difficult to formulate into distribution models. Nonetheless, the
-development of the niche model of food web structure (Williams2000) and its parameterization (Williams2010; Gravel2013) made
-it more operational.
+Part of the problem surrounding the definition of the niche has been
+clarified with the distinction between Eltonian and Grinnellian definitions
+(ChaseLeibold 2003). The Grinnellian dimension of the niche is the effect of
+the environment on the demography of a species, while the Eltonian dimension
+is the effect of a species on its environment \emph{sensu lato}.  % SNOB!
+The Grinnellian niche is the most intuitive one to apply and is the conceptual
+backbone of species distribution models. The Eltonian niche is well known
+by community ecologists, but is trickier to turn into predictive models
+\parencite{Devictor2010a}. Nonetheless, the development of the niche model
+of food web structure (Williams2000) and its parameterization (Williams2010;
+Gravel2013) made it more operational, although it has yet to be applied to
+more than trophic interactions. %Y'a pas que les food webs dans la vie!
 
@@
 been very influential in community ecology at the local scale, it remains
-unpracticable at the biogeographical one. The absence of any mathematical
+unpracticable at the biogeographical one.
+% Why (or more to the point, what do we care about having the same definition at different scales?)?
+The absence of any mathematical
 representation of the niche that could easily be fit to ecological data perhaps

### 2014-03-27 ms_probaweb.tex
paragraph on sampling

@@
 interactions. Berlow(2009) shown previously that almost only first and second
-order interactions do matter in food webs, but we don't know for
+order interactions do matter in ecological networks, but we don't know for
 co-distribution. We neither know what is the sensitiviy to species richness: do
@@
 Gravel2013) made it more operational, although it has yet to be applied to
-more than trophic interactions. %Y'a pas que les food webs dans la vie!
+more than trophic interactions.
 
@@
 
+\subsection*{Guidance for empirical studies}
+
+Ecological networks are known to be extremely sparse, \emph{i.e.} having far
+more absences of interactions that they have interactions. These absences of
+interactions, however, can come from different sources. The fact that unequal
+sampling at the local scale can affect our understanding of network structure
+is well documented \parencite{Martinez1999}. However, in a spatial context,
+some interactions may be undocumented because the species involved have
+never been observed in co-occurence. Although these are reported as a lack
+of interactions, in actuality we cannot make inference about them seeing
+that they have never been observed: it is possible that this interaction
+may happen should the two species co-occur. A second category of absences
+of interactions are those that are reported after multiple observations of
+species co-occurence. However, so as to have a confidence in the fact that the
+probability of an interaction is low, extensive sampling (that is, several
+co-occurences) is needed. Generally, our confidence that the interaction
+is indeed impossible will increase when the number of observations of the
+species pair. Seeing that this is essentialy a Bernoulli process (what is
+the probability that the species will interact given their presence), the
+breadth of the confidence interval is expected to saturate after a fixed
+number of observations, which can be set as a treshold above which a species
+paier has been observed "often enough".
+
 \subsection*{Null model testing}
@@
 Research Chair program. TP is supported by a MELS-FQRNT post-doctoral
-fellowship.
+fellowship. DG, TP, and DBS received financial support from the CIEE.
 \newpage

### 2014-03-28 ms_probaweb.tex
Added two alternative titles
Updated the biblatex command styles, and a bunch of edits in the intro

@@
 \usepackage[top=2.4cm,left=2.4cm,top=2.4cm,bottom=2.4cm,includefoot]{geometry}
-\usepackage[style=bes]{biblatex}
+\usepackage[style=bes, backend=bibtex]{biblatex}
 \usepackage{rotating}
 
-\bibliography{library, tim}
+\addbibresource{tim.bib}
 
@@
 % Alternative: The distribution of ecological interactions 
+% Alternative: The biogeography of ecological interactions
+% Alternative: Community (macro)ecology: integrating species interactions and species distributions
 
-\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Timoth\'ee Poisot$^{1,2,3}$, Neo
-Martinez$^{4}$, Jennifer Dunne$^{5}$, Jason Tylianakis$^{3}$, Nicolas
-Mouquet$^{6}$, Daniel Stouffer$^{3}$ \\
+\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Timoth\'ee Poisot$^{1,2,3}$, N\'eo
+Martinez$^{4}$, Jennifer A. Dunne$^{5}$, Jason Tylianakis$^{3}$, Nicolas
+Mouquet$^{6}$, Daniel B. Stouffer$^{3}$ \\
 
 1: Canada Research Chair in Biogeography and community ecology. D\'epartement de
-biologie, chimie et g\'eographique, Universit\'e du Qu\'ebec \`a Rimouski, 300
+biologie, chimie et g\'eographie, Universit\'e du Qu\'ebec \`a Rimouski, 300
 All\'ee des Ursulines, Qu\'ebec, Canada. G5L 3A1.\\
@@
 
-Most ecology textbooks define the ecological community at \quote{the pool of
-species occupying a given location at a given time, and the list of their
-interactions} (ref to Morin?). Yet we oft forget the last part of this
-definition, focusing on species and neglecting the way they interact.
+Ecology textbooks define the structure of an ecological community as
+\emph{the pool of species occupying a given location at a given time, and
+the way these species interact} (ref to Morin?). It is therefore surprizing
+that ecological research on the variation of community structure has focused
+on species turnover (refs), almost entirely neglecting variation in the way
+species interact (refs).
 
@@
 %========================================================%
-\section*{A probabilistic representation of ecological networks}
+\section*{A probabilistic representation of ecological interactions networks}
 
-Interaction networks do vary in space and time because any given pairwise
-interaction could either occur or not at any particular location. We seek to
-represent the probability an interaction between species $i$ and $j$ occurs at
-location $y$. We consequently define $L_{ijy}$ as a stochastic variable taking a
-value of 1 when an interaction occurs and are thus looking at the probabilty of
-this event, $P(L_{ijy})$. There are several factors that could impact the
-occurrence of an interaction and we will describe them below. But ultimately,
-this probability depends on the spatial and temporal scale of observation. As
-long as the interaction probability is not null, the probability of observing an
-interaction will tend to 1 as the scale of observation increases.
+%% We need to be careful: ecological network / interaction network / etc.
+%% I vote interaction networks, ecological network can be a spatial graph.
+%% Also, since we're going to say "interaction" a lot, interaction network
+%% makes sense. -- tp
 
-The occurrence of an interaction requires the co-occurrence of species
-$i$ and $j$. This argument might seem trivial at first, but the explicit
-consideration of this condition in the probabilistic representation of
-ecological networks will prove fundamental to understand their variation. We
-thus define $X_{iy}$ as a stochastic variable representing the occurrence of a
-species $i$ at location $y$, and similarly $X_{ijy}$ the co-occurrence of species
-$i$ and $j$. The quantity we seek to understand is the probability of a joint
-event:
+Networks of species interactions vary in space and time because any given
+pairwise interaction could either occur or not at any particular location.
+Understanding this variation amounts to be able to determine the probability
+that two species ($i$ and $j$) will interact at a given time/location ($y$);
+the existence of an interaction in this situation is thus essentially a
+stochastic variable, which we note $L_{ij,y}$. It takes a value of 1 where the
+interaction occurs, and 0 elsewhere. We note $P(L_{ij,y})$ the probability
+of this event. There are several factors that could impact the occurrence
+of an interaction and we will describe them below. But ultimately, this
+probability depends on the spatial and temporal scale of observation. As long
+as the probability of a particular interaction is not null, the probability
+of observing it at least once will become asymptotically closer to 1 when
+the scale of observation increases.
+% OK I like this paragraph, but we're REALLY NOT talking about factors or mechanisms here.
+% This whole framework is top-down/inferential, so we should at least have a paragraph in the
+% intro essentially summing up our preprint on network variation, and be clear on the
+% fact that we don't touch on mechanisms.
+
+The occurrence of an interaction requires the co-occurrence of species $i$ and
+$j$. This argument might seem trivial at first, but the explicit consideration
+of this condition in the probabilistic representation of ecological networks
+will prove fundamental to understand their variation.
+% We already make this point in betalink, should we summarize it briefly?
+We thus define $X_{iy}$
+as a stochastic variable representing the occurrence of a species $i$ at
+location $y$, and similarly $X_{ijy}$ the co-occurrence of species $i$ and
+$j$. The quantity we seek to understand is the probability of a joint event:
 
@@
 
-\subsection*{Species \& link distribution models}
+% Do you mean "Patterns-generating models testing"?
+
+\subsection*{Species \& interactions distribution models}
 
@@
 \section*{Acknowledgements}
-This is tis a contribution to the Santa Fe Institute working group \emph{Networks over
-ecological gradients}. DG received financial support from NSERC and Canada
-Research Chair program. TP is supported by a MELS-FQRNT post-doctoral
-fellowship. DG, TP, and DBS received financial support from the CIEE.
+This is a contribution to the working groups \emph{Networks over ecological
+gradients} (Santa Fe Institute) and \emph{Continental-scale variation of
+ecological networks}. (Canadian Institute for Ecology and Evolution). DG
+received financial support from NSERC and Canada Research Chair program. TP
+is supported by a MELS-FQRNT post-doctoral fellowship.
 \newpage
@@
 
-\newpage
-
 \end{document}

### 2014-03-29 ms_probaweb.tex
header
Update to the main text, with a reference to issue #4 on the main repo

@@
 \usepackage{amsmath}
-\usepackage{color,lineno,setspace,multirow,kpfonts}
+\usepackage{color,lineno,setspace,multirow}
+\usepackage[sc]{mathpazo}
 \usepackage{graphicx}
@@
 % We already make this point in betalink, should we summarize it briefly?
-We thus define $X_{iy}$
+We thus define $X_{i,y}$
 as a stochastic variable representing the occurrence of a species $i$ at
-location $y$, and similarly $X_{ijy}$ the co-occurrence of species $i$ and
+location $y$, and similarly $X_{ij,y}$ the co-occurrence of species $i$ and
 $j$. The quantity we seek to understand is the probability of a joint event:
@@
 \begin{equation}
-	P(X_{iy},X_{jy},L_{ijy},)
+   \text{P}(X_{i,y},X_{j,y},L_{ij,y},)
 \end{equation}
@@
 
-Which reads as the probability of observing species $i$, species $j$ and an
-interaction between them. This probability could be further decomposed in two parts using the
-product rule of probabilities:
+Or simply said, the probability of observing both species $i$ and $j$, and
+an interaction from $i$ to $j$. This probability could be further decomposed
+in two parts using the product rule of probabilities:
+
 %-----------------
@@
 %-----------------
+
 We will refer to the left term as the metaweb. It is a conditional probability,

### 2014-03-29 ms_probaweb.tex
1. Added a reference to the bibtex file 2. Some work on the definition of the metaweb

@@
 
+% The following paragraph
+% (1) is too long -- I tried to cut some of it, up to half of it
+% (2) comes at an awkward moment -- this is the key issue we try to solve, it should be in the introduction
+
 The metaweb concept is making its way through the network litterature even
-though it has never been formally and technically defined. It is usually
-conceived as a network of interactions among species that could potentially
-co-occur. It is usually represented by a binary matrix and thus
-deterministically. Here we define it as the matrix of interaction probabilities
-between co-occurring species. It thus represents potential interactions and
-should therefore include interactions between species that never co-occurred but
-are susceptible to. The problem with most representations of metawebs to date is
-that the effect of co-occurrence is never factored out. The traditional approach
-to build a metaweb is to cumulate observations across replicated networks. The
-main problem with that approach is that the co-occurrence of rare species is
-extremely unlikely and thus most often appear as an absence of interactions in
-the metaweb. This approach is inappropriate because the observed co-occurrence
-will have a strong signature on the evaluation of interactions. A rarefaction
-analysis previously shown that interactions accumulate with the addition of
-networks at a slower rate than species richness. It indicates that it is harder
-to have a direct evaluation of interactions from observeration than it is to
-evaluate species richness. If built from the observation of interactions, then
-the only way to fill a metaweb is by running cafeteria experiments between all
-pairs of species. Otherwise, the metaweb should be inferred using traits and
-phylogenetic information. Most of the published metawebs are therefore
-incomplete because of their sensitivity to sampling heterogeneity. We will come
-back to the issue of evaluating the metaweb in the sections Example and Applications
+though it has never been formally and technically defined.
+% Yes, but no. All of the people that ever wrote the word "metaweb" are authors on this paper.
+It is usually conceived as a network of interactions among species
+that could potentially co-occur, and represented by a binary matrix,
+\emph{i.e.} a probabilistic matrix in which the probability of observing
+an interaction is either 0 or 1. As the metaweb is usually constructed by
+aggregating observations, it assigns a probability of 0 to the interaction
+of species that never co-occurred, and is unable to factor-out the effect of
+co-occurrence. The main problem with that approach is that the co-occurrence
+of rare species is extremely unlikely and thus most often appear as an absence
+of interactions in the metaweb. This approach is inappropriate because the
+observed co-occurrence will have a strong signature on the evaluation of
+interactions. A rarefaction analysis previously shown that interactions
+accumulate with the addition of networks at a slower rate than species
+richness \parencite{Poisot2012d}. It indicates that it is harder to have a
+direct evaluation of interactions from observeration than it is to evaluate
+species richness. If built from the observation of interactions, then the
+only way to fill a metaweb is by running cafeteria experiments between all
+pairs of species. Otherwise, the metaweb should be inferred using traits
+and phylogenetic information. Most of the published metawebs are therefore
+incomplete because of their sensitivity to sampling heterogeneity. We will
+come back to the issue of evaluating the metaweb in the sections Applications.
 

### 2014-03-29 ms_probaweb.tex
A few refs and edits in the niche section

@@
 %========================================================%
-\section*{A probabilistic representation of ecological interactions networks}
+\section*{A probabilistic representation of ecological interactions networks in space}
 
@@
 
-The niche concept is key to understand and predict species
-distribution. Several attempts have been made to refresh it, but its main
-usage still follows Hutchinson’s idea that species interactions restrict
-the fundamental niche to a realized one, and ecologists haven't moved far past
-the n-dimensional hypervolume formalism \parencite{Blonder2014}. Despite its
-intuitive interpretation and translation into species distribution models,
-the concept has been constantly criticized (Hardin, 1960; Peters, 1991;
-Chase2003; Silvertown, 2004; Soberon, 2007) and several attempts have been
-made to expand and reinforce it.
+Correctly describing the ecological niche is key to understand and predict
+species distribution. Despite several attempts to refresh the conceptual
+basis of what ecological niches are, ecologists haven't moved far past the
+"n-dimensional hypervolume" formalism \parencite{Holt2009} introduced by
+\textcite{Hutchinson1961}. Despite its intuitive interpretation and translation
+into species distribution models \parencite{Blonder2014}, the concept has been
+constantly criticized (Hardin, 1960; Peters, 1991; Chase2003; Silvertown, 2004;
+Soberon, 2007) and several attempts have been made to expand and reinforce it.
 
@@
 clarified with the distinction between Eltonian and Grinnellian definitions
-(ChaseLeibold 2003). The Grinnellian dimension of the niche is the effect of
-the environment on the demography of a species, while the Eltonian dimension
-is the effect of a species on its environment \emph{sensu lato}.  % SNOB!
-The Grinnellian niche is the most intuitive one to apply and is the conceptual
-backbone of species distribution models. The Eltonian niche is well known
-by community ecologists, but is trickier to turn into predictive models
-\parencite{Devictor2010a}. Nonetheless, the development of the niche model
-of food web structure (Williams2000) and its parameterization (Williams2010;
-Gravel2013) made it more operational, although it has yet to be applied to
-more than trophic interactions.
+\parencite{Chase2003}. The Grinnellian dimension of
+the niche is the effect of the environment on the demography of a species,
+while the Eltonian dimension is the effect of a species on its environment
+\emph{sensu lato}.  % SNOB!
+The Grinnellian niche is the most intuitive one
+to apply and is the conceptual backbone of species distribution models. The
+Eltonian niche is well known by community ecologists, but is trickier to
+turn into predictive models \parencite{Devictor2010a}. Nonetheless, the
+development of the niche model of food web structure (Williams2000) and
+its parameterization (Williams2010; Gravel2013) made it more operational,
+although it has yet to be applied to more than trophic interactions.
 
-While it is straigthforward to represent statistically the hyper volume where a species
-occurs, it is much more challenging to account for ecological interactions.
-Chase and Leibold (2003) attempted this representation in their definition:
+\textcite{Chase2003} attempted this representation in their definition:
 \textit{[The niche is] the joint description of the environmental conditions
 that allow a species to satisfy its minimum requirements so that the birth rate
-of a local population is equal or greater than its death rate along with the set
-of per capita effects of that species on these environmental conditions.} They
-represented the niche graphically with zero-net growth isoclines (the Grinnelian
-niche) and impact vectors (the Eltonian niche). While this representation has
-been very influential in community ecology at the local scale, it remains
-unpracticable at the biogeographical one.
-% Why (or more to the point, what do we care about having the same definition at different scales?)?
-The absence of any mathematical
-representation of the niche that could easily be fit to ecological data perhaps
-explain why biogeographers are still struggling to develop species distribution
-models taking into account ecological interactions.
+of a local population is equal or greater than its death rate along with the
+set of per capita effects of that species on these environmental conditions.}
+Their representation merges zero-net growth figuring the Grinnelian niche
+(when do the population persist) with impact vectors figuring the Eltonian
+niche (what is the population impact). While this representation has been very
+influential in community ecology at the local scale, it remains unpracticable
+%%% WHY?
+at the biogeographical one. The absence of any mathematical representation
+of the niche that could easily be fit to ecological data perhaps explain why
+biogeographers are still struggling to develop species distribution models
+taking into account ecological interactions.
 

### 2014-04-01 ms_probaweb.tex

@@
 \emph{the pool of species occupying a given location at a given time, and
-the way these species interact} (ref to Morin?). It is therefore surprizing
+the way these species interact} (ref to Morin?). It is therefore surprising
 that ecological research on the variation of community structure has focused
@@
 
-\begin{itemize}
-\item Network structure do vary in space in time. \\
+Network structure vary in space and time, metaweb as a large scale
+synthesis. We don't know yet the mechanisms of variation
 
-\item We don't know yet to what extent interactions are varying with the
-environment. \\
+The metaweb concept is making its way through the network literature even
+though it has never been formally and technically defined.
+It is usually conceived as a network of interactions among species that
+could potentially co-occur, and represented by a binary matrix, \emph{i.e.}
+a probabilistic matrix in which the probability of observing an interaction
+is either 0 or 1. As the metaweb is usually constructed by aggregating
+observations, it assigns a probability of 0 to the interaction of species that
+never co-occurred, and is unable to factor-out the effect of co-occurrence. The
+main problem with that approach is that the co-occurrence of rare species is
+extremely unlikely and thus most often appear as an absence of interactions
+in the metaweb. A rarefaction analysis previously shown that interactions
+accumulate with the addition of networks at a slower rate than species richness
+\parencite{Poisot2012d} -- this is because interactions cannot accumulate
+faster than the rate of species observations, and ultimately the rate of
+co-occurrence observations. The only way to build a metaweb \emph{only}
+based on observational data is to compensate for the inflation of 0 due
+to lack of co-occurrence through manipulative experiments (REF). As this is
+impracticable for all but the smallest organisms, predictive probabilistic
+methods are needed.
 
-\item No theory to explain and interpret the meaning of network variation in space.
-Current interpretation fo species turnover involves the effect of the
-environment and stochasticity. \\
+No theory to explain and interpret the meaning of network variation in space.
+Current interpretation of species turnover involves the effect of the
+environment and stochasticity.
 
-\item Objective: Propose a theoretical framework to understand and predict the
-spatial and temporal variation in network structure.\\
-
-\end{itemize}
+Objective: Propose a theoretical framework to understand and predict the
+spatial and temporal variation in network structure.
 
@@
 
-We will refer to the left term as the metaweb. It is a conditional probability,
-representing the probability that an interaction occurs if species $i$ and $j$
-are co-occurring. The right term is the probability of observing the two species
-co-occurring at location $y$.
+We will refer to the left term as the metaweb. It is a conditional
+probability, representing the probability that an interaction occurs if
+species $i$ and $j$ are co-occurring. The right term is the probability
+of observing the two species co-occurring at location $y$. There are many
+variants of the metaweb representing different hypotheses about the origin
+of temporal and spatial variation in network structure (see the explicit
+formulations at Table 1). First, the interaction could be deterministic
+instead of probabilistic. In other words, $P(L_{ijy}) = 1$ if $X_{ijy} =
+1$, and 0 otherwise. This representation of the metaweb is the one mostly
+used so far, as soon as the species are found together they are assumed to
+interact. It is also the only way to represent interactions when there is
+not enough information available to evaluate the interaction probability. It
+should be a reasonable approximation when the sampling and inference scales
+are large enough and that the only variation of networks considered arises
+from species distribution.
 
-% The following paragraph
-% (1) is too long -- I tried to cut some of it, up to half of it
-% (2) comes at an awkward moment -- this is the key issue we try to solve, it should be in the introduction
-
-The metaweb concept is making its way through the network litterature even
-though it has never been formally and technically defined.
-% Yes, but no. All of the people that ever wrote the word "metaweb" are authors on this paper.
-It is usually conceived as a network of interactions among species
-that could potentially co-occur, and represented by a binary matrix,
-\emph{i.e.} a probabilistic matrix in which the probability of observing
-an interaction is either 0 or 1. As the metaweb is usually constructed by
-aggregating observations, it assigns a probability of 0 to the interaction
-of species that never co-occurred, and is unable to factor-out the effect of
-co-occurrence. The main problem with that approach is that the co-occurrence
-of rare species is extremely unlikely and thus most often appear as an absence
-of interactions in the metaweb. This approach is inappropriate because the
-observed co-occurrence will have a strong signature on the evaluation of
-interactions. A rarefaction analysis previously shown that interactions
-accumulate with the addition of networks at a slower rate than species
-richness \parencite{Poisot2012d}. It indicates that it is harder to have a
-direct evaluation of interactions from observeration than it is to evaluate
-species richness. If built from the observation of interactions, then the
-only way to fill a metaweb is by running cafeteria experiments between all
-pairs of species. Otherwise, the metaweb should be inferred using traits
-and phylogenetic information. Most of the published metawebs are therefore
-incomplete because of their sensitivity to sampling heterogeneity. We will
-come back to the issue of evaluating the metaweb in the sections Applications.
-
-There are many variants of the metaweb representing different hypotheses about
-the origin of temporal and spatial variation in network structure (see the
-explicit formulations at Table 1). First, the interaction could be 
-deterministic instead of probabilistic. In other words, $P(L_{ijy}) = 1$ if
-$X_{ijy} = 1$, and 0 otherwise. This representation of the metaweb is the one
-mostly used so far, as soon as the species are found together they are assumed
-to interact. It is also the only way to represent interactions when there is not
-enough information available to evaluate the interaction probability. It should be a
-reasonnable approximation when the sampling and inferrence scales are large
-enough and that the only variation of networks considered arises from species
-distribution.
-
-Ecological interactions could also depend on the environment.
-Although it is not common to see a conditional representation of ecological
-interactions, experimental studies of pairwise interactions revealing their
-sensitivity to the environment are common (REF). For instance, it has been
-documented that the predation risks of shorebirds do vary at the continental
-scale, from the south to the north (REF). The effect of the environment on
-interactions propagate up the community and influence network structure (REF).
-Here the environment is considered in a very broad sense, as any factor
-potentially influencing the probability of a pairwise interaction, provided that
-the species co-occur. It thus includes both the biotic and the abiotic
-components of environment. We note however that here the biotic environment
-includes organisms that are not considered in the co-occurrence matrix.
-Including a biotic component to the metaweb signifies that the pairwise
-interaction is conditional on higher order interactions. An interaction modifier
-occurs for instance when the predation risk by species $j$ might be impacted by
-a parasite $k$ changing the behaviour of the prey $i$. We note that a
-conditional probability approach could thus be used represent non-trophic
-interactions into ecological networks (REF). This topic is however beyond the
-scope of the current paper.
+Ecological interactions could also depend on the environment. Although it
+is not common to see a conditional representation of ecological interactions,
+experimental studies of pairwise interactions revealing their sensitivity to
+the environment are common (REF). For instance, it has been documented that the
+predation risks of shorebirds do vary at the continental scale, from the south
+to the north (REF). The effect of the environment on interactions propagate
+up the community and influence network structure (REF). Here the environment
+is considered in a very broad sense, as any factor potentially influencing the
+probability of a pairwise interaction, provided that the species co-occur. It
+thus includes both the biotic and the abiotic components of environment. We
+note however that here the biotic environment includes organisms that are
+not considered in the co-occurrence matrix. Including a biotic component to
+the metaweb signifies that the pairwise interaction is conditional on higher
+order interactions. An interaction modifier occurs for instance when the
+predation risk by species $j$ might be impacted by a parasite $k$ changing
+the behaviour of the prey $i$. We note that a conditional probability approach
+could thus be used represent non-trophic interactions into ecological networks
+(REF). This topic is however beyond the scope of the current paper.
 
@@
 far co-occurrence is not-random when going along the chain of indirect
-interactions. Berlow(2009) shown previously that almost only first and second
+interactions. Berlow (2009) shown previously that almost only first and second
 order interactions do matter in ecological networks, but we don't know for
-co-distribution. We neither know what is the sensitiviy to species richness: do
-interactions tend to buffer each other? Generalizing knowledge aquired by the
-study of small community modiles will require future research.
+co-distribution. We neither know what is the sensitivity to species richness: do
+interactions tend to buffer each other? Generalizing knowledge acquired by the
+study of small community modules will require future research.
 
@@
 clarified with the distinction between Eltonian and Grinnellian definitions
-\parencite{Chase2003}. The Grinnellian dimension of
-the niche is the effect of the environment on the demography of a species,
-while the Eltonian dimension is the effect of a species on its environment
-\emph{sensu lato}.  % SNOB!
-The Grinnellian niche is the most intuitive one
-to apply and is the conceptual backbone of species distribution models. The
-Eltonian niche is well known by community ecologists, but is trickier to
-turn into predictive models \parencite{Devictor2010a}. Nonetheless, the
-development of the niche model of food web structure (Williams2000) and
-its parameterization (Williams2010; Gravel2013) made it more operational,
-although it has yet to be applied to more than trophic interactions.
+\parencite{Chase2003}. The Grinnellian dimension of the niche is the
+effect of the environment on the demography of a species, while the Eltonian
+dimension is the effect of a species on its environment \emph{sensu lato}. The
+Grinnellian niche is the most intuitive one to apply and is the conceptual
+backbone of species distribution models. The Eltonian niche is well known
+by community ecologists, but is trickier to turn into predictive models
+\parencite{Devictor2010a}. Nonetheless, the development of the niche model
+of food web structure (Williams2000) and its parameterization (Williams2010;
+Gravel2013) made it more operational, although it has yet to be applied to
+more than trophic interactions.
 
@@
 niche (what is the population impact). While this representation has been very
-influential in community ecology at the local scale, it remains unpracticable
+influential in community ecology at the local scale, it remains impracticable
 %%% WHY?
@@
 co-occurrence. Five habitats were sampled along a gradient of habitat
-modification: forest, abandonned coffee agroforest, coffee agroforest, pasture
+modification: forest, abandoned coffee agroforest, coffee agroforest, pasture
 and rice culture. The metaweb consists of 9 parasitoids and kleptoparasites
@@
 
-Tylianakis (2007) investigated if habitat modification affects the structure of
-these networks They found a significant impact of the habitat on their
-structure, despite little variation in species richness. Increasing habitat
-modification led to a higher parasitoid to host species ratio and a paraistoid
-were also more specialized, thus impacting considerably vulnerability. A closer
-inspection of the networks revealed that intensive agricultural systems were
-dominated by a strong interaction and a specialization of the most abundanc
-parasitoid. Although the discussion made clear that both the turnover in species
-composition and the interaction probability changed with habitat modification,
-it was not possible to partition these components.
+Tylianakis (2007) investigated whether habitat modification affects
+the structure of these networks They found a significant impact of
+the habitat on their structure, despite little variation in species
+richness. Increasing habitat modification led to a higher parasitoid
+to host species ratio and a paraistoid were also more specialized, thus
+impacting considerably vulnerability. A closer inspection of the networks
+revealed that intensive agricultural systems were dominated by a strong
+interaction and a specialization of the most abundant parasitoid. Although
+the discussion made clear that both the turnover in species composition and
+the interaction probability changed with habitat modification, it was not
+possible to partition these components.
 
-We developped a R package (REF) to fit alternative formulations of the metaweb
-and the co-occurrence matrix along an environmental gradient and run it to
-re-interpret the data of Tylianaks (2007). The package provides a general
-interface facilitating the development of different species and link
-distribution models. It is also built to facilitate the interaction iwth the
-Mangal database of ecological interactions (REF). The first step consists of
-fitting a probablistic model from the observation of a pairwise interaction
-(binary) and the environment (could be categorical or continuous) from the
-subset of the data where the two species are co-occurring. In other words, it
-fits the equation $P(L_{ijy}|X_{iy},X{jy},E_y)$ to the data where $X_{iy} = 1$
-and $X_{iy} = 1$. Logistic regression was used and is currently programmed, but
-alternative models could be used as well. The second steps consists of fitting a
-a probabilistic model for co-occurrence over the whole dataset,
+We developed the \texttt{probaweb} package for R (REF) to fit
+alternative formulations of the metaweb and the co-occurrence matrix
+along an environmental gradient and run it to re-interpret the data of
+Tylianaks (2007). The package provides a general interface facilitating
+the development of different species and link distribution models. It is
+also built to facilitate the interaction with the\texttt{mangal} database
+of ecological interactions (REF). The first step consists of fitting a
+probabilistic model from the observation of a pairwise interaction (binary)
+and the environment (could be categorical or continuous) from the subset of
+the data where the two species are co-occurring. In other words, it fits
+the equation $P(L_{ijy}|X_{iy},X{jy},E_y)$ to the data where $X_{iy} = 1$
+and $X_{iy} = 1$. Logistic regression was used and is currently programmed,
+but alternative models could be used as well. The second steps consists of
+fitting a probabilistic model for co-occurrence over the whole dataset,
 $P(X_{iy},X{jy}|E_y)$, independently of the observation of an interaction. The
-two probabilities are then multiplied to obtain the probability of observing an
-interaction (Eq. 2). We used this probability to compute the likelihood of each
-observation ($\zeta(\theta|D) = P(L_{ijy},X_{iy},X_{jy})$ if $L_{ijy}=1$ and
-$\zeta(\theta|D) = 1 - P(L_{ijy},X_{iy},X_{jy})$ otherwise). We then after
-compare the models by their AIC.
+two probabilities are then multiplied to obtain the probability of observing
+an interaction (Eq. 2). We used this probability to compute the likelihood of
+each observation ($\zeta(\theta|D) = P(L_{ijy},X_{iy},X_{jy})$ if $L_{ijy}=1$
+and $\zeta(\theta|D) = 1 - P(L_{ijy},X_{iy},X_{jy})$ otherwise). We then
+after compare the models by their AIC.
 
@@
 interactions. Secondly, we find that the deterministic metaweb is the worst
-model (model 3, AIC = ). This result indicate that the traditional appraoch to
+model (model 3, AIC = ). This result indicate that the traditional approach to
 consider that species interact as soon as they co-occur is definitely wrong.
@@
 network structure. Another interesting result is that considering a neutral
-co-occurrence did not impact much the fit of the modeel. The AIC drops to XX
-with model 6, indicating that considering indepdenent SDMs yields similar
+co-occurrence did not impact much the fit of the model. The AIC drops to XX
+with model 6, indicating that considering independent SDMs yields similar
 networks over this environmental gradient. This means that for this particular
@@
 
-It is also possible to obtain for each pairwise interaction an estimate of the
-uncertainty. Not surprisingly, the confidence interval is usually very high for
-the estimation of a probability with a very small sample size. The standard
-error on the evaluation of the interaction probability is provided along with
-the metaweb at Fig. 3. It reveals that the uncertainty is very high for most
-interactions, even if 48 networks were sampled. Such an approach could be used
-to detect wich pairwise interaction requires additional sampling in order to
-reduce the uncertainty to a manageable level.
+It is also possible to obtain for each pairwise interaction an estimate of
+the uncertainty. Not surprisingly, the confidence interval is usually high
+for the estimation of a probability with a small sample size. The standard
+error on the evaluation of the interaction probability is provided along
+with the metaweb at Fig. 3. It reveals that the uncertainty is high for
+most interactions, even if 48 networks were sampled. Such an approach could
+be used to detect which pairwise interaction requires additional sampling
+in order to reduce the uncertainty to a manageable level.
 

### 2014-05-14 ms_probaweb.tex

@@
 
-\textbf{Title:} A quantitative framework for network biogeography\\
+\textbf{Title:} Scaling up patterns of emerging niche complexity in the metaweb of life -- an overarching conceptual synthesis and quantitative framework\\
 % Alternative: The distribution of ecological interactions 
@@
 
-3: \\
+3: University of Canterbury at Christchurch, School of Biological Sciences,\\
 
@@
 
-Ecology textbooks define the structure of an ecological community as
-\emph{the pool of species occupying a given location at a given time, and
-the way these species interact} (ref to Morin?). It is therefore surprising
-that ecological research on the variation of community structure has focused
-on species turnover (refs), almost entirely neglecting variation in the way
-species interact (refs).
+Ecology textbooks define the structure of an ecological community as \emph{the
+pool of species occupying a given location at a given time, and the way
+these species interact} (ref to Morin?). It is therefore surprising that
+ecological research on the variation of community structure has focused
+on species turnover (refs), almost entirely neglecting variation in the
+way species interact (refs). This poses two challenges for the cohesion
+of community ecology as a unified field. First, we need to account, in
+an explicit way, for species interactions in our understanding of species
+occurrence and distributions (refs). Second, we need to expand the work that
+has been done in "species-based" community ecology, \emph{i.e.} measuring
+and predicting variation in species assemblages, into our study of species
+interactions. Here we argue that both of these challenges can be adressed
+as the same time, by considering that species interactions are not a fixed
+covariate in species distribution models, but react in complex ways to the
+presence and absence of species. Adopting this point of view provides a
+more unified way of community ecology, as a field seeking to undertand the
+distribution of species and their interactions.
 
@@
 synthesis. We don't know yet the mechanisms of variation
+
+%%% FORMER NICHE SECTION
+
+Correctly describing the ecological niche is key to understand and predict
+species distribution. Despite several attempts to refresh the conceptual
+basis of what ecological niches are, ecologists haven't moved far past the
+"n-dimensional hypervolume" formalism \parencite{Holt2009} introduced by
+\textcite{Hutchinson1961}. Despite its intuitive interpretation and translation
+into species distribution models \parencite{Blonder2014}, the concept has been
+constantly criticized (Hardin, 1960; Peters, 1991; Chase2003; Silvertown, 2004;
+Soberon, 2007) and several attempts have been made to expand and reinforce it.
+
+Part of the problem surrounding the definition of the niche has been
+clarified with the distinction between Eltonian and Grinnellian definitions
+\parencite{Chase2003}. The Grinnellian dimension of the niche is the
+effect of the environment on the demography of a species, while the Eltonian
+dimension is the effect of a species on its environment \emph{sensu lato}. The
+Grinnellian niche is the most intuitive one to apply and is the conceptual
+backbone of species distribution models. The Eltonian niche is well known
+by community ecologists, but is trickier to turn into predictive models
+\parencite{Devictor2010a}. Nonetheless, the development of the niche model
+of food web structure (Williams2000) and its parameterization (Williams2010;
+Gravel2013) made it more operational, although it has yet to be applied to
+more than trophic interactions.
+
+\textcite{Chase2003} attempted this representation in their definition:
+\textit{[The niche is] the joint description of the environmental conditions
+that allow a species to satisfy its minimum requirements so that the birth rate
+of a local population is equal or greater than its death rate along with the
+set of per capita effects of that species on these environmental conditions.}
+Their representation merges zero-net growth figuring the Grinnelian niche
+(when do the population persist) with impact vectors figuring the Eltonian
+niche (what is the population impact). While this representation has been very
+influential in community ecology at the local scale, it remains impracticable
+%%% WHY?
+at the biogeographical one. The absence of any mathematical representation
+of the niche that could easily be fit to ecological data perhaps explain why
+biogeographers are still struggling to develop species distribution models
+taking into account ecological interactions.
+
+The key point to integrate dimensions of the niche is to represent the Eltonian niche into a Grinnelian space. 
+- We do so by considering that the Eltonian niche is the hyper volume in the trait-space allowing an interaction. \\
+- Doing so, we could project both niches in a plane and find the hypervolume where an interaction should occur (Fig. 2). \\
+- This visual representation is parallel to the probabilistic definition of interaction probability. \\
+- We propose that the metaweb is the Eltonian dimension of the niche, while the matrix of co-occurrence is the Grinnellian dimension. \\
+- Feedbacks between dimensions occur through the inclusion of co-occurrence in the metaweb, and interactions in the co-occurrence matrix. \\
+- This approach radically change the representation of the niche, putting species distribution and ecological interactions at the same level. \\
+- Fitting the probabilistic model allows the evaluation of link distribution and species distribution models. \\
+- Moreover, the integrated niche concept facilitates the formulation of species distribution models taking into account biotic interactions (see the section Applications) \\
+
+%%% END OF FORMER NICHE SECTION
 
@@
 study of small community modules will require future research.
-
-\newpage
-%========================================================%
-\section*{Interpretation: the integrated niche}
-
-Correctly describing the ecological niche is key to understand and predict
-species distribution. Despite several attempts to refresh the conceptual
-basis of what ecological niches are, ecologists haven't moved far past the
-"n-dimensional hypervolume" formalism \parencite{Holt2009} introduced by
-\textcite{Hutchinson1961}. Despite its intuitive interpretation and translation
-into species distribution models \parencite{Blonder2014}, the concept has been
-constantly criticized (Hardin, 1960; Peters, 1991; Chase2003; Silvertown, 2004;
-Soberon, 2007) and several attempts have been made to expand and reinforce it.
-
-Part of the problem surrounding the definition of the niche has been
-clarified with the distinction between Eltonian and Grinnellian definitions
-\parencite{Chase2003}. The Grinnellian dimension of the niche is the
-effect of the environment on the demography of a species, while the Eltonian
-dimension is the effect of a species on its environment \emph{sensu lato}. The
-Grinnellian niche is the most intuitive one to apply and is the conceptual
-backbone of species distribution models. The Eltonian niche is well known
-by community ecologists, but is trickier to turn into predictive models
-\parencite{Devictor2010a}. Nonetheless, the development of the niche model
-of food web structure (Williams2000) and its parameterization (Williams2010;
-Gravel2013) made it more operational, although it has yet to be applied to
-more than trophic interactions.
-
-\textcite{Chase2003} attempted this representation in their definition:
-\textit{[The niche is] the joint description of the environmental conditions
-that allow a species to satisfy its minimum requirements so that the birth rate
-of a local population is equal or greater than its death rate along with the
-set of per capita effects of that species on these environmental conditions.}
-Their representation merges zero-net growth figuring the Grinnelian niche
-(when do the population persist) with impact vectors figuring the Eltonian
-niche (what is the population impact). While this representation has been very
-influential in community ecology at the local scale, it remains impracticable
-%%% WHY?
-at the biogeographical one. The absence of any mathematical representation
-of the niche that could easily be fit to ecological data perhaps explain why
-biogeographers are still struggling to develop species distribution models
-taking into account ecological interactions.
-
-The key point to integrate dimensions of the niche is to represent the Eltonian niche into a Grinnelian space. 
-- We do so by considering that the Eltonian niche is the hyper volume in the trait-space allowing an interaction. \\
-- Doing so, we could project both niches in a plane and find the hypervolume where an interaction should occur (Fig. 2). \\
-- This visual representation is parallel to the probabilistic definition of interaction probability. \\
-- We propose that the metaweb is the Eltonian dimension of the niche, while the matrix of co-occurrence is the Grinnellian dimension. \\
-- Feedbacks between dimensions occur through the inclusion of co-occurrence in the metaweb, and interactions in the co-occurrence matrix. \\
-- This approach radically change the representation of the niche, putting species distribution and ecological interactions at the same level. \\
-- Fitting the probabilistic model allows the evaluation of link distribution and species distribution models. \\
-- Moreover, the integrated niche concept facilitates the formulation of species distribution models taking into account biotic interactions (see the section Applications) \\
-
-% TO BE COMPLETED
 

### 2015-11-23 ms/ms_probaweb.tex
Complete analysis & draft

% Table 1: example for a pair of species
% Table 2: model comparison across all species

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{color,lineno,setspace,multirow}
\usepackage[sc]{mathpazo}
\usepackage{graphicx}
\usepackage[top=2.4cm,left=2.4cm,top=2.4cm,bottom=2.4cm,includefoot]{geometry}
\usepackage{rotating}

\begin{document}

\linenumbers 
\modulolinenumbers[1]

\textbf{Title:} Bringing Elton and Grinnell together: a quantitative framework to represent the biogeography of ecological interactions

\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Timoth\'ee Poisot$^{1,2,3}$, N\'eo
Martinez$^{4}$, Jennifer A. Dunne$^{5}$, Jason Tylianakis$^{3}$, Tomas Roslin$^{6}$, Tommy Nyman$^{6}$, Ben Baiser$^{7}$, Daniel B. Stouffer$^{3}$ \\

1: Canada Research Chair in Integrative Ecology. D\'epartement de
biologie, Universit\'e de Sherbrooke,  2500 Boulevard l'Universit\'e, 
Sherbrooke (Québec).  J1K 2R1\\

2: Qu\'ebec Centre for Biodiversity Sciences\\

3: University of Canterbury at Christchurch, School of Biological Sciences,\\

4: \\

5: \\

6:\\

7:\\

\textbf{Keywords:} networks, spatial ecology, co-occurrence, probability of interaction\\

\textbf{Words in the abstract:}

\textbf{Words in the main text:}

\textbf{Words in the legends:}

\textbf{Figures:}

\textbf{Tables:}

\textbf{References:}

\newpage
\doublespacing

%=============================================================================%
\section*{Abstract}

\newpage

%=============================================================================%
\section*{Introduction}

Community ecology is defined in most textbooks as \emph{the study of the
interactions that determine the distribution and abundance of organisms}
(Krebs2001). Despite a general concensus on this definition (Scheiner2007), it
is surprising that most research on the variation of community structure has
focused mostly on the turnover of species composition (Anderson2011),
neglecting variation in the way they interact with each other (McGill2006).
Not surprisingly given this fact, biogeographers are still struggling to
figure out if interactions do impact species distribution (Wisz2012;
Kissling2012). There has been a step ahead with recent methodological
improvements accounting for interactions in species distribution models
(Pollock2014; Pelissier2013), but those remain nonetheless a 'species- based'
approach to communities where interactions are fixed covariates affecting
distribution. Here we plea for a more integrated approach of species and
interaction distribution.

The problem of community assembly is often formulated as \emph{how do we
sample a regional pool of species to constitute a local community?} This
question could be rewritten to adress the problem of network assembly, as
\emph{how do we sample a regional pool of interactions to constitute a local
interaction network?}. An illustration of this problem for a food web is
provided at Figure 1. The metaweb represents potential interactions among all
species that could be found in a given area. In this particular case, there
are 274 nodes, and 1077 links among plants, herbivores and parasitoids from
Northern Europe. An instance of a local community is also illustrated, with 44
nodes and 160 interactions. Only $51.2\%$ of all potential interactions are
realized. Our objective here is to provide a conceptual framework to explain
the sampling of the regional pool of interactions, along with a quantitative
method to predict it. The problem could be formalized by sequentially
understanding why only a fraction of the species are locally co-occurring, and
after why these species are interacting or not.

There are multiple causes to spatial turnover in community composition. The
first and most studied driver is the effect of variation in the abiotic
environment on species performance. Combined with specific responses in
demography, it generates variation among localities by locally selecting the
fittest species (Leibold2004). Stochasticity additionnaly plays a role, either
because of the inherently unpredictable nature of colonization and extinction
events, or because of strong non-linear feedbacks generating alternative
transients and equilibrium (Chase2007; Vellend2014). The analysis of community
turnover is usually performed with data represented in a table with rows
corresponding to sites (or measurements) and the columns to species. Beta-
diversity metrics quantify the variance of this community data (Legendre2005).
Traditionnal approaches rely on measures of the dissimilarity between
communities, using indices such as the Jaccard or the Bray Curtis measures of
dissimilarity. Recent methods decompose the total variation of the community
data into species and site contributions to beta diversity (Legendre2013).
Even though these methods compare whole list of species between sites, or
measurements, they remain fundamentally 'species-based' since they are all
based on the within column variation. None of them consider the variation of
associations (pairs or higher order motifs) explicitly.

The niche is by far the dominant concept to explain species distribution and
community assembly, from the local to the global scale. Following Hutchinson,
the niche is viewed as the set of environmental conditions allowing a
population to establish and maintain a population (see also Holt2009).
Community turnover arises following successive species replacement along an
environmental gradient, in agreement with a Gleasonian view of communities
(Gleason). The concept is straighforward to operationalize with species
distribution models, as it maps naturally on the available data (both
distribution and environmental data) and a vast array of statistical tools
representing it (e.g. Biomod, MaxEnt). It is however much harder to account
for ecological interactions in this approach (Peterson2011). These are often
viewed as externalities, constraining or expanding the range of environmental
conditions required for a species to maintain a population (Pulliam2000;
Soberon2007).

The network approach proposes a convenient formalism to represent the
structure of local communities. Species are represented as nodes and
interactions by links. The data could also be represented by matrices, with
each species in rows and columns, and the entries representing the occurrence
or the intensity of an interaction. Studies of network diversity are mostly
concerned by the distribution of the interactions within a location and not so
much by the variation among locations (Dunne2005; Bascompte2007; Ings2007;
Kefi2012). Network complexity is computed as the number of interactions in the
case of binary networks or interaction diversity in the case of quantitative
networks (Bersier2002). However, there is now evidence that ecological
interactions do also vary in space and time (Poisot2012; Trojelsgaard2015).
The variability of community structure in this situation arises from the
turnover of species composition, along with the turnover of the interactions
among pairs of species. The occurrence and intensity of interactions could
vary because of the environment, species abundance and higher order
interactions (Poisot2015a). The variation in community composition is often
independent of the variation of ecological interactions, suggesting these two
components of network variability respond to different drivers (Poisot2012).

Interestingly, the ecological network literature also has its own 'niche model' to
position a species in a community (Williams2000). The niche of a species in
this context represents the multidimentional space that could represent all of
its interactions. Each species is characterized by a niche position, an
optimum and a range over 3 to 5 different niche axes (Williams2000;
Eklof2013). The niche model has been successful at explaining the complexity
of a variety of networks, from food webs to plant-pollinator systems. The
conceptual framework is however limited to local communities and does not
provide any explanation to the turnover of network structure along
environmental gradients.

Here we adopt the view that a community structure is best represented as an
ecological network of interactions and develop a theory to explain its
turnover in space and time. We propose a new description of the niche that
integrates the effect of the environment on species distribution and on
ecological interactions. We first present the conceptual framework and then
formalize it mathematically with a probabilistic approach to the sampling of
the regional pool of interactions. We apply the framework to study the spatial
variation of host-parasite interactions across Europe. We find that the
variation of the environment causes both species and interaction turnover. The
network structures changes systematically across the latitudinal gradient,
with a peak of connectance at intermediate latitudes. At the pairwise level,
the statistical approach could be conceived as an interaction distribution
model. At the community level, the approach provides a likelihood based
method to compare different hypotheses of network turnover.

%=============================================================================%
\section*{The integrated niche}

Correctly describing the niche is key to understand turnover in community
structure. Despite several attempts to refresh the conceptual basis of what
ecological niches are, ecologists have not moved far past the "n-dimensional
hypervolume" formalism introduced by Hutchinson. Despite its
intuitive interpretation and translation into species distribution models
(Boulangeat2012; Blonder2014), the concept has been constantly criticized
(Hardin1960; Peters1991; Chase2003; Silvertown2004; Soberon2007) and several
attempts have been made to expand and reinforce it.

Part of the problem surrounding the definition of the niche has been clarified
with the distinction between Eltonian and Grinnellian definitions (Chase2003).
The Grinnellian dimension of the niche is the set of environmental conditions
required for a species to maintain a population in a location. The Grinnellian
niche is the most intuitive to apply and is the conceptual backbone of species
distribution models. The Eltonian niche on the other hand is the effect of a
species on its environment. This aspect of the niche is well known by
community ecologists, but is trickier to turn into predictive models.
Nonetheless, the development of the niche model of food web structure
(Williams2000) and its parameterization (Williams2010; Gravel2013) made it
more operational.

These perspectives are rather orthogonal to each other and thus lead to
considerable confusion in the literature (McIntyre). Chase2003 attempted to
reconcile them in their definition of the niche: \textit{[The niche is] the
joint description of the environmental conditions that allow a species to
satisfy its minimum requirements so that the birth rate of a local population
is equal or greater than its death rate along with the set of per capita
effects of that species on these environmental conditions.} Their
representation merges zero-net growth isoclines figuring the Grinnelian niche
(when do the population persists) with impact vectors figuring the Eltonian
niche (what is the per capita impact). While this representation has been very
influential in community ecology at the local scale (the resource-ratio theory
of coexistence - Tilman1982), it remains impracticable at the large spatial
scale because of the difficulties to measure it. The absence of any
mathematical representation of the niche that could easily be fit to
ecological data perhaps explain why biogeographers are still struggling to
develop species distribution models taking into account ecological
interactions.

We propose to integrate the two perspectives of the niche with a visual
representation of both components. The underlying rationale is that, in
addition to the environmental constraints on demographic performance, any
organism requires resources to sustain its metabolic demand and reproduction.
Abiotic environmental axes are any non-consumable factors affecting the
demographic performance of an organism. Alternatively, the resource axes are
traits of the resources allowing interactions with the consumer. The niche
should therefore be viewed as the set of abiotic environmental factors (the
Grinnelian component) along with the set of traits (the Eltonian component)
allowing a sustainable population to establish and maintain at a location.
Accordingly, each species could be characterized by an optimal position in
both the environmental (x-axis) and the trait (y-axis) plane. The integrated
niche is then the hypervolume where interactions could occur and sustain a
population. This approach radically change the representation of the niche,
putting species distribution and ecological interactions in the same
formalism.

The limits of the niches could be independent of each other (as in the example
at Fig. 2), alternatively interact. For instance, the optimimal prey body size
for predatory fishes could reduce with increasing temperature (Lelong2015),
which would make diet boundaries functions of the environment. The other way
around, we could also consider that the growth rate of the predator could
change with the body size of the preys it feeds on, thereby altering the
environmental boundaries.

\newpage
%========================================================%
\section*{A probabilistic representation of ecological interactions networks in space}

We now formalize the integrated niche with a probabilistic approach to
interactions and distribution. We seek to represent the probability an
interaction between species $i$ and $j$ occurs at location $y$. We
define $L_{ijy}$ as a stochastic variable and are looking
at the probabilty this event occurs, $P(L_{ijy})$. The occurrence of an
interaction is dependent on the co-occurrence of species $i$ and $j$. This
argument might seem trivial at first, but the explicit consideration of this
condition in the probabilistic representation of ecological interactions will
prove fundamental to understand their variation. We thus define $X_{iy}$ as a
stochastic variable representing the occurrence of a species $i$ at location
$y$, and similarly $X_{ijy}$ the co-occurrence of species $i$ and $j$. The
quantity we seek to understand is the probability of a joint event:

%-----------------
\begin{equation}
\text{P}(X_{i,y},X_{j,y},L_{ij,y},)
\end{equation}
%-----------------

Or simply said, the probability of observing both species $i$ and $j$, and
an interaction from $i$ to $j$. This probability could be decomposed
in two parts using the product rule of probabilities:

%-----------------
\begin{equation}
P(X_{iy},X_{jy},L_{ijy})=P(X_{iy},X_{jy}|E_y)P(L_{ijy}|\mathbf{T},X_{iy},X_{jy},E_y)
\end{equation}
%-----------------

The left term is the probability of observing the two species co- occurring at
location $y$. It corresponds to the Grinnelian dimension of the niche. The
right term is a conditional probability, representing the probability that an
interaction occurs between species $i$ and $j$, given their set of traits
$\mathbf{T}$ and they are co- occurring. It is referred as the metaweb and
corresponds to the Eltonian dimension of the niche described above. We will
see below how this formalism could be directly fitted to empirical data. But
before turning to an application, we will discuss the interpretation of
different variants of these two terms.

\subsection*{Variants of co-occurrence}

There are several variants to the co-occurrence probability representing
different hypotheses about the temporal and spatial variation in network
structure (see the explicit formulations at Table 1). The simplest model
relates co- occurrence probability directly to the environment, $P(X_{ijy} |
E_y)$. In this situation there is no underlying assumption about the
ecological processes responsible for co-occurrence. It could arise because of
the impact of ecological interactions on distribution (Pollock2014) or
alternatively because of share environmental requirements. In the former case,
species are not independent to each other and the conditional occurrence must
be accounted for explicitlty, $P(X_{ijy} | E_y) = P(X_i | E_y, X_j)P(X_j |
E_y)$. In the later case, species are independent and only the marginal
occurrence must be accounted for, $P(X_{ijy} | E_y) = P(X_i | E_y)P(X_j |
E_y)$.

The co-occurrence probability itself could be dependent on ecological
interactions. Direct pairwise interactions such as competition, facilitation
and predation have long been studied for their impact on co-distribution (such
as in the cases studied by Diamond1976, Connor1980, Gotelli2000 etc..). Second
and higher order interactions (e.g. trophic cascade) could also impact co-
occurrence. Co-occurrence in ecological networks is however a topic of its
own, influenced by the degree distribution and species richness
(Cazelles2015). Almost only first order and second order interactions do
impact co-occurrence. The covariance of interacting species to an
environmental gradient also influences co-occurrence (Cazelles2016). Because
of the complexity of relating co-occurrence to the interaction network
structure, we  will focus here on the variation of interactions and not on the
distribution, and leave this issue for Discussion and future research.

\subsection*{Variants of the metaweb}

There are also variants of the metaweb. First, most documented metawebs have
thus far considered that ecological interactions are deterministic, not
probabilistic (e.g. Havens1992; Woods2015). Species are assumed to interact if
they are found together in a location, independently of their abundance and
the environment. In other words, $P(L_{ijy}) = 1$ if $X_{ijy} = 1$, and 0
otherwise. This approach might be a reasonnable approximation when the
sampling and inference scales are large enough so that probabilities of
observing at least one interaction converges to unity and that the only
variation of networks considered arises from species distribution.

Ecological interactions could also vary with the environment, such as
$P(L_{ijy} | E_y)$. Although it is not common to see a conditional
representation of ecological interactions, experimental studies of pairwise
interactions revealing their sensitivity to the environment are common (REF).
For instance, it has been documented that the predation risks of shorebirds do
vary at the continental scale, from the south to the north (REF). The effect
of the environment on interactions propagate up the community and influence
network structure (REF).

\newpage
%========================================================%

\section*{Application: continental-scale variation of host-parasite community structure}

In this section we provide an illustration of the framework with an empirical
dataset of host-parasitoid networks sampled throughout continental Europe
along a south-north gradient. The analysis targets networks composed of
willows (genus Salix), their galling insects, and the natural enemies of these
gallers. The questions we address with the framework and the dataset are: i)
how much variation in the network structure is there across the gradient and
ii) what is the primary driver of network turnover across the gradient?

\subsection*{Data}

Communities of both willows and gallers are species-rich and widely
distributed, with pronounced variation in community composition across space.
The genus Salix includes over 400 species, most of which are shrubs or small
trees (ref). The genus is common in most habitats across the Northern
Hemisphere (ref). Willows support a highly diverse community of herbivorous
insects, and one of the main herbivore groups in this system are gall-inducing
sawflies (Hymenoptera: Tenthredinidae: Nematinae: Euurina (ref). Gall
formation is induced by sawfly females during oviposition, and gall formation
includes marked manipulation of plant chemistry by the galler (ref). The enemy
community of the gallers includes nearly 100 species belonging to 17 insect
families of four orders. These enemies encompass both inquilines and
parasitoids: inquiline larvae (Coleoptera, Lepidoptera, Diptera, and
Hymenoptera) feed primarily on gall tissue, but typically kill the galler
larva in the process. Parasitoid larvae (representing many families in
Hymenoptera) kill the galler larvae by direct feeding (REF). In terms of
associations between the trophic levels, phylogeny-based comparative studies
have demonstrated that galls represent "extended phenotypes" of the gallers,
meaning that gall form, location, and chemistry is determined mainly by the
galling insects and not by their host plants [ref]. Because galler parasitoids
have to penetrate a protective wall of modified plant tissue in order to gain
access to their victims, gall morphology has been inferred to strongly affect
the associations between parasitoids and hosts (ref, ref). Thus, the set of
parasitoids attacking each host is presumptively constrained by the form,
size, and thickness of its gall.

Local realizations of the willow–galler–enemy network were reconstructed from
samples collected between 1982 and 2010. Plant galls were collected by J.P.
Kopelke during this period at 374 sites across Central and Northern Europe.
Sampling was conducted in the summer months of June and/or July, during the
latter stages of larval development. Galler species were identified on the
basis of willow host species and gall morphology, as these are distinct for
each sawfly species. At each site, galls were randomly collected from several
willow individuals in an area of about 0.1-0.3 km2. Most sites were visited
only once, with a total of 641 site visits across the 374 sites. GPS
coordinates were recorded for each location and the annual mean temperature
and annual precipitation were obtained from WorldClim. While other covariates
could have been considered, we figured that they are representative of the
most important axes of the European climate, and more easily
interpretable than reduced variables obtained by a PCA,

The methods used for rearing natural enemies from the galls have been
previously described by e.g. [ref, ref]. In brief, galls were opened to score
the presence of galler or parasitoid/inquiline larvae. Enemy larvae were
classified to preliminary morphospecies, and the identity of each
morphospecies was determined by connecting them to adults emerging after
hibernation. The galls were reared by storing single galls in small glass
tubes (Kopelke 1985a, 1994a, 1999, 2003a, b). Hibernation of galls containing
parasitoids took place either within the glass tubes or between blotting paper
in flowerpots filled with clay granulate or a mixture of peat dust and sand.
These pots were stored over the winter in a roof garden and/or in a climatic
chamber. In most cases, the matching of larval morphospecies with adult
individuals emerging from the rearings allowed the identification of the
natural enemies to the species level. Nonetehless, in some cases, individuals
could only be identified to one of the (super)families Braconidae,
Ichneumonidae, and Chalcidoidea. This was particularly the case when only
remains of faeces, vacant cocoons of parasitoids, and/or dead host larvae were
found, as was the case when parasitoids had already emerged from the gall. As
a result, the largest taxon in the data set, “Chalcidoidea indeterminate,”
represents a superfamily of very small parasitoids that are hard to
distinguish.

In total, the sampling targeted 52 Salix taxa, yielding 146,622 galls for
dissection and rearing. These galls represented 96 galler species, and yielded
42,133 individually-identified parasitoids and inquilines. Of these, 25,170
(60\%) could be identified to the species level. Overall, 126 parasitoid and
inquiline taxa were distinguished in the material. Data on host associations
within subsets of this material have been previously reported by (Kopelke ref
ref b) and by Nyman et al. 2007, whereas the current study represents the
first analysis of the full data set from a spatial perspective.

\subsection*{Analysis}

Computing the probability of observing an interaction involves fitting a set
of binomial models and collecting their estimated probabilities. We considered
second-order generalized linear models for the sake of the illustration, but
more sophisticated fitting algorithms (e.g. GAM or Random Forest) could be
used as well, as long as the algorithm can provide an estimated probability
for each observation. The data consists of a simple (albeit large) table with
the observation of each species, $X_i$ and $X_j$, their co-occurrence,
$X_{ij}$, the observation of an interaction $L_{ij}$, and environmental co-
variates. There is one row per pair of species per site. We considered that an
absence of a record of an interaction between co-occurring species at a site
means a true absence.

We compared three models for the co-occurrence probability. The first model
fits directly the co-occurrence probability conditional
on the local environment, $P(X_{ijz}|E_z)$. This model therefore does not make any
hypothesis about the mechanisms driving co-occurrence for any given
environment and use the information directly available in the data. The second
models consider independent co-occurrence of species. In this case, we fit
independently $P(X_{iz}|E_z)$ and $P(X_{jz}|E_z)$ and take their product to
derive co-occurrence probability. This model should be viewed as a null
hypothesis with respect to the first model since their comparison reveals if
there is significant spatial association of the two species once considering
the response to the environment (Cazelles2016). Finally the third model
considers that co-occurrence probability is independent of the environment and
thus constant throughout the landscape.  In other words, $P(X_{ijz})$ is
obtained by simply counting the number of observed co-occurrences, divided by
the total number of observations. The comparison between the first and third
model allows testing the hypothesis that co-occurrence is conditional on the
environment. Whenever the environment is included as a co-variate in the glm,
we considered a second-order polynomial response for both the temperature and
precipitations. There are consequently 5 parameters for the first model when
fitting a given pair of species, 10 parameters for the second model and only 1
for the third model.

Following the same logic, we compared three models for the interaction
probability. The first model fits the interaction probability conditional on
the local environmental variables, $P(L_{ijz}|E_z,X_i,X_j)$. Consequently, the
model was fitted on a subset of the data, when the two species are found co-
occurring. The second model fits the interaction probability independently of
the local environmental variables, $P(L_{ijz}|X_i,X_j)$. It corresponds to the
number of times the two species were observed interacting when co-occurring,
divided by the number of times they co-occurred. The third model is an extreme
case performed only to test the hypothesis that if two species are found to
interact at least once, then they should interect whenever they co-occur,
$P(L_{ijz}|X_i,X_j)=1$. While not necessarily realistic, this model tests an
hypothesis that is commonly done in the representation of local networks from
knowledge of a deterministic metaweb (such as in Havens1992; Piechnik2008;
Wood2015). There are consequently 5 parameters for the first model, a single
parameter for the second model and no parameter to evaluate for the third
model (the interaction probability is fixed by hypothesis).

The different models were fitted to each pair of species and the fitted
probabilities were recorded. The joint probability $P(L_{ij},X_i,X_j)$ was
then computed from Eq. 2 and the likelihood of each observation was computed
as $L(\theta|D) = P(L_{ij},X_i,X_j)$ if an interaction was observed and
$L(\theta|D) = 1 - P(L_{ij},X_i,X_j)$ if no interaction was observed. The log-
likelihood was summed over the entire dataset to compare the different models
by AIC. Not surprisingly, it was impossible to compute this model for a very
large number of pairs of species because they never co-occurred. These pairs
were removed from the analysis because the co-occurrence probability is null
and we have no information for the interaction probability. The reported
likelihood across the entire dataset is summed over all pairs of species that
were observed co-occurring at least one time. We considered separately the
salix-galler and the galler-parasitoid interactions.

Finally, we used the full model (both the co-occurrence and the interaction
are conditional on the environment) interpolate species
distribution and the interaction probability across the entire Europe. We 
reconstructed the expected network for each location in a 1km X 1km grid. We
then after computed the probabilistic connectance following Poisot2015b.

All of the data are openly available in the database \emph{mangal}
(Poisot2015) and all R scripts for querying and pre-processing the data, along
with the analysis are provided in supplementary material.

\subsection*{Results}

We start with an example for a single pair of species that we selected because
of a sufficiently large number of times they were found co-occurring ($N_{ij}
= 41 $). Despite the extent of the sampling, many pairs of species are found
co-occurring only a few times, making it hard to evaluate interaction
probabilities with a reasonnable confidence interval. This particular example
involves the interaction between \textit{Phyllocolpa plicalapponum} and
\textit{Pediobius saulius}, two fairly abundant species, observed respectively
$N_i = 53$ and $N_j = 129$ times across the 374 sites. These two species are
found interacting with marginal probability $P(L_{ij}) = 0.73$, which means
they were found interacting at 30 different locations. The model comparaison
(Table 1) reveals that the interaction probability conditional on the co-
occurrence better explain the distribution (Model 1 vs Model 2). The
probabilistic representation of the metaweb yields a much better fit to the
data than the deterministic version. When the two species co-occur, the
occurrence of the interaction is insensitive to the environment (Model 2 vs
Model 3). Alternatively, climatic variables significantly impact co-
occurrence (Model 3 vs Model 4). The neutral model performs worst than the
non-random co-occurrence model (Model 3 vs Model 6). The full model reveals
that the greatest interaction probability occurs at intermediate temperature
and precipitations, simply because this is where the two species are found co-
occurring the most often (Fig. 3). The co-occurrence and the interaction
probabilities could be represented in space, where we find that the highest
interaction probability occurs in central Europe (Fig. 4).

We did evaluated each model for all pairs of species in order to better
understand the large scale drivers of network turnover. Salix-gallers and
gallers-parasitoids were analyzed separately (Table 2). The results are
comparable, albeit some very minor details. We do find that across all pairs
of species, the probabilistic representation of interactions again does better
than the deterministic (Model 1 vs Model 2). Interactions do not happen
systematically whenever the two species are found co-occurring, meaning that
the stochastic nature of interactions contribute to network variability in
addition to species turnover. There are 1077 recorded pairs of interactions,
with only 224 of them occurring less than 5 times. Out of these 224
interactions, only 77 are found systematically whenever the two species do
co-occur. Even though interactions are better represented probabilistically,
the two environmental variables that were considered are pretty poor
predictors of their occurrence (Model 2 vs Model 3). Not surprisingly, the
likelihood increases for both types of interactions when the environment is
considered. The extra number of parameters however exceed the gain in
likelihood, and therefore the best model excludes the effect of the
environment.

According to the log-likelihood only, the co-occurrence is non-neutral for salix-
galler interactions, while it is neutral for the galler-parasitoid
interaction. However, the gain in log-likelihood for the neutral model of galler-
parasitoid co-occurrence is inferior to the extra number of parameters (twice
as many since two species distribution models are fitted instead of just one),
which has for consequence that the best model according to AIC has non-random
co-occurrence (Model 3 vs Model 6), for both types of interactions.

The approach we present not only has implications for understanding the
biogeography of pairwise interactions and interaction networks, but also the
quality of the evaluation of metawebs. We investigated the reliability of the
estimated metaweb across the entire dataset. As mentionned above, across the
32 412 pairs of species, only 1077 pairs are interacting at least at a single
location, for a connectance of 0.03. However, only 8437 species are found co-
occurring at least one time across all locations. There are consequently 23975
gaps of information in the metaweb (74.0\% - see Fig. 5). Given that we do not
know if the non co-occurring species do indeed co-occur, it means that a more
appropriate estimate of connectance would be $C = 1077/8437 = 0.128$. This
result reveails that the evaluation of the sampling quality of ecological networks is a
problem on its own that worths further attention.

Once we selected the best model (model 3, Table 2), we were able to
reconstruct the expected species richness across Europe, along with the most
likely network for each location, and therefore map the expected distribution
of network properties (Fig. 6). We simply considered connectance, as it could
be easily computed from probablistic networks (Poisot2015b) and is also a good
proxy for many other network properties (Poisot2014). The diversity of Salix
tends to increase toward boreal areas, and we consequently find a peak in
diversity in northern Europe. The distribution of the expected number of
interactions follows the distribution of species richness, but not at the same
rate. Consequently, connectance is peaking in central Europe and in
England.

\newpage
%========================================================%
\section*{Discussion}

\textbf{Summary of the framework}\\
% 	- concept of integrated niche
% 	- visual
% 	- explored it with network data
% 	- useful to characterize not only the turnover in community composition, but also its structure
% 	- useful to understand spatial variation of processes such as top-down control, as well as community build-up.

\textbf{Toward interaction distribution models} \\
% 	- different approach, based on the variance, to investigate the network turnover
% 	- much closer in spirit to species distribution models

\textbf{What are the drivers of network variation in space?}\\
% 	- environment mostly affect co-occurrence
% 	- here links do not vary so much
% 	- we know that some interactions vary with the environment
% 	- perhaps we haven't had the appropriate covariates
% 	- new investigations with other systems will be required to challenge this result

\textbf{Forecasting network structure under global change}\\

% Quantifying the uncertainty and the variability of network structure

\textbf{Investigating the realized niche and the impact of biotic interactions on distribution}\\
% 	- havent look much at the drivers of co-occurrence, single took them granted from the data
% 	- many species are not different from the neutral
% 	- raise the question, once accoutning for the environment, are there true effects of interactions on distribution
% 	- for sure the analysis raise intersting points
% Provided that interactions do matter, could derive SDM
% 	- invert the problem
% 	- needs an hypothesis for 
% 	- could be derived from simple models such as
% 	- or from explicit rules such as

\textbf{Guidance for empirical studies}\\
% Ecological networks are known to be extremely sparse, \emph{i.e.} having far
% more absences of interactions that they have interactions. These absences of
% interactions, however, can come from different sources. The fact that unequal
% sampling at the local scale can affect our understanding of network structure
% is well documented \parencite{Martinez1999}. However, in a spatial context,
% some interactions may be undocumented because the species involved have
% never been observed in co-occurence. Although these are reported as a lack
% of interactions, in actuality we cannot make inference about them seeing
% that they have never been observed: it is possible that this interaction
% may happen should the two species co-occur. A second category of absences
% of interactions are those that are reported after multiple observations of
% species co-occurence. However, so as to have a confidence in the fact that the
% probability of an interaction is low, extensive sampling (that is, several
% co-occurences) is needed. Generally, our confidence that the interaction
% is indeed impossible will increase when the number of observations of the
% species pair. Seeing that this is essentialy a Bernoulli process (what is
% the probability that the species will interact given their presence), the
% breadth of the confidence interval is expected to saturate after a fixed
% number of observations, which can be set as a treshold above which a species
% paier has been observed "often enough".

% Conclusion

\newpage

%========================================================%
\section*{Conclusion}

\textbf{Research agenda on probabilistic interactions}\\
\begin{itemize}
	\item Need a new type of data
	\item Need to investigate the reliability of interactions
	\item From interaction probabilities to a distribution of network properties 
	\item Deeper investigations of the environmental dependence of interactions
	\item Trait-based approach to interactions
	\item The effect of interaction on co-occurrence
\end{itemize}

\newpage

%========================================================%
\section*{Acknowledgements}
This is a contribution to the working groups \emph{Networks over ecological
gradients} (Santa Fe Institute) and \emph{Continental-scale variation of
ecological networks} (Canadian Institute for Ecology and Evolution). 
\newpage

%========================================================%

\newpage
%========================================================%
\section*{Figure legends}

%------------------------
\subsection*{Figure 1}
\textbf{Non-random sampling of the metaweb}. 
Network assembly could be viewed as a sampling process of the regional pool of
potential interactions. Species are sampled first (indicated by colored nodes)
and among the present species in the local network, only some interactions are
occurring (indicated by colored links). The challenge we address with the
quantitive framework proposed is to adequately characterize this sampling
process. The sampling of the metaweb is illustrated with a local interaction
network among Salix, gallers and parasitoids. Here, the metaweb was
constructed by aggregating observed interactions across 374 local networks.
The color nodes represent the species that were found in the most diverse of
these 374 local networks.

%------------------------
\subsection*{Figure 2}
\textbf{Visual representation of the integrated niche}. 
We represent visually the integration between two views of the niche. In
biogeography, the niche is considered the set of environmental conditions
where the intrinsic growth rate $r$ is positive. The horizontal axis
represents an environmental gradient impacting the growth of the focal species
(in red). The location of the different species along this gradient represent
their optimum, and the vertical dotted lines represent the limits of the
[Grinnelian] niche of the focal species. In food web ecology, the [Eltonian]
niche represents the location of a species in the food web, as determined by
its preys and its predators. The vertical axis represents a niche gradient,
presumably a trait such as body size. The location of each species along this
gradient represent their niche position. The focal species will feed on the
different preys whose niche location falls within a given interval around the
optimum, represented by the horizontal dotted lines. The integrated niche
[Grinnelian \& Eltonian] corresponds to the square in the middle where an
interaction is possible. According to our probabilistic framework, the central
square represents the area where the joint probability of observing
interactions and co-occurrence is positive.

%------------------------
\subsection*{Figure 3}
\textbf{Probabilistic representation of the interaction probability between a leaf galler (\textit{Phyllocolpa plicalapponum}) and a parasitoid (\textit{Pediobius saulius}) across a temperature and a precipitation gradient}. The representation is based on predictions from model 3 (see Table 1). For the left panel: open circles represent the absence of both species or of an interaction, the closed circles represent co-occurrence and other symbols the occurrence of only one of the two species. For the other two panels the open circles represent co-occurrence but an absence of interaction and the closed circles represent the occurrence of an interaction.

%------------------------
\subsection*{Figure 4}
\textbf{Probabilistic representation of the interaction probability between a leaf galler (\textit{Phyllocolpa plicalapponum}) and a parasitoid (\textit{Pediobius saulius}) across Europe}.

%------------------------
\subsection*{Figure 5}
\textbf{Representation of the A) metaweb and B) gaps of data in the metaweb}. The salix and gallers were regrouped as 'victims' for the sake of the illustration, as the gallers and the parasitoids were regrouped as 'ennemies'.

%------------------------
\subsection*{Figure 6}
\textbf{Mapping the distribution of species richness, the number of links and connectance across Europe}. The representation is based on predictions from model 3 (see Table 2).

\newpage

%========================================================%
%------------------------
\subsection*{Figure 1}

\begin{figure}[ht!]
\centering\includegraphics[width=0.8\textwidth]{figures/mw_sampling}
\end{figure}

\newpage

%------------------------
\subsection*{Figure 2}

\begin{figure}[ht!]
\centering\includegraphics[width=0.8\textwidth]{figures/integrated_niche}
\end{figure}

\newpage

%------------------------
\subsection*{Figure 3}

\begin{figure}[ht!]
\centering\includegraphics[width=0.8\textwidth]{figures/example_pair}
\end{figure}

\newpage

%------------------------
\subsection*{Figure 4}

\begin{figure}[ht!]
\centering\includegraphics[width=0.8\textwidth]{figures/map_pair}
\end{figure}

\newpage

%------------------------
\subsection*{Figure 5}

\begin{figure}[ht!]
\centering\includegraphics[width=0.8\textwidth]{figures/mw_holes}
\end{figure}

\newpage

%------------------------
\subsection*{Figure 6}

\begin{figure}[ht!]
\centering\includegraphics[width=0.8\textwidth]{figures/map_connectance}
\end{figure}

\newpage

%========================================================%
\end{document}

### 2015-11-23 ms/notes_probaweb.tex
Complete analysis & draft

--- 2014-04-01 ms_probaweb.tex
@@
-\documentclass[12pt]{article}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath}
-\usepackage{color,lineno,setspace,multirow}
-\usepackage[sc]{mathpazo}
-\usepackage{graphicx}
-\usepackage[top=2.4cm,left=2.4cm,top=2.4cm,bottom=2.4cm,includefoot]{geometry}
-\usepackage[style=bes, backend=bibtex]{biblatex}
-\usepackage{rotating}
+% ANALYSIS OF CONTINENTAL WIDE VARIATION IN NETWORK STRUCTURE
+	% Dataset description
 
-\addbibresource{tim.bib}
+	% Description of the parametrization
+		% Data format
 
-\begin{document}
+		% Fit models one pair of species
+		% Compare the different maps
+		% Reconstruct the interaction probability 
+		% Evaluate the likelihood and AIC for the whole network
 
-\linenumbers 
-\modulolinenumbers[1]
+	% Interpretation 
+		% Model comparison 
+		% Drivers of spatial variation in network structure
+		% Implications for the evaluation of the metaweb
 
-\textbf{Title:} A quantitative framework for network biogeography\\
-% Alternative: The distribution of ecological interactions 
-% Alternative: The biogeography of ecological interactions
-% Alternative: Community (macro)ecology: integrating species interactions and species distributions
+% DISCUSSION
 
-\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Timoth\'ee Poisot$^{1,2,3}$, N\'eo
-Martinez$^{4}$, Jennifer A. Dunne$^{5}$, Jason Tylianakis$^{3}$, Nicolas
-Mouquet$^{6}$, Daniel B. Stouffer$^{3}$ \\
+% TO DO FOR THE ANALYSIS
 
-1: Canada Research Chair in Biogeography and community ecology. D\'epartement de
-biologie, chimie et g\'eographie, Universit\'e du Qu\'ebec \`a Rimouski, 300
-All\'ee des Ursulines, Qu\'ebec, Canada. G5L 3A1.\\
+% - Format the data
 
-2: Qu\'ebec Centre for Biodiversity Sciences\\
+% - Fit models for the interactions
+%	P(Lij | Xi, Xj)
+% 	P(Lij | Xi, Xj, E)
 
-3: \\
+% - Fit models for the distribution
+% 	P(Xi,Xj)
+% 	P(Xi,Xj | E )
+% 	P(Xi)P(Xj)
+% 	P(Xi | E)P(Xj | E)
 
-4: \\
+% - Fit models for the joint distribution
+% 	P(Lij)
+% 	P(Lij|E)
 
-5: \\
+% - Compute the likelihood for each model
 
-6:\\
+% - Random network generator
+% 	- species (doable only for independent distributions)
+% 	- links
 
-\textbf{Keywords:} networks, spatial ecology, co-occurrence, probability of interaction\\
+% FIGURES
 
-\textbf{Words in the abstract:}
+% - Illustration of network sampling. A) The metaweb of host-parasitoid interactions across Europe and B) a local network structure.
 
-\textbf{Words in the main text:}
+% - Conceptual representation of the integrated niche
 
-\textbf{Words in the legends:}
+% - Mapping the drivers of spatial variation of network structure at the landscape scale
+% 	A) host species i (observed & predicted)
+% 	B) parasitoid species j (observed & prediced)
+% 	C) co-occurrence of host & parasitoids (observed & predicted)
+% 	D) interactions (observed & predicted by the integrated niche model)
 
-\textbf{Figures:}
+% - Evaluation of the metaweb quality (range of the 95% condifence interval)
 
-\textbf{Tables:}
+% - Network structure over environmental gradients
+% 	A) Map of connectance with the integrated network
+% 	B) Connectance as a function of temperature (with only species distribution - with only the interaction - integrated model)
+% 	C) Map of nestedness
+% 	D) Nestedness as a function of temperature (with only species distribution - with only the interaction - integrated model)
 
-\textbf{References:}
+% TABLES
 
-\newpage
-\doublespacing
-
-%========================================================%
-\section*{Abstract}
-
-\newpage
-%========================================================%
-\section*{Introduction}
-
-Ecology textbooks define the structure of an ecological community as
-\emph{the pool of species occupying a given location at a given time, and
-the way these species interact} (ref to Morin?). It is therefore surprising
-that ecological research on the variation of community structure has focused
-on species turnover (refs), almost entirely neglecting variation in the way
-species interact (refs).
-
-Network structure vary in space and time, metaweb as a large scale
-synthesis. We don't know yet the mechanisms of variation
-
-The metaweb concept is making its way through the network literature even
-though it has never been formally and technically defined.
-It is usually conceived as a network of interactions among species that
-could potentially co-occur, and represented by a binary matrix, \emph{i.e.}
-a probabilistic matrix in which the probability of observing an interaction
-is either 0 or 1. As the metaweb is usually constructed by aggregating
-observations, it assigns a probability of 0 to the interaction of species that
-never co-occurred, and is unable to factor-out the effect of co-occurrence. The
-main problem with that approach is that the co-occurrence of rare species is
-extremely unlikely and thus most often appear as an absence of interactions
-in the metaweb. A rarefaction analysis previously shown that interactions
-accumulate with the addition of networks at a slower rate than species richness
-\parencite{Poisot2012d} -- this is because interactions cannot accumulate
-faster than the rate of species observations, and ultimately the rate of
-co-occurrence observations. The only way to build a metaweb \emph{only}
-based on observational data is to compensate for the inflation of 0 due
-to lack of co-occurrence through manipulative experiments (REF). As this is
-impracticable for all but the smallest organisms, predictive probabilistic
-methods are needed.
-
-No theory to explain and interpret the meaning of network variation in space.
-Current interpretation of species turnover involves the effect of the
-environment and stochasticity.
-
-Objective: Propose a theoretical framework to understand and predict the
-spatial and temporal variation in network structure.
-
-\newpage
-%========================================================%
-\section*{A probabilistic representation of ecological interactions networks in space}
-
-%% We need to be careful: ecological network / interaction network / etc.
-%% I vote interaction networks, ecological network can be a spatial graph.
-%% Also, since we're going to say "interaction" a lot, interaction network
-%% makes sense. -- tp
-
-Networks of species interactions vary in space and time because any given
-pairwise interaction could either occur or not at any particular location.
-Understanding this variation amounts to be able to determine the probability
-that two species ($i$ and $j$) will interact at a given time/location ($y$);
-the existence of an interaction in this situation is thus essentially a
-stochastic variable, which we note $L_{ij,y}$. It takes a value of 1 where the
-interaction occurs, and 0 elsewhere. We note $P(L_{ij,y})$ the probability
-of this event. There are several factors that could impact the occurrence
-of an interaction and we will describe them below. But ultimately, this
-probability depends on the spatial and temporal scale of observation. As long
-as the probability of a particular interaction is not null, the probability
-of observing it at least once will become asymptotically closer to 1 when
-the scale of observation increases.
-% OK I like this paragraph, but we're REALLY NOT talking about factors or mechanisms here.
-% This whole framework is top-down/inferential, so we should at least have a paragraph in the
-% intro essentially summing up our preprint on network variation, and be clear on the
-% fact that we don't touch on mechanisms.
-
-The occurrence of an interaction requires the co-occurrence of species $i$ and
-$j$. This argument might seem trivial at first, but the explicit consideration
-of this condition in the probabilistic representation of ecological networks
-will prove fundamental to understand their variation.
-% We already make this point in betalink, should we summarize it briefly?
-We thus define $X_{i,y}$
-as a stochastic variable representing the occurrence of a species $i$ at
-location $y$, and similarly $X_{ij,y}$ the co-occurrence of species $i$ and
-$j$. The quantity we seek to understand is the probability of a joint event:
-
-%-----------------
-\begin{equation}
-\text{P}(X_{i,y},X_{j,y},L_{ij,y},)
-\end{equation}
-%-----------------
-
-Or simply said, the probability of observing both species $i$ and $j$, and
-an interaction from $i$ to $j$. This probability could be further decomposed
-in two parts using the product rule of probabilities:
-
-%-----------------
-\begin{equation}
-P(X_{iy},X_{jy},L_{ijy})=P(L_{ijy}|X_{iy},X_{jy},E_y)P(X_{iy},X_{jy}|E_y)
-\end{equation}
-%-----------------
-
-We will refer to the left term as the metaweb. It is a conditional
-probability, representing the probability that an interaction occurs if
-species $i$ and $j$ are co-occurring. The right term is the probability
-of observing the two species co-occurring at location $y$. There are many
-variants of the metaweb representing different hypotheses about the origin
-of temporal and spatial variation in network structure (see the explicit
-formulations at Table 1). First, the interaction could be deterministic
-instead of probabilistic. In other words, $P(L_{ijy}) = 1$ if $X_{ijy} =
-1$, and 0 otherwise. This representation of the metaweb is the one mostly
-used so far, as soon as the species are found together they are assumed to
-interact. It is also the only way to represent interactions when there is
-not enough information available to evaluate the interaction probability. It
-should be a reasonable approximation when the sampling and inference scales
-are large enough and that the only variation of networks considered arises
-from species distribution.
-
-Ecological interactions could also depend on the environment. Although it
-is not common to see a conditional representation of ecological interactions,
-experimental studies of pairwise interactions revealing their sensitivity to
-the environment are common (REF). For instance, it has been documented that the
-predation risks of shorebirds do vary at the continental scale, from the south
-to the north (REF). The effect of the environment on interactions propagate
-up the community and influence network structure (REF). Here the environment
-is considered in a very broad sense, as any factor potentially influencing the
-probability of a pairwise interaction, provided that the species co-occur. It
-thus includes both the biotic and the abiotic components of environment. We
-note however that here the biotic environment includes organisms that are
-not considered in the co-occurrence matrix. Including a biotic component to
-the metaweb signifies that the pairwise interaction is conditional on higher
-order interactions. An interaction modifier occurs for instance when the
-predation risk by species $j$ might be impacted by a parasite $k$ changing
-the behaviour of the prey $i$. We note that a conditional probability approach
-could thus be used represent non-trophic interactions into ecological networks
-(REF). This topic is however beyond the scope of the current paper.
-
-There are also variants to the co-occurrence matrix. Akin to the metaweb,
-co-occurrence could be conditional or not. The simplest model relates
-co-occurrence probability directly to the environment. In this situation there
-is no underlying assumption about the ecological processes responsible for
-co-occurrence. Alternatively, the co-occurrence probability could be a function
-of the environment because of shared ecological requirements by the two species.
-Species are independently distributed, but co-occur more often that expected by
-chance alone because they are found on the same environments. We call this model
-later neutral because species are specifically responding to the environment but
-are independently distributed. Co-occurrence is then simply obtained by
-multiplying the result of two independent and specific species distribution
-models (SDM).
-
-Finally, the co-occurrence probability itself could be dependent on ecological
-interactions. Direct pairwise interactions such as competition, facilitation and
-predation have long been studied for their impact on co-distribution. Second and
-higher order interactions (e.g. trophic cascade) could also impact
-co-occurrence. There is however currently no general theory on the expected
-co-occurrence in complex ecological networks. For instance, we do not know how
-far co-occurrence is not-random when going along the chain of indirect
-interactions. Berlow (2009) shown previously that almost only first and second
-order interactions do matter in ecological networks, but we don't know for
-co-distribution. We neither know what is the sensitivity to species richness: do
-interactions tend to buffer each other? Generalizing knowledge acquired by the
-study of small community modules will require future research.
-
-\newpage
-%========================================================%
-\section*{Interpretation: the integrated niche}
-
-Correctly describing the ecological niche is key to understand and predict
-species distribution. Despite several attempts to refresh the conceptual
-basis of what ecological niches are, ecologists haven't moved far past the
-"n-dimensional hypervolume" formalism \parencite{Holt2009} introduced by
-\textcite{Hutchinson1961}. Despite its intuitive interpretation and translation
-into species distribution models \parencite{Blonder2014}, the concept has been
-constantly criticized (Hardin, 1960; Peters, 1991; Chase2003; Silvertown, 2004;
-Soberon, 2007) and several attempts have been made to expand and reinforce it.
-
-Part of the problem surrounding the definition of the niche has been
-clarified with the distinction between Eltonian and Grinnellian definitions
-\parencite{Chase2003}. The Grinnellian dimension of the niche is the
-effect of the environment on the demography of a species, while the Eltonian
-dimension is the effect of a species on its environment \emph{sensu lato}. The
-Grinnellian niche is the most intuitive one to apply and is the conceptual
-backbone of species distribution models. The Eltonian niche is well known
-by community ecologists, but is trickier to turn into predictive models
-\parencite{Devictor2010a}. Nonetheless, the development of the niche model
-of food web structure (Williams2000) and its parameterization (Williams2010;
-Gravel2013) made it more operational, although it has yet to be applied to
-more than trophic interactions.
-
-\textcite{Chase2003} attempted this representation in their definition:
-\textit{[The niche is] the joint description of the environmental conditions
-that allow a species to satisfy its minimum requirements so that the birth rate
-of a local population is equal or greater than its death rate along with the
-set of per capita effects of that species on these environmental conditions.}
-Their representation merges zero-net growth figuring the Grinnelian niche
-(when do the population persist) with impact vectors figuring the Eltonian
-niche (what is the population impact). While this representation has been very
-influential in community ecology at the local scale, it remains impracticable
-%%% WHY?
-at the biogeographical one. The absence of any mathematical representation
-of the niche that could easily be fit to ecological data perhaps explain why
-biogeographers are still struggling to develop species distribution models
-taking into account ecological interactions.
-
-The key point to integrate dimensions of the niche is to represent the Eltonian niche into a Grinnelian space. 
-- We do so by considering that the Eltonian niche is the hyper volume in the trait-space allowing an interaction. \\
-- Doing so, we could project both niches in a plane and find the hypervolume where an interaction should occur (Fig. 2). \\
-- This visual representation is parallel to the probabilistic definition of interaction probability. \\
-- We propose that the metaweb is the Eltonian dimension of the niche, while the matrix of co-occurrence is the Grinnellian dimension. \\
-- Feedbacks between dimensions occur through the inclusion of co-occurrence in the metaweb, and interactions in the co-occurrence matrix. \\
-- This approach radically change the representation of the niche, putting species distribution and ecological interactions at the same level. \\
-- Fitting the probabilistic model allows the evaluation of link distribution and species distribution models. \\
-- Moreover, the integrated niche concept facilitates the formulation of species distribution models taking into account biotic interactions (see the section Applications) \\
-
-% TO BE COMPLETED
-
-\newpage
-%========================================================%
-\section*{Example: network structure in different habitats}
-
-In this section we provide an analysis illustrating the framework with an
-empirical dataset of host-parasitoid networks. Data come from the study of
-Tylianakis(2007) on the impacts of habitat modifications to the network
-structure. The data consists of 48 networks with 4090 recorded interactions. The
-advantage of replicated host-parasitoid networks is that usually every
-interaction is observed, not inferred from a stationary metaweb. It thus allows
-to evaluate interaction probability and to factor out the effect of
-co-occurrence. Five habitats were sampled along a gradient of habitat
-modification: forest, abandoned coffee agroforest, coffee agroforest, pasture
-and rice culture. The metaweb consists of 9 parasitoids and kleptoparasites
-(Hymenoptera: Eulophidae, Ichneumonidae, Leucospidae, Megachilidae and
-Chrysididae; Dyptera: Bombyliidae) of 33 species of bees and wasps (Hymenoptera:
-Apidae, Megachilidae, Mutilidae, Pompilidae, Sphecidae, Vespidae). The metaweb
-is illustrated at Fig. 2, along with an example of one iteration of the metaweb.
-
-Tylianakis (2007) investigated whether habitat modification affects
-the structure of these networks They found a significant impact of
-the habitat on their structure, despite little variation in species
-richness. Increasing habitat modification led to a higher parasitoid
-to host species ratio and a paraistoid were also more specialized, thus
-impacting considerably vulnerability. A closer inspection of the networks
-revealed that intensive agricultural systems were dominated by a strong
-interaction and a specialization of the most abundant parasitoid. Although
-the discussion made clear that both the turnover in species composition and
-the interaction probability changed with habitat modification, it was not
-possible to partition these components.
+% - Model comparison (model description, nb parameters, likelihood, AIC)
 
@@
 in order to reduce the uncertainty to a manageable level.
-
-\newpage
-%========================================================%
-\section*{Applications}
-
-\subsection*{Network descriptors}
-
-\subsection*{Partitionning beta diversity}
-
-\subsection*{Guidance for empirical studies}
-
-Ecological networks are known to be extremely sparse, \emph{i.e.} having far
-more absences of interactions that they have interactions. These absences of
-interactions, however, can come from different sources. The fact that unequal
-sampling at the local scale can affect our understanding of network structure
-is well documented \parencite{Martinez1999}. However, in a spatial context,
-some interactions may be undocumented because the species involved have
-never been observed in co-occurence. Although these are reported as a lack
-of interactions, in actuality we cannot make inference about them seeing
-that they have never been observed: it is possible that this interaction
-may happen should the two species co-occur. A second category of absences
-of interactions are those that are reported after multiple observations of
-species co-occurence. However, so as to have a confidence in the fact that the
-probability of an interaction is low, extensive sampling (that is, several
-co-occurences) is needed. Generally, our confidence that the interaction
-is indeed impossible will increase when the number of observations of the
-species pair. Seeing that this is essentialy a Bernoulli process (what is
-the probability that the species will interact given their presence), the
-breadth of the confidence interval is expected to saturate after a fixed
-number of observations, which can be set as a treshold above which a species
-paier has been observed "often enough".
-
-\subsection*{Null model testing}
-
-% Do you mean "Patterns-generating models testing"?
-
-\subsection*{Species \& interactions distribution models}
-
-\newpage
-%========================================================%
-\section*{Conclusion}
-
-\begin{itemize}
-\item New research agenda\\
-
-\item List of new questions \\
-\end{itemize}
-
-\newpage
-%========================================================%
-\section*{Acknowledgements}
-This is a contribution to the working groups \emph{Networks over ecological
-gradients} (Santa Fe Institute) and \emph{Continental-scale variation of
-ecological networks}. (Canadian Institute for Ecology and Evolution). DG
-received financial support from NSERC and Canada Research Chair program. TP
-is supported by a MELS-FQRNT post-doctoral fellowship.
-\newpage
-
-%========================================================%
-\printbibliography
-
-\newpage
-%========================================================%
-\section*{Figure legends}
-
-%------------------------
-\subsection*{Figure 1}
-\textbf{Non-random sampling of the metaweb}.
-The sampling of the metaweb is illustrated with a local interaction network from the Tylianakis et al (2007) dataset.
-Here the metaweb is simply the number of observed interactions over the 48 networks.
-Arrows points to species that are present in the local network \#34 (represented on the right).
-
-%------------------------
-\subsection*{Figure 2}
-\textbf{The integrated niche}. The Grinnellian niche is the set of environmental conditions
-where the intrinsic growth rate $r$ is positive (axioms i, ii \& iii).
-Contingencies (axiom iv) such as disturbances and stochastic extinctions, in
-conjunction with limited dispersal (axiom v), restrict species distribution to
-the conditions where the colonization rate $c$ is larger than extinction rate
-$e$. The Eltonian niche on the other dimension is represented by the set of
-traits allowing species to interact (axiom viii). The red species is a predator
-with a trophic position $n$, feeding on species whose niche is within a certain
-range around the niche optimum $c$. The integrated niche combines the effects of
-the environment and ecological interactions. The central square represents the
-area where the joint probability of observing interactions and co-occurrence is
-positive.
-
-%------------------------
-\subsection*{Figure 3}
-\textbf{Uncertainty in the evaluation of the metaweb}.
-The inferred metaweb for the XX environment is represented (left), along with the uncertainty in the evaluation of the interaction probability (right).
-Note that the standard error for probabilities is not symetric and thus only the upper bound is represented.
-
-\newpage
-%========================================================%
-%------------------------
-\subsection*{Figure 1}
-
-\begin{figure}[ht!]
-\centering\includegraphics[width=0.8\textwidth]{sampling}
-\end{figure}
-
-\newpage
-
-%------------------------
-\subsection*{Figure 2}
-
-\begin{figure}[ht!]
-\centering\includegraphics[width=0.8\textwidth]{niche}
-\end{figure}
-
-\newpage
-
-%------------------------
-\subsection*{Figure 3}
-
-\begin{figure}[ht!]
-\centering\includegraphics[width=0.8\textwidth]{niche}
-\end{figure}
-
-\newpage
-
-%========================================================%
-
-%------------------------
-\begin{table*}[c]
-\centering
-\begin{tabular}{p{4cm}p{4cm}p{6cm}}
-\hline
-Name & Equation & Details \\
-\hline
-\textbf{Metaweb} &  & \\
-Constant & $P(L_{ijy}|X_{iy},X_{jy})$ & Interaction probability is invariant to the environment \\
-Conditional & $P(L_{ijy}|X_{iy},X_{jy},E_y)$ & Interaction probability is a function of the local environment \\
-Deterministic & $P(L^*_{ijy}|X_{iy},X_{jy})$ & Interaction occurs whenever both species are present \\
-
-\textbf{Co-occurrence} & &\\
-Constant & $P(X_{iy},X_{jy})$ & Species distribution independent of $E$ \\
-Conditional on $E$ & $P(X_{iy},X_{jy} |E_y)$ & Similar to a SDM applied to co-occurrence \\
-Neutral & $P(X_{ix}|E_y)P(X_{jy}|E_y)$ & Independent SDMs fit to both species; could be independent of $E$ \\
-Conditional on $L_y$ & $P(X_{iy},X_{jy} | L_y)$ & Could account for first and higher order interactions \\
-\hline
-\end{tabular}
-\caption{List of different models}
-\end{table*}
-
-\newpage
-
-%------------------------
-
-\begin{sidewaystable}[c]
-\centering
-\begin{tabular}{lllllllll}
-\hline
-\textbf{Model} & \textbf{Metaweb} & & & \textbf{Co-occurrence} & & & \textbf{$L(H|D)$} & AIC\\
-& Constant & Cond. on $E$ & Deterministic & Constant & Cond. on $E$ & Neutral & & \\
-\hline
-1. & X & & & & X & & 0 & 0 \\
-2. & & X & & & X & & 0 & 0 \\
-3. & & & X & & X & & 0 & 0 \\
-4. & & X & & X & & & 0 & 0 \\
-5. & & X & & & X & & 0 & 0 \\
-6. & & X & & & & X & 0 & 0 \\
-\hline
-\end{tabular}
-\caption{Model comparison with the host-parasitoid networks.
-The 48 networks were fitted to different models of interaction networks.
-Note that for the computation of the likelihood all null interaction probabilities, co-occurrences and the pairwise interactions without observed co-occurrences were removed.
-}
-\end{sidewaystable}
-
-\end{document}
-%========================================================%

### 2015-11-23 analysis/scripts/results/2_example_pair.R

@@ -1,0 +1,156 @@
+##################################################################
+# Script for Figure X,
+# Illustrating the computation of interaction probabilities for a 
+# pair of species
+# Dominique Gravel
+# October 29th, 2015
+##################################################################
+
+rm(list = ls())
+
+# Load some functions
+source("analysis/scripts/functions/collect.R")
+source("analysis/scripts/functions/species_models.R")
+source("analysis/scripts/functions/interactions_models.R")
+source("analysis/scripts/functions/get_LL.R")
+source("analysis/scripts/functions/get_probs.R")
+source("analysis/scripts/functions/fit_models.R")
+
+# Load the data
+load("analysis/data/DF_split.Rdata")
+load("analysis/data/expand_data.Rdata")
+
+#########################################################
+# Fit the different models
+#########################################################
+
+# Find the nb of links per pair
+nL  = numeric(length(DF_split))
+nX = numeric(length(DF_split))
+for(x in 1:length(DF_split)) {
+	nL[x] = sum(DF_split[[x]]$Lij)
+	nX[x] = sum(DF_split[[x]]$Xij)
+}
+cbind(nL,nX,nL/nX)[nX>20,]
+
+# Subset the data
+#pair_index = which(nL == 10 & nX == 23) # 15644
+#pair_index = which(nL == 10 & nX == 26)
+#pair_index = which(nL == 21 & nX == 38)
+#pair_index = which(nL == 16 & nX == 23)
+#pair_index = which(nL == 15 & nX == 24)
+#pair_index = which(nL == 14 & nX == 25) # 15626
+pair_index = which(nL == 30 & nX == 41) # 21418
+
+for(i in 1:length(DF_split)) {
+	if(nX[i] > 20 & nL[i]>10 & nL[i]/nX[i] < 0.8 ) {
+		cat(i, " ", nL[i], " ", nX[i], '\n')
+	}
+}
+
+#14038
+#14456
+#14458
+#14476
+#14618
+#15626
+#21395
+#21415
+#21418
+
+
+data = DF_split[[pair_index]]
[…]

### 2015-11-23 analysis/scripts/results/3_map_pair.R

@@ -1,0 +1,129 @@
+##################################################################
+# Script for Figure X,
+# Mapping across Europe the interaction probability between pairs of species
+# Dominique Gravel
+# October 29th, 2015
+##################################################################
+
+rm(list=ls())
+
+	library(raster)
+library(sp)
+library(rgdal)
+
+load("analysis/data/DF_split.Rdata")
+load("analysis/data/expand_data.Rdata")
+
+IDi = data$pairs.IDi
+IDj = data$pairs.IDj
+Si = length(unique(IDi))
+Sj = length(unique(IDj))
+nobs = 374
+np  = length(DF_split)
+
+# Load the stuff to make the raster object
+wrld <- readOGR("analysis/data/map", layer="level1")
+europe <- wrld[1,]
+exteur <- extent(europe)
+
+# Extract the climatic variables
+clim = crop(getData("worldclim", var="bio", res=10), exteur)
+T = getValues(clim$bio1)
+PP = getValues(clim$bio12)
+
+############################################################
+# Extract the local networks over Europe
+############################################################
+
+ncell = length(T)
+map_E = data.frame(T = T, PP = PP, T2 = T^2, PP2 = PP^2)
+#pair = 14038
+#pair = 14456
+#pair = 14458
+#pair = 14476
+#pair = 14618
+#pair = 15626
+#pair = 21395
+#pair = 21415
+pair = 21418
+
+data = DF_split[[pair]]
+Xi = data$Xi
+Xj = data$Xj
+Xij = data$Xij
+Lij = data$Lij
+E = data$E	
+
+i = as.numeric(as.vector(data$IDi[1]))
+j = as.numeric(as.vector(data$IDj[1]))
+
+# Compute the models
+lm_i = glm(Xi ~ T+PP+T2+PP2, family = "binomial", data = E)
+lm_j = glm(Xj ~ T+PP+T2+PP2, family = "binomial", data = E)
+subE = subset(E,Xij == 1)
+subLij = subset(Lij, Xij == 1)
+lm_L = glm(subLij ~ T+PP+T2+PP2, family = "binomial", data = subE)
+
+summary(lm_i)
+summary(lm_j)
+summary(lm_L)
+
+# Compute expected probabilities over the gradient
[…]

### 2015-11-23 analysis/scripts/results/5_metaweb_holes.R

@@ -1,0 +1,98 @@
+##################################################################
+# Script for Figure X,
+# Illustrating the computation of interaction probabilities for a 
+# pair of species
+# Dominique Gravel
+# October 29th, 2015
+##################################################################
+
+rm(list = ls())
+setwd("/Users/DGravel/Documents/Manuscripts/Inprep/ms_probaweb")
+load("analysis/data/DF_split.Rdata")
+load("analysis/data/expand_data.Rdata")
+
+IDi = as.character(data$pairs.IDi)
+IDj = as.character(data$pairs.IDj)
+Si = length(unique(IDi))
+Sj = length(unique(IDj))
+unique_IDi = unique(IDi)
+unique_IDj = unique(IDj)
+IDcomm = IDj[match(unique_IDi,unique_IDj,nomatch=0)]
+unique_ID_all = unique(c(IDi,IDj))
+Sall = length(unique_ID_all)
+DF = data.frame(sites = data$pairs.sites_ID, IDi = IDi, IDj = IDj, Xi=data$Xi, Xj=data$Xj, Xij = data$Xij, Lij = data$Lij)
+
+#########################################################
+# Compile the metaweb
+#########################################################
+
+Lij= matrix(0, nr = Sall, nc = Sall)
+Xij = matrix(0, nr = Sall, nc = Sall)
+
+n = 1
+for(i in 1:Si) {
+	for(j in 1:Sj) {
+
+		# Compute the number of links
+		nL = sum(DF_split[[n]]$Lij)
+
+		# Compute the number of co-occurrences
+		nX = sum(DF_split[[n]]$Xij)
+
+		if(nX!=0) {
+
+			# Get the victim
+			index_i = which(unique_ID_all == as.character(DF_split[[n]]$IDi)[1])
+
+			# Get the ennemy index
+			index_j = which(unique_ID_all == as.character(DF_split[[n]]$IDj)[1])
+
+			# Put the record in the mw
+			Lij[index_i,index_j] = nL
+			Xij[index_i,index_j] = nX
+		}
+		n = n+1
+	}
+}
+
+
+# Subset the two matrices to have an Si X Sj matrix
+PL = Lij/Xij
+subPL = PL[match(unique_IDi,unique_ID_all),match(unique_IDj,unique_ID_all)]
+NAs = is.na(subPL)
+subPL[NAs]=0
+
[…]

### 2015-11-23 ms/ms_probaweb.tex
Minor edits

@@
 
-\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Timoth\'ee Poisot$^{1,2,3}$, N\'eo
-Martinez$^{4}$, Jennifer A. Dunne$^{5}$, Jason Tylianakis$^{3}$, Tomas Roslin$^{6}$, Tommy Nyman$^{6}$, Ben Baiser$^{7}$, Daniel B. Stouffer$^{3}$ \\
+\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Ben Baiser$^{3}$, Jennifer A. Dunne$^{4}$, N\'eo
+Martinez$^{5}$, Tommy Nyman$^{6}$, Timoth\'ee Poisot$^{2,7}$, Tomas Roslin$^{6}$, Spencer Wood$^{8}$, Daniel B. Stouffer$^{9}$, Jason Tylianakis$^{9}$\\
 
@@
 7:\\
+
+8:\\
+
+9:\\
 

### 2016-04-06 ms/ms_probaweb.tex
Quasi final version

@@
 \usepackage{color,lineno,setspace,multirow}
-\usepackage[sc]{mathpazo}
 \usepackage{graphicx}
 \usepackage[top=2.4cm,left=2.4cm,top=2.4cm,bottom=2.4cm,includefoot]{geometry}
-\usepackage{rotating}
+\usepackage{natbib}
+\usepackage{caption}
+\usepackage{pdflscape}
+
+\bibliographystyle{bes}
 
@@
 
-\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Ben Baiser$^{3}$, Jennifer A. Dunne$^{4}$, N\'eo
-Martinez$^{5}$, Tommy Nyman$^{6}$, Timoth\'ee Poisot$^{2,7}$, Tomas Roslin$^{6}$, Spencer Wood$^{8}$, Daniel B. Stouffer$^{9}$, Jason Tylianakis$^{9}$\\
+\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Ben Baiser$^{3}$, Jennifer A. Dunne$^{4}$, Jens-Peter Kopelke$^{5}$, Neo
+Martinez$^{6}$, Tommy Nyman$^{7}$, Timoth\'ee Poisot$^{2,8}$,  Spencer Wood$^{9}$, Daniel B. Stouffer$^{10}$, Jason Tylianakis$^{10,11}$ Tomas Roslin$^{12}$,\\
 
@@
 
-3: University of Canterbury at Christchurch, School of Biological Sciences,\\
+3: \\
 
@@
 
-5: \\
+5: Senckenberg Research Institute and Natural History Museum, Senckenberganlage 25, D-60325 Frankfurt am Main, Germany\\
 
@@
 9:\\
+
+10: University of Canterbury at Christchurch, School of Biological Sciences\\
+
+11:\\
+
+12: Department of Ecology, Swedish University of Agricultural Sciences, Box 7044, 750 07 Uppsala, Sweden\\
 
@@
 
+Biogeography has historically focused on the spatial distribution and
+abundance of species, neglecting variation in the way species interact with
+each other. Models of species distribution and of interactions have
+historically taken different paths. Here, we plea for an integrated approach,
+adopting the view that community structure is best represented as an
+ecological network of interactions. We outline conceptual approach, suggesting
+that the ecological niche may be redefined to encompass the effect of the
+environment on species distribution (the Grinnellian dimension of the niche)
+and on the ecological interactions among them (the Eltonian dimension).
+Starting from this novel concept, we develop a quantitative theory to explain
+turnover of interactions in space and time – i.e. a novel approach to
+interaction distribution modelling. We decompose the probability with which
+two species interact with each other in two parts: the probability with which
+the species co-occur at a given location, and the probability that if they do
+so, they will interact. Both of these probabilities could be conditional on
+the environment. We apply this novel framework to a large data set of
+host–parasite interactions across Europe and find that two aspects of the
+environment (temperature and precipitation) leave a strong imprint on species
+co-occurrence, but not on the probability of local interactions. Even where
+species co-occur, interaction proves a stochastic rather than deterministic
+process, adding to variation in realized network structure. We also find that
+a large majority of species pairs are never found together, thus precluding
+any inferences regarding their probability to interact. Our framework provides
+a first conceptual framework to explain the variation of network structure at
+large spatial scales and opens new perspectives at the frontier between
+species distribution modelling and community ecology.
+
 \newpage
@@
 
-Community ecology is defined in most textbooks as \emph{the study of the
+Community ecology is defined in most textbooks as \textit{the study of the
 interactions that determine the distribution and abundance of organisms}
-(Krebs2001). Despite a general concensus on this definition (Scheiner2007), it
-is surprising that most research on the variation of community structure has
-focused mostly on the turnover of species composition (Anderson2011),
-neglecting variation in the way they interact with each other (McGill2006).
-Not surprisingly given this fact, biogeographers are still struggling to
-figure out if interactions do impact species distribution (Wisz2012;
-Kissling2012). There has been a step ahead with recent methodological
-improvements accounting for interactions in species distribution models
-(Pollock2014; Pelissier2013), but those remain nonetheless a 'species- based'
-approach to communities where interactions are fixed covariates affecting
-distribution. Here we plea for a more integrated approach of species and
-interaction distribution.
+\citep{Krebs2001}. Despite a general consensus on this definition
+(Scheiner2007), it is surprising that research on variation in community
+structure has focused mostly on the turnover of species composition
+\citep{Anderson2011}, neglecting variation in the way species interact with
+each other \citep{Poisot2015a}. Given this omission, it is perhaps not
+surprising that biogeographers are still struggling to establish whether
+interactions actually impact the distribution of species \citep{Wisz2012,
+Kissling2012}. Recent attempts at accounting for interactions in species
+distribution models \citep{Pollock2014, Pelissier2013} have brought some
+methodological advances. Yet, these techniques are still based on a ’species-
+based’ approach to communities, where interactions are merely treated as fixed
+covariates affecting distribution.
 
-The problem of community assembly is often formulated as \emph{how do we
+As a more explicit description of interaction structure among species, the
+network approach offers a convenient representation of communities. Species
+are represented as nodes and interactions by links. To date, studies of
+network diversity have mostly been concerned with the distribution of
+interactions within locations, and less so with the variation among locations
+\citep{Dunne2005, Bascompte2007, Ings2007, Kefi2012}. However, there is now
+ample evidence that interaction networks vary in space and time
+\citep{Poisot2012, Albouy2014, Poisot2016, Trojelsgaard2015}. Metacommunity
+theory provides explanation for the variation in the distribution of the
+different nodes \citep{Gravel2011c, Pillai2011}, but there is no explanation
+to the joint variation of node and link occurrences. We urgently need a
+conceptual framework to formalize these observations.
+
+Given the historically different approaches to modelling the distributions of
+species vs. interactions, there is an evident need to bring the two together.
+Here, we plea for an integrated approach, adopting the view that community
+structure is best represented as an ecological network of interactions. Based
+on this idea, we propose a new description of the basic concept of the
+ecological niche, now integrating the effect of the environment on species
+distribution and on the ecological interactions among them. Starting from this
+redefined concept, we develop a unified theory to explain turnover of
+interactions in space and time. We first present the conceptual framework, and
+then formalize it mathematically, using a probabilistic model to represent the
+sampling of the regional pool of interactions. At the level of species pairs,
+the statistical approach could be conceived as an interaction distribution
+model. At the community level, the approach provides a likelihood-based method
+to compare different hypotheses of network turnover. By applying this novel
+framework to a large data set on host–parasite interactions across Europe, we
+find that variation of the environment causes turnover of both species and
+interactions. The network structure changes systematically across the
+latitudinal gradient, with a peak of connectance at intermediate latitudes.
+
+%=============================================================================%
+\section*{The two dimensions of community structure}
+
+The problem of community assembly is often formulated as \textit{how do we
 sample a regional pool of species to constitute a local community?} This
-question could be rewritten to adress the problem of network assembly, as
-\emph{how do we sample a regional pool of interactions to constitute a local
-interaction network?}. An illustration of this problem for a food web is
-provided at Figure 1. The metaweb represents potential interactions among all
+question could be rewritten to address the problem of network assembly, as
+\textit{how do we sample a regional pool of interactions to constitute a local
+interaction network?} An illustration of this problem for a food web is
+provided in Figure 1. The metaweb represents potential interactions among all
 species that could be found in a given area. In this particular case, there
-are 274 nodes, and 1077 links among plants, herbivores and parasitoids from
-Northern Europe. An instance of a local community is also illustrated, with 44
-nodes and 160 interactions. Only $51.2\%$ of all potential interactions are
-realized. Our objective here is to provide a conceptual framework to explain
-the sampling of the regional pool of interactions, along with a quantitative
-method to predict it. The problem could be formalized by sequentially
-understanding why only a fraction of the species are locally co-occurring, and
-after why these species are interacting or not.
+are 275 nodes, and 1173 links among plants (52 nodes), herbivores (96 nodes),
+and parasitoids (127 nodes) from Northern Europe. An instance of a local
+community is also illustrated, with 45 nodes and 93 interactions. Only 55.0\%
+of all potential interactions are realized. Our objective here is to provide a
+conceptual framework to explain the sampling of the regional pool of
+interactions, along with a quantitative method to predict it. The problem
+could be formalized sequentially by first understanding why only a fraction of
+the species are co- occurring locally, and then why these species interact or
+not.
 
-There are multiple causes to spatial turnover in community composition. The
-first and most studied driver is the effect of variation in the abiotic
+There are multiple causes of spatial turnover in community composition. The
+first and most-studied driver is the effect of variation in the abiotic
 environment on species performance. Combined with specific responses in
-demography, it generates variation among localities by locally selecting the
-fittest species (Leibold2004). Stochasticity additionnaly plays a role, either
-because of the inherently unpredictable nature of colonization and extinction
-events, or because of strong non-linear feedbacks generating alternative
-transients and equilibrium (Chase2007; Vellend2014). The analysis of community
-turnover is usually performed with data represented in a table with rows
-corresponding to sites (or measurements) and the columns to species. Beta-
-diversity metrics quantify the variance of this community data (Legendre2005).
-Traditionnal approaches rely on measures of the dissimilarity between
-communities, using indices such as the Jaccard or the Bray Curtis measures of
-dissimilarity. Recent methods decompose the total variation of the community
-data into species and site contributions to beta diversity (Legendre2013).
-Even though these methods compare whole list of species between sites, or
-measurements, they remain fundamentally 'species-based' since they are all
-based on the within column variation. None of them consider the variation of
-associations (pairs or higher order motifs) explicitly.
+demography, it generates variation among sites by selecting the locally
+fittest species \citep{Leibold2004}. Stochasticity plays an additional role,
+either through the inherently unpredictable nature of colonization and
+extinction events (Hanski1999), or through strong non-linear feedbacks
+generating alternative transients and equilibriums \citep{Chase2007,
+Vellend2014}. Analyses of community turnover are usually performed with data
+represented in a table with rows corresponding to sites (or measurements) and
+columns to species. Metrics of beta diversity quantify the variance of this
+community data \citep{Legendre2005}. Traditional approaches rely on measures
+of dissimilarity among communities, such as the Jaccard or Bray–Curtis
+indices. A more recent approach decomposes the total variation of the
+community data into species and site contributions to beta diversity
+\citep{Legendre2013}. Even though these methods compare whole lists of species
+among sites or measurements, they remain fundamentally ’species-based’, since
+they report the variation within columns. None of them explicitly considers
+the variation of associations (i.e., of pairs or higher- order motifs –
+\citealt{Stouffer2007}).
 
-The niche is by far the dominant concept to explain species distribution and
-community assembly, from the local to the global scale. Following Hutchinson,
-the niche is viewed as the set of environmental conditions allowing a
-population to establish and maintain a population (see also Holt2009).
-Community turnover arises following successive species replacement along an
-environmental gradient, in agreement with a Gleasonian view of communities
-(Gleason). The concept is straighforward to operationalize with species
-distribution models, as it maps naturally on the available data (both
-distribution and environmental data) and a vast array of statistical tools
-representing it (e.g. Biomod, MaxEnt). It is however much harder to account
-for ecological interactions in this approach (Peterson2011). These are often
-viewed as externalities, constraining or expanding the range of environmental
-conditions required for a species to maintain a population (Pulliam2000;
-Soberon2007).
+The “niche” is by far the dominant concept to explain species distributions
+and community assembly, from the local to the global scale. Following
+\citealt{Hutchinson1957}, the niche is viewed as the set of environmental
+conditions allowing a population to establish and persist (see also
+\citealt{Holt2009}. Community turnover arises as a result of successive
+replacement of species along an environmental gradient, in agreement with the
+Gleasonian view of communities \citep{Gleason1926}. The concept is
+straightforward to operationalize with species distribution models, as it maps
+naturally on available distributional and environmental data. In consequence,
+a vast array of statistical tools have been developed to implement it (e.g.
+Biomod \citealt{Thuiller2003}, MaxEnt \citealt{Phillips2006}). It is however
+much harder to account for ecological interactions with this approach
+(Peterson2011). As such, these interactions are often viewed as externalities
+constraining or expanding the range of environmental conditions required for a
+species to maintain a viable population \citep{Pulliam2000, Soberon2007}.
 
-The network approach proposes a convenient formalism to represent the
-structure of local communities. Species are represented as nodes and
-interactions by links. The data could also be represented by matrices, with
-each species in rows and columns, and the entries representing the occurrence
-or the intensity of an interaction. Studies of network diversity are mostly
-concerned by the distribution of the interactions within a location and not so
-much by the variation among locations (Dunne2005; Bascompte2007; Ings2007;
-Kefi2012). Network complexity is computed as the number of interactions in the
-case of binary networks or interaction diversity in the case of quantitative
-networks (Bersier2002). However, there is now evidence that ecological
-interactions do also vary in space and time (Poisot2012; Trojelsgaard2015).
-The variability of community structure in this situation arises from the
-turnover of species composition, along with the turnover of the interactions
-among pairs of species. The occurrence and intensity of interactions could
-vary because of the environment, species abundance and higher order
-interactions (Poisot2015a). The variation in community composition is often
-independent of the variation of ecological interactions, suggesting these two
-components of network variability respond to different drivers (Poisot2012).
+As mentioned above, in the network approach to community structure, species
+and interactions are represented by nodes and links, respectively.
+Associations can also be represented by matrices in which entries represent
+the occurrence or intensity of interactions among species (rows and columns).
+Network complexity is then computed as the number of interactions (in the case
+of binary networks) or interaction diversity (in the case of quantitative
+networks, \citealt{Bersier2002}). Variability in community structure
+consequently arises from the turnover of species composition, along with
+turnover of interactions among pairs of species. The occurrence and intensity
+of interactions could vary because of the environment, species abundance, and
+higher-order interactions \citep{Poisot2015a}. Variation in community
+composition was found independent of the variation of ecological interactions,
+suggesting that these two components of network variability respond to
+different drivers \citep{Poisot2012}.
 
-Interestingly, the ecological network literature also has its own 'niche model' to
-position a species in a community (Williams2000). The niche of a species in
-this context represents the multidimentional space that could represent all of
-its interactions. Each species is characterized by a niche position, an
-optimum and a range over 3 to 5 different niche axes (Williams2000;
-Eklof2013). The niche model has been successful at explaining the complexity
-of a variety of networks, from food webs to plant-pollinator systems. The
-conceptual framework is however limited to local communities and does not
-provide any explanation to the turnover of network structure along
+Interestingly, the ecological network literature also has its own ’niche
+model’ to position a species in a community (Williams2000). The niche of a
+species in this context represents the multidimensional space of all of its
+interactions. Each species is characterized by a niche position, an optimum
+and a range over 3 to 5 different niche axes \citep{Williams2000, Eklof2013}.
+The niche model of food web structure has successfully explained the
+complexity of a variety of networks, from food webs to plant–pollinator
+systems \citep{Allesina2008, Williams2010, Eklof2013}. This
+conceptual framework is, however, limited to local communities, and does not
+provide any explanation for the turnover of network structure along
 environmental gradients.
-
-Here we adopt the view that a community structure is best represented as an
-ecological network of interactions and develop a theory to explain its
-turnover in space and time. We propose a new description of the niche that
-integrates the effect of the environment on species distribution and on
-ecological interactions. We first present the conceptual framework and then
-formalize it mathematically with a probabilistic approach to the sampling of
-the regional pool of interactions. We apply the framework to study the spatial
-variation of host-parasite interactions across Europe. We find that the
-variation of the environment causes both species and interaction turnover. The
-network structures changes systematically across the latitudinal gradient,
-with a peak of connectance at intermediate latitudes. At the pairwise level,
-the statistical approach could be conceived as an interaction distribution
-model. At the community level, the approach provides a likelihood based
-method to compare different hypotheses of network turnover.
 
@@
 
-Correctly describing the niche is key to understand turnover in community
-structure. Despite several attempts to refresh the conceptual basis of what
-ecological niches are, ecologists have not moved far past the "n-dimensional
-hypervolume" formalism introduced by Hutchinson. Despite its
-intuitive interpretation and translation into species distribution models
-(Boulangeat2012; Blonder2014), the concept has been constantly criticized
-(Hardin1960; Peters1991; Chase2003; Silvertown2004; Soberon2007) and several
-attempts have been made to expand and reinforce it.
+A more integrative description of the niche is key to understand spatial and
+temporal turnover in community structure. Despite several attempts to update
+the concept of the ecological niche, ecologists have not moved far past the
+“n-dimensional hypervolume” defined by Hutchinson. Despite its intuitive
+interpretation and easy translation into species distribution models
+\citep{Boulangeat2012, Blonder2014}, the concept has been constantly
+criticized \citep{Hardin1960, Peters1991, Silvertown2004}, and several
+attempts have been made to expand and reinforce it \citep{Pulliam2000,
+Chase2003, Soberon2007, Holt2009, McInerny2012b}.
 
-Part of the problem surrounding the definition of the niche has been clarified
-with the distinction between Eltonian and Grinnellian definitions (Chase2003).
-The Grinnellian dimension of the niche is the set of environmental conditions
+Part of the problem surrounding the niche concept has been clarified with the
+distinction between Eltonian and Grinnellian definitions (Chase2003). The
+Grinnellian dimension of the niche is the set of environmental conditions
 required for a species to maintain a population in a location. The Grinnellian
-niche is the most intuitive to apply and is the conceptual backbone of species
-distribution models. The Eltonian niche on the other hand is the effect of a
-species on its environment. This aspect of the niche is well known by
-community ecologists, but is trickier to turn into predictive models.
+niche is intuitive to apply, and constitutes the conceptual backbone of
+species distribution models. The Eltonian niche, on the other hand, is the
+effect of a species on its environment. This aspect of the niche is well known
+by community ecologists, but is trickier to turn into predictive models.
 Nonetheless, the development of the niche model of food web structure
-(Williams2000) and its parameterization (Williams2010; Gravel2013) made it
-more operational.
+\citep{Williams2000} and its parameterization \citep{Williams2010; Gravel2013}
+made it more operational.
 
-These perspectives are rather orthogonal to each other and thus lead to
-considerable confusion in the literature (McIntyre). Chase2003 attempted to
-reconcile them in their definition of the niche: \textit{[The niche is] the
-joint description of the environmental conditions that allow a species to
-satisfy its minimum requirements so that the birth rate of a local population
-is equal or greater than its death rate along with the set of per capita
-effects of that species on these environmental conditions.} Their
-representation merges zero-net growth isoclines figuring the Grinnelian niche
-(when do the population persists) with impact vectors figuring the Eltonian
-niche (what is the per capita impact). While this representation has been very
-influential in community ecology at the local scale (the resource-ratio theory
-of coexistence - Tilman1982), it remains impracticable at the large spatial
-scale because of the difficulties to measure it. The absence of any
-mathematical representation of the niche that could easily be fit to
-ecological data perhaps explain why biogeographers are still struggling to
-develop species distribution models taking into account ecological
-interactions.
+These perspectives are rather orthogonal to each other, which has resulted in
+considerable confusion in the literature \citep{McInerny2012a}.
+\citealt{Chase2003} attempted to reconcile them in their definition of the
+niche: “[The niche is] the joint description of the environmental conditions
+that allow a species to satisfy its minimum requirements so that the birth
+rate of a local population is equal to or greater than its death rate along
+with the set of per capita effects of that species on these environmental
+conditions”. Their representation merges zero-net growth isoclines delimiting
+the Grinnellian niche (when do populations persist) with impact vectors
+delimiting the Eltonian niche (what is the per-capita impact). While this
+representation has been very influential in local-scale community ecology (the
+resource-ratio theory of coexistence, \citealt{Tilman1982}, it remains
+impractical at larger spatial scales because of the difficulties to measure
+it. The absence of any mathematical representation of the niche that could
+easily be fitted to ecological data may explain why biogeographers are still
+struggling to develop species distribution models that also consider
+ecological interactions.
 
@@
 addition to the environmental constraints on demographic performance, any
-organism requires resources to sustain its metabolic demand and reproduction.
+organism requires resources to sustain its metabolic demands and reproduction.
 Abiotic environmental axes are any non-consumable factors affecting the
@@
 should therefore be viewed as the set of abiotic environmental factors (the
-Grinnelian component) along with the set of traits (the Eltonian component)
-allowing a sustainable population to establish and maintain at a location.
-Accordingly, each species could be characterized by an optimal position in
-both the environmental (x-axis) and the trait (y-axis) plane. The integrated
-niche is then the hypervolume where interactions could occur and sustain a
-population. This approach radically change the representation of the niche,
-putting species distribution and ecological interactions in the same
-formalism.
-
-The limits of the niches could be independent of each other (as in the example
-at Fig. 2), alternatively interact. For instance, the optimimal prey body size
-for predatory fishes could reduce with increasing temperature (Lelong2015),
-which would make diet boundaries functions of the environment. The other way
-around, we could also consider that the growth rate of the predator could
-change with the body size of the preys it feeds on, thereby altering the
+Grinnellian component) along with the set of traits (the Eltonian component)
+allowing a population to establish and to persist at a location. Accordingly,
+each species can be characterized by an optimal position in both the
+environmental (x-axis) and the trait (y-axis) plane. The integrated niche is
+then the hypervolume where interactions can occur and sustain a population.
+This approach radically changes the representation of the niche, putting the
+distributions and ecological interactions of species in the same formalism.
+The limits of the niche axes could be independent of each other (as in the
+example of Fig. 2), but they could also interact. For instance, the optimal
+prey size for predatory fishes could decrease with increasing temperature
+\citep{Lelong2015}, which would make diet boundaries functions of the
+environment. The other way around, we could also consider that the growth rate
+of the predator changes with the size of its prey items, thereby altering the
 environmental boundaries.
 
-\newpage
 %========================================================%
@@
 We now formalize the integrated niche with a probabilistic approach to
-interactions and distribution. We seek to represent the probability an
-interaction between species $i$ and $j$ occurs at location $y$. We
-define $L_{ijy}$ as a stochastic variable and are looking
-at the probabilty this event occurs, $P(L_{ijy})$. The occurrence of an
-interaction is dependent on the co-occurrence of species $i$ and $j$. This
-argument might seem trivial at first, but the explicit consideration of this
-condition in the probabilistic representation of ecological interactions will
-prove fundamental to understand their variation. We thus define $X_{iy}$ as a
-stochastic variable representing the occurrence of a species $i$ at location
-$y$, and similarly $X_{ijy}$ the co-occurrence of species $i$ and $j$. The
-quantity we seek to understand is the probability of a joint event:
+interactions and distributions. We seek to represent the probability that an
+interaction between species $i$ and $j$ occurs at location $y$. We define $L_{ijy}$ as a
+stochastic variable, and are looking at the probability that this event
+occurs, $P(L_{ijy})$. The occurrence of an interaction is dependent on the co-
+occurrence of species $i$ and $j$. This argument might seem trivial at first, but
+the explicit consideration of this condition in the probabilistic
+representation of ecological interactions will prove fundamental to understand
+their variation. We define $X_{iy}$ as a stochastic variable representing the
+occurrence of species $i$ at location $y$, and similarly $X_{ijy}$ the co-occurrence
+of species $i$ and $j$. The quantity we seek to understand is the probability of a
+joint event, conditional on the set of environmental conditions $E_y$:
 
@@
 
-Or simply said, the probability of observing both species $i$ and $j$, and
-an interaction from $i$ to $j$. This probability could be decomposed
-in two parts using the product rule of probabilities:
+Or simply said, the probability of observing both species $i$ and $j$, and an
+interaction between $i$ and $j$. This probability could be decomposed in two parts
+using the product rule of probabilities:
 
@@
 
-The left term is the probability of observing the two species co- occurring at
-location $y$. It corresponds to the Grinnelian dimension of the niche. The
+The left term is the probability of observing the two species co-occurring at
+location $y$. It corresponds to the Grinnellian dimension of the niche. The
 right term is a conditional probability, representing the probability that an
-interaction occurs between species $i$ and $j$, given their set of traits
-$\mathbf{T}$ and they are co- occurring. It is referred as the metaweb and
-corresponds to the Eltonian dimension of the niche described above. We will
-see below how this formalism could be directly fitted to empirical data. But
-before turning to an application, we will discuss the interpretation of
-different variants of these two terms.
+interaction occurs between species $i$ and $j$, given their set of traits $T$ and
+that they are co-occurring. Above, we referred to this entity as the metaweb,
+corresponding to the Eltonian dimension of the niche . Below, we will see how
+this formalism can be directly fitted to empirical data. But before turning to
+an application, we will discuss the interpretation of different variants of
+these two terms.
 
@@
 
-There are several variants to the co-occurrence probability representing
-different hypotheses about the temporal and spatial variation in network
-structure (see the explicit formulations at Table 1). The simplest model
-relates co- occurrence probability directly to the environment, $P(X_{ijy} |
-E_y)$. In this situation there is no underlying assumption about the
-ecological processes responsible for co-occurrence. It could arise because of
-the impact of ecological interactions on distribution (Pollock2014) or
-alternatively because of share environmental requirements. In the former case,
-species are not independent to each other and the conditional occurrence must
-be accounted for explicitlty, $P(X_{ijy} | E_y) = P(X_i | E_y, X_j)P(X_j |
-E_y)$. In the later case, species are independent and only the marginal
-occurrence must be accounted for, $P(X_{ijy} | E_y) = P(X_i | E_y)P(X_j |
-E_y)$.
+There are several variants to the co-occurrence probability, representing
+different hypotheses about temporal and spatial variation in network structure
+(see the explicit formulations in Table 1). The simplest model relates the
+probability of co-occurrence directly to the environment, $P(X_{ijy} |E_y)$. In
+this situation there are no underlying assumptions about the ecological
+processes responsible for co-occurrence. It could arise because of an impact
+of ecological interactions on distributions \citep{Pollock2014} or, alternatively,
+because of environmental requirements shared between i and j. In the former
+case, species are not independent of each other and the conditional occurrence
+must be accounted for explicitly, $P(X_{ijy} |E_y)=P(X_{iy} |E_y,X_{jy})P(X_{jy} |E_y)$.
+In the latter case, species are independent and only the marginal occurrence
+must be accounted for, $P(X_{ijy} |E_y)=P(X_{iy} |E_y)P(X_{jy} |E_y)$.
 
-The co-occurrence probability itself could be dependent on ecological
-interactions. Direct pairwise interactions such as competition, facilitation
-and predation have long been studied for their impact on co-distribution (such
-as in the cases studied by Diamond1976, Connor1980, Gotelli2000 etc..). Second
-and higher order interactions (e.g. trophic cascade) could also impact co-
-occurrence. Co-occurrence in ecological networks is however a topic of its
-own, influenced by the degree distribution and species richness
-(Cazelles2015). Almost only first order and second order interactions do
-impact co-occurrence. The covariance of interacting species to an
-environmental gradient also influences co-occurrence (Cazelles2016). Because
-of the complexity of relating co-occurrence to the interaction network
-structure, we  will focus here on the variation of interactions and not on the
-distribution, and leave this issue for Discussion and future research.
+The co-occurrence probability itself could depend on ecological interactions.
+This should be viewed as the realized component of the niche (i.e. the
+distribution when accounting for species interactions). Direct pairwise
+interactions such as competition, facilitation, and predation have long been
+studied for their impact on co-distribution (e.g. \citealt{Diamond1976, Connor1980,
+Gotelli2000}. Second- and higher-order interactions (e.g. trophic cascades)
+could also affect co-occurrence. Co-occurrence of multiple species embedded in
+ecological networks is however a topic of its own, influenced by the network
+topology and species richness \citep{Cazelles2015}. Not only direct interactions do
+influence co-occurrence, but indirect interactions as well (e.g. plant species
+sharing an herbivore could repulse each other in space. The impact of direct
+interactions and first-order indirect interactions on co-occurrence tends to
+vanish with increasing species richness in the community. Further, co-
+occurrence is also influenced by the covariance of interacting species to an
+environmental gradient \citep{Cazelles2016}. Because of the complexity of relating
+co-occurrence to the structure of interaction networks, we will here focus on
+the variation of interactions and not on their distribution, and leave this
+specific issue for the Discussion and future research.
 
@@
 There are also variants of the metaweb. First, most documented metawebs have
-thus far considered that ecological interactions are deterministic, not
-probabilistic (e.g. Havens1992; Woods2015). Species are assumed to interact if
-they are found together in a location, independently of their abundance and
-the environment. In other words, $P(L_{ijy}) = 1$ if $X_{ijy} = 1$, and 0
-otherwise. This approach might be a reasonnable approximation when the
-sampling and inference scales are large enough so that probabilities of
-observing at least one interaction converges to unity and that the only
-variation of networks considered arises from species distribution.
+thus far considered ecological interactions to be deterministic, not
+probabilistic (e.g. \citealt{Havens1992, Woods2015}). Species are assumed to interact
+whenever they are found together in a location, independently of their
+abundance and the environment. In other words, $P(L_{ijy}|X_{ijy}=1)$ equals 1
+andit equals 0 if $P(L_{ijy}|X_{ijy}=0)$. This approach might be a reasonable
+approximation if the scale of sampling and inference is so large that the
+probability of observing at least one interaction converges to unity and the
+only variation in the networks considered arises from species distributions.
 
-Ecological interactions could also vary with the environment, such as
-$P(L_{ijy} | E_y)$. Although it is not common to see a conditional
-representation of ecological interactions, experimental studies of pairwise
-interactions revealing their sensitivity to the environment are common (REF).
-For instance, it has been documented that the predation risks of shorebirds do
-vary at the continental scale, from the south to the north (REF). The effect
-of the environment on interactions propagate up the community and influence
-network structure (REF).
+Ecological interactions could also vary with the environment, so that $P(L_{ijy}
+|E_y)$. Although it is not common to see a conditional representation of
+pairwise ecological interactions, experimental studies have revealed them to
+frequently be sensitive to the environment. For instance, \citep{Mckinnon2010} shown
+that predation risks of shorebirds vary at the continental scale, decreasing
+from the south to the north. It is also common to see increasing top-down
+control with temperature (e.g. \citealt{Shurin2012, Gray2016}). Effects of the
+environment on interactions propagate up the community and influence network
+structure \citep{Woodward2010; Petchey2010}.
 
-\newpage
 %========================================================%
@@
 
-In this section we provide an illustration of the framework with an empirical
-dataset of host-parasitoid networks sampled throughout continental Europe
-along a south-north gradient. The analysis targets networks composed of
-willows (genus Salix), their galling insects, and the natural enemies of these
-gallers. The questions we address with the framework and the dataset are: i)
-how much variation in the network structure is there across the gradient and
-ii) what is the primary driver of network turnover across the gradient?
+We now turn to an illustration of the framework with the analysis of an
+empirical dataset of host–parasite networks sampled throughout south–north
+gradient in continental Europe. The focal system consists of local food webs
+of willows (genus Salix), their galling insects, and the natural enemies of
+these gallers. Targeting this system, we ask: i) how much does network
+structure vary across the gradient, and ii) what is the primary driver of
+network turnover across the gradient?
 
@@
 
-Communities of both willows and gallers are species-rich and widely
-distributed, with pronounced variation in community composition across space.
-The genus Salix includes over 400 species, most of which are shrubs or small
-trees (ref). The genus is common in most habitats across the Northern
-Hemisphere (ref). Willows support a highly diverse community of herbivorous
-insects, and one of the main herbivore groups in this system are gall-inducing
-sawflies (Hymenoptera: Tenthredinidae: Nematinae: Euurina (ref). Gall
-formation is induced by sawfly females during oviposition, and gall formation
-includes marked manipulation of plant chemistry by the galler (ref). The enemy
-community of the gallers includes nearly 100 species belonging to 17 insect
-families of four orders. These enemies encompass both inquilines and
-parasitoids: inquiline larvae (Coleoptera, Lepidoptera, Diptera, and
-Hymenoptera) feed primarily on gall tissue, but typically kill the galler
-larva in the process. Parasitoid larvae (representing many families in
-Hymenoptera) kill the galler larvae by direct feeding (REF). In terms of
-associations between the trophic levels, phylogeny-based comparative studies
-have demonstrated that galls represent "extended phenotypes" of the gallers,
-meaning that gall form, location, and chemistry is determined mainly by the
-galling insects and not by their host plants [ref]. Because galler parasitoids
-have to penetrate a protective wall of modified plant tissue in order to gain
-access to their victims, gall morphology has been inferred to strongly affect
-the associations between parasitoids and hosts (ref, ref). Thus, the set of
+Communities of willows, gallers, and galler enemies are species-rich and
+widely distributed, with pronounced variation in community composition across
+space. The genus Salix includes over 400 species, most of which are shrubs or
+small trees \citep{Argus1997}. The genus is common in most habitats across the
+Northern Hemisphere \citep{Skvortsov1999}. Willows support a highly diverse
+community of herbivorous insects, with one of the main herbivore groups being
+gall-inducing sawflies (Hymenoptera: Tenthredinidae: Nematinae: Euurina
+\citep{Kopelke1999}. Gall formation is induced by sawfly females during
+oviposition, and includes marked manipulation of host-plant chemistry by the
+galler \citep{Nyman2000}. The enemy community of the gallers includes nearly
+100 species belonging to 17 insect families of four orders
+\citep{Kopelke2000}. These enemies encompass two main types: inquiline larvae
+(Coleoptera, Lepidoptera, Diptera, and Hymenoptera) feed primarily on gall
+tissue, but typically kill the galler larva in the process, while parasitoid
+larvae (representing many families in Hymenoptera) kill the galler larvae by
+direct feeding \citep{Kopelke2003}. In terms of associations between the
+trophic levels, phylogeny-based comparative studies have demonstrated that
+galls represent “extended phenotypes” of the gallers, meaning that gall form,
+location, and chemistry is determined mainly by the galling insects and not by
+their host plants \citep{Nyman2000}. Because galler parasitoids have to
+penetrate a protective wall of modified plant tissue in order to gain access
+to their victims, gall morphology has been inferred to strongly affect the
+associations between parasitoids and hosts \citep{Nyman2007}. Thus, the set of
 parasitoids attacking each host is presumptively constrained by the form,
@@
 Local realizations of the willow–galler–enemy network were reconstructed from
-samples collected between 1982 and 2010. Plant galls were collected by J.P.
-Kopelke during this period at 374 sites across Central and Northern Europe.
-Sampling was conducted in the summer months of June and/or July, during the
-latter stages of larval development. Galler species were identified on the
-basis of willow host species and gall morphology, as these are distinct for
-each sawfly species. At each site, galls were randomly collected from several
-willow individuals in an area of about 0.1-0.3 km2. Most sites were visited
-only once, with a total of 641 site visits across the 374 sites. GPS
-coordinates were recorded for each location and the annual mean temperature
-and annual precipitation were obtained from WorldClim. While other covariates
-could have been considered, we figured that they are representative of the
-most important axes of the European climate, and more easily
-interpretable than reduced variables obtained by a PCA,
+community samples collected between 1982 and 2010. During this period, willow
+galls were collected at 370 sites across Central and Northern Europe. Sampling
+was conducted in the summer months of June and/or July, i.e., during the later
+stages of larval development. Galler species were identified on the basis of
+willow host species and gall morphology, as these are distinct for each sawfly
+species. At each site, galls were randomly collected from numerous willow
+individuals in an area of about 0.1–0.3 km2. Most sites were visited only
+once, with a total of 641 site visits across the 370 sites. GPS coordinates
+were recorded for each location; for our present analyses, the annual mean
+temperature and precipitation were obtained from WorldClim using the R package
+raster \citep{Hijmans2015}. While other covariates could have been considered,
+we assumed mean temperature and annual precipitation to be representative of
+the most important axes of the European climate, and more easily interpretable
+than reduced variables obtained by e.g. PCA.
 
 The methods used for rearing natural enemies from the galls have been
-previously described by e.g. [ref, ref]. In brief, galls were opened to score
-the presence of galler or parasitoid/inquiline larvae. Enemy larvae were
-classified to preliminary morphospecies, and the identity of each
+previously described by \citep{Kopelke1999, Kopelke2003}. In brief, galls were
+opened to score the presence of galler or parasitoid/inquiline larvae. Enemy
+larvae were classified to preliminary morphospecies, and the identity of each
 morphospecies was determined by connecting them to adults emerging after
 hibernation. The galls were reared by storing single galls in small glass
-tubes (Kopelke 1985a, 1994a, 1999, 2003a, b). Hibernation of galls containing
-parasitoids took place either within the glass tubes or between blotting paper
-in flowerpots filled with clay granulate or a mixture of peat dust and sand.
-These pots were stored over the winter in a roof garden and/or in a climatic
-chamber. In most cases, the matching of larval morphospecies with adult
-individuals emerging from the rearings allowed the identification of the
-natural enemies to the species level. Nonetehless, in some cases, individuals
-could only be identified to one of the (super)families Braconidae,
-Ichneumonidae, and Chalcidoidea. This was particularly the case when only
-remains of faeces, vacant cocoons of parasitoids, and/or dead host larvae were
-found, as was the case when parasitoids had already emerged from the gall. As
-a result, the largest taxon in the data set, “Chalcidoidea indeterminate,”
-represents a superfamily of very small parasitoids that are hard to
-distinguish.
+tubes \citep{Kopelke1985a}. Hibernation of galls containing enemies took place
+either within the glass tubes or between blotting paper in flowerpots filled
+with clay granulate or a mixture of peat dust and sand. These pots were stored
+over the winter in a roof garden and/or in a climatic chamber. In most cases,
+the matching of larval morphospecies with adult individuals emerging from the
+rearings allowed the identification of the natural enemies to the species
+level. Nonetheless, in some cases, individuals could only be identified to one
+of the (super)families Braconidae, Ichneumonidae, and Chalcidoidea. This was
+particularly the case when only remains of faeces, vacant cocoons of
+parasitoids, and/or dead host larvae were found, as was the case when
+parasitoids had already emerged from the gall. As a result, the largest taxon
+in the data set, “Chalcidoidea indeterminate,” represents a superfamily of
+very small parasitoids that are hard to distinguish.
 
-In total, the sampling targeted 52 Salix taxa, yielding 146,622 galls for
-dissection and rearing. These galls represented 96 galler species, and yielded
-42,133 individually-identified parasitoids and inquilines. Of these, 25,170
-(60\%) could be identified to the species level. Overall, 126 parasitoid and
+In total, 146,622 galls from 52 Salix taxa were collected for dissection and
+rearing. These galls represented 96 galler species, and yielded 42,133
+individually-identified parasitoids and inquilines. Of these, 25,170 (60\%)
+could be identified to the species level. Overall, 127 parasitoid and
 inquiline taxa were distinguished in the material. Data on host associations
-within subsets of this material have been previously reported by (Kopelke ref
-ref b) and by Nyman et al. 2007, whereas the current study represents the
-first analysis of the full data set from a spatial perspective.
+within subsets of this material have been previously reported by Kopelke1999
+and by Nyman2007, whereas the current study represents the first analysis of
+the full data set from a spatial perspective.
 
@@
 Computing the probability of observing an interaction involves fitting a set
-of binomial models and collecting their estimated probabilities. We considered
-second-order generalized linear models for the sake of the illustration, but
-more sophisticated fitting algorithms (e.g. GAM or Random Forest) could be
-used as well, as long as the algorithm can provide an estimated probability
-for each observation. The data consists of a simple (albeit large) table with
-the observation of each species, $X_i$ and $X_j$, their co-occurrence,
-$X_{ij}$, the observation of an interaction $L_{ij}$, and environmental co-
-variates. There is one row per pair of species per site. We considered that an
-absence of a record of an interaction between co-occurring species at a site
-means a true absence.
+of binomial models and collecting their estimated probabilities. For the sake
+of illustration, we considered second-order generalized linear models –
+whereas more sophisticated fitting algorithms (e.g. GAM or Random Forest)
+could equally well be used, as long as the algorithm can estimate the
+probability for each observation. The data consist of a simple (albeit large
+and full of zeros) table with the observation of each species, $X_{iy}$ and $X_{jy}$,
+their co-occurrence, $X_{ijy}$, the observation of an interaction $L_{ijy}$, and
+environmental co-variates $E_y$. Thus, there is one row per pair of species per
+site. We considered that an absence of a record of an interaction between co-
+occurring species at a site means a true absence (see below for a discussion
+on this issue).
 
-We compared three models for the co-occurrence probability. The first model
-fits directly the co-occurrence probability conditional
-on the local environment, $P(X_{ijz}|E_z)$. This model therefore does not make any
-hypothesis about the mechanisms driving co-occurrence for any given
-environment and use the information directly available in the data. The second
-models consider independent co-occurrence of species. In this case, we fit
-independently $P(X_{iz}|E_z)$ and $P(X_{jz}|E_z)$ and take their product to
-derive co-occurrence probability. This model should be viewed as a null
-hypothesis with respect to the first model since their comparison reveals if
-there is significant spatial association of the two species once considering
-the response to the environment (Cazelles2016). Finally the third model
-considers that co-occurrence probability is independent of the environment and
-thus constant throughout the landscape.  In other words, $P(X_{ijz})$ is
-obtained by simply counting the number of observed co-occurrences, divided by
-the total number of observations. The comparison between the first and third
-model allows testing the hypothesis that co-occurrence is conditional on the
-environment. Whenever the environment is included as a co-variate in the glm,
-we considered a second-order polynomial response for both the temperature and
-precipitations. There are consequently 5 parameters for the first model when
-fitting a given pair of species, 10 parameters for the second model and only 1
-for the third model.
+We compared three models for the co-occurrence probability. The first one
+directly models the co-occurrence probability conditional on the local
+environment, $P(X_{ijy} |E_y)$. Hence, this model makes no assumptions about the
+mechanisms driving co-occurrence for any given environment, and only uses the
+information directly available in the data. It thereby indirectly accounts for
+the effect of interactions on co-occurrence, if there is any. The second model
+considers independent co-occurrence of species. In this case, we independently
+fitted $P(X_{iy} |E_y)$ and $P(X_{jy} |E_y)$, then we took their product to derive the
+probability of co-occurrence. This model should be viewed as a null hypothesis
+with respect to the first model, since a comparison between the respective
+models will reveal if there is significant spatial association of the two
+species beyond a joint response to the shared environment \citep{Cazelles2015}.
+Finally, the third model assumes that the probability of co-occurrence is
+independent of the environment and thus constant throughout the landscape. In
+other words, $P(X_{ijy})$ is obtained by simply counting the number of observed
+co-occurrences, divided by the total number of observations. Thus, the
+comparison between the first and third model allows testing the hypothesis
+that co-occurrence is conditional on the environment. Whenever the environment
+was included as a covariate in the glm, we considered a second-order
+polynomial response for both temperature and precipitation. There are
+consequently 5 parameters for the first model when fitting a given pair of
+species, 10 parameters for the second, and only 1 for the third model.
 
-Following the same logic, we compared three models for the interaction
-probability. The first model fits the interaction probability conditional on
-the local environmental variables, $P(L_{ijz}|E_z,X_i,X_j)$. Consequently, the
-model was fitted on a subset of the data, when the two species are found co-
-occurring. The second model fits the interaction probability independently of
-the local environmental variables, $P(L_{ijz}|X_i,X_j)$. It corresponds to the
-number of times the two species were observed interacting when co-occurring,
-divided by the number of times they co-occurred. The third model is an extreme
-case performed only to test the hypothesis that if two species are found to
-interact at least once, then they should interect whenever they co-occur,
-$P(L_{ijz}|X_i,X_j)=1$. While not necessarily realistic, this model tests an
-hypothesis that is commonly done in the representation of local networks from
-knowledge of a deterministic metaweb (such as in Havens1992; Piechnik2008;
-Wood2015). There are consequently 5 parameters for the first model, a single
-parameter for the second model and no parameter to evaluate for the third
-model (the interaction probability is fixed by hypothesis).
+Following the same logic, we compared three models of the interaction
+probability. The first model conditions the interaction probability on the
+local environmental variables, $P(L_{ijy} |X_{iy},X_{jy},E_y)$. Consequently,
+the model was fitted to a subset of the data where the two species co-occur.
+The second model fits the interaction probability independently of the local
+environmental variables, $P(L_{ijy} |X_{iy},X_{jy})$. It corresponds to the
+number of times the two species were observed to interact when co-occurring,
+divided by the number of times that they co-occurred. The third model is an
+extreme case performed only to test the hypothesis that if two species are
+found to interact at least once, then they should interact whenever they co-
+occur, $P(L_{ijy} |X_{iy},X_{jy})=1$. While not necessarily realistic, this
+model tests an assumption commonly invoked in the representation of local
+networks from the knowledge of a deterministic metaweb. There are consequently
+5 parameters for the first model, a single parameter for the second model and
+no parameter to evaluate for the third model (where the interaction
+probability is fixed by the hypothesis).
 
 The different models were fitted to each pair of species and the fitted
-probabilities were recorded. The joint probability $P(L_{ij},X_i,X_j)$ was
-then computed from Eq. 2 and the likelihood of each observation was computed
-as $L(\theta|D) = P(L_{ij},X_i,X_j)$ if an interaction was observed and
-$L(\theta|D) = 1 - P(L_{ij},X_i,X_j)$ if no interaction was observed. The log-
-likelihood was summed over the entire dataset to compare the different models
-by AIC. Not surprisingly, it was impossible to compute this model for a very
-large number of pairs of species because they never co-occurred. These pairs
-were removed from the analysis because the co-occurrence probability is null
-and we have no information for the interaction probability. The reported
-likelihood across the entire dataset is summed over all pairs of species that
-were observed co-occurring at least one time. We considered separately the
-salix-galler and the galler-parasitoid interactions.
+probabilities were recorded. The joint probability $P(L_{ijy},X_{iy},X_{jy})$
+was then computed from Eq. 2, and the likelihood of each observation was
+computed as $mathcal{L}(\theta_{ijy}|D_{ijy})=P(L_{ij},X_{iy},X_{jy})$ if an
+interaction was observed, and as
+$mathcal{L}(\theta_{ijy}|D_{ijy})=1-P(L_{ijy},X_{iy},X_{jy})$ if no
+interaction was observed. The log- likelihood was summed over the entire
+dataset to compare the different models by AIC. Not surprisingly, there was a
+very large number of species pairs for which this model could not be computed,
+as they simply never co-occurred. For these pairs, we have no information of
+the interaction probability, and they were consequently removed from the
+analysis. The log-likelihood reported across the entire dataset was summed
+over all pairs of species observed to co- occur at least once. Interactions
+among the first (Salix) and second (gallers) trophic layers , and the second
+and third (galler enemies) were considered separately. Finally, we used the
+full model (in which both co-occurrence and the interaction are conditional on
+the environment) to interpolate species distributions and interaction
+probabilities across the entire Europe. We reconstructed the expected network
+for each location in a 1km X 1km grid, and thereafter computed the
+probabilistic connectance following Poisot2015b.
 
-Finally, we used the full model (both the co-occurrence and the interaction
-are conditional on the environment) interpolate species
-distribution and the interaction probability across the entire Europe. We 
-reconstructed the expected network for each location in a 1km X 1km grid. We
-then after computed the probabilistic connectance following Poisot2015b.
-
-All of the data are openly available in the database \emph{mangal}
-(Poisot2015) and all R scripts for querying and pre-processing the data, along
-with the analysis are provided in supplementary material.
+All of the data are openly available in the database mangal \citep{Poisot2015b} and
+all R scripts for querying and pre-processing the data, along with the
+analysis, are provided in the Supplementary material.
 
@@
 
-We start with an example for a single pair of species that we selected because
-of a sufficiently large number of times they were found co-occurring ($N_{ij}
-= 41 $). Despite the extent of the sampling, many pairs of species are found
-co-occurring only a few times, making it hard to evaluate interaction
-probabilities with a reasonnable confidence interval. This particular example
-involves the interaction between \textit{Phyllocolpa plicalapponum} and
-\textit{Pediobius saulius}, two fairly abundant species, observed respectively
-$N_i = 53$ and $N_j = 129$ times across the 374 sites. These two species are
-found interacting with marginal probability $P(L_{ij}) = 0.73$, which means
-they were found interacting at 30 different locations. The model comparaison
-(Table 1) reveals that the interaction probability conditional on the co-
-occurrence better explain the distribution (Model 1 vs Model 2). The
-probabilistic representation of the metaweb yields a much better fit to the
-data than the deterministic version. When the two species co-occur, the
-occurrence of the interaction is insensitive to the environment (Model 2 vs
-Model 3). Alternatively, climatic variables significantly impact co-
-occurrence (Model 3 vs Model 4). The neutral model performs worst than the
-non-random co-occurrence model (Model 3 vs Model 6). The full model reveals
-that the greatest interaction probability occurs at intermediate temperature
-and precipitations, simply because this is where the two species are found co-
-occurring the most often (Fig. 3). The co-occurrence and the interaction
-probabilities could be represented in space, where we find that the highest
-interaction probability occurs in central Europe (Fig. 4).
+Despite the extensive sampling, many pairs of species were found co-occurring
+only a few times. This made it hard to evaluate interaction probabilities with
+any reasonable confidence interval. Thus, we start with an example of a single
+pair of species selected because of its high number of co-occurrences
+($N_{ij}=38$): \textit{Phyllocolpa prussica} and \textit{Chrysocharis
+elongata}, two fairly abundant species, were observed $N_i=49$ and $N_j=121$
+times, respectively, across the 370 sites. These two species were found to
+interact with a marginal probability $P(L_{ij})=0.55$, which means they
+interacted at 21 different locations. Here, a comparison of model fit (Table
+1) reveals that the interaction probability conditional on the co-occurrence
+does not better explains their distribution (Model 1 vs Model 2). When the two
+species co-occur, the occurrence of the interaction is insensitive to the
+environment (Model 2 vs Model 3). Alternatively, climatic variables
+significantly impact co-occurrence (Model 3 vs Model 4). The neutral model
+performs worse than the non-random co- occurrence model (Model 3 vs Model 6).
+The full model reveals that the greatest interaction probability occurs at
+intermediate temperature and precipitation, simply because this is where the
+two species most frequently co-occur (Fig. 3). The probabilities of co-
+occurrence and interaction can be represented in space, where we find that the
+highest interaction probability occurs in central Europe (Fig. 4).
 
-We did evaluated each model for all pairs of species in order to better
-understand the large scale drivers of network turnover. Salix-gallers and
-gallers-parasitoids were analyzed separately (Table 2). The results are
-comparable, albeit some very minor details. We do find that across all pairs
-of species, the probabilistic representation of interactions again does better
-than the deterministic (Model 1 vs Model 2). Interactions do not happen
-systematically whenever the two species are found co-occurring, meaning that
-the stochastic nature of interactions contribute to network variability in
-addition to species turnover. There are 1077 recorded pairs of interactions,
-with only 224 of them occurring less than 5 times. Out of these 224
-interactions, only 77 are found systematically whenever the two species do
-co-occur. Even though interactions are better represented probabilistically,
-the two environmental variables that were considered are pretty poor
-predictors of their occurrence (Model 2 vs Model 3). Not surprisingly, the
-likelihood increases for both types of interactions when the environment is
-considered. The extra number of parameters however exceed the gain in
-likelihood, and therefore the best model excludes the effect of the
-environment.
+In order to better understand the large-scale drivers of network turnover, we
+evaluated each model for all pairs of species. The results are highly
+consistent among trophic layers (Salix–gallers and gallers–enemies; Table 2).
+Across all pairs of species, the conditinal representation of interactions
+does better than the marginal one (Model 1 vs Model 2): interactions do not
+occur systematically whenever the two species are found co-occurring. Hence,
+in addition to species turnover, the stochastic nature of interactions
+contributes to network variability. In total, we recorded 1173 pairs of
+interactions, only 290 of which occurred more than 5 times. Out of these 290
+interactions, 143 are systematically detected whenever the two species do co-
+occur. Of when species co-occurred, the two environmental variables considered
+proved rather poor predictors of their interactions (Model 2 vs Model 3). Not
+surprisingly, for both types of interactions (Salix–gallers and
+gallers–enemies), the likelihood increases when the environment is considered.
+However, the extra number of parameters exceeds the gain in likelihood, and
+inflates AIC. Therefore, the best model excludes the effect of the
+environment. According to the log-likelihood only, co-occurrence is non-
+neutral for both Salix–galler interactions and galler–enemy interaction. Thus,
+according to AIC, the best model is the one of non-random co-occurrence (Model
+3 vs Model 6), for both types of interactions.
 
-According to the log-likelihood only, the co-occurrence is non-neutral for salix-
-galler interactions, while it is neutral for the galler-parasitoid
-interaction. However, the gain in log-likelihood for the neutral model of galler-
-parasitoid co-occurrence is inferior to the extra number of parameters (twice
-as many since two species distribution models are fitted instead of just one),
-which has for consequence that the best model according to AIC has non-random
-co-occurrence (Model 3 vs Model 6), for both types of interactions.
+To investigate the reliability of the estimated metaweb across the entire
+dataset, we may turn to summary statistics of species co-occurrence. As
+mentioned above, across the 17,184 potential pairs of species, only 1,173 pairs
+interacted in at least a single location, for a connectance of 0.068. However,
+only 4,459 pairs of species are found co-occurring at least one time across all
+locations. There are consequently 12,725 gaps of information in the metaweb
+(74.1\% - see Fig. 5). As we cannot know whether the non-co-occurring species
+would indeed interact when found together, a more appropriate estimate of
+connectance would be $C=1173/4459=0.263$. This result reveals that the
+evaluation of the sampling quality of ecological networks is a problem on its
+own and well worth further attention.
 
-The approach we present not only has implications for understanding the
-biogeography of pairwise interactions and interaction networks, but also the
-quality of the evaluation of metawebs. We investigated the reliability of the
-estimated metaweb across the entire dataset. As mentionned above, across the
-32 412 pairs of species, only 1077 pairs are interacting at least at a single
-location, for a connectance of 0.03. However, only 8437 species are found co-
-occurring at least one time across all locations. There are consequently 23975
-gaps of information in the metaweb (74.0\% - see Fig. 5). Given that we do not
-know if the non co-occurring species do indeed co-occur, it means that a more
-appropriate estimate of connectance would be $C = 1077/8437 = 0.128$. This
-result reveails that the evaluation of the sampling quality of ecological networks is a
-problem on its own that worths further attention.
+Once we had selected the best model (Model 3, Table 2), we used it to
+reconstruct the expected species richness, along with the most likely network
+for each location. By this approach, we could factually map the expected
+distribution of network properties across Europe (Fig. 6). For simplicity, we
+chose to consider connectance as descriptor of network configuration, as this
+metric can be easily computed from probabilistic networks \citep{Poisot2015c}) and is
+also a good proxy for many other network properties \citep{Poisot2014}. Overall, we
+find a peak in Salix, gallers and enemies diversity in northern Europe. The
+expected number of interactions roughly follows the distribution of species
+richness, but accumulates at a rate different from species numbers.
+Connectance also peaks in northern Europe (Fig. 6).
 
-Once we selected the best model (model 3, Table 2), we were able to
-reconstruct the expected species richness across Europe, along with the most
-likely network for each location, and therefore map the expected distribution
-of network properties (Fig. 6). We simply considered connectance, as it could
-be easily computed from probablistic networks (Poisot2015b) and is also a good
-proxy for many other network properties (Poisot2014). The diversity of Salix
-tends to increase toward boreal areas, and we consequently find a peak in
-diversity in northern Europe. The distribution of the expected number of
-interactions follows the distribution of species richness, but not at the same
-rate. Consequently, connectance is peaking in central Europe and in
-England.
-
-\newpage
 %========================================================%
@@
 
-\textbf{Summary of the framework}\\
-% 	- concept of integrated niche
-% 	- visual
-% 	- explored it with network data
-% 	- useful to characterize not only the turnover in community composition, but also its structure
-% 	- useful to understand spatial variation of processes such as top-down control, as well as community build-up.
+We proposed that the representation of community structure and its variation
+in space and time is best represented with the formalism of ecological
+networks, because both the distribution of species and their interspecific
+interactions are accounted for. We consequently revised the niche concept in
+order to integrate both the abiotic and the biotic components of the niche
+that are susceptible to vary of time and space. The integrated niche was
+represented visually with an ordination of species into an environmental space
+and a trait space. The fundamental niche of a species is represented as the
+set of environmental conditions and resources that allow a species to be
+maintained in a location, thereby integrating the Eltonian and the Grinnellian
+components of the niche. The concept is translated mathematically by the
+investigation of the probability of the joint occurrences of species and of
+the interaction, which should be interpreted as an interaction distribution
+model. We used this approach to characterize the turnover of the structure of
+ecological interactions in a tri-trophic network across Western Europe and
+found that the primary driver of variation is the turnover in species
+composition. This is to our knowledge the first continental wide analysis of
+the drivers of network structure from empirical data (see \citealt{Albouy2014,
+Poisot2016}).
 
-\textbf{Toward interaction distribution models} \\
-% 	- different approach, based on the variance, to investigate the network turnover
-% 	- much closer in spirit to species distribution models
+Applying the framework to our large data set on host–parasite interactions
+across revealed key features in the interaction between Salix taxa, their
+herbivores, and the natural enemies of these herbivores. Consistent with a
+general increase in the diversity of Salix towards boreal areas
+\citep{Cronk2015}, overall species richness of the networks increased towards
+the north. Distribution of salix species richness  largely matched the one of
+gallers and their ennemies. These observations here seen within Europe are
+also matched by the ones found at a global scale for salix \citep{Argus1997,
+Cronk2015, Wu2015} and sawflies \citep{Kouki1994, Kouki1999}. Species richness
+was originally presumed to show a similar “reversed latitudinal gradient” for
+a common group of parasitic wasps, the Ichneumonidae,, but this observation
+has been challenged by findings of rather high ichneumonid diversity in the
+tropics \citep{Veijalainen2013}. However, the ichneumonid subfamilies
+specifically associated with sawflies (Ctenopelmatinae, Tryphoninae) are
+clearly less diverse in the south.
 
-\textbf{What are the drivers of network variation in space?}\\
-% 	- environment mostly affect co-occurrence
-% 	- here links do not vary so much
-% 	- we know that some interactions vary with the environment
-% 	- perhaps we haven't had the appropriate covariates
-% 	- new investigations with other systems will be required to challenge this result
+Exactly what processes are responsible for the distribution of species
+richness at different trophic levels is yet to be established (but see e.g.
+\citealt{Roininen2005, Nyman2010, Leppanen2014}, but as a net
+outcome of different latitudinal trends across trophic levels, the
+distribution of co-occurrence and therefore of potential interactions differed
+between the first and second link layers. The correlation between the expected
+salix and gallers richness was 0.73, while it was 0.58 between gallers and
+their enemies. The ratio of herbivore to Salix species is essentially constant
+across Europe, whereas each herbivore species is potentially attacked by a
+richer enemy community higher latitudes (i.e. faces higher vulnerability).
+Consequently, overall connectance peaks in Northern Europe (Fig. 6).
 
-\textbf{Forecasting network structure under global change}\\
+In terms of species interacting with each other, our analysis suggest that the
+environment leaves a detectable imprint on species co-occurrence, but only a
+slighter mark on the occurrence of realized links among species in a specific
+place: the probability of finding a given combination of species at a higher
+and a lower trophic level at the same site was clearly affected by the
+environment, whereas the probability of observing an interaction between the
+two was not detectably so. This applies to the example species \textit{Phyllocolpa
+prussica} and \textit{Chrysocharis elongata} (Figs 2-3), but also to all species pairs
+more generally. For the example species pair, the full model reveals that the
+interaction probability is highest at intermediate temperature and
+precipitation, simply because this is where the two species co-occur most
+often. This does not imply that species will always interact when they meet –
+although this is a basic assumption in most documented metawebs to date (e.g.
+\citealt{Havens1992, Woods2015}). Rather, interaction is a stochastic process the
+probability of which is influenced by the probability with which species co-
+occur. What we cannot reliably know is how this stochasticity splits into two
+sampling processes – i.e., the extent to which a species at the higher trophic
+level runs into a species at the lower level co-occurring at the site, and the
+extent to which this interaction is detected by an observer collecting a
+finite sample. Future work will be required to document the relative
+importance of these two sources of uncertainty in the occurrence of
+interactions.
 
-% Quantifying the uncertainty and the variability of network structure
+Naturally, the relative imprint of the environment on network structure may
+depend on the distinctness of the environments that are sampled. In our large
+data set, localities differed mostly in terms of finer aspects of
+precipitation and temperature. However, when Nyman et al. 2015 compared host
+use among parasitoids attacking sawfly larvae on Salix growing in habitats
+ranging from birch forests to highland tundra, they found a strong imprint of
+habitat on links between parasitoids and hosts. When combined with experiments
+showing other ecological interactions to be sensitive to the environment (e.g.
+\citep{Mckinnon2010; Maunsell2015}), this suggests that we may have focused on
+descriptors of the environment with an only secondary impact on interactions
+(i.e. less relevant covariates). In any comparative analysis, the relative
+importance attributed to a factor will depend on the choice of a relevant
+metric. Thus, we hope that our framework will be widely applied to other
+systems, offering results that can be compared with ours.
 
-\textbf{Investigating the realized niche and the impact of biotic interactions on distribution}\\
-% 	- havent look much at the drivers of co-occurrence, single took them granted from the data
-% 	- many species are not different from the neutral
-% 	- raise the question, once accoutning for the environment, are there true effects of interactions on distribution
-% 	- for sure the analysis raise intersting points
-% Provided that interactions do matter, could derive SDM
-% 	- invert the problem
-% 	- needs an hypothesis for 
-% 	- could be derived from simple models such as
-% 	- or from explicit rules such as
+Evidence that the structure of ecological networks do vary across habitats
+(e.g. \citealt{Tylianakis2007, Plein2012}), over environmental gradients (Lurgi2010) and
+in time \citep{Trolsgaard2015} is accumulating rapidly. It is not clear however to
+what extent the turnover of network structure is driven by a systematic change
+in species composition or of pairwise interactions \citep{Poisot2012, Poisot2015a}.
+The model comparison of the host-parasite interactions revealed that most of
+the turnover is driven by a species-specific response to the environment,
+impact species richness and that co-occurrence was mostly neutral. Further,
+the occurrence of interactions in presence of the host and parasite is highly
+stochastic, but not predictable according to the variables we considered. We
+know that interactions vary with the environment in other systems, for
+instance, herbivory \citep{Shurin2012}, predation \citep{McKinnon2010,
+Legagneux2014} are often found increasing with temperature, resulting in
+spatial variation of trophic cascades \citep{(Gray2016}. What remains unclear
+however is to what extent such variation is driven by a turnover of species
+composition along gradients, or a turnover of the interactions. Here we found
+that interactions do vary a lot, but not predictably along the annual
+temperature and the precipitation gradient. Perhaps we we have not found a
+strong signal  the effect of the environment on the occurrence of interactions
+because we had wrong covariates. It was indeed found previously for a similar
+system that habitat characteristics are the primary drivers of interactions
+\citep{Nyman2015}. New investigations with other systems will be required to
+challenge this result because understanding the relationship between the
+occurrence of interactions at the continental scale is critical to understand
+trophic regulation at large spatial scale and make global change predictions
+of ecosystem functioning accounting for biotic interactions \citep{Harfoot2013}.
 
-\textbf{Guidance for empirical studies}\\
-% Ecological networks are known to be extremely sparse, \emph{i.e.} having far
-% more absences of interactions that they have interactions. These absences of
-% interactions, however, can come from different sources. The fact that unequal
-% sampling at the local scale can affect our understanding of network structure
-% is well documented \parencite{Martinez1999}. However, in a spatial context,
-% some interactions may be undocumented because the species involved have
-% never been observed in co-occurence. Although these are reported as a lack
-% of interactions, in actuality we cannot make inference about them seeing
-% that they have never been observed: it is possible that this interaction
-% may happen should the two species co-occur. A second category of absences
-% of interactions are those that are reported after multiple observations of
-% species co-occurence. However, so as to have a confidence in the fact that the
-% probability of an interaction is low, extensive sampling (that is, several
-% co-occurences) is needed. Generally, our confidence that the interaction
-% is indeed impossible will increase when the number of observations of the
-% species pair. Seeing that this is essentialy a Bernoulli process (what is
-% the probability that the species will interact given their presence), the
-% breadth of the confidence interval is expected to saturate after a fixed
-% number of observations, which can be set as a treshold above which a species
-% paier has been observed "often enough".
+We restricted our framework to the effect of co-occurrence on ecological
+interactions and neglected the inverse of the problem. We have not
+investigated in depth the drivers of co-occurrence, taking it simply granted
+from the data. Co-occurrence was indeed many times significantly different
+from the expectation of independent species distribution. It thus raises the
+question that, once accounting for the species-specific effect of the
+environment on distribution, are there significant effects of interactions on
+co-occurrence? We could rephrase this problem asking if the fundamental niche
+differs from the realized niche, and how it applies to our framework. We have
+considered above simply the co-occurrence probability, $P(X_{iy},X_{jy}|E_y)$,
+which could be expanded as  $P(X_{iy}|X_{jy},E_y) P(X_{jy}| E_y )$. The
+marginal occurrence probability, $P(X_{jy}| E_y )$, could be considered as a
+species distribution model taking into account the interaction between these
+species after some re-arrangement of Eq. 2. This derivation would however
+critically depend a strong a priori of the conditional probability of
+observing a species, given the distribution of the other species. This
+assumption seems reasonable for some situations, let say a parasitoid species
+requiring a host to develop. We however found that in many instances, the
+strength of this association is rather weak if not neutral (with the example
+pair for instance). The lack of an association could simply arises when the
+parasitoid is generalist enough so that it is not constrained to track the
+distribution of its host (Cazelles2015). There is currently only indirect
+support to the hypothesis that interacting species are conditionally
+distributed and it should be the topic of more specific hypothesis testing.
+The impact of ecological interactions on the distribution of co-occurrence has
+been the topic of many publications since Diamond's (1975) seminal paper on
+competition and checkerboard distribution, but only recently pairwise
+approaches received attention \citep{Veech2013}. It is yet unclear if two
+interacting species are more closely associated in space because most
+approaches based on null models consider community-level metrics (e.g.
+\citep{Gotelli2000}), such as the C-score, thereby making it hard to evaluate if
+specific interactions do indeed affect co-occurrence. The expansion of the
+framework we described to account for the difference between the realized and
+the fundamental niche will therefore require further investigation of the
+impact of interactions on co-occurrence.
 
-% Conclusion
-
-\newpage
+Ecological networks are known to be extremely sparse, \emph{i.e.} having far
+more absences of interactions that they have interactions. These absences of
+interactions, however, can come from different sources. The fact that unequal
+sampling at the local scale can affect our understanding of network structure
+is well documented \citep{Martinez1999}. However, in a spatial context,
+some interactions may be undocumented because the species involved have never
+been observed in co-occurence. Although these are reported as a lack of
+interactions, in actuality we cannot make inference about them seeing that
+they have never been observed: it is possible that this interaction may happen
+should the two species co-occur. A second category of absences of interactions
+are those that are reported after multiple observations of species co-
+occurence. However, so as to have a confidence in the fact that the
+probability of an interaction is low, extensive sampling (that is, several co-
+occurences) is needed. Generally, our confidence that the interaction is
+indeed impossible will increase when the number of observations of the species
+pair. Seeing that this is essentialy a Bernoulli process (what is the
+probability that the species will interact given their presence), the breadth
+of the confidence interval is expected to saturate after a fixed number of
+observations, which can be set as a treshold above which a species pair has
+been observed "often enough”.
 
@@
 
-\textbf{Research agenda on probabilistic interactions}\\
-\begin{itemize}
-	\item Need a new type of data
-	\item Need to investigate the reliability of interactions
-	\item From interaction probabilities to a distribution of network properties 
-	\item Deeper investigations of the environmental dependence of interactions
-	\item Trait-based approach to interactions
-	\item The effect of interaction on co-occurrence
-\end{itemize}
+Understanding the drivers of the spatial variation in network structure is a
+key problem to solve in order to anticipate global change impacts on ecosystem
+functioning. Our representation of the spatial variation of community
+structure sets a new approach to the study of the biogeography of ecological
+networks. We see the following the following challenges and opportunities
+ahead in this exciting area of research:
 
-\newpage
+\textbf{1. New generation of network data}. The investigation of the spatial variation
+of network structure will require high quality and highly replicated network
+data. We have investigated the most comprehensive spatial network dataset and
+nonetheless found immense gaps of knowledge in its resolution. Species
+richness accumulates much faster than observations of ecological interactions
+\citep{Poisot2012}. Each pair of speices must be observed several times to have
+reliable estimates of their interaction probability.
+
+\textbf{2. Estimation of the reliability of interactions}. We need quantitative tools
+to estimate the confidence interval around an estimate of interaction
+probability, as well as some estimation of the rate of false absences.
+Bayesian methods are promising to that end because we could use information on
+the target species (e.g. if they are known as specialists or generalists) to
+provide prior estimates of the interaction probability.
+
+\textbf{3. From interaction probabilities to a distribution of network properties}.
+Metrics are available to analyse the structure of probabilistic networks
+\citep{Poisot2015c}. These metrics are useful as first approximation, but they
+assume independence among interactions. It might not be the case in nature
+because of the role of co-occurrence and shared environmental requirements. We
+also need to better understand the distribution of network properties arising
+from probabilistic interactions.
+
+\textbf{4. Investigation of the environmental-dependence of ecological interactions}.
+There is evidence that interactions can vary in space, but this problem has
+not been investigated in a systematic program. The paucity of the data
+currently prevents an extensive analysis of this question.
+
+\textbf{5. Effects of ecological interactions on co-occurrence}. We have omitted in
+this framework the feedback of ecological interactions on co-occurrence. As
+abundance can impact the occurrence of interactions and inversely interactions
+do impact abundance \citep{Canard2014}, we could expect the same for co-occurrence.
+There is theory for simple three species modules \citep{Cazelles20157}, but the
+extension to entire co-occurrence networks will prove critical, especially the
+interest in using co-occurrence to infer ecological interactions \citep{Morales2015,
+Morueta-Holme2016}.
 
@@
 %========================================================%
+\bibliography{library}
+
+\newpage
+%========================================================%
+
+\begin{landscape}
+\begin{table}[]
+\centering 
+\caption{Summary of model comparison for the interaction between the leaf
+galler textit{Phyllocolpa prussica}) and the parasitoid \textit{Chrysocharis
+elongata}}
+\begin{tabular}{llllll}
+\hline
+	\# & Metaweb model 						& Co-occurrence model 			& LL 	& npars & AIC \\ \hline
+	1  & $P(L_{ijy})$ 						& $P(X_{iy},X_{jy}|E_y)$ 		& -65.5 & 6 	& 143 \\ 
+	2  & $P(L_{ijy} | X_{iy}, X_{jy})$ 		& $P(X_{iy},X_{jy}|E_y)$ 		& -65.7 & 6 	& 143.4 \\ 
+	3  & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy}|E_y)$ 		& -65.6 & 10 	& 151.3 \\ \hline
+	4  & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy})$ 			& -84.5 & 6 	& 183 \\ 
+	5  & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})P(X_{jy})$ 			& -80.7 & 7 	& 173.4 \\ 
+	6  & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}|E_y)P(X_{jy}|E_y)$ 	& -68.8 & 15 	& 167.6 \\ 
+\hline
+\end{tabular}
+\end{table}
+\end{landscape}
+
+\newpage
+%========================================================%
+
+\begin{landscape}
+\begin{table}[]
+\centering 
+\caption{Summary of model comparison for the interaction across all pairs of salix, gallers and parasitoids.}
+\begin{tabular}{lllllll}
+\hline
+	Interaction & \# & Metaweb model & Co-occurrence model & LL & npars & AIC \\ \hline
+	Plant-Herbivore & 1 & $P(L_{ijy})$ & $P(X_{iy},X_{jy}|E_y)$ & -6137.8 & 7170 & 26615.6 \\ 
+	 & 2 & $P(L_{ijy}|X_{iy},X_{jy})$ & $P(X_{iy},X_{jy}|E_y)$ & -5947.2 & 7170 & 26234.3 \\ 
+	 & 3 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy}|E_y)$ & -5939.8 & 11950 & 35779.6 \\
+	 & 4 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy})$ & -7871.9 & 8365 & 32473.8 \\ 
+	 & 5 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})(X_{jy})$ & -6639.9 & 7170 & 27619.9 \\ 
+	 & 6 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}|E_y)P(X_{jy}|E_y)$ & -7123.2 & 17925 & 50096.4 \\ \hline
+	Herbivore-Parasitoid & 1 & $P(L_{ijy})$ & $P(X_{iy},X_{jy}|E_y)$ & -21397.6 & 18846 & 81963.1 \\ 
+	 & 2 & $P(L_{ijy} | X_{iy}, X_{jy})$ & $P(X_{iy},X_{jy}|E_y)$ & -21105.2 & 18846 & 81378.5 \\ 
+	 & 3 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy}|E_y)$ & -20881.1 & 31410 & 107042.1 \\ 
+	 & 4 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy})$ & -23728.3 & 21987 & 93152.6 \\ 
+	 & 5 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})P(X_{jy})$ & -23509.4 & 18846 & 86186.8 \\ 
+	 & 6 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}|E_y)P(X_{jy}|E_y)$ & -20990 & 47115 & 139900.1 \\ 
+\hline
+\end{tabular}
+\end{table}
+\end{landscape}
 
@@
 \subsection*{Figure 1}
-\textbf{Non-random sampling of the metaweb}. 
-Network assembly could be viewed as a sampling process of the regional pool of
-potential interactions. Species are sampled first (indicated by colored nodes)
-and among the present species in the local network, only some interactions are
-occurring (indicated by colored links). The challenge we address with the
-quantitive framework proposed is to adequately characterize this sampling
-process. The sampling of the metaweb is illustrated with a local interaction
-network among Salix, gallers and parasitoids. Here, the metaweb was
-constructed by aggregating observed interactions across 374 local networks.
-The color nodes represent the species that were found in the most diverse of
-these 374 local networks.
+
+\textbf{Non-random sampling of the metaweb}.  Network assembly can be viewed
+as a sampling process of the regional pool of potential interactions. Species
+(indicated by colored nodes) are sampled first, and among the species found in
+the local network, only some interactions (indicated by colored links) occur.
+We characterize these sampling processes with the quantitative framework
+proposed in this paper. As a concrete illustration of metaweb sampling, we
+here show a local interaction network among Salix, gallers, and galler
+enemies. The metaweb was constructed by aggregating observed interactions
+across 370 local networks. The colored nodes represent the species that were
+found in the most diverse local network.
 
@@
 \subsection*{Figure 2}
-\textbf{Visual representation of the integrated niche}. 
-We represent visually the integration between two views of the niche. In
-biogeography, the niche is considered the set of environmental conditions
-where the intrinsic growth rate $r$ is positive. The horizontal axis
-represents an environmental gradient impacting the growth of the focal species
-(in red). The location of the different species along this gradient represent
-their optimum, and the vertical dotted lines represent the limits of the
-[Grinnelian] niche of the focal species. In food web ecology, the [Eltonian]
-niche represents the location of a species in the food web, as determined by
-its preys and its predators. The vertical axis represents a niche gradient,
-presumably a trait such as body size. The location of each species along this
-gradient represent their niche position. The focal species will feed on the
-different preys whose niche location falls within a given interval around the
-optimum, represented by the horizontal dotted lines. The integrated niche
-[Grinnelian \& Eltonian] corresponds to the square in the middle where an
-interaction is possible. According to our probabilistic framework, the central
-square represents the area where the joint probability of observing
-interactions and co-occurrence is positive.
+
+\textbf{Visual representation of the integrated niche}.  In biogeography, the
+niche is considered the set of environmental conditions where the intrinsic
+growth rate r is positive \citep{Holt2009}. The horizontal axis represents an
+environmental gradient impacting the growth of the focal species (in red). The
+location of each species along this gradient represents their optimum, and the
+vertical dotted lines represent the limits of the Grinnellian niche of the
+focal species. In food web ecology, the Eltonian niche represents the location
+of a species in the food web, as determined by its niche position (n) and its
+niche optimum (c). The vertical axis represents a niche gradient, presumably a
+trait such as body size. The location of each species along this gradient
+represents their niche position. The focal species will feed on preys having
+niche locations within a given interval around the optimum, represented by the
+horizontal lines. The integrated Grinnellian and Eltonian niche corresponds to
+the square in the middle where an interaction is possible. According to our
+probabilistic framework, the central square represents the area where the
+joint probability of observing interactions and co-occurrence is positive.
 
@@
 \subsection*{Figure 3}
-\textbf{Probabilistic representation of the interaction probability between a leaf galler (\textit{Phyllocolpa plicalapponum}) and a parasitoid (\textit{Pediobius saulius}) across a temperature and a precipitation gradient}.
-The representation is based on predictions from model 3 (see Table 1).
-For the left panel: open circles represent the absence of both species or of an interaction, the closed circles represent co-occurrence and other symbols the occurrence of only one of the two species.
-For the other two panels the open circles represent co-occurrence but an absence of interaction and the closed circles represent the occurrence of an interaction.
+
+\textbf{Probabilistic representation of the interaction probability between a
+leaf galler (\textit{Phyllocolpa prussica}) and a parasitoid
+(\textit{Chrysocharis elongata}) across a temperature and a precipitation
+gradient}.  The representation is based on predictions from model 3 (see Table
+1). In the left panel, open circles represent the absence of both species?,
+whereas closed circles represent co-occurrence and plus signs the occurrence
+of only one of the two species. In the other two panels, open circles
+represent co-occurrence but an absence of interaction and the closed circles
+represent the occurrence of an interaction.
 
@@
 \subsection*{Figure 4}
-\textbf{Probabilistic representation of the interaction probability between a leaf galler (\textit{Phyllocolpa plicalapponum}) and a parasitoid (\textit{Pediobius saulius}) across Europe}.
+
+\textbf{Probabilistic representation of the interaction probability between a
+leaf galler (\textit{Phyllocolpa prussica}) and a parasitoid
+(\textit{Chrysocharis elongata}) across Europe}.  The maps are generated from
+predicted probabilities according to the model illustrated at Fig. 3.
 
@@
 \subsection*{Figure 5}
-\textbf{Representation of the A) metaweb and B) gaps of data in the metaweb}.
-The salix and gallers were regrouped as 'victims' for the sake of the illustration, as the gallers and the parasitoids were regrouped as 'ennemies'.
+
+\textbf{Representation of the salix-galls and galls-parasitoids metawebs}.
+Black cells indicate species pairs for which at least one interaction was
+recorded, white cells indicate absence of recorded interactions and the red
+cells show pairs of species never detected at the same site (and hence species
+pairs for which we have no information on whether they would interact should
+they co-occur).
 
@@
 \subsection*{Figure 6}
-\textbf{Mapping the distribution of species richness, the number of links and connectance across Europe}. The representation is based on predictions from model 3 (see Table 2).
+
+\textbf{Mapping the distribution of species richness, the number of links and
+connectance across Europe}.  The representation is based on predictions from
+model 3 (see Table 2). Species richness is obtained by the summation of
+individual occurrence probabilities and link density is obtained by the
+summation of the interaction probabilities.
 
@@
 \begin{figure}[ht!]
-\centering\includegraphics[width=0.8\textwidth]{figures/mw_sampling}
+\centering\includegraphics[width=0.5\textwidth]{figures/metaweb_sampling}
 \end{figure}
@@
 \begin{figure}[ht!]
-\centering\includegraphics[width=0.8\textwidth]{figures/integrated_niche}
+\centering\includegraphics[width=0.6\textwidth]{figures/integrated_niche}
 \end{figure}

### 2016-04-06 analysis/scripts/data_processing/reformat_salix.r

@@ -7,101 +7,141 @@
 ##################################################################
 
 rm(list=ls())
-
+setwd("/Users/DGravel/Documents/Manuscripts/Inprep/ms_probaweb")
 # Load the data
-load("analysis/data/expand_data.Rdata")
-load("analysis/data/salix_int.Rdata")
 
-# Find the IDs
-IDi = unique(salix_int[,5]) # i stands for hosts
-IDj = unique(salix_int[,6]) # j stands for pars
-IDcomm = IDj[match(IDi,IDj,nomatch=0)]
-IDun = unique(c(IDi,IDj))
-Si = length(IDi) 
-Sj = length(IDj)
+# Original data from mangal
+#load("analysis/data/salix_int.Rdata")
 
-sites = salix_int[,1]
-sites_ID = unique(salix_int[,1])
+# Instead work with the original Roslin dataset
+datakop <- read.csv("analysis/data/kopeleke_data.csv",dec=",")
+HP = datakop[,c(9,10,11,1,19,32)]
+#HP = subset(HP, HP[,6]!="no parasitoid or inquiline")
+SH = datakop[,c(9,10,11,1,29,19)]
+names(HP) = c("site","lat","lon","year","from","to")
+names(SH) = c("site","lat","lon","year","from","to")
+SH[,5] = paste("Salix",SH[,5])
+salix_int = rbind(HP,SH)
+save(salix_int, file = "analysis/data/salix_int_direct.Rdata")
+
+# Get the IDs
+sites = as.character(salix_int[,1])
+sites_ID = as.character(unique(salix_int[,1]))
 coords = salix_int[,2:3]
-nsites = length(sites_ID)
-
-salix_ID = unique(salix_int$to[salix_int$type == "epibiosis"])
-gall_ID = unique(c(salix_int$from[salix_int$type == "epibiosis"],salix_int$to[salix_int$type != "epibiosis"]))
-par_ID = unique(salix_int$from[salix_int$type != "epibiosis"])
+n_sites = length(sites_ID)
+ID_S = unique(SH[,5])
+ID_H = as.character(unique(SH[,6]))
+ID_P = as.character(unique(HP[,6]))
+S_S = length(ID_S)
+S_H = length(ID_H)
+S_P = length(ID_P)
 
 # Pairs of interactions
[…]

### 2016-04-06 analysis/scripts/results/6_map_all.R

@@ -1,0 +1,267 @@
+##################################################################
+# Run the models across Europe to compute the expected species
+# richness and the expected number of links
+# Dominique Gravel
+# October 29th, 2015
+##################################################################
+
+rm(list=ls())
+library(raster)
+library(sp)
+library(rgdal)
+
+setwd("/Users/DGravel/Documents/Manuscripts/Inprep/ms_probaweb")
+
+load("analysis/data/DF_split.Rdata")
+load("analysis/data/expand_data.Rdata")
+load("analysis/data/pairs.Rdata")
+
+IDi = data$pairs.from
+IDj = data$pairs.to
+Type = data$pairs.type
+Si = length(unique(IDi))
+Sj = length(unique(IDj))
+nobs = 374
+np  = length(DF_split)
+
+# Load the stuff to make the raster object
+wrld <- readOGR("analysis/data/map", layer="level1")
+europe <- wrld[1,]
+exteur <- extent(europe)
+xmin(exteur) = 0
+xmax(exteur) = 25
+ymin(exteur) = 40
+ymax(exteur) = 70
+
+# Extract the climatic variables
+clim = crop(getData("worldclim", var="bio", res=10), exteur)
+mapT = getValues(clim$bio1)
+mapPP = getValues(clim$bio12)
+ncell = length(T)
+map_E = data.frame(T = mapT, PP = mapPP, T2 = mapT^2, PP2 = mapPP^2)
+
+############################################################
+# Extract the local networks over Europe
+############################################################
+
+#############
+# Compute the distribution of salix richness
+data_S = subset(data[,c(1,2,5,10,21)], data$pairs.type == "SH")
+ID_S = unique(data_S$pairs.from)
+exp_S = numeric(nrow(map_E))
+for(i in 1:length(ID_S)) {
+
+	# Subset the data
+	sub_data = unique(data_S[data_S$pairs.from == ID_S[i],])
+	Xi = sub_data$Xi
+	T = sub_data$climate.bio1
+	PP = sub_data$climate.bio12
+	T2 = T*T
+	PP2 = PP*PP
+
[…]

### 2016-04-06 analysis/scripts/results/table_all_models.R

@@ -29,14 +29,15 @@ Sj = length(unique(IDj))
 unique_IDi = unique(IDi)
 unique_IDj = unique(IDj)
 np = length(DF_split)
+type = numeric(np)
 
 # Lists to store the models 
-C2_L0 = matrix(nr = np, nc = 3)
-C2_L1 = matrix(nr = np, nc = 3)
-C2_L2 = matrix(nr = np, nc = 3)
-C0_L2 = matrix(nr = np, nc = 3)
-C1_L2 = matrix(nr = np, nc = 3)
-C3_L2 = matrix(nr = np, nc = 3)
+C2_L0 = matrix(nr = np, nc = 2)
+C2_L1 = matrix(nr = np, nc = 2)
+C2_L2 = matrix(nr = np, nc = 2)
+C0_L2 = matrix(nr = np, nc = 2)
+C1_L2 = matrix(nr = np, nc = 2)
+C3_L2 = matrix(nr = np, nc = 2)
 
 # Loop around all pairs of species
 count = 1
@@ -45,8 +46,8 @@ for(x in 1:np) {
 	sub_data = DF_split[[x]]
 
 	IDs = as.matrix(sub_data[1,1:2])
-	test = which(pairs[,1] == as.numeric(IDs[1]) & pairs[,2]==as.numeric(IDs[2]) | pairs[,1]==as.numeric(IDs[2]) & pairs[,2]==as.numeric(IDs[1]))
-	if(length(test)!=0)	type[x] = as.character(pairs[test,3])
+	test = which(pairs[,2] == as.character(IDs[1]) & pairs[,3]==as.character(IDs[2]) | pairs[,2]==as.character(IDs[2]) & pairs[,3]==as.character(IDs[1]))
+	if(length(test)!=0)	type[x] = unique(as.character(pairs[test,4]))
 	
 	models_C2_L0 = fit_models.apply(sub_data,selection = FALSE, funC = C2, funL = L0)
 	models_C2_L1 = fit_models.apply(sub_data,selection = FALSE, funC = C2, funL = L1)
@@ -71,36 +72,36 @@ for(x in 1:np) {
 
 # Sum by type of interaction
 npars_SG = c(
[…]

### 2016-04-08 ms/ms_probaweb.tex
Spencer edits

@@
-% Table 1: example for a pair of species
-% Table 2: model comparison across all species
+% TODO:
+% Add Ben and Spencer's edits
+% Revise the model with fixed interaction pribabilites (havens)
+% Compile the references
+% Distribute for a last round of edits
+% Add scussion on other on other types of interactions
 
@@
 
-\textbf{Title:} Bringing Elton and Grinnell together: a quantitative framework to represent the biogeography of ecological interactions
+\textbf{Title:} Bringing Elton and Grinnell together: a quantitative framework to represent the biogeography of ecological interaction networks
 
 \textbf{Authors:} Dominique Gravel$^{1,2,*}$, Ben Baiser$^{3}$, Jennifer A. Dunne$^{4}$, Jens-Peter Kopelke$^{5}$, Neo
-Martinez$^{6}$, Tommy Nyman$^{7}$, Timoth\'ee Poisot$^{2,8}$,  Spencer Wood$^{9}$, Daniel B. Stouffer$^{10}$, Jason Tylianakis$^{10,11}$ Tomas Roslin$^{12}$,\\
+Martinez$^{6}$, Tommy Nyman$^{7}$, Timoth\'ee Poisot$^{2,8}$,  Spencer A. Wood$^{9}$, Daniel B. Stouffer$^{10}$, Jason Tylianakis$^{10,11}$ Tomas Roslin$^{12}$,\\
 
@@
 
-9:\\
+9: University of Washington, School of Environmental and Forest Sciences, 
+Box 352100, Seattle, WA 98195, USA\\
 
@@
 adopting the view that community structure is best represented as an
-ecological network of interactions. We outline conceptual approach, suggesting
-that the ecological niche may be redefined to encompass the effect of the
-environment on species distribution (the Grinnellian dimension of the niche)
-and on the ecological interactions among them (the Eltonian dimension).
+ecological network of interactions. We outline a conceptual approach,
+suggesting that the ecological niche may be redefined to encompass the effect
+of the environment on species distribution (the Grinnellian dimension of the
+niche) and on the ecological interactions among them (the Eltonian dimension).
 Starting from this novel concept, we develop a quantitative theory to explain
 turnover of interactions in space and time – i.e. a novel approach to
-interaction distribution modelling. We decompose the probability with which
-two species interact with each other in two parts: the probability with which
-the species co-occur at a given location, and the probability that if they do
-so, they will interact. Both of these probabilities could be conditional on
-the environment. We apply this novel framework to a large data set of
-host–parasite interactions across Europe and find that two aspects of the
-environment (temperature and precipitation) leave a strong imprint on species
-co-occurrence, but not on the probability of local interactions. Even where
-species co-occur, interaction proves a stochastic rather than deterministic
-process, adding to variation in realized network structure. We also find that
-a large majority of species pairs are never found together, thus precluding
-any inferences regarding their probability to interact. Our framework provides
-a first conceptual framework to explain the variation of network structure at
-large spatial scales and opens new perspectives at the frontier between
-species distribution modelling and community ecology.
+interaction distribution modelling. We apply this novel framework to a large
+data set of host–parasite interactions across Europe and find that two aspects
+of the environment (temperature and precipitation) leave a strong imprint on
+species co-occurrence, but not on the probability of local interactions. Even
+where species co-occur, interaction proves a stochastic rather than
+deterministic process, adding to variation in realized network structure. We
+also find that a large majority of species pairs are never found together,
+thus precluding any inferences regarding their probability to interact. Our
+framework provides a first conceptual framework to explain the variation of
+network structure at large spatial scales and opens new perspectives at the
+frontier between species distribution modelling and community ecology.
 
@@
 \citep{Krebs2001}. Despite a general consensus on this definition
-(Scheiner2007), it is surprising that research on variation in community
-structure has focused mostly on the turnover of species composition
+(Scheiner2007), research on variation in community
+structure has mostly focused on the spatial and temporal turnover of species composition
 \citep{Anderson2011}, neglecting variation in the way species interact with
@@
 surprising that biogeographers are still struggling to establish whether
-interactions actually impact the distribution of species \citep{Wisz2012,
-Kissling2012}. Recent attempts at accounting for interactions in species
-distribution models \citep{Pollock2014, Pelissier2013} have brought some
-methodological advances. Yet, these techniques are still based on a ’species-
-based’ approach to communities, where interactions are merely treated as fixed
-covariates affecting distribution.
-
-As a more explicit description of interaction structure among species, the
+interactions actually impact the distribution of species at large spatial
+scales\citep{Wisz2012, Kissling2012}, even though there is enough evidence
+from community ecology that interactions are critical for determining species
+dynamics, resource use and responses to the environment af finer scales.
+Recent attempts at accounting for interactions in species distribution models
+\citep{Pollock2014, Pelissier2013} have brought some methodological advances.
+Yet, these techniques are still based on a `species-based' approach to
+communities, where interactions are merely treated as fixed covariates
+affecting distribution.
+
+As a more explicit description of interactions among species, the
 network approach offers a convenient representation of communities. Species
@@
 interactions within locations, and less so with the variation among locations
-\citep{Dunne2005, Bascompte2007, Ings2007, Kefi2012}. However, there is now
+\citep{Dunne2005, Bascompte2007, Ings2007, Kefi2012}. There is however 
 ample evidence that interaction networks vary in space and time
-\citep{Poisot2012, Albouy2014, Poisot2016, Trojelsgaard2015}. Metacommunity
+\citep{Laliberté2010, Poisot2012, Albouy2014, Poisot2016, Trojelsgaard2015}. Metacommunity
 theory provides explanation for the variation in the distribution of the
@@
 species vs. interactions, there is an evident need to bring the two together.
-Here, we plea for an integrated approach, adopting the view that community
+Here, we offer an integrated approach, adopting the view that community
 structure is best represented as an ecological network of interactions. Based
@@
 distribution and on the ecological interactions among them. Starting from this
-redefined concept, we develop a unified theory to explain turnover of
+redefined concept, we develop a quantitative theory to explain turnover of
 interactions in space and time. We first present the conceptual framework, and
@@
 model. At the community level, the approach provides a likelihood-based method
-to compare different hypotheses of network turnover. By applying this novel
-framework to a large data set on host–parasite interactions across Europe, we
+to compare different hypotheses of network turnover. We apply this novel
+framework to a large data set on host–parasite interactions across Europe and
 find that variation of the environment causes turnover of both species and
 interactions. The network structure changes systematically across the
-latitudinal gradient, with a peak of connectance at intermediate latitudes.
+latitudinal gradient, with a peak of connectance at intermediate latitude.
 
@@
 
-The problem of community assembly is often formulated as \textit{how do we
-sample a regional pool of species to constitute a local community?} This
-question could be rewritten to address the problem of network assembly, as
-\textit{how do we sample a regional pool of interactions to constitute a local
-interaction network?} An illustration of this problem for a food web is
-provided in Figure 1. The metaweb represents potential interactions among all
-species that could be found in a given area. In this particular case, there
-are 275 nodes, and 1173 links among plants (52 nodes), herbivores (96 nodes),
-and parasitoids (127 nodes) from Northern Europe. An instance of a local
-community is also illustrated, with 45 nodes and 93 interactions. Only 55.0\%
-of all potential interactions are realized. Our objective here is to provide a
-conceptual framework to explain the sampling of the regional pool of
-interactions, along with a quantitative method to predict it. The problem
-could be formalized sequentially by first understanding why only a fraction of
-the species are co- occurring locally, and then why these species interact or
-not.
+The problem of community assembly is often formulated as \textit{how are
+species sampled from a regional pool to constitute a local community
+\citep{Gotzenberger2012}?} This question could be rewritten to address the
+problem of network assembly, as \textit{how do samples from a regional pool of
+interactions constitute a local interaction network?} An illustration of this
+problem for a food web is provided in Figure 1. The metaweb represents
+potential interactions among all species that could be found in a given area.
+In this particular case, there are 275 nodes, and 1173 links among plants (52
+nodes), herbivores (96 nodes), and parasitoids (127 nodes) from Northern
+Europe. An instance of a local community is also illustrated, with 45 nodes
+and 93 interactions. Only 55.0\% of all potential interactions are realized,
+revealing the stochastic nature of ecological interactions. Our objective here
+is to provide a conceptual framework to explain the sampling of the regional
+pool of interactions, along with a quantitative method to predict it. The
+problem could be formalized sequentially by first understanding why only a
+fraction of the species are co-occurring locally and second why these species
+do or do not interact.
 
@@
 fittest species \citep{Leibold2004}. Stochasticity plays an additional role,
-either through the inherently unpredictable nature of colonization and
-extinction events (Hanski1999), or through strong non-linear feedbacks
-generating alternative transients and equilibriums \citep{Chase2007,
-Vellend2014}. Analyses of community turnover are usually performed with data
-represented in a table with rows corresponding to sites (or measurements) and
-columns to species. Metrics of beta diversity quantify the variance of this
-community data \citep{Legendre2005}. Traditional approaches rely on measures
-of dissimilarity among communities, such as the Jaccard or Bray–Curtis
-indices. A more recent approach decomposes the total variation of the
-community data into species and site contributions to beta diversity
-\citep{Legendre2013}. Even though these methods compare whole lists of species
-among sites or measurements, they remain fundamentally ’species-based’, since
-they report the variation within columns. None of them explicitly considers
-the variation of associations (i.e., of pairs or higher- order motifs –
-\citealt{Stouffer2007}).
-
-The “niche” is by far the dominant concept to explain species distributions
+either colonization and extinction events \citep{Hanski1999} are inherently
+unpredictable, or because of strong non-linear feedbacks in community dynamics generating alternative
+transients and equilibria \citep{Chase2007, Vellend2014}. Analyses of
+community turnover are usually performed with data represented in a table with
+rows corresponding to sites (or measurements) and columns to species. Metrics
+of beta diversity quantify the variance of this community data
+\citep{Legendre2005}. Traditional approaches rely on measures of dissimilarity
+among communities, such as the Jaccard or Bray–Curtis indices. A more recent
+approach decomposes the total variation of the community data into species and
+site contributions to beta diversity \citep{Legendre2013}. Even though these
+methods compare whole lists of species among sites or measurements, they
+remain fundamentally ’species-based’, since they report the variation within
+columns. None of them explicitly considers the variation of associations
+(i.e., of pairs or higher-order motifs – \citealt{Stouffer2007}).
+
+The "niche" is by far the dominant concept to explain species distributions
 and community assembly, from the local to the global scale. Following
@@
 conditions allowing a population to establish and persist (see also
-\citealt{Holt2009}. Community turnover arises as a result of successive
+\citealt{Holt2009}). Community turnover arises as a result of successive
 replacement of species along an environmental gradient, in agreement with the
@@
 a vast array of statistical tools have been developed to implement it (e.g.
-Biomod \citealt{Thuiller2003}, MaxEnt \citealt{Phillips2006}). It is however
+BIOMOD \citealt{Thuiller2003}, MaxEnt \citealt{Phillips2006}). It is however
 much harder to account for ecological interactions with this approach
-(Peterson2011). As such, these interactions are often viewed as externalities
+\citep{Peterson2011}. As such, these interactions are often viewed as externalities
 constraining or expanding the range of environmental conditions required for a
-species to maintain a viable population \citep{Pulliam2000, Soberon2007}.
+species to maintain a viable population \citep{Pulliam2000, Soberon2007, Boulangeat2012}.
 
@@
 Interestingly, the ecological network literature also has its own ’niche
-model’ to position a species in a community (Williams2000). The niche of a
+model’ to position a species in a community \citep{Williams2000}. The niche of a
 species in this context represents the multidimensional space of all of its
@@
 and a range over 3 to 5 different niche axes \citep{Williams2000, Eklof2013}.
-The niche model of food web structure has successfully explained the
+The niche model of food web structure and its variants have successfully explained the
 complexity of a variety of networks, from food webs to plant–pollinator
@@
 the concept of the ecological niche, ecologists have not moved far past the
-“n-dimensional hypervolume” defined by Hutchinson. Despite its intuitive
+``n-dimensional hypervolume'' defined by Hutchinson. Despite its intuitive
 interpretation and easy translation into species distribution models
-\citep{Boulangeat2012, Blonder2014}, the concept has been constantly
+\citep{Boulangeat2012, Blonder2014}, the concept has been frequently
 criticized \citep{Hardin1960, Peters1991, Silvertown2004}, and several
@@
 Part of the problem surrounding the niche concept has been clarified with the
-distinction between Eltonian and Grinnellian definitions (Chase2003). The
+distinction between Eltonian and Grinnellian definitions \citep{Chase2003}. The
 Grinnellian dimension of the niche is the set of environmental conditions
@@
 considerable confusion in the literature \citep{McInerny2012a}.
-\citealt{Chase2003} attempted to reconcile them in their definition of the
-niche: “[The niche is] the joint description of the environmental conditions
-that allow a species to satisfy its minimum requirements so that the birth
-rate of a local population is equal to or greater than its death rate along
-with the set of per capita effects of that species on these environmental
-conditions”. Their representation merges zero-net growth isoclines delimiting
-the Grinnellian niche (when do populations persist) with impact vectors
-delimiting the Eltonian niche (what is the per-capita impact). While this
-representation has been very influential in local-scale community ecology (the
-resource-ratio theory of coexistence, \citealt{Tilman1982}, it remains
-impractical at larger spatial scales because of the difficulties to measure
-it. The absence of any mathematical representation of the niche that could
-easily be fitted to ecological data may explain why biogeographers are still
-struggling to develop species distribution models that also consider
-ecological interactions.
+\citealt{Chase2003} attempted to reconcile with the following definition:
+``[The niche is] the joint description of the environmental conditions that
+allow a species to satisfy its minimum requirements so that the birth rate of
+a local population is equal to or greater than its death rate along with the
+set of per capita effects of that species on these environmental conditions''.
+Their representation merges zero-net growth isoclines delimiting the
+Grinnellian niche (when does the population persists) with impact vectors delimiting
+the Eltonian niche (what is the per-capita impact). While this representation
+has been very influential in local-scale community ecology (the resource-ratio
+theory of coexistence, \citealt{Tilman1982}), it remains impractical at larger
+spatial scales because of the difficulties to measure it. The absence of any
+mathematical representation of the niche that could easily be fitted to
+ecological data may explain why biogeographers are still struggling to develop
+species distribution models that also consider ecological interactions.
 
 We propose to integrate the two perspectives of the niche with a visual
-representation of both components. The underlying rationale is that, in
+representation of both components (Fig. 2). The underlying rationale is that, in
 addition to the environmental constraints on demographic performance, any
@@
 demographic performance of an organism. Alternatively, the resource axes are
-traits of the resources allowing interactions with the consumer. The niche
+traits of the resources that allow interactions with the consumer. The niche
 should therefore be viewed as the set of abiotic environmental factors (the
 Grinnellian component) along with the set of traits (the Eltonian component)
-allowing a population to establish and to persist at a location. Accordingly,
+that allow a population to establish and to persist at a location. Accordingly,
 each species can be characterized by an optimal position in both the
@@
 The limits of the niche axes could be independent of each other (as in the
-example of Fig. 2), but they could also interact. For instance, the optimal
-prey size for predatory fishes could decrease with increasing temperature
+example of Fig. 2), or alternatively interact. For instance, the optimal
+prey size for predatory fishes could decline with increasing temperature
 \citep{Lelong2015}, which would make diet boundaries functions of the
@@
 %========================================================%
-\section*{A probabilistic representation of ecological interactions networks in space}
+\section*{A probabilistic representation of interaction networks in space}
 
@@
 interactions and distributions. We seek to represent the probability that an
-interaction between species $i$ and $j$ occurs at location $y$. We define $L_{ijy}$ as a
-stochastic variable, and are looking at the probability that this event
-occurs, $P(L_{ijy})$. The occurrence of an interaction is dependent on the co-
-occurrence of species $i$ and $j$. This argument might seem trivial at first, but
-the explicit consideration of this condition in the probabilistic
-representation of ecological interactions will prove fundamental to understand
-their variation. We define $X_{iy}$ as a stochastic variable representing the
-occurrence of species $i$ at location $y$, and similarly $X_{ijy}$ the co-occurrence
-of species $i$ and $j$. The quantity we seek to understand is the probability of a
-joint event, conditional on the set of environmental conditions $E_y$:
+interaction between species $i$ and $j$ occurs at location $y$. We define
+$L_{ijy}$ as a stochastic variable, and are looking at the probability that
+this event occurs, $P(L_{ijy})$. The occurrence of an interaction is dependent
+on the co-occurrence of species $i$ and $j$. This argument might seem trivial
+at first, but the explicit consideration of this condition in the
+probabilistic representation of ecological interactions will prove fundamental
+to understand their variation. We define $X_{iy}$ as a stochastic variable
+representing the occurrence of species $i$ at location $y$. The quantity we seek to
+understand is the probability of a joint event, conditional on the set of
+environmental conditions $E_y$:
 
@@
 \begin{equation}
-	\text{P}(X_{i,y},X_{j,y},L_{ij,y},)
+	\text{P}(X_{iy},X_{jy},L_{ijy}|E_y)
 \end{equation}
@@
 
-Or simply said, the probability of observing both species $i$ and $j$, and an
-interaction between $i$ and $j$. This probability could be decomposed in two parts
-using the product rule of probabilities:
+Or simply said, the probability of observing both species $i$ and $j$ plus an
+interaction between $i$ and $j$ given the conditions $E_y$. This probability
+could be decomposed into two parts using the product rule of probabilities:
 
@@
 \begin{equation}
-	P(X_{iy},X_{jy},L_{ijy})=P(X_{iy},X_{jy}|E_y)P(L_{ijy}|\mathbf{T},X_{iy},X_{jy},E_y)
+	P(X_{iy},X_{jy},L_{ijy}|E_y)=P(X_{iy},X_{jy}|E_y)P(L_{ijy}|\mathbf{T},X_{iy},X_{jy},E_y)
 \end{equation}
@@
 
-The left term is the probability of observing the two species co-occurring at
-location $y$. It corresponds to the Grinnellian dimension of the niche. The
-right term is a conditional probability, representing the probability that an
-interaction occurs between species $i$ and $j$, given their set of traits $T$ and
-that they are co-occurring. Above, we referred to this entity as the metaweb,
-corresponding to the Eltonian dimension of the niche . Below, we will see how
-this formalism can be directly fitted to empirical data. But before turning to
-an application, we will discuss the interpretation of different variants of
-these two terms.
+The first term on the right-hand side of the equation is the probability of
+observing the two species co-occurring at location $y$. It corresponds to the
+Grinnellian dimension of the niche. The second term represents the probability
+that an interaction occurs between species $i$ and $j$, given their set of
+traits $T$ and that they are co-occurring. Above, we refer to this entity
+as the "metaweb" and it corresponds to the Eltonian dimension of the niche. Below,
+we will see how this formalism can be directly fitted to empirical data. But
+before turning to an application, we will discuss the interpretation of
+different variants of these two terms.
 
@@
 (see the explicit formulations in Table 1). The simplest model relates the
-probability of co-occurrence directly to the environment, $P(X_{ijy} |E_y)$. In
-this situation there are no underlying assumptions about the ecological
-processes responsible for co-occurrence. It could arise because of an impact
-of ecological interactions on distributions \citep{Pollock2014} or, alternatively,
-because of environmental requirements shared between i and j. In the former
-case, species are not independent of each other and the conditional occurrence
-must be accounted for explicitly, $P(X_{ijy} |E_y)=P(X_{iy} |E_y,X_{jy})P(X_{jy} |E_y)$.
-In the latter case, species are independent and only the marginal occurrence
-must be accounted for, $P(X_{ijy} |E_y)=P(X_{iy} |E_y)P(X_{jy} |E_y)$.
+probability of co-occurrence directly to the environment, $P(X_{iy},X_{jy}|E_y)$.
+In this situation there are no underlying assumptions about the ecological
+processes responsible for co-occurrence. It could arise because interactions
+do constraint distribution \citep{Pollock2014, Cazelles2016} or,
+alternatively, because of environmental requirements shared between $i$ and
+$j$. In the former case, species are not independent of each other and the
+conditional occurrence must be accounted for explicitly, $P(X_{iy},X_{jy}
+|E_y)=P(X_{iy}|E_y,X_{jy})P(X_{jy}|E_y)$. In the latter case, species are
+independent and only the marginal occurrence must be accounted for, $P(
+|E_y)=P(X_{iy} |E_y)P(X_{jy} |E_y)$.
 
@@
 could also affect co-occurrence. Co-occurrence of multiple species embedded in
-ecological networks is however a topic of its own, influenced by the network
-topology and species richness \citep{Cazelles2015}. Not only direct interactions do
-influence co-occurrence, but indirect interactions as well (e.g. plant species
-sharing an herbivore could repulse each other in space. The impact of direct
+ecological networks is a topic of its own, however, and is influenced by both network
+topology and species richness \citep{Cazelles2016}. Not only direct interactions do
+influence co-occurrence, but indirect interactions do as well (e.g. plant species
+sharing an herbivore could repulse each other in space). The impact of direct
 interactions and first-order indirect interactions on co-occurrence tends to
-vanish with increasing species richness in the community. Further, co-
-occurrence is also influenced by the covariance of interacting species to an
-environmental gradient \citep{Cazelles2016}. Because of the complexity of relating
+vanish with increasing species richness in the community. Further, co-occurrence
+is also influenced by the covariance of interacting species to an
+environmental gradient \citep{Cazelles2015}. Because of the complexity of relating
 co-occurrence to the structure of interaction networks, we will here focus on
 the variation of interactions and not on their distribution, and leave this
-specific issue for the Discussion and future research.
+specific issue for the Perspectives and future research.
 
@@
 thus far considered ecological interactions to be deterministic, not
-probabilistic (e.g. \citealt{Havens1992, Woods2015}). Species are assumed to interact
-whenever they are found together in a location, independently of their
-abundance and the environment. In other words, $P(L_{ijy}|X_{ijy}=1)$ equals 1
-andit equals 0 if $P(L_{ijy}|X_{ijy}=0)$. This approach might be a reasonable
+probabilistic (e.g. \citealt{Havens1992, Wood2015}). Species are assumed to interact
+whenever they are found together in a location, independent of their
+local abundance and the local environment. In other words, $P(L_{ijy}|X_{ijy}=1) = 1$
+and $P(L_{ijy}|X_{ijy}=0) = 0$. This approach might be a reasonable
 approximation if the scale of sampling and inference is so large that the
@@
 pairwise ecological interactions, experimental studies have revealed them to
-frequently be sensitive to the environment. For instance, \citep{Mckinnon2010} shown
+frequently be sensitive to the environment. For instance, \citep{Mckinnon2010} showed
 that predation risks of shorebirds vary at the continental scale, decreasing
@@
 control with temperature (e.g. \citealt{Shurin2012, Gray2016}). Effects of the
-environment on interactions propagate up the community and influence network
-structure \citep{Woodward2010; Petchey2010}.
+environment on interactions also propagate up the community and influence network
+structure \citep{Tylianakis2007, Woodward2010; Petchey2010; Lelong2015}.
 
@@
 We now turn to an illustration of the framework with the analysis of an
-empirical dataset of host–parasite networks sampled throughout south–north
-gradient in continental Europe. The focal system consists of local food webs
-of willows (genus Salix), their galling insects, and the natural enemies of
+empirical dataset of host–parasite networks sampled throughout the south–north
+environmental gradient in continental Europe. The focal system consists of local food webs
+of willows (genus Salix), their galling insects, and the parasitoids of
 these gallers. Targeting this system, we ask: i) how much does network
@@
 
-Communities of willows, gallers, and galler enemies are species-rich and
+Communities of willows, gallers, and parasitoids are species-rich and
 widely distributed, with pronounced variation in community composition across
@@
 gall-inducing sawflies (Hymenoptera: Tenthredinidae: Nematinae: Euurina
-\citep{Kopelke1999}. Gall formation is induced by sawfly females during
+\citep{Kopelke1999}). Gall formation is induced by sawfly females during
 oviposition, and includes marked manipulation of host-plant chemistry by the
-galler \citep{Nyman2000}. The enemy community of the gallers includes nearly
+galler \citep{Nyman2000}. The parasitoid community includes nearly
 100 species belonging to 17 insect families of four orders
-\citep{Kopelke2000}. These enemies encompass two main types: inquiline larvae
+\citep{Kopelke2000}. These encompass two main types: inquiline larvae
 (Coleoptera, Lepidoptera, Diptera, and Hymenoptera) feed primarily on gall
@@
 trophic levels, phylogeny-based comparative studies have demonstrated that
-galls represent “extended phenotypes” of the gallers, meaning that gall form,
+galls represent ``extended phenotypes'' of the gallers, meaning that gall form,
 location, and chemistry is determined mainly by the galling insects and not by
@@
 associations between parasitoids and hosts \citep{Nyman2007}. Thus, the set of
-parasitoids attacking each host is presumptively constrained by the form,
+parasitoids attacking each host is presumably constrained by the form,
 size, and thickness of its gall.
 
-Local realizations of the willow–galler–enemy network were reconstructed from
-community samples collected between 1982 and 2010. During this period, willow
-galls were collected at 370 sites across Central and Northern Europe. Sampling
-was conducted in the summer months of June and/or July, i.e., during the later
-stages of larval development. Galler species were identified on the basis of
-willow host species and gall morphology, as these are distinct for each sawfly
-species. At each site, galls were randomly collected from numerous willow
-individuals in an area of about 0.1–0.3 km2. Most sites were visited only
-once, with a total of 641 site visits across the 370 sites. GPS coordinates
-were recorded for each location; for our present analyses, the annual mean
-temperature and precipitation were obtained from WorldClim using the R package
-raster \citep{Hijmans2015}. While other covariates could have been considered,
-we assumed mean temperature and annual precipitation to be representative of
-the most important axes of the European climate, and more easily interpretable
-than reduced variables obtained by e.g. PCA.
-
-The methods used for rearing natural enemies from the galls have been
-previously described by \citep{Kopelke1999, Kopelke2003}. In brief, galls were
-opened to score the presence of galler or parasitoid/inquiline larvae. Enemy
+Local realizations of the willow–galler–parasitoid network were reconstructed
+from community samples collected between 1982 and 2010. During this period,
+willow galls were collected at 370 sites across Central and Northern Europe.
+Sampling was conducted in the summer months of June and/or July, i.e., during
+the later stages of larval development. Galler species were identified on the
+basis of willow host species and gall morphology, as these are distinct for
+each sawfly species. At each site, galls were randomly collected from numerous
+willow individuals in an area of about 0.1–0.3 $km^2$. Some sites were visited
+more than once, with a total of 641 site visits across the 370 sites. GPS
+coordinates were recorded for each location; for our analyses, the present day
+annual mean temperature and precipitation were obtained from WorldClim using
+the R package raster \citep{Hijmans2015}. While other covariates could have
+also been considered, these variables are likely representative of the most
+important axes of the European climate, and more easily interpretable than
+reduced variables obtained by e.g. principal component analysis.
+
+The methods used for rearing parasitoids from the galls have been
+previously described by , Kopelke2003}. In brief, galls were
+opened to score the presence of galler or parasitoid/inquiline larvae. Parasitoid
 larvae were classified to preliminary morphospecies, and the identity of each
@@
 hibernation. The galls were reared by storing single galls in small glass
-tubes \citep{Kopelke1985a}. Hibernation of galls containing enemies took place
+tubes \citep{Kopelke1985a}. Hibernation of galls containing parasitoids took place
 either within the glass tubes or between blotting paper in flowerpots filled
@@
 the matching of larval morphospecies with adult individuals emerging from the
-rearings allowed the identification of the natural enemies to the species
+rearings allowed the identification of the parasitoids to the species
 level. Nonetheless, in some cases, individuals could only be identified to one
@@
 parasitoids had already emerged from the gall. As a result, the largest taxon
-in the data set, “Chalcidoidea indeterminate,” represents a superfamily of
+in the data set, ``Chalcidoidea indeterminate'', represents a superfamily of
 very small parasitoids that are hard to distinguish.
@@
 rearing. These galls represented 96 galler species, and yielded 42,133
-individually-identified parasitoids and inquilines. Of these, 25,170 (60\%)
-could be identified to the species level. Overall, 127 parasitoid and
-inquiline taxa were distinguished in the material. Data on host associations
-within subsets of this material have been previously reported by Kopelke1999
-and by Nyman2007, whereas the current study represents the first analysis of
+individually-identified parasitoids. Of these, 25,170 (60\%) could be
+identified to the species level. Overall, 127 parasitoid taxa were
+distinguished in the material. Data on host associations within subsets of
+this material have been previously reported by \citep{Kopelke1999} and
+\citep{Nyman2007}. The current study represents the first analysis of
 the full data set from a spatial perspective.
@@
 of illustration, we considered second-order generalized linear models –
-whereas more sophisticated fitting algorithms (e.g. GAM or Random Forest)
+whereas more flexible fitting algorithms (e.g. GAM or Random Forest)
 could equally well be used, as long as the algorithm can estimate the
@@
 environmental co-variates $E_y$. Thus, there is one row per pair of species per
-site. We considered that an absence of a record of an interaction between co-
-occurring species at a site means a true absence (see below for a discussion
+site. We considered that an absence of a record of an interaction between co-occurring
+species at a site means a true absence (see below for a discussion
 on this issue).
@@
 directly models the co-occurrence probability conditional on the local
-environment, $P(X_{ijy} |E_y)$. Hence, this model makes no assumptions about the
-mechanisms driving co-occurrence for any given environment, and only uses the
-information directly available in the data. It thereby indirectly accounts for
-the effect of interactions on co-occurrence, if there is any. The second model
-considers independent co-occurrence of species. In this case, we independently
-fitted $P(X_{iy} |E_y)$ and $P(X_{jy} |E_y)$, then we took their product to derive the
-probability of co-occurrence. This model should be viewed as a null hypothesis
-with respect to the first model, since a comparison between the respective
-models will reveal if there is significant spatial association of the two
-species beyond a joint response to the shared environment \citep{Cazelles2015}.
-Finally, the third model assumes that the probability of co-occurrence is
-independent of the environment and thus constant throughout the landscape. In
-other words, $P(X_{ijy})$ is obtained by simply counting the number of observed
-co-occurrences, divided by the total number of observations. Thus, the
-comparison between the first and third model allows testing the hypothesis
-that co-occurrence is conditional on the environment. Whenever the environment
-was included as a covariate in the glm, we considered a second-order
-polynomial response for both temperature and precipitation. There are
+environment, $P(X_{iy},X_{jy}|E_y)$ (models are listed at Table 1 and 2).
+Hence, this model makes no assumptions about the mechanisms driving co-
+occurrence for any given environment, and instead uses the information directly
+available in the data. It thereby indirectly accounts for the effect of
+interactions on co-occurrence, if there is any. The second model considers
+independent occurrence of species. In this case, we independently fit
+$P(X_{iy} |E_y)$ and $P(X_{jy} |E_y)$, then we take their product to derive
+the probability of co-occurrence. This model should be viewed as a null
+hypothesis with respect to the first model, since a comparison between the
+respective models will reveal if there is significant spatial association of
+the two species beyond a joint response to the shared environment
+\citep{Cazelles2015}. Finally, the third model assumes that the probability of
+co-occurrence is independent of the environment and thus constant throughout
+the landscape. In other words, $P(X_{iy},X_{jy})$ is obtained by simply counting the
+number of observed co-occurrences divided by the total number of observations.
+Thus, the comparison between the first and third model allows us to test the
+hypothesis that co-occurrence is conditional on the environment. Whenever the
+environment was included as a covariate in the GLM, we considered a second-
+order polynomial response for both temperature and precipitation. There are
 consequently 5 parameters for the first model when fitting a given pair of
@@
 probability. The first model conditions the interaction probability on the
-local environmental variables, $P(L_{ijy} |X_{iy},X_{jy},E_y)$. Consequently,
-the model was fitted to a subset of the data where the two species co-occur.
+local environmental variables, $P(L_{ijy}|X_{iy},X_{jy},E_y)$. Consequently,
+the model was fit to a subset of the data where the two species co-occur.
 The second model fits the interaction probability independently of the local
-environmental variables, $P(L_{ijy} |X_{iy},X_{jy})$. It corresponds to the
+environmental variables, $P(L_{ijy}|X_{iy},X_{jy})$. It corresponds to the
 number of times the two species were observed to interact when co-occurring,
@@
 extreme case performed only to test the hypothesis that if two species are
-found to interact at least once, then they should interact whenever they co-
-occur, $P(L_{ijy} |X_{iy},X_{jy})=1$. While not necessarily realistic, this
+found to interact at least once, then they should interact whenever they co-occur,
+$P(L_{ijy}|X_{iy},X_{jy})=1$. While not necessarily realistic, this
 model tests an assumption commonly invoked in the representation of local
@@
 
-The different models were fitted to each pair of species and the fitted
-probabilities were recorded. The joint probability $P(L_{ijy},X_{iy},X_{jy})$
+The different models were fitted to each pair of species and the 
+predicted probabilities were recorded. The joint probability $P(L_{ijy},X_{iy},X_{jy})$
 was then computed from Eq. 2, and the likelihood of each observation was
@@
 $mathcal{L}(\theta_{ijy}|D_{ijy})=1-P(L_{ijy},X_{iy},X_{jy})$ if no
-interaction was observed. The log- likelihood was summed over the entire
+interaction was observed. The log-likelihood was summed over the entire
 dataset to compare the different models by AIC. Not surprisingly, there was a
@@
 analysis. The log-likelihood reported across the entire dataset was summed
-over all pairs of species observed to co- occur at least once. Interactions
-among the first (Salix) and second (gallers) trophic layers , and the second
-and third (galler enemies) were considered separately. Finally, we used the
-full model (in which both co-occurrence and the interaction are conditional on
-the environment) to interpolate species distributions and interaction
-probabilities across the entire Europe. We reconstructed the expected network
-for each location in a 1km X 1km grid, and thereafter computed the
-probabilistic connectance following Poisot2015b.
-
-All of the data are openly available in the database mangal \citep{Poisot2015b} and
+over all pairs of species observed to co-occur at least once. Interactions
+between the first (Salix) and second (gallers) trophic layers and those
+between the second and third (parasitoids) were considered separately.
+Finally, we used the full model (in which both co-occurrence and the
+interaction are conditional on the environment) to interpolate species
+distributions and interaction probabilities across the entire European
+continent. We reconstructed the expected network for each location in a 1km X
+1km grid and computed the probabilistic connectance following
+\citep{Poisot2015b}.
+
+All of the data are openly available in the database mangal \citep{Poisot2015c} and
 all R scripts for querying and pre-processing the data, along with the
@@
 
-Despite the extensive sampling, many pairs of species were found co-occurring
+Despite the extensive sampling, many pairs of species were observed to co-occur
 only a few times. This made it hard to evaluate interaction probabilities with
@@
 ($N_{ij}=38$): \textit{Phyllocolpa prussica} and \textit{Chrysocharis
-elongata}, two fairly abundant species, were observed $N_i=49$ and $N_j=121$
-times, respectively, across the 370 sites. These two species were found to
+elongata}. These two fairly abundant species, were observed $N_i=49$ and $N_j=121$
+times, respectively, across the 370 sites, and they were found to
 interact with a marginal probability $P(L_{ij})=0.55$, which means they
 interacted at 21 different locations. Here, a comparison of model fit (Table
-1) reveals that the interaction probability conditional on the co-occurrence
-does not better explains their distribution (Model 1 vs Model 2). When the two
-species co-occur, the occurrence of the interaction is insensitive to the
+1) reveals that the interaction probability conditional on co-occurrence
+does not better explain their distribution (Model 1 vs Model 2). Moreover, when the two
+species co-occur, the occurrence of the interaction was insensitive to the
 environment (Model 2 vs Model 3). Alternatively, climatic variables
-significantly impact co-occurrence (Model 3 vs Model 4). The neutral model
-performs worse than the non-random co- occurrence model (Model 3 vs Model 6).
-The full model reveals that the greatest interaction probability occurs at
+significantly impacted co-occurrence (Model 3 vs Model 4). The neutral model
+performed worse than the non-random co-occurrence model (Model 3 vs Model 6).
+The full model revealed that the greatest interaction probability occurred at
 intermediate temperature and precipitation, simply because this is where the
-two species most frequently co-occur (Fig. 3). The probabilities of co-
-occurrence and interaction can be represented in space, where we find that the
-highest interaction probability occurs in central Europe (Fig. 4).
-
-In order to better understand the large-scale drivers of network turnover, we
-evaluated each model for all pairs of species. The results are highly
-consistent among trophic layers (Salix–gallers and gallers–enemies; Table 2).
-Across all pairs of species, the conditinal representation of interactions
-does better than the marginal one (Model 1 vs Model 2): interactions do not
-occur systematically whenever the two species are found co-occurring. Hence,
-in addition to species turnover, the stochastic nature of interactions
-contributes to network variability. In total, we recorded 1173 pairs of
+two species most frequently co-occur (Fig. 3). The probabilities of co-occurrence
+and interaction can be represented in space, where we found that the
+highest interaction probability occurred in central Europe (Fig. 4).
+
+We evaluated each model for all pairs of species in order to better understand
+the large-scale drivers of network turnover. The results were highly consistent
+among trophic layers (Salix–gallers and gallers–parasitoids; Table 2). Across
+all pairs of species, the conditional representation of interactions performed 
+better than the marginal one (Model 1 vs Model 2); that is, interactions did
+not occur systematically whenever the two species were found co-occurring.
+Hence, in addition to species turnover, the stochastic nature of interactions
+contributes to network variability. In total, we recorded 1,173 pairs of
 interactions, only 290 of which occurred more than 5 times. Out of these 290
-interactions, 143 are systematically detected whenever the two species do co-
-occur. Of when species co-occurred, the two environmental variables considered
-proved rather poor predictors of their interactions (Model 2 vs Model 3). Not
-surprisingly, for both types of interactions (Salix–gallers and
-gallers–enemies), the likelihood increases when the environment is considered.
-However, the extra number of parameters exceeds the gain in likelihood, and
-inflates AIC. Therefore, the best model excludes the effect of the
-environment. According to the log-likelihood only, co-occurrence is non-
-neutral for both Salix–galler interactions and galler–enemy interaction. Thus,
-according to AIC, the best model is the one of non-random co-occurrence (Model
-3 vs Model 6), for both types of interactions.
-
-To investigate the reliability of the estimated metaweb across the entire
-dataset, we may turn to summary statistics of species co-occurrence. As
-mentioned above, across the 17,184 potential pairs of species, only 1,173 pairs
-interacted in at least a single location, for a connectance of 0.068. However,
-only 4,459 pairs of species are found co-occurring at least one time across all
-locations. There are consequently 12,725 gaps of information in the metaweb
-(74.1\% - see Fig. 5). As we cannot know whether the non-co-occurring species
-would indeed interact when found together, a more appropriate estimate of
-connectance would be $C=1173/4459=0.263$. This result reveals that the
-evaluation of the sampling quality of ecological networks is a problem on its
-own and well worth further attention.
+interactions, 143 were systematically detected whenever the two species co-
+occurred. In the instances when species co-occurred, the two environmental
+variables considered proved relatively poor predictors of their interactions
+(Model 2 vs Model 3). Not surprisingly, for both types of interactions
+(Salix–galler and galler–parasitoid), the likelihood increased when the
+environment was considered. However, the extra number of parameters exceeded the
+gain in likelihood and inflates AIC. Therefore, the most parsimonious model
+excluded the effect of the environment. On the basis of log-likelihoods only,
+co-occurrence was non-neutral for both Salix–galler interactions and
+galler–parasitoid interactions. Thus, according to AIC, the best model was the
+one of non-random co-occurrence (Model 3 vs Model 6) for both types of
+interactions.
+
+The approach we present not only has implications for understanding the
+biogeography of pairwise interactions and interaction networks, but also the
+quality of the evaluation of metawebs. We investigated the reliability of the
+estimated metaweb across the entire dataset wtih summary statistics of species
+co-occurrence. As mentioned above, across the 17,184 potential pairs of
+species, only 1,173 pairs interacted in at least a single location, yielding a
+connectance of 0.068. However, only 4,459 pairs of species were found co-
+occurring at least once across all locations. There are consequently
+12,725 gaps of information in the metaweb (74.1\% - see Fig. 5). As we cannot
+know whether the non-co-occurring species would indeed interact when found
+together, a more appropriate estimate of connectance would be
+$C=1173/4459=0.263$. This result reveals that the evaluation of the sampling
+quality of ecological networks is a problem on its own and well worth further
+attention.
 
@@
 reconstruct the expected species richness, along with the most likely network
-for each location. By this approach, we could factually map the expected
+for each location. By this approach, we could map the expected
 distribution of network properties across Europe (Fig. 6). For simplicity, we
@@
 also a good proxy for many other network properties \citep{Poisot2014}. Overall, we
-find a peak in Salix, gallers and enemies diversity in northern Europe. The
+find a peak in Salix, gallers and parasitoid diversity in northern Europe. The
 expected number of interactions roughly follows the distribution of species
@@
 %========================================================%
-\section*{Discussion}
-
-We proposed that the representation of community structure and its variation
+\section*{Interpretation}
+
+We have proposed that the representation of community structure and its variation
 in space and time is best represented with the formalism of ecological
-networks, because both the distribution of species and their interspecific
-interactions are accounted for. We consequently revised the niche concept in
+networks because both the distribution of species and their interspecific
+interactions can then be accounted for. We consequently revised the niche concept in
 order to integrate both the abiotic and the biotic components of the niche
-that are susceptible to vary of time and space. The integrated niche was
+that are susceptible to vary over time and space. This integrated niche was
 represented visually with an ordination of species into an environmental space
@@
 maintained in a location, thereby integrating the Eltonian and the Grinnellian
-components of the niche. The concept is translated mathematically by the
-investigation of the probability of the joint occurrences of species and of
-the interaction, which should be interpreted as an interaction distribution
+components of the niche. We then translated the concept mathematically by
+investigating the probability of the joint occurrences of species and 
+their interaction, which should be interpreted as an interaction distribution
 model. We used this approach to characterize the turnover of the structure of
@@
 found that the primary driver of variation is the turnover in species
-composition. This is to our knowledge the first continental wide analysis of
+composition. To our knowledge, this is the first continental-wide analysis of
 the drivers of network structure from empirical data (see \citealt{Albouy2014,
@@
 Applying the framework to our large data set on host–parasite interactions
-across revealed key features in the interaction between Salix taxa, their
+across Europe revealed key features in the interaction between Salix taxa, their
 herbivores, and the natural enemies of these herbivores. Consistent with a
@@
 \citep{Cronk2015}, overall species richness of the networks increased towards
-the north. Distribution of salix species richness  largely matched the one of
-gallers and their ennemies. These observations here seen within Europe are
-also matched by the ones found at a global scale for salix \citep{Argus1997,
+the north. The distribution of Salix species richness largely matched those of
+gallers and parasitoids. These observations within Europe are
+also matched by the ones found at a global scale for Salix \citep{Argus1997,
 Cronk2015, Wu2015} and sawflies \citep{Kouki1994, Kouki1999}. Species richness
-was originally presumed to show a similar “reversed latitudinal gradient” for
-a common group of parasitic wasps, the Ichneumonidae,, but this observation
+was originally presumed to show a similar "reversed latitudinal gradient" for
+a common group of parasitic wasps, the Ichneumonidae, but this observation
 has been challenged by findings of rather high ichneumonid diversity in the
@@
 richness at different trophic levels is yet to be established (but see e.g.
-\citealt{Roininen2005, Nyman2010, Leppanen2014}, but as a net
+\citealt{Roininen2005, Nyman2010, Leppanen2014}), but as a net
 outcome of different latitudinal trends across trophic levels, the
@@
 between the first and second link layers. The correlation between the expected
-salix and gallers richness was 0.73, while it was 0.58 between gallers and
-their enemies. The ratio of herbivore to Salix species is essentially constant
+Salix and gallers richness was 0.73, while it was 0.58 between gallers and
+their parasitoids. The ratio of herbivore to Salix species is essentially constant
 across Europe, whereas each herbivore species is potentially attacked by a
@@
 
-In terms of species interacting with each other, our analysis suggest that the
+In terms of species interacting with each other, our analysis suggests that the
 environment leaves a detectable imprint on species co-occurrence, but only a
-slighter mark on the occurrence of realized links among species in a specific
+slight mark on the occurrence of realized links among species in a specific
 place: the probability of finding a given combination of species at a higher
@@
 prussica} and \textit{Chrysocharis elongata} (Figs 2-3), but also to all species pairs
-more generally. For the example species pair, the full model reveals that the
+more generally. For the example species pair, the full model revealed that the
 interaction probability is highest at intermediate temperature and
@@
 although this is a basic assumption in most documented metawebs to date (e.g.
-\citealt{Havens1992, Woods2015}). Rather, interaction is a stochastic process the
-probability of which is influenced by the probability with which species co-
-occur. What we cannot reliably know is how this stochasticity splits into two
+\citealt{Havens1992, Wood2015}). Rather, an interaction is a stochastic process whose
+probability is also influenced by the probability with which species co-occur.
+What we cannot reliably know is how this stochasticity splits into two
 sampling processes – i.e., the extent to which a species at the higher trophic
@@
 
-Naturally, the relative imprint of the environment on network structure may
-depend on the distinctness of the environments that are sampled. In our large
-data set, localities differed mostly in terms of finer aspects of
-precipitation and temperature. However, when Nyman et al. 2015 compared host
-use among parasitoids attacking sawfly larvae on Salix growing in habitats
-ranging from birch forests to highland tundra, they found a strong imprint of
-habitat on links between parasitoids and hosts. When combined with experiments
-showing other ecological interactions to be sensitive to the environment (e.g.
-\citep{Mckinnon2010; Maunsell2015}), this suggests that we may have focused on
-descriptors of the environment with an only secondary impact on interactions
-(i.e. less relevant covariates). In any comparative analysis, the relative
-importance attributed to a factor will depend on the choice of a relevant
-metric. Thus, we hope that our framework will be widely applied to other
-systems, offering results that can be compared with ours.
-
-Evidence that the structure of ecological networks do vary across habitats
-(e.g. \citealt{Tylianakis2007, Plein2012}), over environmental gradients (Lurgi2010) and
-in time \citep{Trolsgaard2015} is accumulating rapidly. It is not clear however to
-what extent the turnover of network structure is driven by a systematic change
-in species composition or of pairwise interactions \citep{Poisot2012, Poisot2015a}.
-The model comparison of the host-parasite interactions revealed that most of
-the turnover is driven by a species-specific response to the environment,
-impact species richness and that co-occurrence was mostly neutral. Further,
-the occurrence of interactions in presence of the host and parasite is highly
-stochastic, but not predictable according to the variables we considered. We
-know that interactions vary with the environment in other systems, for
-instance, herbivory \citep{Shurin2012}, predation \citep{McKinnon2010,
-Legagneux2014} are often found increasing with temperature, resulting in
-spatial variation of trophic cascades \citep{(Gray2016}. What remains unclear
-however is to what extent such variation is driven by a turnover of species
-composition along gradients, or a turnover of the interactions. Here we found
-that interactions do vary a lot, but not predictably along the annual
-temperature and the precipitation gradient. Perhaps we we have not found a
-strong signal  the effect of the environment on the occurrence of interactions
+%========================================================%
+\section*{Perspectives}
+
+Evidence that the structure of ecological networks does vary across habitats
+(e.g. \citealt{Tylianakis2007, Plein2012}), over environmental gradients
+\citealt{Lurgi2010} and in time \citep{Trolsgaard2015} is accumulating
+rapidly. It is not clear however to what extent the turnover of network
+structure is driven by a systematic change in species composition or of
+pairwise interactions \citep{Poisot2012, Poisot2015a}. The model comparison of
+the host-parasite interactions revealed that most of the turnover is driven by
+a species-specific response to the environment, impacting species richness,
+and that co-occurrence was mostly neutral. Further, the occurrence of
+interactions in presence of the host and parasite is highly stochastic, but
+not predictable according to the variables we considered. We know that
+interactions vary with the environment in other systems, for instance,
+herbivory \citep{Shurin2012}, predation \citep{McKinnon2010, Legagneux2014}
+are often found increasing with temperature, resulting in spatial variation of
+trophic cascades \citep{(Gray2016}. What remains unclear, however, is the
+extent to which such variation is driven by a turnover of species composition
+along gradients, or a turnover of the interactions. Here we found that
+interactions vary substantially, but not predictably along the annual
+temperature and the precipitation gradient. Perhaps we have not found a strong
+signal of the effect of the environment on the occurrence of interactions
 because we had wrong covariates. It was indeed found previously for a similar
@@
 \citep{Nyman2015}. New investigations with other systems will be required to
-challenge this result because understanding the relationship between the
-occurrence of interactions at the continental scale is critical to understand
-trophic regulation at large spatial scale and make global change predictions
-of ecosystem functioning accounting for biotic interactions \citep{Harfoot2013}.
+challenge this result. Documenting the relationship between the occurrence of
+interactions at the continental scale and the environment is critical to
+understand how trophic regulation at large spatial scales do influence
+community dynamics and ecosystem functioning  \citep{Harfoot2013}.
 
 We restricted our framework to the effect of co-occurrence on ecological
-interactions and neglected the inverse of the problem. We have not
-investigated in depth the drivers of co-occurrence, taking it simply granted
-from the data. Co-occurrence was indeed many times significantly different
-from the expectation of independent species distribution. It thus raises the
-question that, once accounting for the species-specific effect of the
-environment on distribution, are there significant effects of interactions on
-co-occurrence? We could rephrase this problem asking if the fundamental niche
-differs from the realized niche, and how it applies to our framework. We have
+interactions and neglected the inverse of the problem. We did not investigated
+in depth the drivers of co-occurrence and simply took it for granted from the
+data. Co-occurrence was indeed many times significantly different from the
+expectation of independent species distribution. It thus raises the question
+that, once accounting for the species-specific effect of the environment on
+distribution, are there significant effects of interactions on co-occurrence?
+We could rephrase this problem asking if the fundamental niche differs from
+the realized niche, and how it applies to our framework. For example, we have
 considered above simply the co-occurrence probability, $P(X_{iy},X_{jy}|E_y)$,
 which could be expanded as  $P(X_{iy}|X_{jy},E_y) P(X_{jy}| E_y )$. The
-marginal occurrence probability, $P(X_{jy}| E_y )$, could be considered as a
+marginal occurrence probability, $P(X_{jy}|E_y )$, could be considered as a
 species distribution model taking into account the interaction between these
 species after some re-arrangement of Eq. 2. This derivation would however
-critically depend a strong a priori of the conditional probability of
-observing a species, given the distribution of the other species. This
-assumption seems reasonable for some situations, let say a parasitoid species
-requiring a host to develop. We however found that in many instances, the
-strength of this association is rather weak if not neutral (with the example
-pair for instance). The lack of an association could simply arises when the
-parasitoid is generalist enough so that it is not constrained to track the
-distribution of its host (Cazelles2015). There is currently only indirect
-support to the hypothesis that interacting species are conditionally
-distributed and it should be the topic of more specific hypothesis testing.
-The impact of ecological interactions on the distribution of co-occurrence has
-been the topic of many publications since Diamond's (1975) seminal paper on
-competition and checkerboard distribution, but only recently pairwise
-approaches received attention \citep{Veech2013}. It is yet unclear if two
-interacting species are more closely associated in space because most
+critically depend on a strong a priori expectation of the conditional
+probability of observing a species given the distribution of the other
+species. This assumption seems reasonable for some situations, such as a
+parasitoid species that requires a host to develop. On the other hand, we
+found the strength of this association is often rather weak if not neutral
+(with the example pair for instance analysed at Table 1). The lack of an
+association could simply arises when the parasitoid is generalist enough so
+that it is not constrained to track the distribution of its host
+\citep{Cazelles2015}. At present, there is only indirect support to the
+hypothesis that interacting species are conditionally distributed and it
+should be the topic of more specific hypothesis testing. The impact of
+ecological interactions on the distribution of co-occurrence has been the
+topic of many publications since \citeal{Diamond1975} seminal study on
+competition and the checkerboard distribution, but only recently pairwise
+approaches received attention \citep{Veech2013}. It therefore remains unclear
+if two interacting species are more closely associated in space because most
 approaches based on null models consider community-level metrics (e.g.
-\citep{Gotelli2000}), such as the C-score, thereby making it hard to evaluate if
-specific interactions do indeed affect co-occurrence. The expansion of the
-framework we described to account for the difference between the realized and
-the fundamental niche will therefore require further investigation of the
-impact of interactions on co-occurrence.
+\citealt{Gotelli2000}), such as the C-score, thereby making it hard to
+evaluate if specific interactions do indeed affect co-occurrence. The
+expansion of the framework we described to account for the difference between
+the realized and the fundamental niche will therefore require further
+investigation of the impact of interactions on co-occurrence.
 
@@
 sampling at the local scale can affect our understanding of network structure
-is well documented \citep{Martinez1999}. However, in a spatial context,
-some interactions may be undocumented because the species involved have never
-been observed in co-occurence. Although these are reported as a lack of
-interactions, in actuality we cannot make inference about them seeing that
-they have never been observed: it is possible that this interaction may happen
-should the two species co-occur. A second category of absences of interactions
-are those that are reported after multiple observations of species co-
-occurence. However, so as to have a confidence in the fact that the
-probability of an interaction is low, extensive sampling (that is, several co-
-occurences) is needed. Generally, our confidence that the interaction is
-indeed impossible will increase when the number of observations of the species
-pair. Seeing that this is essentialy a Bernoulli process (what is the
-probability that the species will interact given their presence), the breadth
-of the confidence interval is expected to saturate after a fixed number of
-observations, which can be set as a treshold above which a species pair has
-been observed "often enough”.
+is well documented \citep{Martinez1999}. However, in a spatial context, some
+interactions may be undocumented because the species involved have never been
+observed to co-occur. Although these are reported as a lack of interactions,
+in actuality we can not make inference about them since they have never been
+observed: it remains possible that this interaction may happen should the two
+species co-occur. A second category of absences of interactions are those that
+are reported after multiple observations of species co-occurence. However, so
+as to have a confidence in the fact that the probability of an interaction is
+low, extensive sampling (that is, several records of co-occurence) is needed. Generally,
+our confidence that the interaction is indeed impossible will increase with
+the number of observations of the species pair. Seeing that this is essentially
+a Bernoulli process (the probability that the species will interact given
+their presence), the breadth of the confidence interval is expected to
+saturate after a fixed number of observations, which can be set as a threshold
+above which a species pair has finally been observed "often enough".
 
@@
 Understanding the drivers of the spatial variation in network structure is a
-key problem to solve in order to anticipate global change impacts on ecosystem
-functioning. Our representation of the spatial variation of community
-structure sets a new approach to the study of the biogeography of ecological
-networks. We see the following the following challenges and opportunities
-ahead in this exciting area of research:
-
-\textbf{1. New generation of network data}. The investigation of the spatial variation
-of network structure will require high quality and highly replicated network
-data. We have investigated the most comprehensive spatial network dataset and
-nonetheless found immense gaps of knowledge in its resolution. Species
-richness accumulates much faster than observations of ecological interactions
-\citep{Poisot2012}. Each pair of speices must be observed several times to have
-reliable estimates of their interaction probability.
+key problem to solve in order to anticipate the impacts of global changes on
+biodiversity. Our representation of the spatial variation of community
+structure presents a new approach for the study of the biogeography of ecological
+networks. We see the following key challenges and opportunities ahead in this
+exciting area of research:
+
+\textbf{1. New generation of network data}. The investigation of the spatial
+variation of network structure will require high quality and highly replicated
+network data. We have investigated one the most comprehensive spatial network
+datasets we are aware of and nonetheless found immense gaps of knowledge in its
+resolution. Species richness accumulates much faster than observations of
+ecological interactions \citep{Poisot2012}. Each pair of species must be
+observed several times to have reliable estimates of their interaction
+probability.
 
@@
 \citep{Poisot2015c}. These metrics are useful as first approximation, but they
-assume independence among interactions. It might not be the case in nature
+assume independence among interactions. This might not be the case in nature
 because of the role of co-occurrence and shared environmental requirements. We
@@
 There is evidence that interactions can vary in space, but this problem has
-not been investigated in a systematic program. The paucity of the data
-currently prevents an extensive analysis of this question.
-
-\textbf{5. Effects of ecological interactions on co-occurrence}. We have omitted in
-this framework the feedback of ecological interactions on co-occurrence. As
-abundance can impact the occurrence of interactions and inversely interactions
-do impact abundance \citep{Canard2014}, we could expect the same for co-occurrence.
-There is theory for simple three species modules \citep{Cazelles20157}, but the
-extension to entire co-occurrence networks will prove critical, especially the
-interest in using co-occurrence to infer ecological interactions \citep{Morales2015,
+not been investigated in a systematic fashion. The paucity of the data
+currently available precludes an extensive analysis of this question.
+
+\textbf{5. Effects of ecological interactions on co-occurrence}. We have
+intentionally omitted the feedback of ecological interactions on co-occurrence
+in this framework. As abundance can impact the occurrence of interactions, and
+inversely since interactions do impact abundance \citep{Canard2014}, we could
+reasonably expect the same for co-occurrence. Theory does exist for simple
+three-species modules \citep{Cazelles2015}, but the extension to entire co-
+occurrence networks will prove critical, especially given the interest in
+using co-occurrence to infer ecological interactions \citep{Morales2015,
 Morueta-Holme2016}.
@@
 \caption{Summary of model comparison for the interaction between the leaf
-galler textit{Phyllocolpa prussica}) and the parasitoid \textit{Chrysocharis
+galler \textit{Phyllocolpa prussica}) and the parasitoid \textit{Chrysocharis
 elongata}}
@@
 	Interaction & \# & Metaweb model & Co-occurrence model & LL & npars & AIC \\ \hline
-	Plant-Herbivore & 1 & $P(L_{ijy})$ & $P(X_{iy},X_{jy}|E_y)$ & -6137.8 & 7170 & 26615.6 \\ 
+	Plant-Galler & 1 & $P(L_{ijy})$ & $P(X_{iy},X_{jy}|E_y)$ & -6137.8 & 7170 & 26615.6 \\ 
 	 & 2 & $P(L_{ijy}|X_{iy},X_{jy})$ & $P(X_{iy},X_{jy}|E_y)$ & -5947.2 & 7170 & 26234.3 \\ 
@@
 	 & 6 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}|E_y)P(X_{jy}|E_y)$ & -7123.2 & 17925 & 50096.4 \\ \hline
-	Herbivore-Parasitoid & 1 & $P(L_{ijy})$ & $P(X_{iy},X_{jy}|E_y)$ & -21397.6 & 18846 & 81963.1 \\ 
+	Galler-Parasitoid & 1 & $P(L_{ijy})$ & $P(X_{iy},X_{jy}|E_y)$ & -21397.6 & 18846 & 81963.1 \\ 
 	 & 2 & $P(L_{ijy} | X_{iy}, X_{jy})$ & $P(X_{iy},X_{jy}|E_y)$ & -21105.2 & 18846 & 81378.5 \\ 
@@
 
-\textbf{Non-random sampling of the metaweb}.  Network assembly can be viewed
-as a sampling process of the regional pool of potential interactions. Species
+\textbf{Non-random sampling of the metaweb}. Network assembly can be viewed as
+a sampling process of the regional pool of potential interactions. Species
 (indicated by colored nodes) are sampled first, and among the species found in
@@
 proposed in this paper. As a concrete illustration of metaweb sampling, we
-here show a local interaction network among Salix, gallers, and galler
-enemies. The metaweb was constructed by aggregating observed interactions
-across 370 local networks. The colored nodes represent the species that were
-found in the most diverse local network.
+here show a local interaction network among Salix, gallers, andparasitoids.
+The metaweb was constructed by aggregating observed interactionsb across 370
+local networks.
 
@@
 niche is considered the set of environmental conditions where the intrinsic
-growth rate r is positive \citep{Holt2009}. The horizontal axis represents an
+growth rate $r$ is positive \citep{Holt2009}. The horizontal axis represents an
 environmental gradient impacting the growth of the focal species (in red). The
@@
 focal species. In food web ecology, the Eltonian niche represents the location
-of a species in the food web, as determined by its niche position (n) and its
-niche optimum (c). The vertical axis represents a niche gradient, presumably a
+of a species in the food web, as determined by its niche position ($n$) and its
+niche optimum ($c$). The vertical axis represents a niche gradient, presumably a
 trait such as body size. The location of each species along this gradient
@@
 leaf galler (\textit{Phyllocolpa prussica}) and a parasitoid
-(\textit{Chrysocharis elongata}) across a temperature and a precipitation
-gradient}.  The representation is based on predictions from model 3 (see Table
-1). In the left panel, open circles represent the absence of both species?,
-whereas closed circles represent co-occurrence and plus signs the occurrence
-of only one of the two species. In the other two panels, open circles
-represent co-occurrence but an absence of interaction and the closed circles
-represent the occurrence of an interaction.
+(\textit{Chrysocharis elongata}) across an annueal average temperature and an
+annual precipitation gradient}. The representation is based on predictions
+from model 3 (see Table 1). In the left panel, open circles represent the
+absence of both species, whereas closed circles represent co-occurrence and
+plus signs the occurrence of only one of the two species. In the other two
+panels, open circles represent co-occurrence but an absence of interaction and
+the closed circles represent the occurrence of an interaction.
 
@@
 
-\textbf{Representation of the salix-galls and galls-parasitoids metawebs}.
+\textbf{Representation of the Salix-galler and galler-parasitoid metawebs}.
 Black cells indicate species pairs for which at least one interaction was

### 2016-04-08 ms/ms_probaweb.tex
Ben edits

@@
 
-\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Ben Baiser$^{3}$, Jennifer A. Dunne$^{4}$, Jens-Peter Kopelke$^{5}$, Neo
+\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Benjamin Baiser$^{3}$, Jennifer A. Dunne$^{4}$, Jens-Peter Kopelke$^{5}$, Neo
 Martinez$^{6}$, Tommy Nyman$^{7}$, Timoth\'ee Poisot$^{2,8}$,  Spencer A. Wood$^{9}$, Daniel B. Stouffer$^{10}$, Jason Tylianakis$^{10,11}$ Tomas Roslin$^{12}$,\\
@@
 
-3: \\
+3: University of Florida, Department of Wildlife Ecology and Conservation, 110 Newins-Ziegler Hall, PO Box 110430, Gainesville, Fl. 32611-0430 \\
 
@@
 either colonization and extinction events \citep{Hanski1999} are inherently
-unpredictable, or because of strong non-linear feedbacks in community dynamics generating alternative
-transients and equilibria \citep{Chase2007, Vellend2014}. Analyses of
-community turnover are usually performed with data represented in a table with
-rows corresponding to sites (or measurements) and columns to species. Metrics
-of beta diversity quantify the variance of this community data
-\citep{Legendre2005}. Traditional approaches rely on measures of dissimilarity
-among communities, such as the Jaccard or Bray–Curtis indices. A more recent
-approach decomposes the total variation of the community data into species and
-site contributions to beta diversity \citep{Legendre2013}. Even though these
-methods compare whole lists of species among sites or measurements, they
-remain fundamentally ’species-based’, since they report the variation within
-columns. None of them explicitly considers the variation of associations
-(i.e., of pairs or higher-order motifs – \citealt{Stouffer2007}).
+unpredictable, or because of strong non-linear feedbacks in community dynamics
+generating alternative transients and equilibria \citep{Chase2007,
+Vellend2014}. Analyses of community turnover are usually performed with data
+represented in a table with rows corresponding to sites (or measurements) and
+columns to species. Metrics of beta diversity quantify the variance of this
+community data \citep{Legendre2005}. Traditional approaches rely on measures
+of dissimilarity among communities, such as the Jaccard or Bray–Curtis
+indices. A more recent approach decomposes the total variation of the
+community data into species and site contributions to beta diversity
+\citep{Legendre2013}, and further partition into dissimilarity due to changes
+in species richness and those due to actual species turnover \citep{Baselga2010;
+Carvalho et al. 2012}. Even though these methods compare whole lists of
+species among sites or measurements, they remain fundamentally ’species-
+based’, since they report the variation within columns. None of them
+explicitly considers the variation of associations (i.e., of pairs or higher-
+order motifs – \citealt{Stouffer2007}).
 
@@
 criticized \citep{Hardin1960, Peters1991, Silvertown2004}, and several
-attempts have been made to expand and reinforce it \citep{Pulliam2000,
+attempts have been made to expand and improve it \citep{Pulliam2000,
 Chase2003, Soberon2007, Holt2009, McInerny2012b}.
@@
 theory of coexistence, \citealt{Tilman1982}), it remains impractical at larger
-spatial scales because of the difficulties to measure it. The absence of any
+spatial scales because of the difficulties in measuring it. The absence of any
 mathematical representation of the niche that could easily be fitted to
@@
 distributions and ecological interactions of species in the same formalism.
+
 The limits of the niche axes could be independent of each other (as in the
-example of Fig. 2), or alternatively interact. For instance, the optimal
+example in Fig. 2), or  they could interact. For instance, the optimal
 prey size for predatory fishes could decline with increasing temperature
 \citep{Lelong2015}, which would make diet boundaries functions of the
-environment. The other way around, we could also consider that the growth rate
+environment. Alternatively, we could also consider that the growth rate
 of the predator changes with the size of its prey items, thereby altering the
@@
 thus far considered ecological interactions to be deterministic, not
-probabilistic (e.g. \citealt{Havens1992, Wood2015}). Species are assumed to interact
-whenever they are found together in a location, independent of their
-local abundance and the local environment. In other words, $P(L_{ijy}|X_{ijy}=1) = 1$
-and $P(L_{ijy}|X_{ijy}=0) = 0$. This approach might be a reasonable
-approximation if the scale of sampling and inference is so large that the
-probability of observing at least one interaction converges to unity and the
-only variation in the networks considered arises from species distributions.
+probabilistic (e.g. \citealt{Havens1992, Wood2015}). Species are assumed to
+interact whenever they are found together in a location, independent of their
+local abundance and the local environment. In other words,
+$P(L_{ijy}|X_{ijy}=1) = 1$ and $P(L_{ijy}|X_{ijy}=0) = 0$. This approach might
+be a reasonable approximation if the scale of sampling and inference is so
+large that the probability of observing at least one interaction converges to
+unity In this cenario, network variation solely arises from species
+distributions.
 
@@
 
-We now turn to an illustration of the framework with the analysis of an
+We now turn to an illustration of our framework with the analysis of an
 empirical dataset of host–parasite networks sampled throughout the south–north
-environmental gradient in continental Europe. The focal system consists of local food webs
-of willows (genus Salix), their galling insects, and the parasitoids of
-these gallers. Targeting this system, we ask: i) how much does network
-structure vary across the gradient, and ii) what is the primary driver of
-network turnover across the gradient?
+environmental gradient in continental Europe. The focal system consists of
+local food webs of willows (genus Salix), their galling insects, and the
+parasitoids of these gallers. Targeting this system, we ask: i) how much does
+network structure vary across the gradient, and ii) what is the primary driver
+of network turnover across the gradient?
 
@@
 niche is considered the set of environmental conditions where the intrinsic
-growth rate $r$ is positive \citep{Holt2009}. The horizontal axis represents an
-environmental gradient impacting the growth of the focal species (in red). The
-location of each species along this gradient represents their optimum, and the
-vertical dotted lines represent the limits of the Grinnellian niche of the
+growth rate $r$ is positive \citep{Holt2009}. The horizontal axis represents
+an environmental gradient impacting the growth of the focal species (in red).
+The location of each species along this gradient represents their optimum, and
+the vertical dotted lines represent the limits of the Grinnellian niche of the
 focal species. In food web ecology, the Eltonian niche represents the location
-of a species in the food web, as determined by its niche position ($n$) and its
-niche optimum ($c$). The vertical axis represents a niche gradient, presumably a
-trait such as body size. The location of each species along this gradient
-represents their niche position. The focal species will feed on preys having
-niche locations within a given interval around the optimum, represented by the
-horizontal lines. The integrated Grinnellian and Eltonian niche corresponds to
-the square in the middle where an interaction is possible. According to our
+of a species in the food web, as determined by its niche position ($n$) and
+its niche optimum ($c$). The vertical axis represents a niche gradient,
+presumably a trait such as body size. The location of each species along this
+gradient represents their niche position. The focal species will feed on prey
+species  niche locations within a given interval around the optimum,
+represented by the horizontal lines. The integrated Grinnellian and Eltonian
+niche corresponds to the square in the middle where an interaction is possible
+owing to a match of traits and spatial distribution. According to our
 probabilistic framework, the central square represents the area where the

### 2016-04-08 ms/ms_probaweb.tex
Compile in various formats

@@
 ample evidence that interaction networks vary in space and time
-\citep{Laliberté2010, Poisot2012, Albouy2014, Poisot2016, Trojelsgaard2015}. Metacommunity
+\citep{Laliberte2010, Poisot2012, Albouy2014, Poisot2016, Trojelsgaard2015}. Metacommunity
 theory provides explanation for the variation in the distribution of the
@@
 The methods used for rearing parasitoids from the galls have been
-previously described by , Kopelke2003}. In brief, galls were
+previously described by \citealt{Kopelke2003}. In brief, galls were
 opened to score the presence of galler or parasitoid/inquiline larvae. Parasitoid
@@
 ecological interactions on the distribution of co-occurrence has been the
-topic of many publications since \citeal{Diamond1975} seminal study on
+topic of many publications since \citealt{Diamond1975} seminal study on
 competition and the checkerboard distribution, but only recently pairwise

### 2016-04-11 ms/ms_probaweb.tex

@@
 
-10: University of Canterbury at Christchurch, School of Biological Sciences\\
+10: Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch, New Zealand\\
 
@@
 turnover of interactions in space and time – i.e. a novel approach to
-interaction distribution modelling. We apply this novel framework to a large
+interaction distribution modelling. We apply this framework to a large
 data set of host–parasite interactions across Europe and find that two aspects
@@
 interactions within locations, and less so with the variation among locations
-\citep{Dunne2005, Bascompte2007, Ings2007, Kefi2012}. There is however 
+\citep{Dunne2005, Bascompte2007, Ings2007, Kefi2012}. There is, however, 
 ample evidence that interaction networks vary in space and time
 \citep{Laliberte2010, Poisot2012, Albouy2014, Poisot2016, Trojelsgaard2015}. Metacommunity
-theory provides explanation for the variation in the distribution of the
+theory provides an explanation for the variation in the distribution of the
 different nodes \citep{Gravel2011c, Pillai2011}, but there is no explanation
-to the joint variation of node and link occurrences. We urgently need a
+to the joint variation of node and link occurrences. Consequently, we urgently need a
 conceptual framework to formalize these observations.
@@
 Given the historically different approaches to modelling the distributions of
-species vs. interactions, there is an evident need to bring the two together.
-Here, we offer an integrated approach, adopting the view that community
+species vs. interactions, there is a clear need to bring the two together.
+Here, we offer an integrated approach to do so, adopting the view that community
 structure is best represented as an ecological network of interactions. Based
 on this idea, we propose a new description of the basic concept of the
-ecological niche, now integrating the effect of the environment on species
+ecological niche that integrates the effect of the environment on species
 distribution and on the ecological interactions among them. Starting from this
@@
 interactions. The network structure changes systematically across the
-latitudinal gradient, with a peak of connectance at intermediate latitude.
+latitudinal gradient, with a peak of connectance at intermediate latitudes.
 
@@
 interactions constitute a local interaction network?} An illustration of this
-problem for a food web is provided in Figure 1. The metaweb represents
+problem for a food web is provided in Figure 1. The regional pool of interactions, or metaweb, represents
 potential interactions among all species that could be found in a given area.
-In this particular case, there are 275 nodes, and 1173 links among plants (52
+In this particular case, there are 275 nodes, and 1173 links among the plants (52
 nodes), herbivores (96 nodes), and parasitoids (127 nodes) from Northern
 Europe. An instance of a local community is also illustrated, with 45 nodes
-and 93 interactions. Only 55.0\% of all potential interactions are realized,
+and 93 interactions. Only 55.0\% of all potential interactions are realized locally,
 revealing the stochastic nature of ecological interactions. Our objective here
@@
 fittest species \citep{Leibold2004}. Stochasticity plays an additional role,
-either colonization and extinction events \citep{Hanski1999} are inherently
-unpredictable, or because of strong non-linear feedbacks in community dynamics
+either because colonization and extinction events \citep{Hanski1999} are inherently
+unpredictable or because of strong non-linear feedbacks in community dynamics
 generating alternative transients and equilibria \citep{Chase2007,
@@
 community data into species and site contributions to beta diversity
-\citep{Legendre2013}, and further partition into dissimilarity due to changes
+\citep{Legendre2013}, and further partitions into dissimilarity due to changes
 in species richness and those due to actual species turnover \citep{Baselga2010;
 Carvalho et al. 2012}. Even though these methods compare whole lists of
-species among sites or measurements, they remain fundamentally ’species-
-based’, since they report the variation within columns. None of them
-explicitly considers the variation of associations (i.e., of pairs or higher-
-order motifs – \citealt{Stouffer2007}).
-
-The "niche" is by far the dominant concept to explain species distributions
+species among sites or measurements, they remain fundamentally `species-based',
+since they report the variation within columns. None of them
+explicitly considers the variation of associations (i.e., of pairs or higher-order
+motifs – \citealt{Stouffer2007}).
+
+The ``niche'' is by far the dominant concept to explain species distributions
 and community assembly, from the local to the global scale. Following
@@
 BIOMOD \citealt{Thuiller2003}, MaxEnt \citealt{Phillips2006}). It is however
-much harder to account for ecological interactions with this approach
+much harder to account for ecological interactions within this approach
 \citep{Peterson2011}. As such, these interactions are often viewed as externalities
@@
 higher-order interactions \citep{Poisot2015a}. Variation in community
-composition was found independent of the variation of ecological interactions,
-suggesting that these two components of network variability respond to
+composition was found to be independent of the variation of ecological interactions,
+suggesting that these two components of network variability may well respond to
 different drivers \citep{Poisot2012}.
@@
 
-A more integrative description of the niche is key to understand spatial and
+A more integrative description of the niche is key to understanding spatial and
 temporal turnover in community structure. Despite several attempts to update
-the concept of the ecological niche, ecologists have not moved far past the
+the concept of the ecological niche, ecologists have not moved far beyond the
 ``n-dimensional hypervolume'' defined by Hutchinson. Despite its intuitive
@@
 
-These perspectives are rather orthogonal to each other, which has resulted in
+These perspectives are rather orthogonal to each other, and this has resulted in
 considerable confusion in the literature \citep{McInerny2012a}.
@@
 spatial scales because of the difficulties in measuring it. The absence of any
-mathematical representation of the niche that could easily be fitted to
+mathematical representation of the niche that could be easily fit to
 ecological data may explain why biogeographers are still struggling to develop
@@
 then the hypervolume where interactions can occur and sustain a population.
-This approach radically changes the representation of the niche, putting the
-distributions and ecological interactions of species in the same formalism.
-
-The limits of the niche axes could be independent of each other (as in the
-example in Fig. 2), or  they could interact. For instance, the optimal
+
+This approach radically changes the representation of the niche, putting species
+distributions and ecological interactions into the same formalism.
+Moreover, it allows the limits of the niche axes to be independent of each other (as in the
+example in Fig. 2), or to interact. For instance, the optimal
 prey size for predatory fishes could decline with increasing temperature
@@
 We now formalize the integrated niche with a probabilistic approach to
-interactions and distributions. We seek to represent the probability that an
+interactions and distributions. In particular, we seek to represent the probability that an
 interaction between species $i$ and $j$ occurs at location $y$. We define
-$L_{ijy}$ as a stochastic variable, and are looking at the probability that
-this event occurs, $P(L_{ijy})$. The occurrence of an interaction is dependent
+$L_{ijy}$ as a stochastic variable, and focus on the probability that
+this event occurs, $P(L_{ijy})$. We note that the occurrence of an interaction is dependent
 on the co-occurrence of species $i$ and $j$. This argument might seem trivial
 at first, but the explicit consideration of this condition in the
-probabilistic representation of ecological interactions will prove fundamental
+probabilistic representation of ecological interactions will prove instrumental
 to understand their variation. We define $X_{iy}$ as a stochastic variable
@@
 that an interaction occurs between species $i$ and $j$, given their set of
-traits $T$ and that they are co-occurring. Above, we refer to this entity
-as the "metaweb" and it corresponds to the Eltonian dimension of the niche. Below,
-we will see how this formalism can be directly fitted to empirical data. But
+traits $T$ and that they are co-occurring. Above, we referred to this entity
+as the ``metaweb'' and it corresponds to the Eltonian dimension of the niche. Below,
+we will see how this formalism can be directly fit to empirical data. But
 before turning to an application, we will discuss the interpretation of
@@
 probability of co-occurrence directly to the environment, $P(X_{iy},X_{jy}|E_y)$.
-In this situation there are no underlying assumptions about the ecological
+In this situation, there are no underlying assumptions about the ecological
 processes responsible for co-occurrence. It could arise because interactions
-do constraint distribution \citep{Pollock2014, Cazelles2016} or,
+do in fact constrain distributions \citep{Pollock2014, Cazelles2016} or,
 alternatively, because of environmental requirements shared between $i$ and
@@
 |E_y)=P(X_{iy}|E_y,X_{jy})P(X_{jy}|E_y)$. In the latter case, species are
-independent and only the marginal occurrence must be accounted for, $P(
+independent, and only the marginal occurrence must be accounted for, $P(
 |E_y)=P(X_{iy} |E_y)P(X_{jy} |E_y)$.
@@
 studied for their impact on co-distribution (e.g. \citealt{Diamond1976, Connor1980,
-Gotelli2000}. Second- and higher-order interactions (e.g. trophic cascades)
+Gotelli2000}). Second- and higher-order interactions (e.g. trophic cascades)
 could also affect co-occurrence. Co-occurrence of multiple species embedded in
 ecological networks is a topic of its own, however, and is influenced by both network
-topology and species richness \citep{Cazelles2016}. Not only direct interactions do
+topology and species richness \citep{Cazelles2016}. Not only do direct interactions
 influence co-occurrence, but indirect interactions do as well (e.g. plant species
-sharing an herbivore could repulse each other in space). The impact of direct
+sharing an herbivore could repel each other in space). The impact of direct
 interactions and first-order indirect interactions on co-occurrence tends to
@@
 environmental gradient \citep{Cazelles2015}. Because of the complexity of relating
-co-occurrence to the structure of interaction networks, we will here focus on
+co-occurrence to the structure of interaction networks, we will focus here on
 the variation of interactions and not on their distribution, and leave this
@@
 large that the probability of observing at least one interaction converges to
-unity In this cenario, network variation solely arises from species
+unity. In this scenario, network variation solely arises from species
 distributions.
@@
 space. The genus Salix includes over 400 species, most of which are shrubs or
-small trees \citep{Argus1997}. The genus is common in most habitats across the
+small trees \citep{Argus1997}, and is common in most habitats across the
 Northern Hemisphere \citep{Skvortsov1999}. Willows support a highly diverse
@@
 important axes of the European climate, and more easily interpretable than
-reduced variables obtained by e.g. principal component analysis.
+reduced variables obtained, for example, by principal component analysis.
 
@@
 environment, $P(X_{iy},X_{jy}|E_y)$ (models are listed at Table 1 and 2).
-Hence, this model makes no assumptions about the mechanisms driving co-
-occurrence for any given environment, and instead uses the information directly
+Hence, this model makes no assumptions about the mechanisms driving co-occurrence
+for any given environment, and instead uses the information directly
 available in the data. It thereby indirectly accounts for the effect of
-interactions on co-occurrence, if there is any. The second model considers
+interactions on co-occurrence, if there are any. The second model considers
 independent occurrence of species. In this case, we independently fit
-$P(X_{iy} |E_y)$ and $P(X_{jy} |E_y)$, then we take their product to derive
+$P(X_{iy} |E_y)$ and $P(X_{jy} |E_y)$, and we then take their product to derive
 the probability of co-occurrence. This model should be viewed as a null
@@
 hypothesis that co-occurrence is conditional on the environment. Whenever the
-environment was included as a covariate in the GLM, we considered a second-
-order polynomial response for both temperature and precipitation. There are
+environment was included as a covariate in the GLM, we considered a second-order
+polynomial response for both temperature and precipitation. There are
 consequently 5 parameters for the first model when fitting a given pair of
@@
 local environmental variables, $P(L_{ijy}|X_{iy},X_{jy},E_y)$. Consequently,
-the model was fit to a subset of the data where the two species co-occur.
+the model was fit to the subset of the data where the two species co-occur.
 The second model fits the interaction probability independently of the local
@@
 
-The different models were fitted to each pair of species and the 
-predicted probabilities were recorded. The joint probability $P(L_{ijy},X_{iy},X_{jy})$
+We fit the different models to each pair of species and recorded the 
+predicted probabilities. The joint probability $P(L_{ijy},X_{iy},X_{jy})$
 was then computed from Eq. 2, and the likelihood of each observation was
-computed as $mathcal{L}(\theta_{ijy}|D_{ijy})=P(L_{ij},X_{iy},X_{jy})$ if an
+computed as $\mathcal{L}(\theta_{ijy}|D_{ijy})=P(L_{ij},X_{iy},X_{jy})$ if an
 interaction was observed, and as
-$mathcal{L}(\theta_{ijy}|D_{ijy})=1-P(L_{ijy},X_{iy},X_{jy})$ if no
+$\mathcal{L}(\theta_{ijy}|D_{ijy})=1-P(L_{ijy},X_{iy},X_{jy})$ if no
 interaction was observed. The log-likelihood was summed over the entire
@@
 interactions, only 290 of which occurred more than 5 times. Out of these 290
-interactions, 143 were systematically detected whenever the two species co-
-occurred. In the instances when species co-occurred, the two environmental
+interactions, 143 were systematically detected whenever the two species co-occurred.
+In the instances when species co-occurred, the two environmental
 variables considered proved relatively poor predictors of their interactions
@@
 species, only 1,173 pairs interacted in at least a single location, yielding a
-connectance of 0.068. However, only 4,459 pairs of species were found co-
-occurring at least once across all locations. There are consequently
+connectance of 0.068. However, only 4,459 pairs of species were found co-occurring
+at least once across all locations. There are consequently
 12,725 gaps of information in the metaweb (74.1\% - see Fig. 5). As we cannot
@@
 distribution of network properties across Europe (Fig. 6). For simplicity, we
-chose to consider connectance as descriptor of network configuration, as this
+chose to consider connectance as our descriptor of network configuration, as this
 metric can be easily computed from probabilistic networks \citep{Poisot2015c}) and is
 also a good proxy for many other network properties \citep{Poisot2014}. Overall, we
-find a peak in Salix, gallers and parasitoid diversity in northern Europe. The
+find a peak in Salix, gallers and parasitoid diversity in Northern Europe. The
 expected number of interactions roughly follows the distribution of species
 richness, but accumulates at a rate different from species numbers.
-Connectance also peaks in northern Europe (Fig. 6).
+Connectance also peaks in Northern Europe (Fig. 6).
 
@@
 Cronk2015, Wu2015} and sawflies \citep{Kouki1994, Kouki1999}. Species richness
-was originally presumed to show a similar "reversed latitudinal gradient" for
+was originally presumed to show a similar ``reversed latitudinal gradient'' for
 a common group of parasitic wasps, the Ichneumonidae, but this observation
@@
 structure is driven by a systematic change in species composition or of
-pairwise interactions \citep{Poisot2012, Poisot2015a}. The model comparison of
+pairwise interactions \citep{Poisot2012, Poisot2015a}. Our model comparison of
 the host-parasite interactions revealed that most of the turnover is driven by
@@
 interactions vary with the environment in other systems, for instance,
-herbivory \citep{Shurin2012}, predation \citep{McKinnon2010, Legagneux2014}
+herbivory \citep{Shurin2012} and predation \citep{McKinnon2010, Legagneux2014}
 are often found increasing with temperature, resulting in spatial variation of
@@
 interactions at the continental scale and the environment is critical to
-understand how trophic regulation at large spatial scales do influence
+understand how trophic regulation at large spatial scales influences
 community dynamics and ecosystem functioning  \citep{Harfoot2013}.
@@
 We restricted our framework to the effect of co-occurrence on ecological
-interactions and neglected the inverse of the problem. We did not investigated
+interactions and neglected the inverse of the problem. We did not investigate
 in depth the drivers of co-occurrence and simply took it for granted from the
@@
 (with the example pair for instance analysed at Table 1). The lack of an
-association could simply arises when the parasitoid is generalist enough so
+association could simply arise when the parasitoid is generalist enough so
 that it is not constrained to track the distribution of its host
@@
 evaluate if specific interactions do indeed affect co-occurrence. The
-expansion of the framework we described to account for the difference between
+expansion of the framework we describe to account for the difference between
 the realized and the fundamental niche will therefore require further
@@
 
-Ecological networks are known to be extremely sparse, \emph{i.e.} having far
-more absences of interactions that they have interactions. These absences of
+Ecological networks are known to be extremely sparse, \emph{i.e.} they have far
+more absences of interactions than they have interactions. These absences of
 interactions, however, can come from different sources. The fact that unequal
@@
 observed to co-occur. Although these are reported as a lack of interactions,
-in actuality we can not make inference about them since they have never been
-observed: it remains possible that this interaction may happen should the two
+in actuality we can make no inference about them since they have never been
+observed: it remains entirely possible that this interaction may happen should the two
 species co-occur. A second category of absences of interactions are those that
-are reported after multiple observations of species co-occurence. However, so
-as to have a confidence in the fact that the probability of an interaction is
+are reported after multiple observations of species co-occurence. However, to
+have confidence in the fact that the probability of an interaction is
 low, extensive sampling (that is, several records of co-occurence) is needed. Generally,
@@
 saturate after a fixed number of observations, which can be set as a threshold
-above which a species pair has finally been observed "often enough".
+above which a species pair has finally been observed ``often enough''.
 
@@
 There is evidence that interactions can vary in space, but this problem has
-not been investigated in a systematic fashion. The paucity of the data
-currently available precludes an extensive analysis of this question.
+not been investigated in a systematic fashion. The paucity of currently available data
+precludes an extensive analysis of this question at present.
 
@@
 in this framework. As abundance can impact the occurrence of interactions, and
-inversely since interactions do impact abundance \citep{Canard2014}, we could
+conversely since interactions impact abundance \citep{Canard2014}, we could
 reasonably expect the same for co-occurrence. Theory does exist for simple
-three-species modules \citep{Cazelles2015}, but the extension to entire co-
-occurrence networks will prove critical, especially given the interest in
+three-species modules \citep{Cazelles2015}, but the extension to entire co-occurrence
+networks will prove critical, especially given the interest in
 using co-occurrence to infer ecological interactions \citep{Morales2015,

### 2016-04-13 ms/ms_probaweb.tex
Edits to the intro and model section

@@
 
-Biogeography has historically focused on the spatial distribution and
-abundance of species, neglecting variation in the way species interact with
-each other. Models of species distribution and of interactions have
-historically taken different paths. Here, we plea for an integrated approach,
-adopting the view that community structure is best represented as an
-ecological network of interactions. We outline a conceptual approach,
-suggesting that the ecological niche may be redefined to encompass the effect
-of the environment on species distribution (the Grinnellian dimension of the
-niche) and on the ecological interactions among them (the Eltonian dimension).
-Starting from this novel concept, we develop a quantitative theory to explain
-turnover of interactions in space and time – i.e. a novel approach to
-interaction distribution modelling. We apply this framework to a large
-data set of host–parasite interactions across Europe and find that two aspects
-of the environment (temperature and precipitation) leave a strong imprint on
-species co-occurrence, but not on the probability of local interactions. Even
-where species co-occur, interaction proves a stochastic rather than
-deterministic process, adding to variation in realized network structure. We
-also find that a large majority of species pairs are never found together,
-thus precluding any inferences regarding their probability to interact. Our
-framework provides a first conceptual framework to explain the variation of
-network structure at large spatial scales and opens new perspectives at the
-frontier between species distribution modelling and community ecology.
+Biogeography has historically focused on the spatial distribution and abundance
+of species. Both are driven by the way species interact with one another,
+but also by the way these interactions vary across time and space. Here,
+we call for an integrated approach in which community structure represented
+as a network of ecological interactions, and show how it translates to
+biogeography questions. Under this representation, the niche is intergratively
+defined to be both the effect of the environment on species distribution (the
+Grinnellian dimension of the niche) and on the ecological interactions among
+them (the Eltonian dimension). Starting from this novel concept, we develop a
+quantitative theory to explain turnover of interactions in space and time -–
+\emph{i.e.} a novel approach to interaction distribution modelling. We apply
+this framework to host–parasite interactions across Europe and find that
+two aspects of the environment (temperature and precipitation) leave a strong
+imprint on species co-occurrence, but not on species interactions. Even where
+species co-occur, interaction proves a stochastic rather than deterministic
+process, adding to variation in realized network structure. We also find
+that a large majority of species pairs are never found together, thus
+precluding any inferences regarding their probability to interact. Our
+framework provides a basis to explain the variation of network structure
+at large spatial scales and opens new perspectives at the frontier between
+species distribution modelling and community ecology.
 
@@
 
-Community ecology is defined in most textbooks as \textit{the study of the
-interactions that determine the distribution and abundance of organisms}
-\citep{Krebs2001}. Despite a general consensus on this definition
-(Scheiner2007), research on variation in community
-structure has mostly focused on the spatial and temporal turnover of species composition
-\citep{Anderson2011}, neglecting variation in the way species interact with
-each other \citep{Poisot2015a}. Given this omission, it is perhaps not
-surprising that biogeographers are still struggling to establish whether
-interactions actually impact the distribution of species at large spatial
-scales\citep{Wisz2012, Kissling2012}, even though there is enough evidence
-from community ecology that interactions are critical for determining species
-dynamics, resource use and responses to the environment af finer scales.
-Recent attempts at accounting for interactions in species distribution models
-\citep{Pollock2014, Pelissier2013} have brought some methodological advances.
-Yet, these techniques are still based on a `species-based' approach to
-communities, where interactions are merely treated as fixed covariates
-affecting distribution.
-
-As a more explicit description of interactions among species, the
-network approach offers a convenient representation of communities. Species
-are represented as nodes and interactions by links. To date, studies of
-network diversity have mostly been concerned with the distribution of
-interactions within locations, and less so with the variation among locations
-\citep{Dunne2005, Bascompte2007, Ings2007, Kefi2012}. There is, however, 
-ample evidence that interaction networks vary in space and time
-\citep{Laliberte2010, Poisot2012, Albouy2014, Poisot2016, Trojelsgaard2015}. Metacommunity
-theory provides an explanation for the variation in the distribution of the
-different nodes \citep{Gravel2011c, Pillai2011}, but there is no explanation
-to the joint variation of node and link occurrences. Consequently, we urgently need a
-conceptual framework to formalize these observations.
+Community ecology is \textit{the study of the interactions that determine
+the distribution and abundance of organisms} \citep{Krebs2001}. Despite a
+general consensus on this definition (Scheiner2007), research on variation in
+community structure has mostly focused on the spatial and temporal turnover
+of species composition \citep{Anderson2011}, neglecting variation in the way
+species interact with each other, despite accumulating empirical evidence that
+this is a major source of diversity \citep{Poisot2015a}. Given this omission,
+it is perhaps not surprising that biogeographers are still struggling to
+establish whether interactions actually impact the distribution of species at
+large spatial scales \citep{Wisz2012, Kissling2012}: treating interactions
+as fixed events neglects a large part of the complexity of empirical
+communities, and will most likely deliver underwhelming results. Recent
+attempts at accounting for interactions in species distribution models
+\citep{Pollock2014, Pelissier2013} have brought some methodological advances,
+but are not sufficient for two reasons. First, these techniques are still
+based on a `species-based' approach to communities, where interactions
+are merely treated as fixed covariates affecting distribution. Second,
+they failed to provide a conceptual step forward, both in their treatment
+of interactions and in the quality of the predictions they make.
+
+Because it is an explicit description of species interactions, the network
+approach offers a convenient representation of communities. Species are
+represented as nodes, so that networks already encompass all the information
+used by current approaches; in addition, interactions are represented by links,
+so that networks provide additional, higher-order information on community
+structure. To date, studies of network diversity have mostly been concerned
+with the distribution of interactions within locations, and less so with
+the variation among locations \citep{Dunne2005, Bascompte2007, Ings2007,
+Kefi2012}. There is however ample evidence that interaction networks vary
+in space and time \citep{Laliberte2010, Poisot2012, Albouy2014, Poisot2016,
+Trojelsgaard2015}. Metacommunity theory provides explanations for the variation
+in the distribution species \citep{Gravel2011c, Pillai2011}, but there is
+no such explanation to the variation of node and link occurrences, nor do
+we expect their distribution to covary in a positive way. Consequently,
+we urgently need a conceptual framework to formalize these observations,
+as it is the only way towards fulfilling the goal of community ecology:
+providing cogent predictions about, and understanding of, the structure of
+ecollogical communities.
 
@@
 \begin{equation}
-	P(X_{iy},X_{jy},L_{ijy}|E_y)=P(X_{iy},X_{jy}|E_y)P(L_{ijy}|\mathbf{T},X_{iy},X_{jy},E_y)
+	P(X_{iy},X_{jy},L_{ijy}|E_y)=P(X_{iy},X_{jy}|E_y)P(L_{ijy}|X_{iy},X_{jy},E_y)
 \end{equation}
@@
 
-The first term on the right-hand side of the equation is the probability of
-observing the two species co-occurring at location $y$. It corresponds to the
-Grinnellian dimension of the niche. The second term represents the probability
-that an interaction occurs between species $i$ and $j$, given their set of
-traits $T$ and that they are co-occurring. Above, we referred to this entity
-as the ``metaweb'' and it corresponds to the Eltonian dimension of the niche. Below,
-we will see how this formalism can be directly fit to empirical data. But
-before turning to an application, we will discuss the interpretation of
-different variants of these two terms.
+The first term on the right-hand side of the equation is the probability
+of observing the two species co-occurring at location $y$. It corresponds
+to the Grinnellian dimension of the niche. The second term represents the
+probability that an interaction occurs between species $i$ and $j$, given that
+they are co-occurring. This predicate can be refined using information on
+trait distribution and trait matching rules (\textbf{Bartomeus Func Ecol}).
+Above, we referred to this entity as the ``metaweb'' and it corresponds to
+the Eltonian dimension of the niche. Below, we will see how this formalism
+can be directly fit to empirical data. But before turning to an application,
+we will discuss the interpretation of different variants of these two terms.
 

### 2016-04-13 analysis/scripts/results/1_metaweb_sampling.R
ABSOLUTE PATHS ARE THE DEVIL AND THOU SHALT SUFFER FOR YOUR SINS

@@ -7,7 +7,7 @@
 ##################################################################
 
 rm(list = ls())
-setwd("/Users/DGravel/Documents/Manuscripts/Inprep/ms_probaweb")
+#setwd("/Users/DGravel/Documents/Manuscripts/Inprep/ms_probaweb")
 
 # Load the data
 load("analysis/data/expand_data.Rdata")

### 2016-05-16 ms/ms_probaweb.tex
Edits from all

@@
-% TODO:
-% Add Ben and Spencer's edits
-% Revise the model with fixed interaction pribabilites (havens)
-% Compile the references
-% Distribute for a last round of edits
-% Add scussion on other on other types of interactions
-
 \documentclass[12pt]{article}
@@
 \textbf{Authors:} Dominique Gravel$^{1,2,*}$, Benjamin Baiser$^{3}$, Jennifer A. Dunne$^{4}$, Jens-Peter Kopelke$^{5}$, Neo
-Martinez$^{6}$, Tommy Nyman$^{7}$, Timoth\'ee Poisot$^{2,8}$, Spencer A. Wood$^{9}$, Daniel B. Stouffer$^{10}$, Jason Tylianakis$^{10,11}$ Tomas Roslin$^{12}$,\\
+Martinez$^{6}$, Tommi Nyman$^{7}$, Timoth\'ee Poisot$^{2,8}$, Spencer A. Wood$^{9}$, Daniel B. Stouffer$^{10}$, Jason M. Tylianakis$^{10,11}$ Tomas Roslin$^{12}$,\\
 
@@
 
-4: \\
+4: Santa Fe Institute, 1399 Hyde Park Road, Santa Fe, NM 87501, USA.\\
 
@@
 
-6:\\
-
-7:\\
-
-8:\\
+6: Ecology and Evolutionary Biology Department, University of Arizona, P.O. Box 210088, Tucson, AZ 85721, USA\\
+
+7: University of Eastern Finland, Department of Environmental and Biological Sciences, P.O. Box 111, FI-80101 Joensuu, Finland\\
+
+8: Université de Montréal, Département des Sciences Biologiques, 90 Avenue Vincent d’Indy, Montréal, QC H2V3S9, Canada.\\
 
@@
 
-11:\\
+11: Department of Life Sciences, Imperial College London, Silwood Park Campus, 
+Buckhurst Road, Ascot, Berkshire SL5 7PY, United Kingdom\\
 
@@
 
-\textbf{Figures:}
-
-\textbf{Tables:}
+\textbf{Figures: 6}
+
+\textbf{Tables: 2}
 
@@
 
-Biogeography has historically focused on the spatial distribution and abundance
-of species. Both are driven by the way species interact with one another,
-but also by the way these interactions vary across time and space. Here,
-we call for an integrated approach in which community structure represented
-as a network of ecological interactions, and show how it translates to
-biogeography questions. Under this representation, the niche is intergratively
-defined to be both the effect of the environment on species distribution (the
-Grinnellian dimension of the niche) and on the ecological interactions among
-them (the Eltonian dimension). Starting from this novel concept, we develop a
-quantitative theory to explain turnover of interactions in space and time -–
-\emph{i.e.} a novel approach to interaction distribution modelling. We apply
-this framework to host–parasite interactions across Europe and find that
-two aspects of the environment (temperature and precipitation) leave a strong
-imprint on species co-occurrence, but not on species interactions. Even where
-species co-occur, interaction proves a stochastic rather than deterministic
-process, adding to variation in realized network structure. We also find
-that a large majority of species pairs are never found together, thus
-precluding any inferences regarding their probability to interact. Our
-framework provides a basis to explain the variation of network structure
-at large spatial scales and opens new perspectives at the frontier between
-species distribution modelling and community ecology.
+Biogeography has traditionally focused on the spatial distribution and
+abundance of species. Both are driven by the way species interact with one
+another, but also by the way these interactions vary across time and space.
+Here, we call for an integrated approach in which community structure
+represented as a network of ecological interactions, and show how it
+translates to biogeography questions. We propose that the ecological niche may
+be redefined to encompass the effect of the environment on species
+distribution (the Grinnellian dimension of the niche) and on the ecological
+interactions among them (the Eltonian dimension). Starting from this 
+concept, we develop a quantitative theory to explain turnover of interactions
+in space and time -– \emph{i.e.} a novel approach to interaction distribution
+modelling. We apply this framework to host–parasite interactions across Europe
+and find that two aspects of the environment (temperature and precipitation)
+exert a strong imprint on species co-occurrence, but not on species
+interactions. Even where species co-occur, interaction proves to be stochastic
+rather than deterministic, adding to variation in realized network structure.
+We also find that a large majority of host-parasite pairs are never found
+together, thus precluding any inferences regarding their probability to
+interact. This first attempt to explain variation of network
+structure at large spatial scales opens new perspectives at the interface
+of species distribution modelling and community ecology.
 
@@
 
-Because it is an explicit description of species interactions, the network
-approach offers a convenient representation of communities. Species are
+Because it is an explicit description of species interactions, network
+approaches offer a convenient representation of communities. Species are
 represented as nodes, so that networks already encompass all the information
-used by current approaches; in addition, interactions are represented by links,
-so that networks provide additional, higher-order information on community
-structure. To date, studies of network diversity have mostly been concerned
-with the distribution of interactions within locations, and less so with
-the variation among locations \citep{Dunne2005, Bascompte2007, Ings2007,
-Kefi2012}. There is however ample evidence that interaction networks vary
-in space and time \citep{Laliberte2010, Poisot2012, Albouy2014, Poisot2016,
-Trojelsgaard2015}. Metacommunity theory provides explanations for the variation
-in the distribution species \citep{Gravel2011c, Pillai2011}, but there is
-no such explanation to the variation of node and link occurrences, nor do
-we expect their distribution to covary in a positive way. Consequently,
-we urgently need a conceptual framework to formalize these observations,
-as it is the only way towards fulfilling the goal of community ecology:
-providing cogent predictions about, and understanding of, the structure of
-ecollogical communities.
+used by current approaches; in addition, interactions are represented by
+links, so that networks provide additional, higher-order information on
+community structure. To date, studies of network diversity have mostly been
+concerned with the distribution of interactions within locations, and less so
+with variation among locations \citep{Dunne2005, Bascompte2007, Ings2007,
+Kefi2012}. There is, however, ample evidence that interaction networks vary in
+space and time \citep{Laliberte2010, Poisot2012, Albouy2014, Poisot2016,
+Trojelsgaard2015}, even though there is no common framework with which to
+generalize these results. Metacommunity theory provides explanations for
+variation in the distribution of the nodes \citep{Gravel2011c, Pillai2011},
+but there is no such explanation to the variation of node and link
+occurrences. Consequently, we urgently need a conceptual framework to
+formalize these observations, as it is the only way towards fulfilling the
+goal of community ecology: providing cogent predictions about, and
+understanding of, the structure of ecological communities.
 
@@
 species vs. interactions, there is a clear need to bring the two together.
-Here, we offer an integrated approach to do so, adopting the view that community
-structure is best represented as an ecological network of interactions. Based
-on this idea, we propose a new description of the basic concept of the
-ecological niche that integrates the effect of the environment on species
-distribution and on the ecological interactions among them. Starting from this
-redefined concept, we develop a quantitative theory to explain turnover of
-interactions in space and time. We first present the conceptual framework, and
-then formalize it mathematically, using a probabilistic model to represent the
-sampling of the regional pool of interactions. At the level of species pairs,
-the statistical approach could be conceived as an interaction distribution
-model. At the community level, the approach provides a likelihood-based method
-to compare different hypotheses of network turnover. We apply this novel
-framework to a large data set on host–parasite interactions across Europe and
-find that variation of the environment causes turnover of both species and
-interactions. The network structure changes systematically across the
-latitudinal gradient, with a peak of connectance at intermediate latitudes.
+Here, we offer an integrated approach to do so, adopting the view that
+community structure is best represented as a network of ecological
+interactions. Based on this idea, we propose a new description of the basic
+concept of the ecological niche that integrates the effect of the environment
+on species distribution and on the ecological interactions among them.
+Starting from this redefined concept, we develop a quantitative theory to
+explain turnover of interactions in space and time. We first present the
+conceptual framework, and then formalize it mathematically, using a
+probabilistic model to represent the sampling of the regional pool of
+interactions. At the level of species pairs, the statistical approach could be
+conceived as an interaction distribution model. At the community level, the
+approach provides a likelihood-based method to compare different hypotheses of
+network turnover. As an illustrative example, we apply this novel framework to
+a large data set on host–parasite interactions across Europe and perform test
+hypotheses underlying variation of species and interactions. The network
+structure changes systematically across the latitudinal gradient, with a peak
+of connectance at intermediate latitudes.
 
@@
 interactions constitute a local interaction network?} An illustration of this
-problem for a food web is provided in Figure 1. The regional pool of interactions, or metaweb, represents
-potential interactions among all species that could be found in a given area.
-In this particular case, there are 275 nodes, and 1173 links among the plants (52
-nodes), herbivores (96 nodes), and parasitoids (127 nodes) from Northern
-Europe. An instance of a local community is also illustrated, with 45 nodes
-and 93 interactions. Only 55.0\% of all potential interactions are realized locally,
-revealing the stochastic nature of ecological interactions. Our objective here
-is to provide a conceptual framework to explain the sampling of the regional
-pool of interactions, along with a quantitative method to predict it. The
-problem could be formalized sequentially by first understanding why only a
-fraction of the species are co-occurring locally and second why these species
-do or do not interact.
-
-There are multiple causes of spatial turnover in community composition. The
-first and most-studied driver is the effect of variation in the abiotic
-environment on species performance. Combined with specific responses in
-demography, it generates variation among sites by selecting the locally
-fittest species \citep{Leibold2004}. Stochasticity plays an additional role,
-either because colonization and extinction events \citep{Hanski1999} are inherently
-unpredictable or because of strong non-linear feedbacks in community dynamics
-generating alternative transients and equilibria \citep{Chase2007,
-Vellend2014}. Analyses of community turnover are usually performed with data
-represented in a table with rows corresponding to sites (or measurements) and
-columns to species. Metrics of beta diversity quantify the variance of this
-community data \citep{Legendre2005}. Traditional approaches rely on measures
-of dissimilarity among communities, such as the Jaccard or Bray–Curtis
-indices. A more recent approach decomposes the total variation of the
-community data into species and site contributions to beta diversity
-\citep{Legendre2013}, and further partitions into dissimilarity due to changes
-in species richness and those due to actual species turnover \citep{Baselga2010;
-Carvalho et al. 2012}. Even though these methods compare whole lists of
-species among sites or measurements, they remain fundamentally `species-based',
-since they report the variation within columns. None of them
-explicitly considers the variation of associations (i.e., of pairs or higher-order
-motifs – \citealt{Stouffer2007}).
-
-The ``niche'' is by far the dominant concept to explain species distributions
-and community assembly, from the local to the global scale. Following
-\citealt{Hutchinson1957}, the niche is viewed as the set of environmental
-conditions allowing a population to establish and persist (see also
-\citealt{Holt2009}). Community turnover arises as a result of successive
-replacement of species along an environmental gradient, in agreement with the
-Gleasonian view of communities \citep{Gleason1926}. The concept is
-straightforward to operationalize with species distribution models, as it maps
-naturally on available distributional and environmental data. In consequence,
-a vast array of statistical tools have been developed to implement it (e.g.
-BIOMOD \citealt{Thuiller2003}, MaxEnt \citealt{Phillips2006}). It is however
-much harder to account for ecological interactions within this approach
-\citep{Peterson2011}. As such, these interactions are often viewed as externalities
-constraining or expanding the range of environmental conditions required for a
-species to maintain a viable population \citep{Pulliam2000, Soberon2007, Boulangeat2012}.
-
-As mentioned above, in the network approach to community structure, species
-and interactions are represented by nodes and links, respectively.
-Associations can also be represented by matrices in which entries represent
-the occurrence or intensity of interactions among species (rows and columns).
-Network complexity is then computed as the number of interactions (in the case
-of binary networks) or interaction diversity (in the case of quantitative
+problem for a food web is provided in Fig. 1. The regional pool of
+interactions, or \emph{metaweb}, represents potential interactions among all
+species that could be found in a given area. In this particular case, there
+are 275 nodes, and 1173 links among the plants (52 nodes), herbivores (96
+nodes), and parasitoids (127 nodes) from Northern Europe. An instance of a
+local community is also illustrated, with 45 nodes and 93 interactions. Only
+55.0\% of all potential interactions (plant-herbivore or herbivore parasitoid
+combinations) are realized locally, revealing the stochastic nature of
+ecological interactions. Our objective here is to provide a conceptual
+framework to explain the sampling of the regional pool of interactions, along
+with a quantitative method to predict it. The problem could be formalized
+sequentially by understanding first why only a fraction of the species co-
+occur locally and second why these species do or do not interact.
+
+There are multiple causes of spatial turnover of species co-occurrence. The first
+and most-studied driver is the effect of variation in the abiotic environment
+on species performance. Combined with specific responses in demography, it
+generates variation among sites by selecting the locally fittest species
+\citep{Leibold2004}. Stochasticity plays an additional role, either because
+colonization and extinction events \citep{Hanski1999} are inherently
+unpredictable or because strong non-linear feedbacks in community dynamics
+generate alternative transients and equilibria \citep{Chase2007, Vellend2014}.
+Analyses of community turnover are usually performed with data represented in
+a table with rows corresponding to sites (or measurements) and columns to
+species. Metrics of beta diversity quantify the variance of this community
+data \citep{Legendre2005}. Traditional approaches rely on measures of
+dissimilarity among communities, such as the Jaccard or Bray–Curtis indices.
+More recent approaches decompose total variation of the community data into
+species and site contributions to beta diversity \citep{Legendre2013}, and
+further partition it into dissimilarity due to changes in species richness and
+dissimilarity due to actual species turnover \citep{Baselga2010;
+Carvalho2012}. Even though these methods compare whole lists of species among
+sites or measurements, they remain fundamentally `species-based', since they
+report variation within columns. None of them explicitly considers variation
+of associations (i.e., of pairs or higher-order motifs –
+\citealt{Stouffer2007}).
+
+Similarly, we are getting a better understanding of interaction turnover. As
+mentioned above, in the network approach to community structure, species and
+interactions are represented by nodes and links, respectively. Associations
+can also be represented by matrices in which entries represent the occurrence
+or intensity of interactions among species (rows and columns). Network
+complexity is then computed as the number of interactions (in the case of
+binary networks) or interaction diversity (in the case of quantitative
 networks, \citealt{Bersier2002}). Variability in community structure
@@
 higher-order interactions \citep{Poisot2015a}. Variation in community
-composition was found to be independent of the variation of ecological interactions,
-suggesting that these two components of network variability may well respond to
-different drivers \citep{Poisot2012}.
-
-Interestingly, the ecological network literature also has its own ’niche
-model’ to position a species in a community \citep{Williams2000}. The niche of a
-species in this context represents the multidimensional space of all of its
+composition can be independent of variation of ecological
+interactions, suggesting that species and interaction distribution may well
+respond to different drivers \citep{Poisot2012}.
+
+The "niche" is by far the dominant concept invoked to explain species
+distributions and community assembly, from the local to the global scale.
+Following \citealt{Hutchinson1957}, the niche is viewed as the set of
+environmental conditions allowing a population to establish and persist (see
+also \citealt{Holt2009}). Community turnover arises as a result of successive
+replacement of species along an environmental gradient, in agreement with the
+Gleasonian view of communities \citep{Gleason1926}. The concept is
+straightforward to put into practice with species distribution models, as it
+maps naturally on available distributional and environmental data. Consequently, a vast array of statistical tools have been developed to
+implement it (e.g. BIOMOD \citealt{Thuiller2003}, MaxEnt
+\citealt{Phillips2006}). It is however much harder to account for ecological
+interactions within this approach \citep{Peterson2011}. As such, these
+interactions are often viewed as externalities constraining or expanding the
+range of environmental conditions required for a species to maintain a viable
+population \citep{Pulliam2000, Soberon2007, Boulangeat2012}.
+
+Interestingly, the ecological network literature also has its own "niche
+model" to position a species in a community \citep{Williams2000}. The niche of
+a species in this context represents the multidimensional space of all of its
 interactions. Each species is characterized by a niche position, an optimum
-and a range over 3 to 5 different niche axes \citep{Williams2000, Eklof2013}.
-The niche model of food web structure and its variants have successfully explained the
-complexity of a variety of networks, from food webs to plant–pollinator
-systems \citep{Allesina2008, Williams2010, Eklof2013}. This
+and a range over three to five different niche axes \citep{Williams2000, Eklof2013}.
+The niche model of food web structure and its variants have successfully
+explained the complexity of a variety of networks, from food webs to
+plant–pollinator systems \citep{Allesina2008, Williams2010, Eklof2013}. This
 conceptual framework is, however, limited to local communities, and does not
@@
 
-A more integrative description of the niche is key to understanding spatial and
-temporal turnover in community structure. Despite several attempts to update
-the concept of the ecological niche, ecologists have not moved far beyond the
-``n-dimensional hypervolume'' defined by Hutchinson. Despite its intuitive
-interpretation and easy translation into species distribution models
-\citep{Boulangeat2012, Blonder2014}, the concept has been frequently
-criticized \citep{Hardin1960, Peters1991, Silvertown2004}, and several
-attempts have been made to expand and improve it \citep{Pulliam2000,
-Chase2003, Soberon2007, Holt2009, McInerny2012b}.
+Despite several attempts to update the concept of the ecological niche,
+ecologists have not moved far beyond the "n-dimensional hypervolume" defined
+by Hutchinson. Despite its intuitive interpretation and easy translation into
+species distribution models \citep{Boulangeat2012, Blonder2014}, the concept
+has been frequently criticized \citep{Hardin1960, Peters1991, Silvertown2004},
+and several attempts have been made to expand and improve it
+\citep{Pulliam2000, Chase2003, Soberon2007, Holt2009, McInerny2012b}.
 
 Part of the problem surrounding the niche concept has been clarified with the
-distinction between Eltonian and Grinnellian definitions \citep{Chase2003}. The
-Grinnellian dimension of the niche is the set of environmental conditions
+distinction between Eltonian and Grinnellian definitions \citep{Chase2003}.
+The Grinnellian dimension of the niche is the set of environmental conditions
 required for a species to maintain a population in a location. The Grinnellian
@@
 species distribution models. The Eltonian niche, on the other hand, is the
-effect of a species on its environment. This aspect of the niche is well known
-by community ecologists, but is trickier to turn into predictive models.
+effect of a species on its environment. While this aspect of the niche is well
+known by community ecologists, it is trickier to turn into predictive models.
 Nonetheless, the development of the niche model of food web structure
-\citep{Williams2000} and its parameterization \citep{Williams2010; Gravel2013}
-made it more operational.
-
-These perspectives are rather orthogonal to each other, and this has resulted in
-considerable confusion in the literature \citep{McInerny2012a}.
+\citep{Williams2000} and its parameterization using functional traits
+\citep{Gravel2013; Bartomeus2016} made it more operational.
+
+These perspectives are rather orthogonal to each other, and this has resulted
+in considerable confusion in the literature \citep{McInerny2012a}.
 \citealt{Chase2003} attempted to reconcile with the following definition:
-``[The niche is] the joint description of the environmental conditions that
+"[The niche is] the joint description of the environmental conditions that
 allow a species to satisfy its minimum requirements so that the birth rate of
 a local population is equal to or greater than its death rate along with the
-set of per capita effects of that species on these environmental conditions''.
-Their representation merges zero-net growth isoclines delimiting the
-Grinnellian niche (when does the population persists) with impact vectors delimiting
-the Eltonian niche (what is the per-capita impact). While this representation
-has been very influential in local-scale community ecology (the resource-ratio
-theory of coexistence, \citealt{Tilman1982}), it remains impractical at larger
-spatial scales because of the difficulties in measuring it. The absence of any
-mathematical representation of the niche that could be easily fit to
-ecological data may explain why biogeographers are still struggling to develop
-species distribution models that also consider ecological interactions.
-
-We propose to integrate the two perspectives of the niche with a visual
-representation of both components (Fig. 2). The underlying rationale is that, in
-addition to the environmental constraints on demographic performance, any
-organism requires resources to sustain its metabolic demands and reproduction.
-Abiotic environmental axes are any non-consumable factors affecting the
-demographic performance of an organism. Alternatively, the resource axes are
-traits of the resources that allow interactions with the consumer. The niche
-should therefore be viewed as the set of abiotic environmental factors (the
-Grinnellian component) along with the set of traits (the Eltonian component)
-that allow a population to establish and to persist at a location. Accordingly,
-each species can be characterized by an optimal position in both the
+set of per capita effects of that species on these environmental conditions".
+Their representation merges zero-net-growth isoclines delimiting the
+Grinnellian niche ("when does the population persists?"") with impact vectors
+delimiting the Eltonian niche ("what is the per-capita impact?"). While this
+representation has been very influential in local-scale community ecology (the
+resource-ratio theory of coexistence, \citealt{Tilman1982}), it remains
+impractical at larger spatial scales because of the difficulties in measuring
+it. The absence of any mathematical representation of the niche that can be
+easily fit to ecological data may explain why biogeographers are still
+struggling to develop species distribution models that also consider
+ecological interactions. Thus, a more integrative description of the niche
+will be key to understand spatial and temporal turnover in community
+structure.
+
+We propose to integrate the two perspectives of the niche using a visual
+representation of both components (Fig. 2). The underlying rationale is that,
+in addition to the environmental constraints on demographic performance (Fig.2
+top panel), any organism requires resources to meet its metabolic demands and
+to sustain reproduction (Fig. 2 nodes in network of bottom panel). Abiotic
+environmental axes are any non-consumable factors affecting the demographic
+performance of an organism. Alternatively, the resource axes are traits of the
+resources that allow interactions with the consumer. The niche can therefore
+be viewed as the set of abiotic environmental variables (the Grinnellian
+component) along with the set of traits (the Eltonian component) that allow a
+population to establish and to persist at a location. Accordingly, each
+species can be characterized by an optimal position along both the
 environmental (x-axis) and the trait (y-axis) plane. The integrated niche is
@@
 We now formalize the integrated niche with a probabilistic approach to
-interactions and distributions. In particular, we seek to represent the probability that an
-interaction between species $i$ and $j$ occurs at location $y$. We define
-$L_{ijy}$ as a stochastic variable, and focus on the probability that
-this event occurs, $P(L_{ijy})$. We note that the occurrence of an interaction is dependent
-on the co-occurrence of species $i$ and $j$. This argument might seem trivial
-at first, but the explicit consideration of this condition in the
-probabilistic representation of ecological interactions will prove instrumental
-to understand their variation. We define $X_{iy}$ as a stochastic variable
-representing the occurrence of species $i$ at location $y$. The quantity we seek to
-understand is the probability of a joint event, conditional on the set of
-environmental conditions $E_y$:
+interactions and distributions. In particular, we seek to represent the
+probability that an interaction between species $i$ and $j$ occurs at location
+$y$. We define $L_{ijy}$ as a stochastic variable, and focus on the
+probability that this event occurs, $P(L_{ijy})$. We note that the occurrence
+of an interaction is dependent on the co-occurrence of species $i$ and $j$.
+This argument might seem trivial at first, but the explicit consideration of
+this condition in the probabilistic representation of ecological interactions
+will prove instrumental to understanding their variation. We define $X_{iy}$
+as a stochastic variable representing the occurrence of species $i$ at
+location $y$. The quantity we seek to understand is the probability of a joint
+event, conditional on the set of environmental conditions $E_y$:
 
@@
 Or simply said, the probability of observing both species $i$ and $j$ plus an
-interaction between $i$ and $j$ given the conditions $E_y$. This probability
-could be decomposed into two parts using the product rule of probabilities:
+interaction between $i$ and $j$ given the conditions $E_y$ at location $y$.
+This probability could be decomposed into two parts using the product rule of
+probabilities:
 
@@
 they are co-occurring. This predicate can be refined using information on
-trait distribution and trait matching rules (\textbf{Bartomeus Func Ecol}).
-Above, we referred to this entity as the ``metaweb'' and it corresponds to
+trait distribution and trait matching rules (\citep{Bartomeus2016}).
+Above, we referred to this entity as the "metaweb" and it corresponds to
 the Eltonian dimension of the niche. Below, we will see how this formalism
@@
 There are several variants to the co-occurrence probability, representing
-different hypotheses about temporal and spatial variation in network structure
+different hypotheses concerning temporal and spatial variation in network structure
 (see the explicit formulations in Table 1). The simplest model relates the
@@
 processes responsible for co-occurrence. It could arise because interactions
-do in fact constrain distributions \citep{Pollock2014, Cazelles2016} or,
+constrain distribution \citep{Pollock2014, Cazelles2016} or,
 alternatively, because of environmental requirements shared between $i$ and
@@
 independent, and only the marginal occurrence must be accounted for, $P(
-|E_y)=P(X_{iy} |E_y)P(X_{jy} |E_y)$.
+X_{ijy}}|E_y)=P(X_{iy} |E_y)P(X_{jy} |E_y)$.
 
@@
 interactions such as competition, facilitation, and predation have long been
-studied for their impact on co-distribution (e.g. \citealt{Diamond1976, Connor1980,
-Gotelli2000}). Second- and higher-order interactions (e.g. trophic cascades)
-could also affect co-occurrence. Co-occurrence of multiple species embedded in
-ecological networks is a topic of its own, however, and is influenced by both network
-topology and species richness \citep{Cazelles2016}. Not only do direct interactions
-influence co-occurrence, but indirect interactions do as well (e.g. plant species
-sharing an herbivore could repel each other in space). The impact of direct
-interactions and first-order indirect interactions on co-occurrence tends to
-vanish with increasing species richness in the community. Further, co-occurrence
-is also influenced by the covariance of interacting species to an
-environmental gradient \citep{Cazelles2015}. Because of the complexity of relating
-co-occurrence to the structure of interaction networks, we will focus here on
-the variation of interactions and not on their distribution, and leave this
-specific issue for the Perspectives and future research.
+studied for their impact on co-distribution (e.g. \citealt{Diamond1976,
+Connor1980, Gotelli2000}). Second- and higher-order interactions (e.g. trophic
+cascades) could also affect co-occurrence. Co-occurrence of multiple species
+embedded in ecological networks is a topic of its own, however, and is
+influenced by both network topology and species richness \citep{Cazelles2016}.
+Not only direct interactions influence co-occurrence, but indirect
+interactions do as well (e.g. plant species sharing an herbivore, or
+herbivores sharing parasitoids, could repel each other in space
+\citealt{Holt1993}). The impact of direct interactions and first-order
+indirect interactions on co-occurrence tends to vanish with increasing species
+richness in the community. Further, co-occurrence is also influenced by the
+covariance of interacting species to an environmental gradient
+\citep{Cazelles2015}. Because of the complexity of relating co-occurrence to
+the structure of interaction networks, we will focus here on the variation of
+interactions and not on their distribution, and leave this specific issue for
+the Perspectives section and future research.
 
@@
 There are also variants of the metaweb. First, most documented metawebs have
-thus far considered ecological interactions to be deterministic, not
+thus far considered ecological interactions to be deterministic, rather than
 probabilistic (e.g. \citealt{Havens1992, Wood2015}). Species are assumed to
@@
 $P(L_{ijy}|X_{ijy}=1) = 1$ and $P(L_{ijy}|X_{ijy}=0) = 0$. This approach might
-be a reasonable approximation if the scale of sampling and inference is so
+be a reasonable approximation if the spatial or temporal scale of sampling and inference is so
 large that the probability of observing at least one interaction converges to
-unity. In this scenario, network variation solely arises from species
+unity. In this scenario, network variation arises solely from species
 distributions.
 
-Ecological interactions could also vary with the environment, so that $P(L_{ijy}
-|E_y)$. Although it is not common to see a conditional representation of
-pairwise ecological interactions, experimental studies have revealed them to
-frequently be sensitive to the environment. For instance, \citep{Mckinnon2010} showed
-that predation risks of shorebirds vary at the continental scale, decreasing
-from the south to the north. It is also common to see increasing top-down
-control with temperature (e.g. \citealt{Shurin2012, Gray2016}). Effects of the
-environment on interactions also propagate up the community and influence network
-structure \citep{Tylianakis2007, Woodward2010; Petchey2010; Lelong2015}.
+Second, ecological interactions could also vary with the environment, so that
+$P(L_{ijy} |E_y)$. Although it is rare to see a conditional representation of
+pairwise ecological interactions, experimental studies have frequently
+revealed interactions to  be sensitive to the environment. For instance,
+\citep{Mckinnon2010} showed that predation risks of shorebirds vary at the
+continental scale, decreasing from the south to the north. It is also common
+to see increasing top-down control with temperature (e.g. \citealt{Shurin2012,
+Gray2016}). Effects of the environment on interactions also propagate up the
+community and influence network structure \citep{Tylianakis2007, Woodward2010;
+Petchey2010; Lelong2015}.
 
@@
 local food webs of willows (genus Salix), their galling insects, and the
-parasitoids of these gallers. Targeting this system, we ask: i) how much does
-network structure vary across the gradient, and ii) what is the primary driver
-of network turnover across the gradient?
+natural enemies (parasitoids and inquilines) of these gallers. Targeting this
+system, we ask: i) how much does network structure vary across the gradient,
+and ii) what is the primary driver of network turnover across the gradient?
 
@@
 oviposition, and includes marked manipulation of host-plant chemistry by the
-galler \citep{Nyman2000}. The parasitoid community includes nearly
+galler \citep{Nyman2000}. The enemy community of the gallers includes nearly
 100 species belonging to 17 insect families of four orders
@@
 more than once, with a total of 641 site visits across the 370 sites. GPS
-coordinates were recorded for each location; for our analyses, the present day
+coordinates were recorded for each location; for our analyses, current
 annual mean temperature and precipitation were obtained from WorldClim using
 the R package raster \citep{Hijmans2015}. While other covariates could have
-also been considered, these variables are likely representative of the most
-important axes of the European climate, and more easily interpretable than
+also been considered, these two variables are likely representative of the most
+important axes of the European climate, and are also more easily interpretable than
 reduced variables obtained, for example, by principal component analysis.
@@
 individually-identified parasitoids. Of these, 25,170 (60\%) could be
-identified to the species level. Overall, 127 parasitoid taxa were
+identified to the species level. Overall, 127 parasitoid and inquiline taxa were
 distinguished in the material. Data on host associations within subsets of
@@
 of illustration, we considered second-order generalized linear models –
-whereas more flexible fitting algorithms (e.g. GAM or Random Forest)
+although more flexible fitting algorithms (e.g. GAM or Random Forest)
 could equally well be used, as long as the algorithm can estimate the
@@
 environment, $P(X_{iy},X_{jy}|E_y)$ (models are listed at Table 1 and 2).
-Hence, this model makes no assumptions about the mechanisms driving co-occurrence
-for any given environment, and instead uses the information directly
-available in the data. It thereby indirectly accounts for the effect of
-interactions on co-occurrence, if there are any. The second model considers
+Hence, this model makes no assumptions about the mechanisms driving co-
+occurrence for any given environment, and instead uses the information
+directly available in the data. It thereby indirectly accounts for the effect
+of interactions on co-occurrence, if there are any. The second model considers
 independent occurrence of species. In this case, we independently fit
-$P(X_{iy} |E_y)$ and $P(X_{jy} |E_y)$, and we then take their product to derive
-the probability of co-occurrence. This model should be viewed as a null
+$P(X_{iy} |E_y)$ and $P(X_{jy} |E_y)$, and we then take their product to
+derive the probability of co-occurrence. This model should be viewed as a null
 hypothesis with respect to the first model, since a comparison between the
@@
 co-occurrence is independent of the environment and thus constant throughout
-the landscape. In other words, $P(X_{iy},X_{jy})$ is obtained by simply counting the
-number of observed co-occurrences divided by the total number of observations.
-Thus, the comparison between the first and third model allows us to test the
-hypothesis that co-occurrence is conditional on the environment. Whenever the
-environment was included as a covariate in the GLM, we considered a second-order
-polynomial response for both temperature and precipitation. There are
-consequently 5 parameters for the first model when fitting a given pair of
-species, 10 parameters for the second, and only 1 for the third model.
+the landscape. In other words, $P(X_{iy},X_{jy})$ is obtained by simply
+counting the number of observed co-occurrences divided by the total number of
+observations. Thus, the comparison between the first and third model allows us
+to test the hypothesis that co-occurrence is conditional on the environment.
+Whenever the environment was included as a covariate in the GLM, we considered
+a second-order polynomial response for both temperature and precipitation in
+order to account for optima in environmental conditions. There are
+consequently five parameters for the first model when fitting a given pair of
+species, 10 parameters for the second, and only one for the third model.
 
@@
 networks from the knowledge of a deterministic metaweb. There are consequently
-5 parameters for the first model, a single parameter for the second model and
+five parameters for the first model, a single parameter for the second model and
 no parameter to evaluate for the third model (where the interaction
@@
 distributions and interaction probabilities across the entire European
-continent. We reconstructed the expected network for each location in a 1km X
-1km grid and computed the probabilistic connectance following
+continent. We reconstructed the expected network for each location in a 1 X
+1 km grid and computed the probabilistic connectance following
 \citep{Poisot2015b}.
@@
 
-Despite the extensive sampling, many pairs of species were observed to co-occur
-only a few times. This made it hard to evaluate interaction probabilities with
-any reasonable confidence interval. Thus, we start with an example of a single
-pair of species selected because of its high number of co-occurrences
-($N_{ij}=38$): \textit{Phyllocolpa prussica} and \textit{Chrysocharis
-elongata}. These two fairly abundant species, were observed $N_i=49$ and $N_j=121$
-times, respectively, across the 370 sites, and they were found to
-interact with a marginal probability $P(L_{ij})=0.55$, which means they
-interacted at 21 different locations. Here, a comparison of model fit (Table
-1) reveals that the interaction probability conditional on co-occurrence
-does not better explain their distribution (Model 1 vs Model 2). Moreover, when the two
-species co-occur, the occurrence of the interaction was insensitive to the
-environment (Model 2 vs Model 3). Alternatively, climatic variables
-significantly impacted co-occurrence (Model 3 vs Model 4). The neutral model
-performed worse than the non-random co-occurrence model (Model 3 vs Model 6).
-The full model revealed that the greatest interaction probability occurred at
-intermediate temperature and precipitation, simply because this is where the
-two species most frequently co-occur (Fig. 3). The probabilities of co-occurrence
-and interaction can be represented in space, where we found that the
-highest interaction probability occurred in central Europe (Fig. 4).
+Despite the extensive sampling, many pairs of species were observed to co-
+occur only a few times. This made it difficult to evaluate interaction
+probabilities with any reasonable confidence interval. Thus, we start with an
+example of a single pair of species selected because of its high number of co-
+occurrences ($N_{ij}=38$): the leaf folder \textit{Phyllocolpa prussica} and
+the parasidoid \textit{Chrysocharis elongata}. These two fairly abundant
+species were observed $N_i=49$ and $N_j=121$ times, respectively, across the
+370 sites, and they were found to interact with a marginal probability
+$P(L_{ij})=0.55$, which means they interacted at 21 different locations. Here,
+a comparison of model fit (Table 1) reveals that conditioning the interaction
+probability on local environmental conditions adds no explanatory power beyond
+a model assuming the same probability of interaction anywhere in space(Model 1
+vs Model 2). Moreover, when the two species co-occur, the occurrence of the
+interaction was insensitive to the environment (Model 2 vs Model 3).
+Alternatively, climatic variables significantly impacted co-occurrence (Model
+3 vs Model 4). The neutral model performed worse than the non-random co-
+occurrence model (Model 3 vs Model 6). The full model revealed that the
+greatest interaction probability occurred at intermediate temperature and
+precipitation, simply because this is where the two species most frequently
+co-occur (Fig. 3). The probabilities of co-occurrence and interaction can be
+represented in space, where we found that the highest interaction probability
+occurred in Central Europe (Fig. 4).
 
@@
 contributes to network variability. In total, we recorded 1,173 pairs of
-interactions, only 290 of which occurred more than 5 times. Out of these 290
+interactions, only 290 of which occurred more than five times. Out of these 290
 interactions, 143 were systematically detected whenever the two species co-occurred.
@@
 environment was considered. However, the extra number of parameters exceeded the
-gain in likelihood and inflates AIC. Therefore, the most parsimonious model
+gain in likelihood and inflated AIC. Therefore, the most parsimonious model
 excluded the effect of the environment. On the basis of log-likelihoods only,
-co-occurrence was non-neutral for both Salix–galler interactions and
+co-occurrence was non-neutral for both Salix–galler and
 galler–parasitoid interactions. Thus, according to AIC, the best model was the
@@
 The approach we present not only has implications for understanding the
-biogeography of pairwise interactions and interaction networks, but also the
-quality of the evaluation of metawebs. We investigated the reliability of the
+biogeography of pairwise interactions and interaction networks, but also for
+evaluating the quality of metawebs. We investigated the reliability of the
 estimated metaweb across the entire dataset wtih summary statistics of species
@@
 species, only 1,173 pairs interacted in at least a single location, yielding a
-connectance of 0.068. However, only 4,459 pairs of species were found co-occurring
-at least once across all locations. There are consequently
-12,725 gaps of information in the metaweb (74.1\% - see Fig. 5). As we cannot
-know whether the non-co-occurring species would indeed interact when found
+connectance of 0.068. However, only 4,459 pairs of species were found co-
+occurring at least once across all locations. There are consequently 12,725
+gaps of information in the metaweb (74.1\% - see Fig. 5). As we cannot know
+whether the non-co-occurring species would indeed interact if found
 together, a more appropriate estimate of connectance would be
@@
 
-Once we had selected the best model (Model 3, Table 2), we used it to
+Once we had selected the best model based on AIC (Model 3, Table 2), we used it to
 reconstruct the expected species richness, along with the most likely network
-for each location. By this approach, we could map the expected
-distribution of network properties across Europe (Fig. 6). For simplicity, we
-chose to consider connectance as our descriptor of network configuration, as this
-metric can be easily computed from probabilistic networks \citep{Poisot2015c}) and is
-also a good proxy for many other network properties \citep{Poisot2014}. Overall, we
-find a peak in Salix, gallers and parasitoid diversity in Northern Europe. The
-expected number of interactions roughly follows the distribution of species
-richness, but accumulates at a rate different from species numbers.
-Connectance also peaks in Northern Europe (Fig. 6).
+for each location. Using this approach, we mapped the expected distribution of
+network properties across Europe (Fig. 6). For simplicity, we chose to
+consider connectance as our descriptor of network configuration, as this
+metric can be easily computed from probabilistic networks \citep{Poisot2015c}
+and is also a good proxy for many other network properties \citep{Poisot2014}.
+Overall, we find a peak in Salix, gallers and parasitoid diversity in Northern
+Europe. The expected number of interactions roughly follows the distribution
+of species richness, but accumulates at a rate different from species numbers.
+Connectance likewise peaks in Northern Europe (Fig. 6).
 
@@
 
-We have proposed that the representation of community structure and its variation
-in space and time is best represented with the formalism of ecological
-networks because both the distribution of species and their interspecific
-interactions can then be accounted for. We consequently revised the niche concept in
-order to integrate both the abiotic and the biotic components of the niche
-that are susceptible to vary over time and space. This integrated niche was
-represented visually with an ordination of species into an environmental space
-and a trait space. The fundamental niche of a species is represented as the
-set of environmental conditions and resources that allow a species to be
-maintained in a location, thereby integrating the Eltonian and the Grinnellian
-components of the niche. We then translated the concept mathematically by
-investigating the probability of the joint occurrences of species and
-their interaction, which should be interpreted as an interaction distribution
-model. We used this approach to characterize the turnover of the structure of
-ecological interactions in a tri-trophic network across Western Europe and
-found that the primary driver of variation is the turnover in species
-composition. To our knowledge, this is the first continental-wide analysis of
-the drivers of network structure from empirical data (see \citealt{Albouy2014,
+We have proposed that the representation of community structure and its
+variation in space and time is best captured by the formalism of
+ecological networks, as both the distribution of species and their
+interspecific interactions can then be accounted for. We consequently revised
+the niche concept in order to integrate its abiotic and biotic
+components that vary over time and space. This
+integrated niche was represented visually with an ordination of species into
+an environmental space and a trait space. The fundamental niche of a species
+is represented as the set of environmental conditions and resources that allow
+a species to establish in a location, thereby integrating the Eltonian and the
+Grinnellian components of the niche. We then translated the concept
+mathematically by investigating the probability of the joint occurrences of
+species and their interaction, which should be interpreted as an interaction
+distribution model. We used this approach to characterize the turnover of the
+structure of ecological interactions in a species-rich tri-trophic network
+across Western Europe, finding that the primary driver of variation is the
+turnover in species composition. To our knowledge, this is the first
+continental-wide analysis of the drivers of network structure from empirical
+data on the occurrence of interactions (see \citealt{Baiser2012,Albouy2014,
 Poisot2016}).
@@
 Applying the framework to our large data set on host–parasite interactions
-across Europe revealed key features in the interaction between Salix taxa, their
-herbivores, and the natural enemies of these herbivores. Consistent with a
-general increase in the diversity of Salix towards boreal areas
+across Europe revealed key features in the interaction between Salix taxa,
+their herbivores, and the natural enemies of these herbivores. Consistent with
+a general increase in the diversity of Salix towards boreal areas
 \citep{Cronk2015}, overall species richness of the networks increased towards
 the north. The distribution of Salix species richness largely matched those of
-gallers and parasitoids. These observations within Europe are
-also matched by the ones found at a global scale for Salix \citep{Argus1997,
-Cronk2015, Wu2015} and sawflies \citep{Kouki1994, Kouki1999}. Species richness
-was originally presumed to show a similar ``reversed latitudinal gradient'' for
-a common group of parasitic wasps, the Ichneumonidae, but this observation
-has been challenged by findings of rather high ichneumonid diversity in the
-tropics \citep{Veijalainen2013}. However, the ichneumonid subfamilies
+gallers and parasitoids. These observations within Europe are also matched by
+the ones found at a global scale for Salix \citep{Argus1997, Cronk2015,
+Wu2015} and sawflies \citep{Kouki1994, Kouki1999}. Species richness in a
+common groupd of parasitic wasps, the Ichneumonidae, was originally presumed
+to show a similar ``reversed latitudinal gradient'', but this observation has
+been recently challenged by findings of rather high ichneumonid diversity in
+the tropics \citep{Veijalainen2013}. Nevertheless, ichneumonid subfamilies
 specifically associated with sawflies (Ctenopelmatinae, Tryphoninae) are
@@
 richness at different trophic levels is yet to be established (but see e.g.
-\citealt{Roininen2005, Nyman2010, Leppanen2014}), but as a net
-outcome of different latitudinal trends across trophic levels, the
-distribution of co-occurrence and therefore of potential interactions differed
-between the first and second link layers. The correlation between the expected
-Salix and gallers richness was 0.73, while it was 0.58 between gallers and
-their parasitoids. The ratio of herbivore to Salix species is essentially constant
-across Europe, whereas each herbivore species is potentially attacked by a
-richer enemy community higher latitudes (i.e. faces higher vulnerability).
-Consequently, overall connectance peaks in Northern Europe (Fig. 6).
+\citealt{Roininen2005, Nyman2010, Leppanen2014}), but as a net outcome of
+different latitudinal trends across trophic levels, the distribution of co-
+occurrence and therefore of potential interactions differed between the first
+and second layers of feeding links. The correlation between expected Salix and gallers
+richness was 0.73, while it was 0.58 between gallers and their parasitoids.
+Therefore, the ratio of herbivores to Salix species is essentially constant
+across Europe, while each herbivore species is potentially attacked by a and
+a lower trophic level at the same site was clearly affected by the richer
+enemy community at higher latitudes. Consequently, overall connectance peaks
+in Northern Europe (Fig. 6).
 
@@
 two was not detectably so. This applies to the example species \textit{Phyllocolpa
-prussica} and \textit{Chrysocharis elongata} (Figs 2-3), but also to all species pairs
+prussica} and \textit{Chrysocharis elongata} (Figs 2 and 3), but also to all species pairs
 more generally. For the example species pair, the full model revealed that the
-interaction probability is highest at intermediate temperature and
+interaction probability peaks at intermediate temperature and
 precipitation, simply because this is where the two species co-occur most
@@
 \citealt{Lurgi2010} and in time \citep{Trolsgaard2015} is accumulating
-rapidly. It is not clear however to what extent the turnover of network
+rapidly. It is not clear, however, to what extent the turnover of network
 structure is driven by a systematic change in species composition or of
 pairwise interactions \citep{Poisot2012, Poisot2015a}. Our model comparison of
-the host-parasite interactions revealed that most of the turnover is driven by
-a species-specific response to the environment, impacting species richness,
-and that co-occurrence was mostly neutral. Further, the occurrence of
-interactions in presence of the host and parasite is highly stochastic, but
-not predictable according to the variables we considered. We know that
-interactions vary with the environment in other systems, for instance,
-herbivory \citep{Shurin2012} and predation \citep{McKinnon2010, Legagneux2014}
-are often found increasing with temperature, resulting in spatial variation of
-trophic cascades \citep{(Gray2016}. What remains unclear, however, is the
-extent to which such variation is driven by a turnover of species composition
-along gradients, or a turnover of the interactions. Here we found that
-interactions vary substantially, but not predictably along the annual
-temperature and the precipitation gradient. Perhaps we have not found a strong
-signal of the effect of the environment on the occurrence of interactions
-because we had wrong covariates. It was indeed found previously for a similar
-system that habitat characteristics are the primary drivers of interactions
-\citep{Nyman2015}. New investigations with other systems will be required to
-challenge this result. Documenting the relationship between the occurrence of
-interactions at the continental scale and the environment is critical to
-understand how trophic regulation at large spatial scales influences
-community dynamics and ecosystem functioning \citep{Harfoot2013}.
+host-parasite interactions revealed that most of the turnover is driven by
+species-specific responses to the environment, impacting species richness, and
+that co-occurrence was mostly neutral. Further, the occurrence of interactions
+among host and parasite is highly stochastic even when both are present, and
+not predictable by the variables considered by us. We know that interactions
+vary with the environment in other systems, for instance, herbivory
+\citep{Shurin2012} and predation \citep{McKinnon2010, Legagneux2014} are often
+found to increase with temperature, resulting in spatial variation of trophic
+cascades \citep{(Gray2016}. What remains unclear, however, is the extent to
+which such variation is driven by a turnover of species composition along
+gradients, or a turnover of the interactions. Here we found that interactions
+vary substantially but non-predictably along the annual temperature and the
+precipitation gradient. Clearly, the lack of detectable signal may be due to
+our choice of covariates. Indeed, a previous study on a similar system
+identified habitat characteristics as the primary drivers of interactions
+\citep{Nyman2015}. New investigations with other systems will thus be required
+to challenge this result. Under all circumstances, documenting the
+relationship between the environment and the occurrence of interactions at
+continental scales is critical for understanding how large-scale variation of
+trophic regulation influences community dynamics and ecosystem functioning
+\citep{Harfoot2013}.
 
 We restricted our framework to the effect of co-occurrence on ecological
-interactions and neglected the inverse of the problem. We did not investigate
-in depth the drivers of co-occurrence and simply took it for granted from the
+interactions, neglecting the inverse of the problem. We did not investigate in
+depth the drivers of co-occurrence and simply took it for granted from the
 data. Co-occurrence was indeed many times significantly different from the
-expectation of independent species distribution. It thus raises the question
-that, once accounting for the species-specific effect of the environment on
-distribution, are there significant effects of interactions on co-occurrence?
-We could rephrase this problem asking if the fundamental niche differs from
-the realized niche, and how it applies to our framework. For example, we have
-considered above simply the co-occurrence probability, $P(X_{iy},X_{jy}|E_y)$,
-which could be expanded as $P(X_{iy}|X_{jy},E_y) P(X_{jy}| E_y )$. The
-marginal occurrence probability, $P(X_{jy}|E_y )$, could be considered as a
-species distribution model taking into account the interaction between these
-species after some re-arrangement of Eq. 2. This derivation would however
-critically depend on a strong a priori expectation of the conditional
-probability of observing a species given the distribution of the other
-species. This assumption seems reasonable for some situations, such as a
-parasitoid species that requires a host to develop. On the other hand, we
-found the strength of this association is often rather weak if not neutral
-(with the example pair for instance analysed at Table 1). The lack of an
-association could simply arise when the parasitoid is generalist enough so
-that it is not constrained to track the distribution of its host
-\citep{Cazelles2015}. At present, there is only indirect support to the
-hypothesis that interacting species are conditionally distributed and it
-should be the topic of more specific hypothesis testing. The impact of
-ecological interactions on the distribution of co-occurrence has been the
-topic of many publications since \citealt{Diamond1975} seminal study on
-competition and the checkerboard distribution, but only recently pairwise
-approaches received attention \citep{Veech2013}. It therefore remains unclear
-if two interacting species are more closely associated in space because most
-approaches based on null models consider community-level metrics (e.g.
-\citealt{Gotelli2000}), such as the C-score, thereby making it hard to
-evaluate if specific interactions do indeed affect co-occurrence. The
-expansion of the framework we describe to account for the difference between
-the realized and the fundamental niche will therefore require further
-investigation of the impact of interactions on co-occurrence.
-
-Ecological networks are known to be extremely sparse, \emph{i.e.} they have far
-more absences of interactions than they have interactions. These absences of
-interactions, however, can come from different sources. The fact that unequal
-sampling at the local scale can affect our understanding of network structure
-is well documented \citep{Martinez1999}. However, in a spatial context, some
-interactions may be undocumented because the species involved have never been
-observed to co-occur. Although these are reported as a lack of interactions,
-in actuality we can make no inference about them since they have never been
-observed: it remains entirely possible that this interaction may happen should the two
-species co-occur. A second category of absences of interactions are those that
-are reported after multiple observations of species co-occurence. However, to
-have confidence in the fact that the probability of an interaction is
-low, extensive sampling (that is, several records of co-occurence) is needed. Generally,
-our confidence that the interaction is indeed impossible will increase with
-the number of observations of the species pair. Seeing that this is essentially
-a Bernoulli process (the probability that the species will interact given
-their presence), the breadth of the confidence interval is expected to
-saturate after a fixed number of observations, which can be set as a threshold
-above which a species pair has finally been observed ``often enough''.
+expectation of independent species distributions. It thus begs the question of
+whether, once environmental effects on species-specific distribution have been
+accounted for, interactions come with significant effects on co-occurrence? We
+could rephrase this problem by asking whether the fundamental niche differs
+from the realized niche, and how this applies to our framework. For example,
+we have considered above simply the co-occurrence probability,
+$P(X_{iy},X_{jy}|E_y)$, which could be expanded as $P(X_{iy}|X_{jy},E_y)
+P(X_{jy}| E_y )$. After some re-arrangement of Eq. 2, the marginal occurrence
+probability, $P(X_{jy}|E_y )$, could be considered as a species distribution
+model taking into account the interaction between these species. This
+derivation would however critically depend on a strong \emph{a priori} expectation of
+the conditional probability of observing a species given the distribution of
+the other species. This assumption seems reasonable for some situations, such
+as a parasitoid species that requires a host to develop. On the other hand, we
+found that the strength of this association is often rather weak if not
+neutral (for instance, with the example pair analyzed at Table 1). The lack of
+an association could simply arise when the parasitoid is generalist enough 
+that it is not obligated to track the distribution of any single/given host
+\citep{Cazelles2015}.
+
+At present, there is only indirect support for the hypothesis that interacting
+species are conditionally distributed but this possibility  should be the
+topic of more specific hypothesis testing. The impact of ecological
+interactions on the distribution of co-occurrence has been the topic of many
+publications since \citealt{Diamond1975} seminal study on competition and
+"checkerboard" distribution, but pairwise approaches have only recently
+received attention \citep{Veech2013}. Whether two interacting species are more
+closely associated in space remains unclear, since most approaches based on
+null models consider community-level metrics (e.g. \citealt{Gotelli2000}),
+such as the C-score, thereby making it hard to evaluate if specific
+interactions do indeed affect co-occurrence. The expansion of the framework we
+describe to account for the difference between the realized and the
+fundamental niche will therefore require further investigation of the impact
+of interactions on co-occurrence.
+
+Ecological networks are known to be extremely sparse, \emph{i.e.} they have
+far more absences than presences of interactions. Absences of interactions,
+however, can come from different sources. The fact that unequal sampling at
+the local scale can affect our understanding of network structure is well
+documented \citep{Martinez1999}. However, in a spatial context, some
+interactions may be undocumented simply because the species involved have
+never been observed to co-occur. Although these cases are reported as a lack
+of interactions, in actuality we cannot make any reliable inference from them:
+since the species have never been observed together, it remains possible that
+they would interact if they did. A fundamentally different category of
+absences of interactions are then those reported after multiple observations
+of species co-occurence. Thus, to gain confidence that the probability of an
+interaction is low, extensive sampling (that is, several records of co-
+occurence) is needed. Generally, our confidence that the interaction is indeed
+impossible will increase with the number of observations of the species pair.
+Seeing that this is essentially a Bernoulli process (the probability that the
+species will interact given their presence), the breadth of the confidence
+interval is expected to saturate after a fixed number of observations, which
+can be set as a threshold above which a species pair has finally been observed
+"often enough". this will allow us to deal with both confirmed absences of
+interactions and mere absence of evidence.
 
@@
 
-Understanding the drivers of the spatial variation in network structure is a
+Understanding the drivers of spatial variation in network structure is a
 key problem to solve in order to anticipate the impacts of global changes on
-biodiversity. Our representation of the spatial variation of community
+biodiversity. Our representation of spatial variation of community
 structure presents a new approach for the study of the biogeography of ecological
@@
 
-\textbf{1. New generation of network data}. The investigation of the spatial
+\textbf{1. New generation of network data}. Investigating spatial
 variation of network structure will require high quality and highly replicated
@@
 ecological interactions \citep{Poisot2012}. Each pair of species must be
-observed several times to have reliable estimates of their interaction
+observed several times in order to obtain reliable estimates of their interaction
 probability.
 
-\textbf{2. Estimation of the reliability of interactions}. We need quantitative tools
-to estimate the confidence interval around an estimate of interaction
-probability, as well as some estimation of the rate of false absences.
-Bayesian methods are promising to that end because we could use information on
-the target species (e.g. if they are known as specialists or generalists) to
-provide prior estimates of the interaction probability.
+\textbf{2. Estimation of the reliability of interactions}. We need
+quantitative tools to estimate the confidence intervals around inferred
+interaction probabilities, as well as estimators? of the frequency of false
+absences. Bayesian methods are promising to that end, because we could use
+information on the target species (e.g. if they are known as specialists or
+generalists) to provide prior estimates of the interaction probability.
 
 \textbf{3. From interaction probabilities to a distribution of network properties}.
-Metrics are available to analyse the structure of probabilistic networks
+Metrics are available to analyze the structure of probabilistic networks
 \citep{Poisot2015c}. These metrics are useful as first approximation, but they
@@
 conversely since interactions impact abundance \citep{Canard2014}, we could
-reasonably expect the same for co-occurrence. Theory does exist for simple
-three-species modules \citep{Cazelles2015}, but the extension to entire co-occurrence
-networks will prove critical, especially given the interest in
-using co-occurrence to infer ecological interactions \citep{Morales2015,
-Morueta-Holme2016}.
+reasonably expect that interactions will also influence co-occurrence. Theory
+in this regard does exist for simple three-species modules
+\citep{Cazelles2015}, but its extension to entire co-occurrence networks will
+prove critical in the future, especially given the interest in using co-
+occurrence to infer ecological interactions \citep{Morales2015, Morueta-
+Holme2016}.
 
@@
 \section*{Acknowledgements}
-This is a contribution to the working groups \emph{Networks over ecological
-gradients} (Santa Fe Institute) and \emph{Continental-scale variation of
-ecological networks} (Canadian Institute for Ecology and Evolution).
+
+This is a contribution to the working groups \emph {Continental-scale
+variation of ecological networks} supported by the Canadian Institute for
+Ecology and Evolution), and the \emph{ Next Generation Data, Models, and
+Theory Working Group}, supported by the Santa Fe Institute, the Betsy and
+Jesse Fink Foundation, the ASU-SFI Center for Biosocial Complex Systems, and
+NSF Grant PHY-1240192. DG also acknowledge financial support from NSERC-
+Discovery grant program and Canada Research Chair program.
+
 \newpage
@@
 
-\textbf{Non-random sampling of the metaweb}. Network assembly can be viewed as
-a sampling process of the regional pool of potential interactions. Species
+\textbf{Non-random sampling of the metaweb}.  Network assembly can be viewed
+as a sampling process of the regional pool of potential interactions. Species
 (indicated by colored nodes) are sampled first, and among the species found in
@@
 proposed in this paper. As a concrete illustration of metaweb sampling, we
-here show a local interaction network among Salix, gallers, andparasitoids.
-The metaweb was constructed by aggregating observed interactionsb across 370
-local networks.
+here show a local interaction network among Salix (left/green), gallers
+(center/red), and parasitoids (red/blue). The metaweb was constructed by
+aggregating interactions observed across 370 local networks.
 
@@
 its niche optimum ($c$). The vertical axis represents a niche gradient,
-presumably a trait such as body size. The location of each species along this
-gradient represents their niche position. The focal species will feed on prey
-species niche locations within a given interval around the optimum,
+for example a trait such as body size. The location of each species along this
+gradient represents their niche position. The focal species will feed only on prey
+species occupying niche locations within a given interval around the optimum,
 represented by the horizontal lines. The integrated Grinnellian and Eltonian
@@
 probabilistic framework, the central square represents the area where the
-joint probability of observing interactions and co-occurrence is positive.
+joint probability of observing co-occurrence and interactions is positive.
 
@@
 \textbf{Probabilistic representation of the interaction probability between a
-leaf galler (\textit{Phyllocolpa prussica}) and a parasitoid
-(\textit{Chrysocharis elongata}) across an annueal average temperature and an
-annual precipitation gradient}. The representation is based on predictions
-from model 3 (see Table 1). In the left panel, open circles represent the
-absence of both species, whereas closed circles represent co-occurrence and
-plus signs the occurrence of only one of the two species. In the other two
-panels, open circles represent co-occurrence but an absence of interaction and
-the closed circles represent the occurrence of an interaction.
+leaf folder (\textit{Phyllocolpa prussica}) and a parasitoid
+(\textit{Chrysocharis elongata}) across gradients of annual average
+temperature and annual precipitation}. The representation is based on
+predictions from Model 3 (see Table 1). In the left panel, open circles
+represent the absence of both species, whereas closed circles represent co-
+occurrence and plus signs the occurrence of only one of the two species. In
+the other two panels, open circles represent co-occurrence but an absence of
+interaction and closed circles the occurrence of an interaction.
 
@@
 \textbf{Probabilistic representation of the interaction probability between a
-leaf galler (\textit{Phyllocolpa prussica}) and a parasitoid
+leaf folder (\textit{Phyllocolpa prussica}) and a parasitoid
 (\textit{Chrysocharis elongata}) across Europe}. The maps are generated from 
-predicted probabilities according to the model illustrated at Fig. 3.
+probabilities predicted by the model illustrated inFig. 3.
 
@@
 Black cells indicate species pairs for which at least one interaction was
-recorded, white cells indicate absence of recorded interactions and the red
+recorded, white cells indicate absence of recorded interactions and grey
 cells show pairs of species never detected at the same site (and hence species
@@
 connectance across Europe}. The representation is based on predictions from
-model 3 (see Table 2). Species richness is obtained by the summation of
-individual occurrence probabilities and link density is obtained by the
-summation of the interaction probabilities.
+Model 3 (see Table 2). Species richness is obtained by summation of individual 
+occurrence probabilities, and link density by summation of interaction probabilities.
 

### 2016-05-24 analysis/scripts/results/1_metaweb_sampling.R
Final edits to Fig 1

@@ -25,12 +25,8 @@ Sall = length(unique_ID_all)
 DF = data.frame(sites = data$pairs.sites_ID, IDi = IDi, IDj = IDj, Xi=data$Xi, Xj=data$Xj, Xij = data$Xij, Lij = data$Lij)
 
 #########################################################
-# Network sampling
-#########################################################
-
 # Adjacency matrix for the metaweb
-# Loop around all pairs of species to test if there are interactions
-# Put everything in a square matrix
+#########################################################
 
 mw = data.frame(matrix(0, nr = Sall, nc = Sall))
 names(mw) = unique_ID_all
@@ -56,10 +52,12 @@ for(n in 1:nrow(pairs)) {
 }
 
 #########################################
-# Compute the local network for one site
+# Adjacency matrix for one site
 #########################################
 
-lw = matrix(0, nr = Sall, nc = Sall)
+lw = data.frame(matrix(0, nr = Sall, nc = Sall))
+names(lw) = unique_ID_all
+row.names(lw) = unique_ID_all
 DF_split_sites = split(DF,DF$sites)
 site_index = 369 # Pick one that has a decent number of links
 
@@ -82,13 +80,14 @@ for(n in 1:nrow(pairs)) {
 }
 
 #########################################################
-# Convert the metaweb to igraph
+# Convert the adjacency matrices to igraph
 #########################################################
 
 library(igraph)
-g = graph.incidence(mw,add.names=NULL, mode = "undirected")
+g_mw = graph.adjacency(as.matrix(mw))
+g_lw = graph.adjacency(as.matrix(lw))  
 
-#########################################################
+########################################################
 # Set the layer attribute for every node
 #########################################################
 
@@ -96,21 +95,12 @@ salix_ID = as.character(unique(pairs[pairs$pairs.type=="SH",1]))
 gall_ID = as.character(unique(pairs[pairs$pairs.type=="HP",1]))
[…]

### 2016-05-24 analysis/scripts/functions/get_LL.R
Edits to Figure 3 and 4

@@ -8,6 +8,7 @@ get_LL = function(model_list, data) {
 		sumLL = 0
 		npars = 0
 	}
+
 	else {
 		# NUMBER OF PARAMETERS
 		if(is.null(modelC$ij)) nparsXij = length(modelC$i$coefficients)*2	
@@ -16,7 +17,7 @@ get_LL = function(model_list, data) {
 		npars = (nparsXij+nparsLij)
 
 		# COMPUTATION OF THE PROBABILITIES
-		probs = get_probs(newE = data$E,modelC,modelL)
+		probs = get_probs(model_list, newE = data$E)
 		PLijXij = probs$PLij*probs$PXij 
 
 		# COMPUTATION OF THE LIKELIHOOD

### 2016-05-24 analysis/scripts/functions/get_probs.r

@@ -12,13 +12,13 @@ get_probs = function(model_list, newE) {
 		PLijhigh = NA
 	}
 	else {
-		probs = get_probs(modelC, modelL, newE)
-		PXij = probs$PXij 
-		PLij = probs$PLij 
+		if(is.null(modelC$ij)) 
+			PXij = predict(modelC$i, type = "response", newdata = newE)*predict(modelC$j, type = "response", newdata = newE)	
+		else 
+			PXij = predict(modelC$ij, type = "response", newdata = newE)	
+		PLij = predict(modelL, type = "response", newdata = newE)
 		PLijXij = PXij*PLij 			
-		PLijlow = probs$PLijlow
-		PLijhigh = probs$PLijhigh	
 	}
 
-	return(list(PXij = PXij, PLij = PLij, PLijXij = PLijXij, PLijlow = PLijlow, PLijhigh = PLijhigh))	
+	return(list(PXij = PXij, PLij = PLij, PLijXij = PLijXij))	
 } 

### 2016-05-24 analysis/scripts/results/2_example_pair.R

@@ -53,12 +53,12 @@ models_C1_L2 = fit_models(data, selection = FALSE, funC = C1, funL = L2)
 models_C3_L2 = fit_models(data, selection = FALSE, funC = C3, funL = L2)
 
 # Compute the LL
-LL_C2_L0 = get_LL(models_C2_L0,data)
-LL_C2_L1 = get_LL(models_C2_L1,data)
-LL_C2_L2 = get_LL(models_C2_L2,data)
-LL_C0_L2 = get_LL(models_C0_L2,data)
-LL_C1_L2 = get_LL(models_C1_L2,data)
-LL_C3_L2 = get_LL(models_C3_L2,data)
+LL_C2_L0 = get_LL(models_C2_L0, data)
+LL_C2_L1 = get_LL(models_C2_L1, data)
+LL_C2_L2 = get_LL(models_C2_L2, data)
+LL_C0_L2 = get_LL(models_C0_L2, data)
+LL_C1_L2 = get_LL(models_C1_L2, data)
+LL_C3_L2 = get_LL(models_C3_L2, data)
 
 # Collect the results
 LL = c(
@@ -88,9 +88,8 @@ write.table(cbind(LL,npars,AIC), file = "./tables/table1.txt")
 # Plot the results
 #########################################################
 
-# Compute predicted values for each observation
+# Compute the model
 models = models_C2_L2
-probs = get_probs(modelC=models$modelC, modelL=models$modelL, newE=data$E)
 
 # Compute predicted values for the environmental space
 nsteps = 250
@@ -104,7 +103,7 @@ expT2 = expT^2
 expPP2 = expPP^2
 
 newE = data.frame(T = expT,T2 = expT2, PP = expPP, PP2 = expPP2)
-probs = get_probs(modelC=models$modelC, modelL=models$modelL, newE=newE)
+probs = get_probs(models, newE=newE)
 
 # Plot the results
 PXijmat = matrix(probs$PXij, nr = nsteps, nc = nsteps, byrow = FALSE)

### 2016-05-24 analysis/scripts/results/3_map_pair.R

@@ -58,10 +58,6 @@ subE = subset(E,Xij == 1)
 subLij = subset(Lij, Xij == 1)
 lm_L = glm(subLij ~ T+PP+T2+PP2, family = "binomial", data = subE)
 
-summary(lm_i)
-summary(lm_j)
-summary(lm_L)
-
 # Compute expected probabilities over the gradient
 PXi_E = predict(lm_i, type="response", newdata=map_E)
 PXj_E = predict(lm_j, type="response", newdata=map_E)

### 2016-05-24 ms/ms_probaweb.tex
Edits to Fig 6

@@
 	\# & Metaweb model 						& Co-occurrence model 			& LL 	& npars & AIC \\ \hline
-	1 & $P(L_{ijy})$ 						& $P(X_{iy},X_{jy}|E_y)$ 		& -65.5 & 6 	& 143 \\
+	1 & $P(L_{ijy})$ 						& $P(X_{iy},X_{jy}|E_y)$ 		& -591.3 & 6 	& 1194.5 \\
 	2 & $P(L_{ijy} | X_{iy}, X_{jy})$ 		& $P(X_{iy},X_{jy}|E_y)$ 		& -65.7 & 6 	& 143.4 \\

### 2016-05-24 analysis/scripts/results/1_metaweb_sampling.R

@@ -3,12 +3,11 @@
 # Illustrating the sampling of the metaweb of interactions among salix,
 # gall insects and parasitoids across Europe
 # Dominique Gravel
-# October 29th, 2015
 ##################################################################
 
 rm(list = ls())
 
-# Load the data
+# Load & prepare the data
 load("./data/expand_data.Rdata")
 load("./data/DF_split.Rdata")
 load("./data/pairs.Rdata")

### 2016-05-24 analysis/scripts/results/2_example_pair.R

@@ -3,7 +3,6 @@
 # Illustrating the computation of interaction probabilities for a 
 # pair of species
 # Dominique Gravel
-# October 29th, 2015
 ##################################################################
 
 rm(list = ls())

### 2016-05-24 analysis/scripts/results/3_map_pair.R

@@ -2,7 +2,6 @@
 # Script for Figure 4
 # Mapping across Europe the interaction probability between pairs of species
 # Dominique Gravel
-# October 29th, 2015
 ##################################################################
 
 rm(list=ls())
@@ -11,6 +10,7 @@ library(raster)
 library(sp)
 library(rgdal)
 
+# Load & prepare the data
 load("./data/DF_split.Rdata")
 load("./data/expand_data.Rdata")
 

### 2016-05-24 analysis/scripts/results/4_metaweb_holes.r

@@ -3,10 +3,11 @@
 # Illustrating the computation of interaction probabilities for a 
 # pair of species
 # Dominique Gravel
-# October 29th, 2015
 ##################################################################
 
 rm(list = ls())
+
+# Load & prepare the data
 load("./data/DF_split.Rdata")
 load("./data/pairs.Rdata")
 

### 2016-05-24 analysis/scripts/results/5_map_all.r

@@ -2,14 +2,15 @@
 # Script for Figure 6
 # Mapping network properties across Europe
 # Dominique Gravel
-# October 29th, 2015
 ##################################################################
 
 rm(list=ls())
+
 library(raster)
 library(sp)
 library(rgdal)
 
+# Load & prepare the data
 load("./data/DF_split.Rdata")
 load("./data/expand_data.Rdata")
 load("./data/pairs.Rdata")
@@ -22,63 +23,102 @@ nobs = 374
 np  = length(DF_split)
 
 # Load the stuff to make the raster object
-wrld <- readOGR("data/map", layer="level1")
+wrld <- readOGR("analysis/data/map", layer="level1")
 europe <- wrld[1,]
 exteur <- extent(europe)
+xmin(exteur) = 0
+xmax(exteur) = 25
+ymin(exteur) = 40
+ymax(exteur) = 70
 
 # Extract the climatic variables
 clim = crop(getData("worldclim", var="bio", res=10), exteur)
 mapT = getValues(clim$bio1)
 mapPP = getValues(clim$bio12)
+ncell = length(T)
+map_E = data.frame(T = mapT, PP = mapPP, T2 = mapT^2, PP2 = mapPP^2)
 
 ############################################################
 # Extract the local networks over Europe
 ############################################################
 
-ncell = length(T)
-map_E = data.frame(T = mapT, PP = mapPP, T2 = mapT^2, PP2 = mapPP^2)
-
-# Loop around all species pairs
-expS = numeric(ncell)
-expL = numeric(ncell)
-
-
 #############
-# Compute the expected local species richness
-# Stack 
-Xi = data[,7]
-Xj = data[,8]
-site = data[,1]
-T = data[,12]
-PP = data[,23]
+# Compute the distribution of salix richness
+data_S = subset(data[,c(1,2,5,10,21)], data$pairs.type == "SH")
+ID_S = unique(data_S$pairs.from)
+exp_S = numeric(nrow(map_E))
+for(i in 1:length(ID_S)) {
 
-data_i = cbind(site,IDi,Xi,T,PP)
[…]

### 2016-05-24 analysis/scripts/results/table_all_models.R

@@ -2,7 +2,6 @@
 # Compute the likelihood for each model and each species pair
 # Record the results in a summary table
 # Dominique Gravel
-# October 29th, 2015
 ##################################################################
 
 rm(list = ls())
@@ -14,7 +13,7 @@ source("./scripts/functions/get_probs.R")
 source("./scripts/functions/get_LL.R")
 source("./scripts/functions/fit_models.R")
 
-# Load the data
+# Load & prepare the data
 load("./data/expand_data.Rdata")
 load("./data/DF_split.Rdata")
 load("./data/pairs.Rdata")

### 2016-05-24 analysis/source_all.R

@@ -1,8 +1,11 @@
+# Make sure to have all the required packages
+install.packages(c("igraph", "rgdal", "raster", "sp", "viridis","dismo"))
+
 # init parallel option
 parallel = TRUE
 
 # Process the data
-source("./scripts/data_processing/reformat_salix.r")
+source("./scripts/data_processing/reformat_salix.r") # Note this one will take a lot of time (few hours)
 source("./scripts/data_processing/split_data.r")
 
 # Get the results

### 2016-05-24 analysis/scripts/functions/get_LL.r
Fix a problem with Havens model

@@ -1,0 +1,32 @@
+# Compute the likelihood for a set of observations, given the model
+get_LL = function(model_list, data) {
+
+	modelC = model_list$modelC
+	modelL = model_list$modelL
+
+	if(is.null(modelC)) {
+		sumLL = 0
+		npars = 0
+	}
+
+	else {
+		# NUMBER OF PARAMETERS
+		if(is.null(modelC$ij)) nparsXij = length(modelC$i$coefficients)*2	
+		else nparsXij = length(modelC$ij$coefficients)
+		nparsLij = length(modelL$coefficients)	
+		npars = (nparsXij+nparsLij)
+
+		# COMPUTATION OF THE PROBABILITIES
+		probs = get_probs(model_list, newE = data$E)
+		PLijXij = probs$PLij*probs$PXij 
+
+		# COMPUTATION OF THE LIKELIHOOD
+		LL = numeric(length(data$Xij))
+		LL[data$Lij == 1] = log(PLijXij[data$Lij==1])
+		LL[data$Lij == 0] = log(1 - PLijXij[data$Lij==0])	
+		sumLL = sum(LL)
+	}
+
+	return(c(sumLL, npars))
+
+}

### 2016-05-24 analysis/scripts/functions/interactions_models.r

@@ -1,0 +1,41 @@
+# Returns the probability of observing the interaction ij 
+# independently of co-occurrence and of the environment
+# Havens type of interaction
+# We have to trick the glm function so that it returns a probability 
+# of 1 if the species do interact at least once, and 0 if they never
+# interact
+L0 <- function(data, selection) {
+   with(as.list(data),{
+
+        if(sum(Lij)>0) Lij_trick = numeric(length(Lij)) + 1
+          else Lij_trick = numeric(length(Lij))
+        model <- glm(Lij_trick ~ 1, family = "binomial")
+
+        if(selection) {return(step(model,trace=0))}
+        else {return(model)}
+   })
+}
+
+# Returns the probability of observing the interaction ij when i 
+# and j are present independently of the environment
+L1 <- function(data, selection) {
+   with(as.list(data),{
+        model <- glm(Lij[Xij==1] ~ 1, family = "binomial")
+        if(selection) {return(step(model,trace=0))}
+        else {return(model)}
+   })
+}
+
+# Returns the probability of observing the interaction ij when i 
+# and j are present for each level of the environment
+L2 <- function(data, selection) {
+   with(as.list(data),{
+    subLij = Lij[Xij==1] 
+    subE = E[Xij==1,]  
+    Enames = expression("T","T2","PP","PP2")
+    fmla <- as.formula(paste("subLij ~ ", paste(Enames, collapse= "+")))     
+    model <- glm(fmla, family = "binomial",data=subE)
+    if(selection) {return(step(model,trace=0,direction = "forward"))}
+    else {return(model)}
+   })
+}

### 2016-05-24 analysis/scripts/results/1_metaweb_sampling.r

@@ -1,0 +1,139 @@
+##################################################################
+# Script for Figure 1
+# Illustrating the sampling of the metaweb of interactions among salix,
+# gall insects and parasitoids across Europe
+# Dominique Gravel
+##################################################################
+
+rm(list = ls())
+
+# Load & prepare the data
+load("./data/expand_data.Rdata")
+load("./data/DF_split.Rdata")
+load("./data/pairs.Rdata")
+
+IDi = as.character(data$pairs.from)
+IDj = as.character(data$pairs.to)
+Si = length(unique(IDi))
+Sj = length(unique(IDj))
+unique_IDi = unique(IDi)
+unique_IDj = unique(IDj)
+IDcomm = IDj[match(unique_IDi,unique_IDj,nomatch=0)]
+unique_ID_all = unique(c(IDi,IDj))
+Sall = length(unique_ID_all)
+DF = data.frame(sites = data$pairs.sites_ID, IDi = IDi, IDj = IDj, Xi=data$Xi, Xj=data$Xj, Xij = data$Xij, Lij = data$Lij)
+
+#########################################################
+# Adjacency matrix for the metaweb
+#########################################################
+
+mw = data.frame(matrix(0, nr = Sall, nc = Sall))
+names(mw) = unique_ID_all
+row.names(mw) = unique_ID_all
+
+for(n in 1:nrow(pairs)) {
+
+	# Compute the number of links
+	nL = sum(DF_split[[n]]$Lij)
+
+	if(nL!=0) {
+
+		# Get the victim
+		i = which(unique_ID_all == DF_split[[n]]$IDi[1])
+
+		# Get the ennemy index
+		j = which(unique_ID_all == DF_split[[n]]$IDj[1])
+
+		# Put the record in the mw
+		mw[i,j] = 1
+		mw[j,i] = 1		
+	}
+}
+
+#########################################
+# Adjacency matrix for one site
+#########################################
+
+lw = data.frame(matrix(0, nr = Sall, nc = Sall))
+names(lw) = unique_ID_all
+row.names(lw) = unique_ID_all
+DF_split_sites = split(DF,DF$sites)
+site_index = 369 # Pick one that has a decent number of links
+
+for(n in 1:nrow(pairs)) {
+	# Compute the number of links
[…]

### 2016-05-24 analysis/scripts/results/3_example_pair.r

@@ -1,0 +1,135 @@
+##################################################################
+# Script for Figure 3
+# Illustrating the computation of interaction probabilities for a 
+# pair of species
+# Dominique Gravel
+##################################################################
+
+rm(list = ls())
+
+# Load some functions
+source("./scripts/functions/species_models.r")
+source("./scripts/functions/interactions_models.r")
+source("./scripts/functions/get_LL.r")
+source("./scripts/functions/get_probs.r")
+source("./scripts/functions/fit_models.r")
+
+# Load the data
+load("./data/DF_split.Rdata")
+load("./data/expand_data.Rdata")
+
+#########################################################
+# Fit the different models
+#########################################################
+
+# Find the nb of links per pair
+nL  = numeric(length(DF_split))
+nXi = numeric(length(DF_split))
+nXj = numeric(length(DF_split))
+nXij = numeric(length(DF_split))
+for(x in 1:length(DF_split)) {
+	nL[x] = sum(DF_split[[x]]$Lij)
+	nXi[x] = sum(DF_split[[x]]$Xi)
+	nXj[x] = sum(DF_split[[x]]$Xj)
+	nXij[x] = sum(DF_split[[x]]$Xij)
+}
+
+cbind(nL,nXi,nXj,nXij,nL,nL/nXij)[nL/nXij<0.7 & nL > 10,]
+
+# Subset the data
+pair_index = which(nL == 21 & nXij == 38) 
+data = DF_split[[pair_index]]
+data$E = data.frame(T = data$E$T/12, PP = data$E$PP/1000, T2 = data$E$T2/12^2, PP2 = data$E$PP2/1000^2)
+sum(data$Lij)
+sum(data$Xij)
+
+# Pick the model
+models_C2_L0 = fit_models(data, selection = FALSE, funC = C2, funL = L0)
+models_C2_L1 = fit_models(data, selection = FALSE, funC = C2, funL = L1)
+models_C2_L2 = fit_models(data, selection = FALSE, funC = C2, funL = L2)
[…]

### 2016-05-24 analysis/scripts/results/4_map_pair.r

@@ -1,0 +1,113 @@
+##################################################################
+# Script for Figure 4
+# Mapping across Europe the interaction probability between pairs of species
+# Dominique Gravel
+##################################################################
+
+rm(list=ls())
+
+library(raster)
+library(sp)
+library(rgdal)
+
+# Load & prepare the data
+load("./data/DF_split.Rdata")
+load("./data/expand_data.Rdata")
+
+IDi = data$pairs.IDi
+IDj = data$pairs.IDj
+Si = length(unique(IDi))
+Sj = length(unique(IDj))
+
+# Load the stuff to make the raster object
+wrld <- readOGR("data/map", layer="level1")
+europe <- wrld[1,]
+exteur <- extent(europe)
+xmin(exteur) = 0
+xmax(exteur) = 25
+ymin(exteur) = 40
+ymax(exteur) = 70
+
+# Extract the climatic variables
+clim = crop(getData("worldclim", var="bio", res=10), exteur)
+T = getValues(clim$bio1)
+PP = getValues(clim$bio12)
+
+############################################################
+# Extract the local networks over Europe
+############################################################
+
+ncell = length(T)
+map_E = data.frame(T = T, PP = PP, T2 = T^2, PP2 = PP^2)
+pair = 6128
+
+data = DF_split[[pair]]
+Xi = data$Xi
+Xj = data$Xj
+Xij = data$Xij
+Lij = data$Lij
+E = data$E	
+
+i = as.numeric(as.vector(data$IDi[1]))
+j = as.numeric(as.vector(data$IDj[1]))
+
+# Compute the models
+lm_i = glm(Xi ~ T+PP+T2+PP2, family = "binomial", data = E)
+lm_j = glm(Xj ~ T+PP+T2+PP2, family = "binomial", data = E)
+subE = subset(E,Xij == 1)
+subLij = subset(Lij, Xij == 1)
+lm_L = glm(subLij ~ T+PP+T2+PP2, family = "binomial", data = subE)
+
+# Compute expected probabilities over the gradient
+PXi_E = predict(lm_i, type="response", newdata=map_E)
+PXj_E = predict(lm_j, type="response", newdata=map_E)
[…]

### 2016-05-24 analysis/scripts/results/6_metaweb_holes.r

@@ -1,0 +1,116 @@
+##################################################################
+# Script for Figure 5
+# Illustrating the computation of interaction probabilities for a 
+# pair of species
+# Dominique Gravel
+##################################################################
+
+rm(list = ls())
+
+# Load & prepare the data
+load("./data/DF_split.Rdata")
+load("./data/pairs.Rdata")
+
+ID_S = unique(as.character(pairs$pairs.from[pairs$pairs.type=="SH"]))
+ID_H = unique(as.character(pairs$pairs.to[pairs$pairs.type=="SH"]))
+ID_P = unique(as.character(pairs$pairs.to[pairs$pairs.type=="HP"]))
+
+S_S = length(ID_S)
+S_H = length(ID_H)
+S_P = length(ID_P)
+
+#########################################################
+# Compile the metaweb
+#########################################################
+
+L_SH = matrix(0, nr = S_S, nc = S_H)
+X_SH = matrix(0,nr = S_S, nc = S_H)
+
+L_HP = matrix(0, nr = S_H, nc = S_P)
+X_HP = matrix(0,nr = S_H, nc = S_P)
+
+for(n in 1:length(DF_split)) {
+
+	# Compute the number of links
+	nL = sum(DF_split[[n]]$Lij)
+
+	# Compute the number of co-occurrences
+	nX = sum(DF_split[[n]]$Xij)
+
+	if(nX!=0) {
+
+		# Indices for the different species
+		if(pairs$pairs.type[n]=="SH") {
+			i = which(ID_S == pairs$pairs.from[n])
+			j = which(ID_H == pairs$pairs.to[n])			
+			L_SH[i,j] = nL/nX
+			X_SH[i,j] = nX
+		}
+
+		else {
+			i = which(ID_H == pairs$pairs.from[n])
+			j = which(ID_P == pairs$pairs.to[n])
+			L_HP[i,j] = nL/nX
+			X_HP[i,j] = nX			
+		}
+	}
+	cat(n,'\n')
+}
+
+# Sort the matrices by degree
+d_S = apply(L_SH,1,sum,na.rm=TRUE)
+d_Hi = apply(L_SH,2,sum,na.rm=TRUE)
+d_Hj = apply(L_HP,1,sum,na.rm=TRUE)
[…]

### 2016-05-24 analysis/scripts/results/table_all_models (Conflit de casse).r

@@ -1,0 +1,111 @@
+##################################################################
+# Compute the likelihood for each model and each species pair
+# Record the results in a summary table
+# Dominique Gravel
+##################################################################
+
+rm(list = ls())
+
+# Source the functions
+source("./scripts/functions/species_models.r")
+source("./scripts/functions/interactions_models.r")
+source("./scripts/functions/get_probs.r")
+source("./scripts/functions/get_LL.r")
+source("./scripts/functions/fit_models.r")
+
+# Load & prepare the data
+load("./data/expand_data.Rdata")
+load("./data/DF_split.Rdata")
+load("./data/pairs.Rdata")
+
+IDi = data$pairs.IDi
+IDj = data$pairs.IDj
+Si = length(unique(IDi))
+Sj = length(unique(IDj))
+unique_IDi = unique(IDi)
+unique_IDj = unique(IDj)
+np = length(DF_split)
+type = numeric(np)
+
+# Matrices to store the results
+C2_L0 = matrix(nr = np, nc = 2)
+C2_L1 = matrix(nr = np, nc = 2)
+C2_L2 = matrix(nr = np, nc = 2)
+C0_L2 = matrix(nr = np, nc = 2)
+C1_L2 = matrix(nr = np, nc = 2)
+C3_L2 = matrix(nr = np, nc = 2)
+
+# Loop around all pairs of species
+count = 1
+for(x in 1:np) {
+
+	sub_data = DF_split[[x]]
+
+	IDs = as.matrix(sub_data[1,1:2])
+	test = which(pairs[,2] == as.character(IDs[1]) & pairs[,3]==as.character(IDs[2]) | pairs[,2]==as.character(IDs[2]) & pairs[,3]==as.character(IDs[1]))
+	if(length(test)!=0)	type[x] = unique(as.character(pairs[test,4]))
+	
+	# Compute the models
+	models_C2_L0 = fit_models(sub_data, selection = FALSE, funC = C2, funL = L0)
+	models_C2_L1 = fit_models(sub_data, selection = FALSE, funC = C2, funL = L1)
[…]

### 2016-05-24 analysis/scripts/results/table_all_models.r

@@ -1,0 +1,111 @@
+##################################################################
+# Compute the likelihood for each model and each species pair
+# Record the results in a summary table
+# Dominique Gravel
+##################################################################
+
+rm(list = ls())
+
+# Source the functions
+source("./scripts/functions/species_models.r")
+source("./scripts/functions/interactions_models.r")
+source("./scripts/functions/get_probs.r")
+source("./scripts/functions/get_LL.r")
+source("./scripts/functions/fit_models.r")
+
+# Load & prepare the data
+load("./data/expand_data.Rdata")
+load("./data/DF_split.Rdata")
+load("./data/pairs.Rdata")
+
+IDi = data$pairs.IDi
+IDj = data$pairs.IDj
+Si = length(unique(IDi))
+Sj = length(unique(IDj))
+unique_IDi = unique(IDi)
+unique_IDj = unique(IDj)
+np = length(DF_split)
+type = numeric(np)
+
+# Lists to store the models 
+C2_L0 = matrix(nr = np, nc = 2)
+C2_L1 = matrix(nr = np, nc = 2)
+C2_L2 = matrix(nr = np, nc = 2)
+C0_L2 = matrix(nr = np, nc = 2)
+C1_L2 = matrix(nr = np, nc = 2)
+C3_L2 = matrix(nr = np, nc = 2)
+
+# Loop around all pairs of species
+count = 1
+for(x in 1:np) {
+
+	sub_data = DF_split[[x]]
+
+	IDs = as.matrix(sub_data[1,1:2])
+	test = which(pairs[,2] == as.character(IDs[1]) & pairs[,3]==as.character(IDs[2]) | pairs[,2]==as.character(IDs[2]) & pairs[,3]==as.character(IDs[1]))
+	if(length(test)!=0)	type[x] = unique(as.character(pairs[test,4]))
+	
+	# Compute the models
+	models_C2_L0 = fit_models(sub_data, selection = FALSE, funC = C2, funL = L0)
+	models_C2_L1 = fit_models(sub_data, selection = FALSE, funC = C2, funL = L1)
[…]

### 2016-05-24 analysis/source_all.r

@@ -1,0 +1,17 @@
+# Make sure to have all the required packages
+install.packages(c("igraph", "rgdal", "raster", "sp", "viridis","dismo"))
+
+# init parallel option
+parallel = TRUE
+
+# Process the data
+source("./scripts/data_processing/reformat_salix.r") # Note this one will take a lot of time (few hours)
+source("./scripts/data_processing/split_data.r")
+
+# Get the results
+source("./scripts/results/1_metaweb_sampling.r")
+source("./scripts/results/2_example_pair.r")
+source("./scripts/results/3_map_pair.r")
+source("./scripts/results/4_metaweb_holes.r")
+source("./scripts/results/5_map_all.r")
+source("./scripts/results/table_all_models.r")

### 2016-05-24 analysis/scripts/results/table_all_models (Conflit de casse (4)).r
Double check of the tables

@@ -1,0 +1,110 @@
+##################################################################
+# Compute the likelihood for each model and each species pair
+# Record the results in a summary table
+# Dominique Gravel
+##################################################################
+
+rm(list = ls())
+
+# Source the functions
+source("./scripts/functions/species_models.r")
+source("./scripts/functions/interactions_models.r")
+source("./scripts/functions/get_probs.r")
+source("./scripts/functions/get_LL.r")
+source("./scripts/functions/fit_models.r")
+
+# Load & prepare the data
+load("./data/expand_data.Rdata")
+load("./data/DF_split.Rdata")
+load("./data/pairs.Rdata")
+
+IDi = data$pairs.IDi
+IDj = data$pairs.IDj
+Si = length(unique(IDi))
+Sj = length(unique(IDj))
+unique_IDi = unique(IDi)
+unique_IDj = unique(IDj)
+np = length(DF_split)
+type = numeric(np)
+
+# Matrices to store the results
+C2_L0 = matrix(nr = np, nc = 2)
+C2_L1 = matrix(nr = np, nc = 2)
+C2_L2 = matrix(nr = np, nc = 2)
+C0_L2 = matrix(nr = np, nc = 2)
+C1_L2 = matrix(nr = np, nc = 2)
+C3_L2 = matrix(nr = np, nc = 2)
+
+# Loop around all pairs of species
+count = 1
+for(x in 1:np) {
+
+	sub_data = DF_split[[x]]
+
+	IDs = as.matrix(sub_data[1,1:2])
+	type[x] = unique(as.character(pairs[x,3]))
+	
+	# Compute the models
+	models_C2_L0 = fit_models(sub_data, selection = FALSE, funC = C2, funL = L0)
+	models_C2_L1 = fit_models(sub_data, selection = FALSE, funC = C2, funL = L1)
+	models_C2_L2 = fit_models(sub_data, selection = FALSE, funC = C2, funL = L2)
+	models_C0_L2 = fit_models(sub_data, selection = FALSE, funC = C0, funL = L2)
[…]

### 2016-05-24 analysis/source_all.r

@@ -1,6 +1,3 @@
-# Make sure to have all the required packages
-install.packages(c("igraph", "rgdal", "raster", "sp", "viridis","dismo"))
-
 # init parallel option
 parallel = TRUE
 

### 2016-05-24 ms/ms_probaweb.tex
Ready for submission

--- 2016-05-16 ms/ms_probaweb.tex
@@
 
-\textbf{Title:} Bringing Elton and Grinnell together: a quantitative framework to represent the biogeography of ecological interaction networks
-
-\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Benjamin Baiser$^{3}$, Jennifer A. Dunne$^{4}$, Jens-Peter Kopelke$^{5}$, Neo
-Martinez$^{6}$, Tommi Nyman$^{7}$, Timoth\'ee Poisot$^{2,8}$, Spencer A. Wood$^{9}$, Daniel B. Stouffer$^{10}$, Jason M. Tylianakis$^{10,11}$ Tomas Roslin$^{12}$,\\
-
-1: Canada Research Chair in Integrative Ecology. D\'epartement de
-biologie, Universit\'e de Sherbrooke, 2500 Boulevard l'Universit\'e,
+\textbf{Title:} Bringing Elton and Grinnell together: a quantitative framework
+to represent the biogeography of ecological interaction networks\\
+
+\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Benjamin Baiser$^{3}$, Jennifer
+A. Dunne$^{4}$, Jens-Peter Kopelke$^{5}$, Neo D. Martinez$^{6}$, Tommi
+Nyman$^{7}$, Timothée Poisot$^{2,8}$, Spencer A. Wood$^{9}$, Daniel B.
+Stouffer$^{10}$, Jason M. Tylianakis$^{10,11}$ Tomas Roslin$^{12}$ \\
+
+\textbf{1}: Canada Research Chair in Integrative Ecology. Département de
+biologie, Université de Sherbrooke, 2500 Boulevard l'Université,
 Sherbrooke (Québec). J1K 2R1\\
-
-2: Qu\'ebec Centre for Biodiversity Sciences\\
-
-3: University of Florida, Department of Wildlife Ecology and Conservation, 110 Newins-Ziegler Hall, PO Box 110430, Gainesville, Fl. 32611-0430 \\
-
-4: Santa Fe Institute, 1399 Hyde Park Road, Santa Fe, NM 87501, USA.\\
-
-5: Senckenberg Research Institute and Natural History Museum, Senckenberganlage 25, D-60325 Frankfurt am Main, Germany\\
-
-6: Ecology and Evolutionary Biology Department, University of Arizona, P.O. Box 210088, Tucson, AZ 85721, USA\\
-
-7: University of Eastern Finland, Department of Environmental and Biological Sciences, P.O. Box 111, FI-80101 Joensuu, Finland\\
-
-8: Université de Montréal, Département des Sciences Biologiques, 90 Avenue Vincent d’Indy, Montréal, QC H2V3S9, Canada.\\
-
-9: University of Washington, School of Environmental and Forest Sciences,
+\textbf{2}: Québec Centre for Biodiversity Sciences\\
+\textbf{3}: University of Florida, Department of Wildlife Ecology and Conservation, 110 Newins-Ziegler Hall, PO Box 110430, Gainesville, Fl. 32611-0430 \\
+\textbf{4}: Santa Fe Institute, 1399 Hyde Park Road, Santa Fe, NM 87501, USA.\\
+\textbf{5}: Senckenberg Research Institute and Natural History Museum, Senckenberganlage 25, D-60325 Frankfurt am Main, Germany\\
+\textbf{6}: Ecology and Evolutionary Biology Department, University of Arizona, P.O. Box 210088, Tucson, AZ 85721, USA\\
+\textbf{7}: University of Eastern Finland, Department of Environmental and Biological Sciences, P.O. Box 111, FI-80101 Joensuu, Finland\\
+\textbf{8}: Université de Montréal, Département des Sciences Biologiques, 90 Avenue Vincent d’Indy, Montréal, QC H2V3S9, Canada.\\
+\textbf{9}: University of Washington, School of Environmental and Forest Sciences,
 Box 352100, Seattle, WA 98195, USA\\
-
-10: Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch, New Zealand\\
-
-11: Department of Life Sciences, Imperial College London, Silwood Park Campus, 
+\textbf{10}: Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch, New Zealand\\
+\textbf{11}: Department of Life Sciences, Imperial College London, Silwood Park Campus, 
 Buckhurst Road, Ascot, Berkshire SL5 7PY, United Kingdom\\
-
-12: Department of Ecology, Swedish University of Agricultural Sciences, Box 7044, 750 07 Uppsala, Sweden\\
+\textbf{12}: Department of Ecology, Swedish University of Agricultural Sciences, Box 7044, 750 07 Uppsala, Sweden\\
 
@@
 
-\textbf{Words in the abstract:}
-
-\textbf{Words in the main text:}
-
-\textbf{Words in the legends:}
-
-\textbf{Figures: 6}
-
-\textbf{Tables: 2}
-
-\textbf{References:}
+\textbf{Words in the abstract: 226}
+
+\textbf{Words in the main text: 7043}
+
+\textbf{Words in the legends: 502}
 
@@
 another, but also by the way these interactions vary across time and space.
-Here, we call for an integrated approach in which community structure
-represented as a network of ecological interactions, and show how it
-translates to biogeography questions. We propose that the ecological niche may
-be redefined to encompass the effect of the environment on species
-distribution (the Grinnellian dimension of the niche) and on the ecological
-interactions among them (the Eltonian dimension). Starting from this 
-concept, we develop a quantitative theory to explain turnover of interactions
-in space and time -– \emph{i.e.} a novel approach to interaction distribution
-modelling. We apply this framework to host–parasite interactions across Europe
-and find that two aspects of the environment (temperature and precipitation)
-exert a strong imprint on species co-occurrence, but not on species
-interactions. Even where species co-occur, interaction proves to be stochastic
-rather than deterministic, adding to variation in realized network structure.
-We also find that a large majority of host-parasite pairs are never found
-together, thus precluding any inferences regarding their probability to
-interact. This first attempt to explain variation of network
-structure at large spatial scales opens new perspectives at the interface
-of species distribution modelling and community ecology.
+Here, we call for an integrated approach, adopting the view that community
+structure is best represented as a network of ecological interactions, and
+show how it translates to biogeography questions. We propose that the
+ecological niche should encompass the effect of the environment
+on species distribution (the Grinnellian dimension of the niche) and on the
+ecological interactions among them (the Eltonian dimension). Starting from
+this concept, we develop a quantitative theory to explain turnover of
+interactions in space and time -- \emph{i.e.} a novel approach to interaction
+distribution modelling. We apply this framework to host–parasite interactions
+across Europe and find that two aspects of the environment (temperature and
+precipitation) exert a strong imprint on species co-occurrence, but not on
+species interactions. Even where species co-occur, interaction proves to be
+stochastic rather than deterministic, adding to variation in realized network
+structure. We also find that a large majority of host-parasite pairs are never
+found together, thus precluding any inferences regarding their probability to
+interact. This first attempt to explain variation of network structure at
+large spatial scales opens new perspectives at the interface of species
+distribution modelling and community ecology.
 
@@
 the distribution and abundance of organisms} \citep{Krebs2001}. Despite a
-general consensus on this definition (Scheiner2007), research on variation in
+general consensus on this definition \citep{Scheiner2007a}, research on variation in
 community structure has mostly focused on the spatial and temporal turnover
 of species composition \citep{Anderson2011}, neglecting variation in the way
-species interact with each other, despite accumulating empirical evidence that
+species interact with each other despite accumulating empirical evidence that
 this is a major source of diversity \citep{Poisot2015a}. Given this omission,
@@
 
-Because it is an explicit description of species interactions, network
-approaches offer a convenient representation of communities. Species are
-represented as nodes, so that networks already encompass all the information
-used by current approaches; in addition, interactions are represented by
-links, so that networks provide additional, higher-order information on
-community structure. To date, studies of network diversity have mostly been
-concerned with the distribution of interactions within locations, and less so
-with variation among locations \citep{Dunne2005, Bascompte2007, Ings2007,
-Kefi2012}. There is, however, ample evidence that interaction networks vary in
-space and time \citep{Laliberte2010, Poisot2012, Albouy2014, Poisot2016,
-Trojelsgaard2015}, even though there is no common framework with which to
-generalize these results. Metacommunity theory provides explanations for
-variation in the distribution of the nodes \citep{Gravel2011c, Pillai2011},
-but there is no such explanation to the variation of node and link
-occurrences. Consequently, we urgently need a conceptual framework to
+Network approaches offer a convenient representation of communities because
+they simultaneously account for species composition and their interactions.
+Species are represented as nodes, so that networks already encompass all the
+information used by current approaches; in addition, interactions are
+represented by links, so that networks provide additional, higher-order
+information on community structure. To date, studies of network diversity have
+mostly been concerned with the distribution of interactions within locations,
+and less so with variation among locations \citep{Dunne2006, Bascompte2007,
+Ings2009, Kefi2012}. There is, however, ample evidence that interaction
+networks vary in space and time \citep{Laliberte2010, Poisot2012, Albouy2014,
+Poisot2016, Trojelsgaard2015}, even though there is no common framework with
+which to generalize these results. Metacommunity theory provides explanations
+for variation in the distribution of the nodes \citep{Gravel2011c,
+Pillai2011}, but there is no such explanation to the variation of node and
+link occurrences. Consequently, we urgently need a conceptual framework to
 formalize these observations, as it is the only way towards fulfilling the
@@
 on species distribution and on the ecological interactions among them.
-Starting from this redefined concept, we develop a quantitative theory to
-explain turnover of interactions in space and time. We first present the
-conceptual framework, and then formalize it mathematically, using a
-probabilistic model to represent the sampling of the regional pool of
-interactions. At the level of species pairs, the statistical approach could be
-conceived as an interaction distribution model. At the community level, the
-approach provides a likelihood-based method to compare different hypotheses of
-network turnover. As an illustrative example, we apply this novel framework to
-a large data set on host–parasite interactions across Europe and perform test
-hypotheses underlying variation of species and interactions. The network
-structure changes systematically across the latitudinal gradient, with a peak
-of connectance at intermediate latitudes.
+Building on this concept, we develop a quantitative theory to explain turnover
+of interactions in space and time. We first present the conceptual framework,
+and then formalize it mathematically, using a probabilistic model to represent
+the sampling of the regional pool of interactions. At the level of species
+pairs, the statistical approach could be conceived as an interaction
+distribution model. At the community level, the approach provides a
+likelihood-based method to compare different hypotheses of network turnover.
+As an illustrative example, we apply this novel framework to a large data set
+on host–parasite interactions across Europe and find that two aspects of the
+environment (temperature and precipitation) exert a strong imprint on species
+co-occurrence, but not on species interactions. The network structure changes
+systematically across the latitudinal gradient, with a peak of connectance at
+intermediate latitudes.
 
@@
 problem for a food web is provided in Fig. 1. The regional pool of
-interactions, or \emph{metaweb}, represents potential interactions among all
+interactions, the \emph{metaweb}, represents potential interactions among all
 species that could be found in a given area. In this particular case, there
@@
 
-There are multiple causes of spatial turnover of species co-occurrence. The first
-and most-studied driver is the effect of variation in the abiotic environment
-on species performance. Combined with specific responses in demography, it
-generates variation among sites by selecting the locally fittest species
-\citep{Leibold2004}. Stochasticity plays an additional role, either because
-colonization and extinction events \citep{Hanski1999} are inherently
-unpredictable or because strong non-linear feedbacks in community dynamics
-generate alternative transients and equilibria \citep{Chase2007, Vellend2014}.
-Analyses of community turnover are usually performed with data represented in
-a table with rows corresponding to sites (or measurements) and columns to
-species. Metrics of beta diversity quantify the variance of this community
-data \citep{Legendre2005}. Traditional approaches rely on measures of
-dissimilarity among communities, such as the Jaccard or Bray–Curtis indices.
-More recent approaches decompose total variation of the community data into
-species and site contributions to beta diversity \citep{Legendre2013}, and
-further partition it into dissimilarity due to changes in species richness and
-dissimilarity due to actual species turnover \citep{Baselga2010;
-Carvalho2012}. Even though these methods compare whole lists of species among
-sites or measurements, they remain fundamentally `species-based', since they
-report variation within columns. None of them explicitly considers variation
-of associations (i.e., of pairs or higher-order motifs –
+There are multiple causes of spatial turnover of species co-occurrence. The
+first and most-studied driver is the effect of variation in the abiotic
+environment on species performance. Combined with specific responses in
+demography, it generates variation among sites by selecting the locally
+fittest species \citep{Leibold2004a}. Stochasticity plays an additional role,
+either because colonization and extinction events \citep{Hanski1999} are
+inherently unpredictable or because strong non-linear feedbacks in community
+dynamics generate alternative transients and equilibria \citep{Chase2007,
+Vellend2014}. Analyses of community turnover are usually performed with data
+represented in a table with rows corresponding to sites (or measurements) and
+columns to species. Metrics of beta diversity quantify the variance of this
+community data \citep{Legendre2005}. Traditional approaches rely on measures
+of dissimilarity among communities, such as the Jaccard or Bray–Curtis
+indices. More recent approaches decompose total variation of the community
+data into species and site contributions to beta diversity
+\citep{Legendre2013}, and further partition it into dissimilarity due to
+changes in species richness and dissimilarity due to actual species turnover
+\citep{Baselga2010}. Even though these methods compare whole lists of species
+among sites or measurements, they remain fundamentally "species-based", since
+they report variation within columns. None of them explicitly considers
+variation of associations (i.e., of pairs or higher-order motifs –
 \citealt{Stouffer2007}).
 
-Similarly, we are getting a better understanding of interaction turnover. As
+Similarly, we are now getting a better understanding of interaction turnover. As
 mentioned above, in the network approach to community structure, species and
@@
 environmental conditions allowing a population to establish and persist (see
-also \citealt{Holt2009}). Community turnover arises as a result of successive
+also \citealt{Holt2009a}). Community turnover arises as a result of successive
 replacement of species along an environmental gradient, in agreement with the
@@
 straightforward to put into practice with species distribution models, as it
-maps naturally on available distributional and environmental data. Consequently, a vast array of statistical tools have been developed to
+maps naturally on available distributional and environmental data.
+Consequently, a vast array of statistical tools have been developed to
 implement it (e.g. BIOMOD \citealt{Thuiller2003}, MaxEnt
@@
 range of environmental conditions required for a species to maintain a viable
-population \citep{Pulliam2000, Soberon2007, Boulangeat2012}.
+population \citep{Pulliam2000, Soberon2007}.
 
 Interestingly, the ecological network literature also has its own "niche
-model" to position a species in a community \citep{Williams2000}. The niche of
+model" to position a species in a community \citep{Williams2000a}. The niche of
 a species in this context represents the multidimensional space of all of its
 interactions. Each species is characterized by a niche position, an optimum
-and a range over three to five different niche axes \citep{Williams2000, Eklof2013}.
+and a range over three to five different niche axes \citep{Williams2000a, Eklof2013}.
 The niche model of food web structure and its variants have successfully
@@
 and several attempts have been made to expand and improve it
-\citep{Pulliam2000, Chase2003, Soberon2007, Holt2009, McInerny2012b}.
+\citep{Pulliam2000, Chase2003, Soberon2007, Holt2009a, McInerny2012b}.
 
@@
 Nonetheless, the development of the niche model of food web structure
-\citep{Williams2000} and its parameterization using functional traits
-\citep{Gravel2013; Bartomeus2016} made it more operational.
+\citep{Williams2000a} and its parameterization using functional traits
+\citep{Gravel2013, Bartomeus2016} made it more operational.
 
@@
 \citealt{Chase2003} attempted to reconcile with the following definition:
-"[The niche is] the joint description of the environmental conditions that
+\emph{"[The niche is] the joint description of the environmental conditions that
 allow a species to satisfy its minimum requirements so that the birth rate of
 a local population is equal to or greater than its death rate along with the
-set of per capita effects of that species on these environmental conditions".
+set of per capita effects of that species on these environmental conditions"}.
 Their representation merges zero-net-growth isoclines delimiting the
-Grinnellian niche ("when does the population persists?"") with impact vectors
+Grinnellian niche ("when does the population persists?") with impact vectors
 delimiting the Eltonian niche ("what is the per-capita impact?"). While this
@@
 
-This approach radically changes the representation of the niche, putting species
-distributions and ecological interactions into the same formalism.
-Moreover, it allows the limits of the niche axes to be independent of each other (as in the
-example in Fig. 2), or to interact. For instance, the optimal
+This approach radically changes the representation of the niche, putting
+species distributions and ecological interactions into the same formalism.
+Moreover, it allows the limits of the niche axes to be independent of each
+other (as in the example in Fig. 2), or to interact. For instance, the optimal
 prey size for predatory fishes could decline with increasing temperature
-\citep{Lelong2015}, which would make diet boundaries functions of the
-environment. Alternatively, we could also consider that the growth rate
-of the predator changes with the size of its prey items, thereby altering the
+\citep{Gibert2014}, which would make diet boundaries functions of the
+environment. Alternatively, we could also consider that the growth rate of the
+predator changes with the size of its prey items, thereby altering the
 environmental boundaries.
@@
 independent, and only the marginal occurrence must be accounted for, $P(
-X_{ijy}}|E_y)=P(X_{iy} |E_y)P(X_{jy} |E_y)$.
+X_{ijy}|E_y)=P(X_{iy} |E_y)P(X_{jy} |E_y)$.
 
@@
 interactions such as competition, facilitation, and predation have long been
-studied for their impact on co-distribution (e.g. \citealt{Diamond1976,
-Connor1980, Gotelli2000}). Second- and higher-order interactions (e.g. trophic
+studied for their impact on co-distribution (e.g. \citealt{Diamond1975,
+Connor1979, Gotelli2000}). Second- and higher-order interactions (e.g. trophic
 cascades) could also affect co-occurrence. Co-occurrence of multiple species
@@
 $P(L_{ijy}|X_{ijy}=1) = 1$ and $P(L_{ijy}|X_{ijy}=0) = 0$. This approach might
-be a reasonable approximation if the spatial or temporal scale of sampling and inference is so
-large that the probability of observing at least one interaction converges to
-unity. In this scenario, network variation arises solely from species
-distributions.
+be a reasonable approximation if the spatial or temporal scale of sampling and
+inference is so large that the probability of observing at least one
+interaction converges to unity. In this scenario, network variation arises
+solely from species distributions.
 
@@
 Gray2016}). Effects of the environment on interactions also propagate up the
-community and influence network structure \citep{Tylianakis2007, Woodward2010;
-Petchey2010; Lelong2015}.
+community and influence network structure \citep{Tylianakis2007, Woodward2010,
+Petchey2010a}.
 
@@
 
-Communities of willows, gallers, and parasitoids are species-rich and
-widely distributed, with pronounced variation in community composition across
-space. The genus Salix includes over 400 species, most of which are shrubs or
-small trees \citep{Argus1997}, and is common in most habitats across the
-Northern Hemisphere \citep{Skvortsov1999}. Willows support a highly diverse
-community of herbivorous insects, with one of the main herbivore groups being
-gall-inducing sawflies (Hymenoptera: Tenthredinidae: Nematinae: Euurina
+Communities of willows, gallers, and parasitoids are species-rich and widely
+distributed, with pronounced variation in community composition across space.
+The genus Salix includes over 400 species, most of which are shrubs or small
+trees \citep{Argus1997}, and is common in most habitats across the Northern
+Hemisphere \citep{Skvortsov1999}. Willows support a highly diverse community
+of herbivorous insects, with one of the main herbivore groups being gall-
+inducing sawflies (Hymenoptera: Tenthredinidae: Nematinae: Euurina
 \citep{Kopelke1999}). Gall formation is induced by sawfly females during
@@
 100 species belonging to 17 insect families of four orders
-\citep{Kopelke2000}. These encompass two main types: inquiline larvae
+\citep{Kopelke2003}. These encompass two main types: inquiline larvae
 (Coleoptera, Lepidoptera, Diptera, and Hymenoptera) feed primarily on gall
@@
 trophic levels, phylogeny-based comparative studies have demonstrated that
-galls represent ``extended phenotypes'' of the gallers, meaning that gall form,
+galls represent "extended phenotypes" of the gallers, meaning that gall form,
 location, and chemistry is determined mainly by the galling insects and not by
@@
 associations between parasitoids and hosts \citep{Nyman2007}. Thus, the set of
-parasitoids attacking each host is presumably constrained by the form,
-size, and thickness of its gall.
+parasitoids attacking each host is presumably constrained by the form, size,
+and thickness of its gall.
 
@@
 parasitoids had already emerged from the gall. As a result, the largest taxon
-in the data set, ``Chalcidoidea indeterminate'', represents a superfamily of
+in the data set, "Chalcidoidea indeterminate", represents a superfamily of
 very small parasitoids that are hard to distinguish.
@@
 of illustration, we considered second-order generalized linear models –
-although more flexible fitting algorithms (e.g. GAM or Random Forest)
-could equally well be used, as long as the algorithm can estimate the
-probability for each observation. The data consist of a simple (albeit large
-and full of zeros) table with the observation of each species, $X_{iy}$ and $X_{jy}$,
-their co-occurrence, $X_{ijy}$, the observation of an interaction $L_{ijy}$, and
-environmental co-variates $E_y$. Thus, there is one row per pair of species per
-site. We considered that an absence of a record of an interaction between co-occurring
-species at a site means a true absence (see below for a discussion
-on this issue).
+although more flexible fitting algorithms (e.g. GAM or Random Forest) could
+equally well be used, as long as the algorithm can estimate the probability
+for each observation. The data consist of a simple (albeit large and full of
+zeros) table with the observation of each species, $X_{iy}$ and $X_{jy}$,
+their co-occurrence, $X_{ijy}$, the observation of an interaction $L_{ijy}$,
+and environmental co-variates $E_y$. Thus, there is one row per pair of
+species per site. We considered that an absence of a record of an interaction
+between co-occurring species at a site means a true absence (see below for a
+discussion on this issue).
 
@@
 the two species beyond a joint response to the shared environment
-\citep{Cazelles2015}. Finally, the third model assumes that the probability of
+\citep{Cazelles2016}. Finally, the third model assumes that the probability of
 co-occurrence is independent of the environment and thus constant throughout
@@
 
-We fit the different models to each pair of species and recorded the
-predicted probabilities. The joint probability $P(L_{ijy},X_{iy},X_{jy})$
-was then computed from Eq. 2, and the likelihood of each observation was
-computed as $\mathcal{L}(\theta_{ijy}|D_{ijy})=P(L_{ij},X_{iy},X_{jy})$ if an
-interaction was observed, and as
-$\mathcal{L}(\theta_{ijy}|D_{ijy})=1-P(L_{ijy},X_{iy},X_{jy})$ if no
-interaction was observed. The log-likelihood was summed over the entire
-dataset to compare the different models by AIC. Not surprisingly, there was a
-very large number of species pairs for which this model could not be computed,
-as they simply never co-occurred. For these pairs, we have no information of
-the interaction probability, and they were consequently removed from the
-analysis. The log-likelihood reported across the entire dataset was summed
-over all pairs of species observed to co-occur at least once. Interactions
-between the first (Salix) and second (gallers) trophic layers and those
-between the second and third (parasitoids) were considered separately.
+We fit the different models to each pair of species and recorded the predicted
+probabilities. The joint probability $P(L_{ijy},X_{iy},X_{jy})$ was then
+computed from Eq. 2, and the likelihood of each observation was computed as
+$\mathcal{L}(\theta_{ijy}|D_{ijy})=P(L_{ij},X_{iy},X_{jy})$ if an interaction
+was observed, and as $\mathcal{L}(\theta_{ijy}|D_{ijy}) = 1-P(L_{ijy}, X_{iy},
+X_{jy})$ if no interaction was observed. The log-likelihood was summed over
+the entire dataset to compare the different models by AIC. Not surprisingly,
+there was a very large number of species pairs for which this model could not
+be computed, as they simply never co-occurred. For these pairs, we have no
+information of the interaction probability, and they were consequently removed
+from the analysis. The log-likelihood reported across the entire dataset was
+summed over all pairs of species observed to co- occur at least once.
+Interactions between the first (Salix) and second (gallers) trophic layers and
+those between the second and third (parasitoids) were considered separately.
 Finally, we used the full model (in which both co-occurrence and the
@@
 distributions and interaction probabilities across the entire European
-continent. We reconstructed the expected network for each location in a 1 X
-1 km grid and computed the probabilistic connectance following
-\citep{Poisot2015b}.
-
-All of the data are openly available in the database mangal \citep{Poisot2015c} and
-all R scripts for querying and pre-processing the data, along with the
-analysis, are provided in the Supplementary material.
+continent. We reconstructed the expected network for each location in a 1 X 1
+km grid and computed the probabilistic connectance following
+\citep{Poisot2015c}.
+
+All of the data are openly available in the database \emph{mangal}
+\citep{Poisot2015b} and all R scripts for running the analysis, are provided
+in the Supplementary Material.
 
@@
 probability on local environmental conditions adds no explanatory power beyond
-a model assuming the same probability of interaction anywhere in space(Model 1
+a model assuming the same probability of interaction anywhere in space (Model 1
 vs Model 2). Moreover, when the two species co-occur, the occurrence of the
@@
 We evaluated each model for all pairs of species in order to better understand
-the large-scale drivers of network turnover. The results were highly consistent
-among trophic layers (Salix–gallers and gallers–parasitoids; Table 2). Across
-all pairs of species, the conditional representation of interactions performed
-better than the marginal one (Model 1 vs Model 2); that is, interactions did
-not occur systematically whenever the two species were found co-occurring.
-Hence, in addition to species turnover, the stochastic nature of interactions
-contributes to network variability. In total, we recorded 1,173 pairs of
-interactions, only 290 of which occurred more than five times. Out of these 290
-interactions, 143 were systematically detected whenever the two species co-occurred.
-In the instances when species co-occurred, the two environmental
-variables considered proved relatively poor predictors of their interactions
-(Model 2 vs Model 3). Not surprisingly, for both types of interactions
-(Salix–galler and galler–parasitoid), the likelihood increased when the
-environment was considered. However, the extra number of parameters exceeded the
-gain in likelihood and inflated AIC. Therefore, the most parsimonious model
-excluded the effect of the environment. On the basis of log-likelihoods only,
-co-occurrence was non-neutral for both Salix–galler and
-galler–parasitoid interactions. Thus, according to AIC, the best model was the
-one of non-random co-occurrence (Model 3 vs Model 6) for both types of
-interactions.
+the large-scale drivers of network turnover. The results were highly
+consistent among trophic layers (Salix–gallers and gallers–parasitoids; Table
+2). Across all pairs of species, the conditional representation of
+interactions performed better than the marginal one (Model 1 vs Model 2); that
+is, interactions did not occur systematically whenever the two species were
+found co-occurring. Hence, in addition to species turnover, the stochastic
+nature of interactions contributes to network variability. In total, we
+recorded 1,173 pairs of interactions, only 290 of which occurred more than
+five times. Out of these 290 interactions, 143 were systematically detected
+whenever the two species co-occurred. In the instances when species co-
+occurred, the two environmental variables considered proved relatively poor
+predictors of their interactions (Model 2 vs Model 3). Not surprisingly, for
+both types of interactions (Salix–galler and galler–parasitoid), the log-
+likelihood increased when the environment was considered. However, the extra
+number of parameters exceeded the gain in log-likelihood and inflated AIC.
+Therefore, the most parsimonious model excluded the effect of the environment.
+On the basis of log-likelihood only, co-occurrence was non-neutral for both
+Salix–galler and galler–parasitoid interactions. Thus, according to AIC, the
+best model was the one of non-random co-occurrence (Model 3 vs Model 6) for
+both types of interactions.
 
@@
 and is also a good proxy for many other network properties \citep{Poisot2014}.
-Overall, we find a peak in Salix, gallers and parasitoid diversity in Northern
-Europe. The expected number of interactions roughly follows the distribution
-of species richness, but accumulates at a rate different from species numbers.
-Connectance likewise peaks in Northern Europe (Fig. 6).
+Overall, we found a peak in Salix, gallers and parasitoid diversity in Northern
+Europe. The expected number of interactions roughly followed the distribution
+of species richness, but accumulated at a rate different from species numbers.
+Connectance likewise peaked in Northern Europe (Fig. 6).
 
@@
 We have proposed that the representation of community structure and its
-variation in space and time is best captured by the formalism of
-ecological networks, as both the distribution of species and their
-interspecific interactions can then be accounted for. We consequently revised
-the niche concept in order to integrate its abiotic and biotic
-components that vary over time and space. This
-integrated niche was represented visually with an ordination of species into
-an environmental space and a trait space. The fundamental niche of a species
-is represented as the set of environmental conditions and resources that allow
-a species to establish in a location, thereby integrating the Eltonian and the
-Grinnellian components of the niche. We then translated the concept
-mathematically by investigating the probability of the joint occurrences of
-species and their interaction, which should be interpreted as an interaction
-distribution model. We used this approach to characterize the turnover of the
-structure of ecological interactions in a species-rich tri-trophic network
-across Western Europe, finding that the primary driver of variation is the
-turnover in species composition. To our knowledge, this is the first
-continental-wide analysis of the drivers of network structure from empirical
-data on the occurrence of interactions (see \citealt{Baiser2012,Albouy2014,
-Poisot2016}).
+variation in space and time is best captured by the formalism of ecological
+networks, as both the distribution of species and their interspecific
+interactions can then be accounted for. We consequently revised the niche
+concept in order to integrate its abiotic and biotic components that vary over
+time and space. This integrated niche was represented visually with an
+ordination of species into an environmental space and a trait space. The
+fundamental niche of a species is represented as the set of environmental
+conditions and resources that allow a species to establish in a location,
+thereby integrating the Eltonian and the Grinnellian components of the niche.
+We then translated the concept mathematically by investigating the probability
+of the joint occurrences of species and their interaction, which should be
+interpreted as an interaction distribution model. We used this approach to
+characterize the turnover of the structure of ecological interactions in a
+species-rich tri-trophic network across Western Europe, finding that the
+primary driver of network variation is the turnover in species composition. To
+our knowledge, this is the first continental-wide analysis of the drivers of
+network structure from empirical data on the occurrence of interactions (see
+\citealt{Baiser2012, Albouy2014, Poisot2016}).
 
@@
 common groupd of parasitic wasps, the Ichneumonidae, was originally presumed
-to show a similar ``reversed latitudinal gradient'', but this observation has
+to show a similar "reversed latitudinal gradient", but this observation has
 been recently challenged by findings of rather high ichneumonid diversity in
@@
 occurrence and therefore of potential interactions differed between the first
-and second layers of feeding links. The correlation between expected Salix and gallers
-richness was 0.73, while it was 0.58 between gallers and their parasitoids.
-Therefore, the ratio of herbivores to Salix species is essentially constant
-across Europe, while each herbivore species is potentially attacked by a and
-a lower trophic level at the same site was clearly affected by the richer
-enemy community at higher latitudes. Consequently, overall connectance peaks
-in Northern Europe (Fig. 6).
-
-In terms of species interacting with each other, our analysis suggests that the
-environment leaves a detectable imprint on species co-occurrence, but only a
-slight mark on the occurrence of realized links among species in a specific
+and second layers of feeding links. The correlation between expected Salix and
+gallers richness was 0.73, while it was 0.58 between gallers and their
+parasitoids. Therefore, the ratio of herbivores to Salix species is
+essentially constant across Europe, while each herbivore species is
+potentially attacked by a and a lower trophic level at the same site was
+clearly affected by the richer enemy community at higher latitudes.
+Consequently, overall connectance peaks in Northern Europe (Fig. 6).
+
+In terms of species interacting with each other, our analysis suggests that
+the environment leaves a detectable imprint on species co-occurrence, but only
+a slight mark on the occurrence of realized links among species in a specific
 place: the probability of finding a given combination of species at a higher
@@
 environment, whereas the probability of observing an interaction between the
-two was not detectably so. This applies to the example species \textit{Phyllocolpa
-prussica} and \textit{Chrysocharis elongata} (Figs 2 and 3), but also to all species pairs
-more generally. For the example species pair, the full model revealed that the
-interaction probability peaks at intermediate temperature and
-precipitation, simply because this is where the two species co-occur most
-often. This does not imply that species will always interact when they meet –
-although this is a basic assumption in most documented metawebs to date (e.g.
-\citealt{Havens1992, Wood2015}). Rather, an interaction is a stochastic process whose
-probability is also influenced by the probability with which species co-occur.
-What we cannot reliably know is how this stochasticity splits into two
-sampling processes – i.e., the extent to which a species at the higher trophic
-level runs into a species at the lower level co-occurring at the site, and the
-extent to which this interaction is detected by an observer collecting a
-finite sample. Future work will be required to document the relative
-importance of these two sources of uncertainty in the occurrence of
-interactions.
+two was not detectably so. This applies to the example species
+\textit{Phyllocolpa prussica} and \textit{Chrysocharis elongata} (Figs 2 and
+3), but also to all species pairs more generally. For the example species
+pair, the full model revealed that the interaction probability peaks at
+intermediate temperature and precipitation, simply because this is where the
+two species co-occur most often. This does not imply that species will always
+interact when they meet – although this is a basic assumption in most
+documented metawebs to date (e.g. \citealt{Havens1992, Wood2015}). Rather, an
+interaction is a stochastic process whose probability is also influenced by
+the probability with which species co-occur. What we cannot reliably know is
+how this stochasticity splits into two sampling processes – i.e., the extent
+to which a species at the higher trophic level runs into a species at the
+lower level co-occurring at the site, and the extent to which this interaction
+is detected by an observer collecting a finite sample. Future work will be
+required to document the relative importance of these two sources of
+uncertainty in the occurrence of interactions.
 
@@
 Evidence that the structure of ecological networks does vary across habitats
-(e.g. \citealt{Tylianakis2007, Plein2012}), over environmental gradients
-\citealt{Lurgi2010} and in time \citep{Trolsgaard2015} is accumulating
+(e.g. \citealt{Tylianakis2007}), over environmental gradients
+\citealt{Lurgi2012} and in time \citep{Trojelsgaard2015} is accumulating
 rapidly. It is not clear, however, to what extent the turnover of network
@@
 vary with the environment in other systems, for instance, herbivory
-\citep{Shurin2012} and predation \citep{McKinnon2010, Legagneux2014} are often
+\citep{Shurin2012} and predation \citep{Mckinnon2010,Legagneux2014} are often
 found to increase with temperature, resulting in spatial variation of trophic
-cascades \citep{(Gray2016}. What remains unclear, however, is the extent to
+cascades \citep{Gray2016}. What remains unclear, however, is the extent to
 which such variation is driven by a turnover of species composition along
@@
 trophic regulation influences community dynamics and ecosystem functioning
-\citep{Harfoot2013}.
+\citep{Harfoot2014}.
 
@@
 the local scale can affect our understanding of network structure is well
-documented \citep{Martinez1999}. However, in a spatial context, some
+documented \citep{Martinez1999}. In a spatial context, however, some
 interactions may be undocumented simply because the species involved have
@@
 can be set as a threshold above which a species pair has finally been observed
-"often enough". this will allow us to deal with both confirmed absences of
+"often enough". This will allow us to deal with both confirmed absences of
 interactions and mere absence of evidence.
@@
 
-Understanding the drivers of spatial variation in network structure is a
-key problem to solve in order to anticipate the impacts of global changes on
-biodiversity. Our representation of spatial variation of community
-structure presents a new approach for the study of the biogeography of ecological
-networks. We see the following key challenges and opportunities ahead in this
-exciting area of research:
+Our representation of spatial variation of community structure presents a new
+approach for the study of the biogeography of ecological networks. We see the
+following key challenges and opportunities ahead in this exciting area of
+research:
 
@@
 interaction probabilities, as well as estimators? of the frequency of false
-absences. Bayesian methods are promising to that end, because we could use
+absences. Bayesian methods are promising to that end because we could use
 information on the target species (e.g. if they are known as specialists or
@@
 
-\textbf{3. From interaction probabilities to a distribution of network properties}.
-Metrics are available to analyze the structure of probabilistic networks
-\citep{Poisot2015c}. These metrics are useful as first approximation, but they
-assume independence among interactions. This might not be the case in nature
-because of the role of co-occurrence and shared environmental requirements. We
-also need to better understand the distribution of network properties arising
-from probabilistic interactions.
-
-\textbf{4. Investigation of the environmental-dependence of ecological interactions}.
-There is evidence that interactions can vary in space, but this problem has
-not been investigated in a systematic fashion. The paucity of currently available data
-precludes an extensive analysis of this question at present.
+\textbf{3. From interaction probabilities to a distribution of network
+properties}. Metrics are available to analyze the structure of probabilistic
+networks \citep{Poisot2015c}. These metrics are useful as first approximation,
+but they assume independence among interactions. This might not be the case in
+nature because of the role of co-occurrence and shared environmental
+requirements. We also need to better understand the distribution of network
+properties arising from probabilistic interactions.
+
+\textbf{4. Investigation of the environmental-dependence of ecological
+interactions}. There is evidence that interactions can vary in space, but this
+problem has not been investigated in a systematic fashion. The paucity of
+currently available data precludes an extensive analysis of this question at
+present.
 
@@
 prove critical in the future, especially given the interest in using co-
-occurrence to infer ecological interactions \citep{Morales2015, Morueta-
-Holme2016}.
+occurrence to infer ecological interactions \citep{Morales-Castilla2015,
+Morueta-Holme2016}.
 
@@
 \caption{Summary of model comparison for the interaction between the leaf
-galler \textit{Phyllocolpa prussica}) and the parasitoid \textit{Chrysocharis
+folder \textit{Phyllocolpa prussica}) and the parasitoid \textit{Chrysocharis
 elongata}}
@@
 	\# & Metaweb model 						& Co-occurrence model 			& LL 	& npars & AIC \\ \hline
-	1 & $P(L_{ijy})$ 						& $P(X_{iy},X_{jy}|E_y)$ 		& -65.5 & 6 	& 143 \\
+	1 & $P(L_{ijy})$ 						& $P(X_{iy},X_{jy}|E_y)$ 		& -71.1 & 6 	& 154.2 \\
 	2 & $P(L_{ijy} | X_{iy}, X_{jy})$ 		& $P(X_{iy},X_{jy}|E_y)$ 		& -65.7 & 6 	& 143.4 \\
@@
 	6 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}|E_y)P(X_{jy}|E_y)$ 	& -68.8 & 15 	& 167.6 \\
-\hline
 \end{tabular}
@@
 	Interaction & \# & Metaweb model & Co-occurrence model & LL & npars & AIC \\ \hline
-	Plant-Galler & 1 & $P(L_{ijy})$ & $P(X_{iy},X_{jy}|E_y)$ & -6137.8 & 7170 & 26615.6 \\
-	 & 2 & $P(L_{ijy}|X_{iy},X_{jy})$ & $P(X_{iy},X_{jy}|E_y)$ & -5947.2 & 7170 & 26234.3 \\
-	 & 3 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy}|E_y)$ & -5939.8 & 11950 & 35779.6 \\
-	 & 4 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy})$ & -7871.9 & 8365 & 32473.8 \\
-	 & 5 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})(X_{jy})$ & -6639.9 & 7170 & 27619.9 \\
-	 & 6 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}|E_y)P(X_{jy}|E_y)$ & -7123.2 & 17925 & 50096.4 \\ \hline
-	Galler-Parasitoid & 1 & $P(L_{ijy})$ & $P(X_{iy},X_{jy}|E_y)$ & -21397.6 & 18846 & 81963.1 \\
-	 & 2 & $P(L_{ijy} | X_{iy}, X_{jy})$ & $P(X_{iy},X_{jy}|E_y)$ & -21105.2 & 18846 & 81378.5 \\
-	 & 3 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy}|E_y)$ & -20881.1 & 31410 & 107042.1 \\
-	 & 4 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy})$ & -23728.3 & 21987 & 93152.6 \\
-	 & 5 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})P(X_{jy})$ & -23509.4 & 18846 & 86186.8 \\
-	 & 6 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}|E_y)P(X_{jy}|E_y)$ & -20990 & 47115 & 139900.1 \\
+	Salix-Galler & 1 & $P(L_{ijy})$ & $P(X_{iy},X_{jy}|E_y)$ & -6022.1 & 7548 & 27140.3 \\
+	 & 2 & $P(L_{ijy}|X_{iy},X_{jy})$ & $P(X_{iy},X_{jy}|E_y)$ & -5547.9 & 7548 & 26191.8 \\
+	 & 3 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy}|E_y)$ & -5364.0 & 12580 & 35888.0 \\
+	 & 4 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy})$ & -5998.4 & 8806 & 30287.2 \\
+	 & 5 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})(X_{jy})$ & -6636.1 & 7548 & 27092.7 \\
+	 & 6 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}|E_y)P(X_{jy}|E_y)$ & -6002.9 & 18870 & 49745.7 \\ \hline
+	Galler-Parasitoid & 1 & $P(L_{ijy})$ & $P(X_{iy},X_{jy}|E_y)$ & -22068.1 & 19206 & 82548.2 \\
+	 & 2 & $P(L_{ijy} | X_{iy}, X_{jy})$ & $P(X_{iy},X_{jy}|E_y)$ & -19504.8 & 19206 & 77421.6 \\
+	 & 3 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy}|E_y)$ & -20217.0 & 32010 & 104454.1 \\
+	 & 4 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy})$ & -19591.3 & 22407 & 77594.5 \\
+	 & 5 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})P(X_{jy})$ & -22491.5 & 19206 & 89796.9 \\
+	 & 6 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}|E_y)P(X_{jy}|E_y)$ & -18936.9 & 48015 & 133903.7 \\
 \hline
@@
 (indicated by colored nodes) are sampled first, and among the species found in
-the local network, only some interactions (indicated by colored links) occur.
+the local network, only some interactions (indicated by blue links) occur.
 We characterize these sampling processes with the quantitative framework
@@
 niche is considered the set of environmental conditions where the intrinsic
-growth rate $r$ is positive \citep{Holt2009}. The horizontal axis represents
+growth rate $r$ is positive \citep{Holt2009a}. The horizontal axis represents
 an environmental gradient impacting the growth of the focal species (in red).
@@
 \begin{figure}[ht!]
-\centering\includegraphics[width=0.5\textwidth]{figures/metaweb_sampling}
+\centering\includegraphics[width=0.4\textwidth]{figures/mw_sampling}
 \end{figure}

### 2018-03-20 ms/ms_probaweb.tex
Authorship
Revisions for Ecography

@@
 \usepackage{pdflscape}
+\usepackage{hyperref}
 
@@
 A. Dunne$^{4}$, Jens-Peter Kopelke$^{5}$, Neo D. Martinez$^{6}$, Tommi
-Nyman$^{7}$, Timothée Poisot$^{2,8}$, Spencer A. Wood$^{9}$, Daniel B.
-Stouffer$^{10}$, Jason M. Tylianakis$^{10,11}$ Tomas Roslin$^{12}$ \\
+Nyman$^{7}$, Timothée Poisot$^{2,8}$, Daniel B.
+Stouffer$^{9}$, Jason M. Tylianakis$^{9,10}$, Spencer A. Wood$^{11}$, Tomas Roslin$^{12}$ \\
 
@@
 Sherbrooke (Québec). J1K 2R1\\
-\textbf{2}: Québec Centre for Biodiversity Sciences\\
+\textbf{2}: Québec Centre for Biodiversity Science\\
 \textbf{3}: University of Florida, Department of Wildlife Ecology and Conservation, 110 Newins-Ziegler Hall, PO Box 110430, Gainesville, Fl. 32611-0430 \\
@@
 \textbf{8}: Université de Montréal, Département des Sciences Biologiques, 90 Avenue Vincent d’Indy, Montréal, QC H2V3S9, Canada.\\
-\textbf{9}: University of Washington, School of Environmental and Forest Sciences,
+\textbf{9}: Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch, New Zealand\\
+\textbf{10}: Department of Life Sciences, Imperial College London, Silwood Park Campus, 
+Buckhurst Road, Ascot, Berkshire SL5 7PY, United Kingdom\\
+\textbf{11}: University of Washington, School of Environmental and Forest Sciences,
 Box 352100, Seattle, WA 98195, USA\\
-\textbf{10}: Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch, New Zealand\\
-\textbf{11}: Department of Life Sciences, Imperial College London, Silwood Park Campus, 
-Buckhurst Road, Ascot, Berkshire SL5 7PY, United Kingdom\\
 \textbf{12}: Department of Ecology, Swedish University of Agricultural Sciences, Box 7044, 750 07 Uppsala, Sweden\\
@@
 \textbf{Keywords:} networks, spatial ecology, co-occurrence, probability of interaction\\
-
-\textbf{Words in the abstract: 226}
-
-\textbf{Words in the main text: 7043}
-
-\textbf{Words in the legends: 502}
+%\textbf{Words in the abstract: 226} \\ 
+%\textbf{Words in the main text: 7043} \\
+%\textbf{Words in the legends: 502} \\
+
+Authorship: DG, BB, JAD, NDM, TP, SAW, DBS and JMT contributed to the
+concepts; JPK, TN and TR contributed the data; DG developped the probabilistic
+approach and performed the analysis; DG, TP and TR wroted the first draft and
+all of the authors edited the manuscript.
 
@@
 
-Community ecology is \textit{the study of the interactions that determine
-the distribution and abundance of organisms} \citep{Krebs2001}. Despite a
-general consensus on this definition \citep{Scheiner2007a}, research on variation in
-community structure has mostly focused on the spatial and temporal turnover
-of species composition \citep{Anderson2011}, neglecting variation in the way
-species interact with each other despite accumulating empirical evidence that
-this is a major source of diversity \citep{Poisot2015a}. Given this omission,
-it is perhaps not surprising that biogeographers are still struggling to
-establish whether interactions actually impact the distribution of species at
-large spatial scales \citep{Wisz2012, Kissling2012}: treating interactions
-as fixed events neglects a large part of the complexity of empirical
-communities, and will most likely deliver underwhelming results. Recent
-attempts at accounting for interactions in species distribution models
-\citep{Pollock2014, Pelissier2013} have brought some methodological advances,
-but are not sufficient for two reasons. First, these techniques are still
-based on a `species-based' approach to communities, where interactions
-are merely treated as fixed covariates affecting distribution. Second,
-they failed to provide a conceptual step forward, both in their treatment
-of interactions and in the quality of the predictions they make.
+Community ecology is \textit{the study of the interactions that determine the
+distribution and abundance of organisms} \citep{Krebs2001}. Despite a general
+consensus on this definition \citep{Scheiner2007a}, research on variation in
+community structure (beta-diversity) has mostly focused on the spatial and
+temporal turnover of species composition \citep{Anderson2011}. Such research
+usually neglects variation in the way species interact with each other,
+despite accumulating empirical evidence that this is a major source of
+diversity \citep{Poisot2015a}. Given this omission, it is perhaps not
+surprising that biogeographers are still struggling to establish whether
+interactions actually impact the distribution of species at large spatial
+scales \citep{Kissling2012}. An interaction is conceived as the direct effect
+of the action of one species on the demography on another species; whether it
+scales up and impact the (co-)distribution of species remains matter of debate
+at the moment \citep{Wisz2012, GonzalezSalazar2013, Cazelles2016b,
+Harris2016, Godsoe2017}. Treating interactions as fixed events nonetheless
+neglects a large part of the complexity of empirical communities, and will
+most likely deliver underwhelming results \citep{Poisot2015c}. Recent attempts
+at accounting for interactions in species distribution models
+\citep{Pollock2014, Pelissier2013, Ovaskainen2017} have brought some
+methodological advances, but are not sufficient for two reasons. First, these
+techniques are still based on a `species-based' approach to communities, where
+interactions are merely treated as fixed covariates affecting distribution.
+Second, they failed to provide a conceptual step forward, both in their
+treatment of interactions and in the quality of the predictions they make.
 
@@
 Species are represented as nodes, so that networks already encompass all the
-information used by current approaches; in addition, interactions are
-represented by links, so that networks provide additional, higher-order
-information on community structure. To date, studies of network diversity have
-mostly been concerned with the distribution of interactions within locations,
-and less so with variation among locations \citep{Dunne2006, Bascompte2007,
-Ings2009, Kefi2012}. There is, however, ample evidence that interaction
-networks vary in space and time \citep{Laliberte2010, Poisot2012, Albouy2014,
-Poisot2016, Trojelsgaard2015}, even though there is no common framework with
-which to generalize these results. Metacommunity theory provides explanations
-for variation in the distribution of the nodes \citep{Gravel2011c,
-Pillai2011}, but there is no such explanation to the variation of node and
-link occurrences. Consequently, we urgently need a conceptual framework to
+information used by current approaches of species distribution modelling; in
+addition, interactions are represented by links, so that networks provide
+additional information on community structure. To date, studies of network
+diversity have mostly been concerned with the distribution of interactions
+within locations, and less so with variation among locations \citep{Dunne2006,
+Bascompte2007, Ings2009, Kefi2012}. There is, however, ample evidence that
+interaction networks vary in space and, time \citep{Laliberte2010, Poisot2012,
+Schleuning2012, Albouy2014, Poisot2016, Trojelsgaard2015}, even though there
+is no common framework with which to generalize these results. Metacommunity
+theory provides explanations for variation in the distribution of the nodes
+\citep{Gravel2011c, Pillai2011,Cazelles2015}, but there is no such explanation
+to the variation of node and link occurrences. Consequently, we need theory to
 formalize these observations, as it is the only way towards fulfilling the
@@
 Given the historically different approaches to modelling the distributions of
-species vs. interactions, there is a clear need to bring the two together.
-Here, we offer an integrated approach to do so, adopting the view that
-community structure is best represented as a network of ecological
-interactions. Based on this idea, we propose a new description of the basic
-concept of the ecological niche that integrates the effect of the environment
-on species distribution and on the ecological interactions among them.
-Building on this concept, we develop a quantitative theory to explain turnover
-of interactions in space and time. We first present the conceptual framework,
-and then formalize it mathematically, using a probabilistic model to represent
-the sampling of the regional pool of interactions. At the level of species
-pairs, the statistical approach could be conceived as an interaction
-distribution model. At the community level, the approach provides a
-likelihood-based method to compare different hypotheses of network turnover.
-As an illustrative example, we apply this novel framework to a large data set
-on host–parasite interactions across Europe and find that two aspects of the
-environment (temperature and precipitation) exert a strong imprint on species
-co-occurrence, but not on species interactions. The network structure changes
-systematically across the latitudinal gradient, with a peak of connectance at
-intermediate latitudes.
+species vs. interactions, there is need to bring the two together. Here, we
+offer an integrated approach to do so, adopting the view that community
+structure is best represented as a network of ecological interactions. Based
+on this idea, we propose a description of the ecological niche that
+integrates the effect of the environment on species distribution and on the
+ecological interactions among them. Building on this concept, we develop a
+quantitative theory to explain turnover of interactions in space and time. We
+first present the concept and then formalize it mathematically, using a
+probabilistic model to represent the sampling of the regional pool of
+interactions. At the level of species pairs, the statistical approach could be
+conceived as an interaction distribution model. At the community level, the
+approach provides a likelihood-based method to compare different hypotheses of
+network turnover. As an illustrative example, we apply this novel framework to
+a large data set on host–parasite interactions across Europe and find that two
+aspects of the environment (temperature and precipitation) exert a strong
+imprint on species co-occurrence, but not on species interactions. The network
+structure changes systematically across the latitudinal gradient, with a peak
+of connectance at intermediate latitudes.
 
@@
 55.0\% of all potential interactions (plant-herbivore or herbivore parasitoid
-combinations) are realized locally, revealing the stochastic nature of
-ecological interactions. Our objective here is to provide a conceptual
-framework to explain the sampling of the regional pool of interactions, along
-with a quantitative method to predict it. The problem could be formalized
+combinations) are realized in this local network, revealing the stochastic
+nature of ecological interactions. Our objective here is to provide theory to
+explain the sampling of the regional pool of interactions, along with a
+quantitative method to predict it. The problem could be formalized
 sequentially by understanding first why only a fraction of the species co-
@@
 dynamics generate alternative transients and equilibria \citep{Chase2007,
-Vellend2014}. Analyses of community turnover are usually performed with data
-represented in a table with rows corresponding to sites (or measurements) and
-columns to species. Metrics of beta diversity quantify the variance of this
-community data \citep{Legendre2005}. Traditional approaches rely on measures
-of dissimilarity among communities, such as the Jaccard or Bray–Curtis
-indices. More recent approaches decompose total variation of the community
-data into species and site contributions to beta diversity
-\citep{Legendre2013}, and further partition it into dissimilarity due to
-changes in species richness and dissimilarity due to actual species turnover
-\citep{Baselga2010}. Even though these methods compare whole lists of species
-among sites or measurements, they remain fundamentally "species-based", since
-they report variation within columns. None of them explicitly considers
-variation of associations (i.e., of pairs or higher-order motifs –
-\citealt{Stouffer2007}).
+Vellend2014}. Interaction themselves may impact co-distribution, as
+hypothesized long ago by Diamond \citet{Diamond1975}. Analyses of community
+turnover are usually performed with data represented in a table with rows
+corresponding to sites (or measurements) and columns to species. Metrics of
+beta diversity quantify the variance of this community data
+\citep{Legendre2005}. Traditional approaches rely on measures of dissimilarity
+among communities, such as the Jaccard or Bray–Curtis indices. More recent
+approaches decompose total variation of the community data into species and
+site contributions to beta diversity \citep{Legendre2013}, and further
+partition it into dissimilarity due to changes in species richness and
+dissimilarity due to actual species turnover \citep{Baselga2010}. T Even
+though all of these methods compare whole lists of species among sites or
+measurements, they remain fundamentally "species-based", since they report
+variation within columns. None of them explicitly considers variation of
+associations (i.e., of pairs or higher-order motifs – \citealt{Stouffer2007}).
+The only exceptions are the Joint Species Distribution Models
+\citep{Warton2015, Ovaskainen2017}, which further account for the covariance
+among species after representing their response to the environment.
 
@@
 of interactions could vary because of the environment, species abundance, and
-higher-order interactions \citep{Poisot2015a}. Variation in community
+higher-order ecological interactions \citep{Poisot2015a}. Variation in community
 composition can be independent of variation of ecological
@@
 environmental conditions allowing a population to establish and persist (see
-also \citealt{Holt2009a}). Community turnover arises as a result of successive
-replacement of species along an environmental gradient, in agreement with the
-Gleasonian view of communities \citep{Gleason1926}. The concept is
-straightforward to put into practice with species distribution models, as it
-maps naturally on available distributional and environmental data.
-Consequently, a vast array of statistical tools have been developed to
+also \citealt{Holt2009a}). In other words, the niche is the location in that
+multidimensional space that allow a species to have a positive growth rate
+when rare \citep{Godsoe2017}.  Community turnover arises as a result of
+successive replacement of species along an environmental gradient, in
+agreement with the Gleasonian view of communities \citep{Gleason1926}. The
+concept is straightforward to put into practice with species distribution
+models, as it maps naturally on available distributional and environmental
+data. Consequently, a vast array of statistical tools have been developed to
 implement it (e.g. BIOMOD \citealt{Thuiller2003}, MaxEnt
@@
 
-Interestingly, the ecological network literature also has its own "niche
-model" to position a species in a community \citep{Williams2000a}. The niche of
-a species in this context represents the multidimensional space of all of its
+Interestingly, the food web literature also has its own "niche model" to
+position a species in a community \citep{Williams2000a}, generalized later to
+other types of interaction networks \citep{Eklof2013}. The niche of a species
+in this context represents the multidimensional space of all of its
 interactions. Each species is characterized by a niche position, an optimum
-and a range over three to five different niche axes \citep{Williams2000a, Eklof2013}.
-The niche model of food web structure and its variants have successfully
-explained the complexity of a variety of networks, from food webs to
-plant–pollinator systems \citep{Allesina2008, Williams2010, Eklof2013}. This
-conceptual framework is, however, limited to local communities, and does not
-provide any explanation for the turnover of network structure along
+and a range over three to five different niche axes \citep{Williams2000a,
+Eklof2013}. The niche model of food web structure and its variants have
+successfully explained the complexity of a variety of networks, from food webs
+to plant–pollinator systems \citep{Allesina2008, Williams2010, Eklof2013}.
+This conceptual framework is, however, limited to local communities, and does
+not provide any explanation for the turnover of network structure along
 environmental gradients.
@@
 distinction between Eltonian and Grinnellian definitions \citep{Chase2003}.
-The Grinnellian dimension of the niche is the set of environmental conditions
+The Grinnellian dimension of the niche is the set of abiotic environmental conditions
 required for a species to maintain a population in a location. The Grinnellian
 niche is intuitive to apply, and constitutes the conceptual backbone of
-species distribution models. The Eltonian niche, on the other hand, is the
-effect of a species on its environment. While this aspect of the niche is well
-known by community ecologists, it is trickier to turn into predictive models.
-Nonetheless, the development of the niche model of food web structure
-\citep{Williams2000a} and its parameterization using functional traits
-\citep{Gravel2013, Bartomeus2016} made it more operational.
+species distribution models. The Eltonian niche, on the other hand, is 'the
+place of a species in its biotic environment, its relations to food and
+enemies'. While this aspect of the niche is well known by community
+ecologists, it is trickier to turn into predictive models. Nonetheless, the
+development of the niche model of food web structure \citep{Williams2000a} and
+its parameterization using functional traits \citep{Gravel2013, Bartomeus2016}
+made it more operational.
 
@@
 performance of an organism. Alternatively, the resource axes are traits of the
-resources that allow interactions with the consumer. The niche can therefore
-be viewed as the set of abiotic environmental variables (the Grinnellian
-component) along with the set of traits (the Eltonian component) that allow a
-population to establish and to persist at a location. Accordingly, each
+resources that allow interactions with the consumers. By definition of what an
+interaction is, these axes also influence the growth rate. The niche can
+therefore be viewed as the set of abiotic environmental conditions (the
+Grinnellian component) along with the set of traits (the Eltonian component)
+that allow a population to establish and to grow at a location. This visual
+representation make operational the theoretical interpretation of the niche
+and species ranges by Godsoe et al. \citealt{Godsoe2017}. Accordingly, each
 species can be characterized by an optimal position along both the
 environmental (x-axis) and the trait (y-axis) plane. The integrated niche is
-then the hypervolume where interactions can occur and sustain a population.
-
-This approach radically changes the representation of the niche, putting
-species distributions and ecological interactions into the same formalism.
-Moreover, it allows the limits of the niche axes to be independent of each
-other (as in the example in Fig. 2), or to interact. For instance, the optimal
-prey size for predatory fishes could decline with increasing temperature
-\citep{Gibert2014}, which would make diet boundaries functions of the
-environment. Alternatively, we could also consider that the growth rate of the
-predator changes with the size of its prey items, thereby altering the
-environmental boundaries.
+then the hypervolume where interactions can occur and where a population has a
+positive growth rate.
+
+This approach changes the representation of the niche, putting species
+distributions and ecological interactions into the same formalism. Moreover,
+it allows the limits of the niche axes to be independent of each other (as in
+the example in Fig. 2), or to interact.  Some of these axes may not be
+independent. For instance, the optimal prey size for predatory fishes could
+decline with increasing temperature \citep{Gibert2014}, which would make diet
+boundaries functions of the environment. Alternatively, we could also consider
+that the growth rate of the predator changes with the size of its prey items,
+thereby altering the environmental boundaries and changing the shape of the
+niche in the middle of this visual representation. It is also important that
+this conceptual representation depicts a reality that could be highly
+dimensional and sometimes difficult to represent statistically
+\citep{Clark2007}.
 
@@
 probability that an interaction between species $i$ and $j$ occurs at location
-$y$. We define $L_{ijy}$ as a stochastic variable, and focus on the
-probability that this event occurs, $P(L_{ijy})$. We note that the occurrence
-of an interaction is dependent on the co-occurrence of species $i$ and $j$.
-This argument might seem trivial at first, but the explicit consideration of
-this condition in the probabilistic representation of ecological interactions
-will prove instrumental to understanding their variation. We define $X_{iy}$
-as a stochastic variable representing the occurrence of species $i$ at
-location $y$. The quantity we seek to understand is the probability of a joint
+$y$. We define $L_{ijy}$ as a stochastic process taking a value of 1 when an
+interaction occurs and a value of 0 when it does not, and focus on the
+probability that this event occurs, $P(L_{ijy} = 1)$, over a given sampling
+interval and space. We note that the occurrence of an interaction is dependent
+on the co-occurrence of species $i$ and $j$. This argument might seem trivial
+at first, but the explicit consideration of this condition in the
+probabilistic representation of ecological interactions will prove
+instrumental to understanding their variation. We note this phenomenon we aim
+to describe differs fundamentally from the effect that interactions do have on
+co-occurrence \citep{Cazelles2016}. We similarly define $X_{iy}$ as a
+stochastic process representing the occurrence of species $i$ at location
+$y$, taking a value of 1 when the species occurs and a value of 0 when it is
+absent. The quantity we seek to understand is the probability of a joint
 event, conditional on the set of environmental conditions $E_y$:
@@
 There are several variants to the co-occurrence probability, representing
-different hypotheses concerning temporal and spatial variation in network structure
-(see the explicit formulations in Table 1). The simplest model relates the
-probability of co-occurrence directly to the environment, $P(X_{iy},X_{jy}|E_y)$.
-In this situation, there are no underlying assumptions about the ecological
-processes responsible for co-occurrence. It could arise because interactions
-constrain distribution \citep{Pollock2014, Cazelles2016} or,
-alternatively, because of environmental requirements shared between $i$ and
-$j$. In the former case, species are not independent of each other and the
-conditional occurrence must be accounted for explicitly, $P(X_{iy},X_{jy}
-|E_y)=P(X_{iy}|E_y,X_{jy})P(X_{jy}|E_y)$. In the latter case, species are
-independent, and only the marginal occurrence must be accounted for, $P(
-X_{ijy}|E_y)=P(X_{iy} |E_y)P(X_{jy} |E_y)$.
+different hypotheses concerning spatial variation in network structure (see
+the explicit formulations in Table 1). The simplest model relates the
+probability of co-occurrence directly to the environment,
+$P(X_{iy},X_{jy}|E_y)$. In this situation, there are no underlying assumptions
+about the ecological processes responsible for co-occurrence. It could arise
+because interactions constrain distribution, where in such case the co-
+occurrence would be conditional on $L$, or, alternatively, because of
+environmental requirements shared between $i$ and $j$ \citep{Pollock2014,
+Cazelles2016}. In the former case, species are not independent of each other
+and the conditional occurrence must be accounted for explicitly,
+$P(X_{iy},X_{jy} |E_y)=P(X_{iy}|E_y,X_{jy})P(X_{jy}|E_y)$. In the latter case,
+species are independent, and only the marginal occurrence must be accounted
+for, $P( X_{ijy}|E_y)=P(X_{iy} |E_y)P(X_{jy} |E_y)$.
 
@@
 Connor1979, Gotelli2000}). Second- and higher-order interactions (e.g. trophic
-cascades) could also affect co-occurrence. Co-occurrence of multiple species
-embedded in ecological networks is a topic of its own, however, and is
-influenced by both network topology and species richness \citep{Cazelles2016}.
-Not only direct interactions influence co-occurrence, but indirect
-interactions do as well (e.g. plant species sharing an herbivore, or
-herbivores sharing parasitoids, could repel each other in space
-\citealt{Holt1993}). The impact of direct interactions and first-order
-indirect interactions on co-occurrence tends to vanish with increasing species
-richness in the community. Further, co-occurrence is also influenced by the
-covariance of interacting species to an environmental gradient
-\citep{Cazelles2015}. Because of the complexity of relating co-occurrence to
-the structure of interaction networks, we will focus here on the variation of
-interactions and not on their distribution, and leave this specific issue for
-the Perspectives section and future research.
+cascades) could also affect co-occurrence \citep{Harris2017,
+Staniczenko2017}. Co-occurrence of multiple species embedded in ecological
+networks is a topic of its own, however, and is influenced by both network
+topology and species richness \citep{Cazelles2016}. Not only direct
+interactions influence co-occurrence, but indirect interactions do as well
+(e.g. plant species sharing an herbivore, or herbivores sharing parasitoids,
+could repel each other in space \citealt{Holt1993}). The impact of direct
+interactions and first-order indirect interactions on co-occurrence tends to
+vanish with increasing species richness in the community \citep{Cazelles2016}.
+Further, co-occurrence is also influenced by the covariance of interacting
+species to an environmental gradient \citep{Cazelles2015}.
+
+The interpretation that interactions may impact co-occurrence, and that the
+realization of an interaction requires co-occurrence are not mutually
+exclusive. But since here the object is to describe the variation in the
+occurrence of interactions, which absolutely requires co-occurrence, we will
+give attention to this part of the problem. Relating co-occurrence to the
+structure of interaction networks is a problem on its own (and vice-versa). We
+will therefore focus here on the variation of interactions and not on their
+distribution, and leave this specific issue for the Perspectives section and
+future research.
 
@@
 Second, ecological interactions could also vary with the environment, so that
-$P(L_{ijy} |E_y)$. Although it is rare to see a conditional representation of
+$P(L_{ijy}|E_y)$. Although it is rare to see a conditional representation of
 pairwise ecological interactions, experimental studies have frequently
@@
 to see increasing top-down control with temperature (e.g. \citealt{Shurin2012,
-Gray2016}). Effects of the environment on interactions also propagate up the
-community and influence network structure \citep{Tylianakis2007, Woodward2010,
-Petchey2010a}.
+Gray2016}). Effects of the environment on interactions \citep{Gibert2014} also
+propagate up the community and influence network structure
+\citep{Tylianakis2007, Woodward2010, Petchey2010a}.
 
@@
 
-We now turn to an illustration of our framework with the analysis of an
-empirical dataset of host–parasite networks sampled throughout the south–north
-environmental gradient in continental Europe. The focal system consists of
-local food webs of willows (genus Salix), their galling insects, and the
-natural enemies (parasitoids and inquilines) of these gallers. Targeting this
-system, we ask: i) how much does network structure vary across the gradient,
-and ii) what is the primary driver of network turnover across the gradient?
+We now turn to an illustration of our theory with the analysis of an empirical
+dataset of host–parasite networks sampled throughout the south–north
+environmental gradient in continental Europe \citep{Kopelke2017}. Our
+objective here is to illustrate potential applications of the approach
+outlined above, rather than a specific attempt at describing the biogeography
+of this particular community. The focal system consists of local food webs of
+willows (genus \textit{Salix}), their galling insects, and the natural enemies
+(parasitoids and inquilines) of these gallers. We ask:
+i) how much does network structure vary across the gradient, and ii) what is
+the primary driver of network turnover across the gradient?
 
@@
 distributed, with pronounced variation in community composition across space.
-The genus Salix includes over 400 species, most of which are shrubs or small
-trees \citep{Argus1997}, and is common in most habitats across the Northern
-Hemisphere \citep{Skvortsov1999}. Willows support a highly diverse community
-of herbivorous insects, with one of the main herbivore groups being gall-
-inducing sawflies (Hymenoptera: Tenthredinidae: Nematinae: Euurina
+The genus \textit{Salix} includes over 400 species, most of which are shrubs
+or small trees \citep{Argus1997}, and is common in moist habitats across the
+Northern Hemisphere \citep{Skvortsov1999}. Willows support a highly diverse
+community of herbivorous insects, with one of the main herbivore groups being
+gall- inducing sawflies (Hymenoptera: Tenthredinidae: Nematinae: Euurina
 \citep{Kopelke1999}). Gall formation is induced by sawfly females during
@@
 larvae (representing many families in Hymenoptera) kill the galler larvae by
-direct feeding \citep{Kopelke2003}. In terms of associations between the
-trophic levels, phylogeny-based comparative studies have demonstrated that
-galls represent "extended phenotypes" of the gallers, meaning that gall form,
-location, and chemistry is determined mainly by the galling insects and not by
-their host plants \citep{Nyman2000}. Because galler parasitoids have to
-penetrate a protective wall of modified plant tissue in order to gain access
-to their victims, gall morphology has been inferred to strongly affect the
-associations between parasitoids and hosts \citep{Nyman2007}. Thus, the set of
-parasitoids attacking each host is presumably constrained by the form, size,
-and thickness of its gall.
+direct feeding \citep{Kopelke2003}.
 
@@
 willow galls were collected at 370 sites across Central and Northern Europe.
-Sampling was conducted in the summer months of June and/or July, i.e., during
-the later stages of larval development. Galler species were identified on the
-basis of willow host species and gall morphology, as these are distinct for
-each sawfly species. At each site, galls were randomly collected from numerous
-willow individuals in an area of about 0.1–0.3 $km^2$. Some sites were visited
-more than once, with a total of 641 site visits across the 370 sites. GPS
-coordinates were recorded for each location; for our analyses, current
-annual mean temperature and precipitation were obtained from WorldClim using
-the R package raster \citep{Hijmans2015}. While other covariates could have
-also been considered, these two variables are likely representative of the most
-important axes of the European climate, and are also more easily interpretable than
-reduced variables obtained, for example, by principal component analysis.
-
-The methods used for rearing parasitoids from the galls have been
-previously described by \citealt{Kopelke2003}. In brief, galls were
-opened to score the presence of galler or parasitoid/inquiline larvae. Parasitoid
-larvae were classified to preliminary morphospecies, and the identity of each
-morphospecies was determined by connecting them to adults emerging after
-hibernation. The galls were reared by storing single galls in small glass
-tubes \citep{Kopelke1985a}. Hibernation of galls containing parasitoids took place
-either within the glass tubes or between blotting paper in flowerpots filled
-with clay granulate or a mixture of peat dust and sand. These pots were stored
-over the winter in a roof garden and/or in a climatic chamber. In most cases,
-the matching of larval morphospecies with adult individuals emerging from the
-rearings allowed the identification of the parasitoids to the species
-level. Nonetheless, in some cases, individuals could only be identified to one
-of the (super)families Braconidae, Ichneumonidae, and Chalcidoidea. This was
-particularly the case when only remains of faeces, vacant cocoons of
-parasitoids, and/or dead host larvae were found, as was the case when
-parasitoids had already emerged from the gall. As a result, the largest taxon
-in the data set, "Chalcidoidea indeterminate", represents a superfamily of
-very small parasitoids that are hard to distinguish.
-
-In total, 146,622 galls from 52 Salix taxa were collected for dissection and
-rearing. These galls represented 96 galler species, and yielded 42,133
-individually-identified parasitoids. Of these, 25,170 (60\%) could be
-identified to the species level. Overall, 127 parasitoid and inquiline taxa were
-distinguished in the material. Data on host associations within subsets of
-this material have been previously reported by \citep{Kopelke1999} and
-\citep{Nyman2007}. The current study represents the first analysis of
-the full data set from a spatial perspective.
+In total, 52, 96 and 127 \textit{Salix}, galler and parasitoid and inquiline
+taxa were distinguished, respectively. The strength of this dataset is that
+observations were observed in situ, rather than inferred from expert knowledge
+or other sources of information, thereby allowing the analysis of their
+spatial variation. The drawback is that, because many species are rare, some
+of the pairs of species may have been observed co-occurring only a few times,
+or never.
+As a consequence, despite the extent of the sampling, there is significant uncertainty in the quantification of some of the links.
+The above described methodology explicitly aims at describing this uncertainty, and research should be done to develop methods to reduce it (see Conclusion).
+
+The current study represents the first analysis of the full data set
+from a spatial perspective. Full details about the data collection and species
+identification are provided in \citep{Kopelke2017}. Annual mean temperature
+and precipitation were obtained from WorldClim using the R package dismo
+\citep{Hijmans2015} and GPS coordinates of the sampling locations. While other
+covariates could have also been considered to represent the high
+dimensionality of the niceh, these two variables are likely representative of
+the most important axes of the European climate, and are also more easily
+interpretable than reduced variables obtained, for example, by principal
+component analysis.
 
@@
 of binomial models and collecting their estimated probabilities. For the sake
-of illustration, we considered second-order generalized linear models –
-although more flexible fitting algorithms (e.g. GAM or Random Forest) could
-equally well be used, as long as the algorithm can estimate the probability
-for each observation. The data consist of a simple (albeit large and full of
-zeros) table with the observation of each species, $X_{iy}$ and $X_{jy}$,
-their co-occurrence, $X_{ijy}$, the observation of an interaction $L_{ijy}$,
-and environmental co-variates $E_y$. Thus, there is one row per pair of
-species per site. We considered that an absence of a record of an interaction
-between co-occurring species at a site means a true absence (see below for a
-discussion on this issue).
+of illustration, we considered generalized linear models – although more
+flexible fitting algorithms (e.g. GAM or Random Forest) could equally well be
+used, as long as the algorithm can estimate the probability for each
+observation. The data consist of a simple (albeit large and sparse) table with
+the observation of each species, $X_{iy}$ and $X_{jy}$, their co-occurrence,
+$X_{ijy}$, the observation of an interaction $L_{ijy}$, and environmental co-
+variates $E_y$. Thus, there is one row per pair of species per site. We
+considered that an absence of a record of an interaction between co-occurring
+species at a site means a true absence (see below for a discussion on this
+issue).
 
 We compared three models for the co-occurrence probability. The first one
-directly models the co-occurrence probability conditional on the local
+directly represents the co-occurrence probability conditional on the local
 environment, $P(X_{iy},X_{jy}|E_y)$ (models are listed at Table 1 and 2).
-Hence, this model makes no assumptions about the mechanisms driving co-
+Hence, this model makes no assumption about the mechanisms driving co-
 occurrence for any given environment, and instead uses the information
@@
 Whenever the environment was included as a covariate in the GLM, we considered
-a second-order polynomial response for both temperature and precipitation in
+a second-order polynomial term for both temperature and precipitation in
 order to account for optima in environmental conditions. There are
@@
 extreme case performed only to test the hypothesis that if two species are
-found to interact at least once, then they should interact whenever they co-occur,
-$P(L_{ijy}|X_{iy},X_{jy})=1$. While not necessarily realistic, this
+found to interact at least once, then they should interact whenever they co-
+occur, $P(L_{ijy}|X_{iy},X_{jy})=1$. While not necessarily realistic, this
 model tests an assumption commonly invoked in the representation of local
-networks from the knowledge of a deterministic metaweb. There are consequently
-five parameters for the first model, a single parameter for the second model and
-no parameter to evaluate for the third model (where the interaction
-probability is fixed by the hypothesis).
-
-We fit the different models to each pair of species and recorded the predicted
-probabilities. The joint probability $P(L_{ijy},X_{iy},X_{jy})$ was then
-computed from Eq. 2, and the likelihood of each observation was computed as
-$\mathcal{L}(\theta_{ijy}|D_{ijy})=P(L_{ij},X_{iy},X_{jy})$ if an interaction
-was observed, and as $\mathcal{L}(\theta_{ijy}|D_{ijy}) = 1-P(L_{ijy}, X_{iy},
-X_{jy})$ if no interaction was observed. The log-likelihood was summed over
-the entire dataset to compare the different models by AIC. Not surprisingly,
-there was a very large number of species pairs for which this model could not
-be computed, as they simply never co-occurred. For these pairs, we have no
-information of the interaction probability, and they were consequently removed
-from the analysis. The log-likelihood reported across the entire dataset was
-summed over all pairs of species observed to co- occur at least once.
-Interactions between the first (Salix) and second (gallers) trophic layers and
-those between the second and third (parasitoids) were considered separately.
-Finally, we used the full model (in which both co-occurrence and the
-interaction are conditional on the environment) to interpolate species
-distributions and interaction probabilities across the entire European
-continent. We reconstructed the expected network for each location in a 1 X 1
-km grid and computed the probabilistic connectance following
-\citep{Poisot2015c}.
+networks from the knowledge of a deterministic metaweb. It represents
+potential interactions, rather than realized ones. There are consequently five
+parameters for the first model, a single parameter for the second model and no
+parameter to evaluate for the third model (where the interaction probability
+is fixed by the hypothesis).
+
+We fitted the different models to each pair of species and recorded the
+predicted probabilities. The joint probability $P(L_{ijy},X_{iy},X_{jy})$ was
+then computed from Eq. 2, and the likelihood of each observation $D_{ijy}$ was computed
+as $\mathcal{L}(\theta_{ijy}|D_{ijy})=P(L_{ij},X_{iy},X_{jy})$ if an
+interaction was observed, and as $\mathcal{L}(\theta_{ijy}|D_{ijy}) =
+1-P(L_{ijy}, X_{iy}, X_{jy})$ if no interaction was observed. The log-
+likelihood was summed over the entire dataset to compare the different models
+by AIC. We therefore evaluate the likelihood of all local networks, given the
+model. Not surprisingly, there was a very large number of species pairs for
+which this model could not be computed, as they simply never co-occurred. For
+these pairs, we have no information of the interaction probability, and they
+were consequently removed from the analysis. The log-likelihood reported
+across the entire dataset was summed over all pairs of species observed to co-
+occur at least once. Interactions between the first (\textit{Salix}) and
+second (gallers) trophic layers and those between the second and third
+(parasitoids) were considered separately. Finally, we used the full model (in
+which both co-occurrence and the interaction are conditional on the
+environment) to interpolate species distributions and interaction
+probabilities across the entire European continent. We reconstructed the
+expected network for each location in a 1 X 1 km grid and computed the
+probabilistic connectance following \citep{Poisot2015c}.
 
@@
 \citep{Poisot2015b} and all R scripts for running the analysis, are provided
-in the Supplementary Material.
+in the github repository 
+%\hyperref[https://github.com/DominiqueGravel/ms_probaweb]{https://github.com/DominiqueGravel/ms_probaweb}.
+\url{https://github.com/DominiqueGravel/ms_probaweb}.
 
@@
 the large-scale drivers of network turnover. The results were highly
-consistent among trophic layers (Salix–gallers and gallers–parasitoids; Table
-2). Across all pairs of species, the conditional representation of
-interactions performed better than the marginal one (Model 1 vs Model 2); that
-is, interactions did not occur systematically whenever the two species were
-found co-occurring. Hence, in addition to species turnover, the stochastic
-nature of interactions contributes to network variability. In total, we
-recorded 1,173 pairs of interactions, only 290 of which occurred more than
-five times. Out of these 290 interactions, 143 were systematically detected
-whenever the two species co-occurred. In the instances when species co-
-occurred, the two environmental variables considered proved relatively poor
-predictors of their interactions (Model 2 vs Model 3). Not surprisingly, for
-both types of interactions (Salix–galler and galler–parasitoid), the log-
-likelihood increased when the environment was considered. However, the extra
-number of parameters exceeded the gain in log-likelihood and inflated AIC.
-Therefore, the most parsimonious model excluded the effect of the environment.
-On the basis of log-likelihood only, co-occurrence was non-neutral for both
-Salix–galler and galler–parasitoid interactions. Thus, according to AIC, the
-best model was the one of non-random co-occurrence (Model 3 vs Model 6) for
-both types of interactions.
-
-The approach we present not only has implications for understanding the
-biogeography of pairwise interactions and interaction networks, but also for
-evaluating the quality of metawebs. We investigated the reliability of the
-estimated metaweb across the entire dataset wtih summary statistics of species
-co-occurrence. As mentioned above, across the 17,184 potential pairs of
-species, only 1,173 pairs interacted in at least a single location, yielding a
-connectance of 0.068. However, only 4,459 pairs of species were found co-
-occurring at least once across all locations. There are consequently 12,725
-gaps of information in the metaweb (74.1\% - see Fig. 5). As we cannot know
-whether the non-co-occurring species would indeed interact if found
-together, a more appropriate estimate of connectance would be
-$C=1173/4459=0.263$. This result reveals that the evaluation of the sampling
-quality of ecological networks is a problem on its own and well worth further
-attention.
-
-Once we had selected the best model based on AIC (Model 3, Table 2), we used it to
-reconstruct the expected species richness, along with the most likely network
-for each location. Using this approach, we mapped the expected distribution of
-network properties across Europe (Fig. 6). For simplicity, we chose to
-consider connectance as our descriptor of network configuration, as this
-metric can be easily computed from probabilistic networks \citep{Poisot2015c}
-and is also a good proxy for many other network properties \citep{Poisot2014}.
-Overall, we found a peak in Salix, gallers and parasitoid diversity in Northern
-Europe. The expected number of interactions roughly followed the distribution
-of species richness, but accumulated at a rate different from species numbers.
-Connectance likewise peaked in Northern Europe (Fig. 6).
+consistent among trophic layers (\textit{Salix}–gallers and
+gallers–parasitoids; Table 2), despite very significant variability in the fit
+of the models to the different pairs of species. This variability was
+particularly important for the models of interactions, given co-occurrence.
+Across all pairs of species, the conditional representation of interactions
+performed better than the marginal one (Model 1 vs Model 2); that is,
+interactions did not occur systematically whenever the two species were found
+co-occurring. Hence, in addition to species turnover, the stochastic nature of
+interactions contributes to network variability. In total, we recorded 1,173
+pairs of interactions, only 290 of which occurred more than five times. Out of
+these 290 interactions, 143 were systematically detected whenever the two
+species co-occurred. In the instances when species co-occurred, the two
+environmental variables considered proved relatively poor predictors of their
+interactions (Model 2 vs Model 3). Not surprisingly, for both types of
+interactions (\textit{Salix}–galler and galler–parasitoid), the log-likelihood
+increased when the environment was considered. However, the extra number of
+parameters exceeded the gain in log-likelihood and inflated AIC. Therefore,
+the most parsimonious model excluded the effect of the environment. On the
+basis of log-likelihood only, co-occurrence was non-neutral for both
+\textit{Salix}–galler and galler–parasitoid interactions. Thus, according to
+AIC, the best model was the one of non-random co-occurrence (Model 3 vs Model
+6) for both types of interactions.
+
+% The approach we present not only has implications for understanding the
+% biogeography of pairwise interactions and interaction networks, but also for
+% evaluating the quality of metawebs. We investigated the reliability of the
+% estimated metaweb across the entire dataset wtih summary statistics of species
+% co-occurrence. As mentioned above, across the 17,184 potential pairs of
+% species, only 1,173 pairs interacted in at least a single location, yielding a
+% connectance of 0.068. However, only 4,459 pairs of species were found co-
+% occurring at least once across all locations. There are consequently 12,725
+% gaps of information in the metaweb (74.1\% - see Fig. 5). As we cannot know
+% whether the non-co-occurring species would indeed interact if found
+% together, a more appropriate estimate of connectance would be
+% $C=1173/4459=0.263$. This result reveals that the evaluation of the sampling
+% quality of ecological networks is a problem on its own and well worth further
+% attention.
+
+Once we had selected the best model based on AIC (Model 3, Table 2), we used
+it to reconstruct the expected species richness, along with the most likely
+network for each location. Using this approach, we mapped the expected
+distribution of network properties across Europe (Fig. 6). For simplicity, we
+chose to consider connectance as our descriptor of network configuration, as
+this metric can be easily computed from probabilistic networks
+\citep{Poisot2015c} and is also a good proxy for many other network properties
+\citep{Poisot2014}. Overall, we found a peak in \textit{Salix}, gallers and
+parasitoid diversity in Northern Europe. The expected number of interactions
+roughly followed the distribution of species richness, but accumulated at a
+rate different from species numbers. Connectance likewise peaked in Northern
+Europe (Fig. 6).
 
@@
 We have proposed that the representation of community structure and its
-variation in space and time is best captured by the formalism of ecological
-networks, as both the distribution of species and their interspecific
-interactions can then be accounted for. We consequently revised the niche
-concept in order to integrate its abiotic and biotic components that vary over
-time and space. This integrated niche was represented visually with an
-ordination of species into an environmental space and a trait space. The
-fundamental niche of a species is represented as the set of environmental
-conditions and resources that allow a species to establish in a location,
-thereby integrating the Eltonian and the Grinnellian components of the niche.
-We then translated the concept mathematically by investigating the probability
-of the joint occurrences of species and their interaction, which should be
-interpreted as an interaction distribution model. We used this approach to
-characterize the turnover of the structure of ecological interactions in a
-species-rich tri-trophic network across Western Europe, finding that the
-primary driver of network variation is the turnover in species composition. To
-our knowledge, this is the first continental-wide analysis of the drivers of
-network structure from empirical data on the occurrence of interactions (see
-\citealt{Baiser2012, Albouy2014, Poisot2016}).
+variation in space is best captured by the formalism of ecological networks,
+as both the distribution of species and their interspecific interactions can
+then be accounted for. We consequently revised the niche concept in order to
+integrate its abiotic and biotic components. This integrated niche was
+represented visually with an ordination of species into an environmental space
+and a trait space. The fundamental niche of a species is represented as the
+set of environmental conditions and resources that allow a species to
+establish in a location, thereby integrating the Eltonian and the Grinnellian
+components of the niche. We then translated the concept mathematically by
+investigating the probability of the joint occurrences of species and their
+interaction, which should be interpreted as an interaction distribution model.
+We used this approach to characterize the turnover of the structure of
+ecological interactions in a species-rich tri-trophic network across Western
+Europe, finding that the primary driver of network variation is the turnover
+in species composition.
+
+%To
+%our knowledge, this is the first continental-wide analysis of the drivers of
+%network structure from empirical data on the occurrence of interactions (see
+%\citealt{Baiser2012, Albouy2014, Poisot2016}).
 
 Applying the framework to our large data set on host–parasite interactions
-across Europe revealed key features in the interaction between Salix taxa,
-their herbivores, and the natural enemies of these herbivores. Consistent with
-a general increase in the diversity of Salix towards boreal areas
-\citep{Cronk2015}, overall species richness of the networks increased towards
-the north. The distribution of Salix species richness largely matched those of
-gallers and parasitoids. These observations within Europe are also matched by
-the ones found at a global scale for Salix \citep{Argus1997, Cronk2015,
-Wu2015} and sawflies \citep{Kouki1994, Kouki1999}. Species richness in a
-common groupd of parasitic wasps, the Ichneumonidae, was originally presumed
-to show a similar "reversed latitudinal gradient", but this observation has
-been recently challenged by findings of rather high ichneumonid diversity in
-the tropics \citep{Veijalainen2013}. Nevertheless, ichneumonid subfamilies
-specifically associated with sawflies (Ctenopelmatinae, Tryphoninae) are
-clearly less diverse in the south.
+across Europe revealed key features in the interaction between \textit{Salix}
+taxa, their herbivores, and the natural enemies of these herbivores.
+Consistent with a general increase in the diversity of \textit{Salix} towards
+boreal areas \citep{Cronk2015}, overall species richness of the networks
+increased towards the north. The distribution of \textit{Salix} species
+richness largely matched those of gallers and parasitoids. These observations
+within Europe are also matched by the ones found at a global scale for
+\textit{Salix} \citep{Argus1997, Cronk2015, Wu2015} and sawflies
+\citep{Kouki1994, Kouki1999}. Species richness in a common group of parasitic
+wasps, the Ichneumonidae, was originally presumed to show a similar "reversed
+latitudinal gradient", but this observation has been recently challenged by
+findings of rather high ichneumonid diversity in the tropics
+\citep{Veijalainen2013}. Nevertheless, ichneumonid subfamilies specifically
+associated with sawflies (Ctenopelmatinae, Tryphoninae) are clearly less
+diverse in the south.
 
@@
 occurrence and therefore of potential interactions differed between the first
-and second layers of feeding links. The correlation between expected Salix and
-gallers richness was 0.73, while it was 0.58 between gallers and their
-parasitoids. Therefore, the ratio of herbivores to Salix species is
-essentially constant across Europe, while each herbivore species is
-potentially attacked by a and a lower trophic level at the same site was
-clearly affected by the richer enemy community at higher latitudes.
-Consequently, overall connectance peaks in Northern Europe (Fig. 6).
+and second layers of feeding links. The correlation between expected
+\textit{Salix} and gallers richness was 0.73, while it was 0.58 between
+gallers and their parasitoids. Therefore, the ratio of herbivores to
+\textit{Salix} species is essentially constant across Europe, whereas each
+herbivore species is potentially attacked by a richer enemy community higher
+latitudes. Consequently, overall connectance peaks in Northern Europe (Fig.
+6).
 
@@
 environment, whereas the probability of observing an interaction between the
-two was not detectably so. This applies to the example species
+two was, given co-occurrence, not detectably so. The interactions were  highly
+uncertain, as only few pairs of species were systematically interacting when
+co-occurring but most not. This applies to the example species
 \textit{Phyllocolpa prussica} and \textit{Chrysocharis elongata} (Figs 2 and
 3), but also to all species pairs more generally. For the example species
-pair, the full model revealed that the interaction probability peaks at
-intermediate temperature and precipitation, simply because this is where the
-two species co-occur most often. This does not imply that species will always
-interact when they meet – although this is a basic assumption in most
-documented metawebs to date (e.g. \citealt{Havens1992, Wood2015}). Rather, an
-interaction is a stochastic process whose probability is also influenced by
-the probability with which species co-occur. What we cannot reliably know is
-how this stochasticity splits into two sampling processes – i.e., the extent
-to which a species at the higher trophic level runs into a species at the
-lower level co-occurring at the site, and the extent to which this interaction
-is detected by an observer collecting a finite sample. Future work will be
-required to document the relative importance of these two sources of
-uncertainty in the occurrence of interactions.
+pair, the full model revealed that the joint probability event (interaction
+and co-occurrence) peaks at intermediate temperature and precipitation, simply
+because this is where the two species co-occur most often. This does not imply
+that species will always interact when they meet – although this is a basic
+assumption in most documented metawebs to date (e.g. \citealt{Havens1992,
+Wood2015}). Rather, an interaction is better represented as aa stochastic
+process whose probability is also influenced by the probability with which
+species co-occur. What we cannot reliably know is how this stochasticity
+splits into different sources of uncertainty – i.e., the extent to which a
+species at the higher trophic level runs into a species at the lower level co-
+occurring at the site, the extent to which this interaction is detected by an
+observer collecting a finite sample, or simply the uncertainty arising from
+incomplete description of a highly dimensional niche. Future work will be
+required to document the relative importance of these sources of uncertainty
+in the occurrence of interactions.
 
@@
 (e.g. \citealt{Tylianakis2007}), over environmental gradients
-\citealt{Lurgi2012} and in time \citep{Trojelsgaard2015} is accumulating
+\citep{Lurgi2012} and in time \citep{Trojelsgaard2015} is accumulating
 rapidly. It is not clear, however, to what extent the turnover of network
@@
 vary with the environment in other systems, for instance, herbivory
-\citep{Shurin2012} and predation \citep{Mckinnon2010,Legagneux2014} are often
-found to increase with temperature, resulting in spatial variation of trophic
-cascades \citep{Gray2016}. What remains unclear, however, is the extent to
-which such variation is driven by a turnover of species composition along
-gradients, or a turnover of the interactions. Here we found that interactions
-vary substantially but non-predictably along the annual temperature and the
-precipitation gradient. Clearly, the lack of detectable signal may be due to
-our choice of covariates. Indeed, a previous study on a similar system
-identified habitat characteristics as the primary drivers of interactions
-\citep{Nyman2015}. New investigations with other systems will thus be required
-to challenge this result. Under all circumstances, documenting the
-relationship between the environment and the occurrence of interactions at
-continental scales is critical for understanding how large-scale variation of
-trophic regulation influences community dynamics and ecosystem functioning
-\citep{Harfoot2014}.
-
-We restricted our framework to the effect of co-occurrence on ecological
+\citep{Shurin2012, Baskett2018} and predation \citep{Mckinnon2010,
+Legagneux2014} are often found to increase with temperature, resulting in
+spatial variation of trophic cascades \citep{Gray2016}. What remains unclear,
+however, is the extent to which such variation is driven by a turnover of
+species composition along gradients, or a turnover of the interactions. Here
+we found that interactions vary substantially but non-predictably along the
+annual temperature and the precipitation gradient. The lack of detectable
+signal may be due to our choice of covariates. Indeed, a previous study on a
+similar system identified habitat characteristics as the primary drivers of
+interactions \citep{Nyman2015}. New investigations with other systems will
+thus be required to challenge this result. Under all circumstances,
+documenting the relationship between the environment and the occurrence of
+interactions at continental scales is critical for understanding how large-
+scale variation of trophic regulation influences community dynamics and
+ecosystem functioning \citep{Harfoot2014}.
+
+We restricted our analysis to the effect of co-occurrence on ecological
 interactions, neglecting the inverse of the problem. We did not investigate in
 depth the drivers of co-occurrence and simply took it for granted from the
-data. Co-occurrence was indeed many times significantly different from the
-expectation of independent species distributions. It thus begs the question of
-whether, once environmental effects on species-specific distribution have been
-accounted for, interactions come with significant effects on co-occurrence? We
-could rephrase this problem by asking whether the fundamental niche differs
-from the realized niche, and how this applies to our framework. For example,
-we have considered above simply the co-occurrence probability,
-$P(X_{iy},X_{jy}|E_y)$, which could be expanded as $P(X_{iy}|X_{jy},E_y)
-P(X_{jy}| E_y )$. After some re-arrangement of Eq. 2, the marginal occurrence
-probability, $P(X_{jy}|E_y )$, could be considered as a species distribution
-model taking into account the interaction between these species. This
-derivation would however critically depend on a strong \emph{a priori} expectation of
-the conditional probability of observing a species given the distribution of
-the other species. This assumption seems reasonable for some situations, such
-as a parasitoid species that requires a host to develop. On the other hand, we
-found that the strength of this association is often rather weak if not
-neutral (for instance, with the example pair analyzed at Table 1). The lack of
-an association could simply arise when the parasitoid is generalist enough 
-that it is not obligated to track the distribution of any single/given host
-\citep{Cazelles2015}.
+data. Co-occurrence was indeed different from the expectation of independent
+species distributions. It thus begs the question of whether, once
+environmental effects on species-specific distribution have been accounted
+for, interactions come with significant effects on co-occurrence? We could
+rephrase this problem by asking whether the fundamental niche differs from the
+realized niche, and how this applies to our framework. For example, we have
+considered above simply the co-occurrence probability, $P(X_{iy},X_{jy}|E_y)$,
+which could be expanded as $P(X_{iy}|X_{jy},E_y) P(X_{jy}| E_y )$. After some
+re-arrangement of Eq. 2, the marginal occurrence probability, $P(X_{jy}|E_y
+)$, could be considered as a species distribution model taking into account
+the interaction between these species. This derivation would however
+critically depend on a strong \emph{a priori} expectation of the conditional
+probability of observing a species given the distribution of the other
+species. This assumption seems reasonable for some situations, such as a
+parasitoid species that requires a host to develop. On the other hand,
+\citealt{Cazelles2016b} found that the strength of this association is often
+rather weak if not neutral (for instance, with the example pair analysed at
+Table 1). The lack of an association could simply arise when the parasitoid is
+generalist enough that it is not obligated to track the distribution of any
+single/given host \citep{Cazelles2015}.
 
@@
 species are conditionally distributed but this possibility should be the
-topic of more specific hypothesis testing. The impact of ecological
+topic of theoretical investigation with dynamical metacommunity models \citep{Cazelles2015} and empirical hypothesis testing. The impact of ecological
 interactions on the distribution of co-occurrence has been the topic of many
@@
 
-Our representation of spatial variation of community structure presents a new
+Our representation of spatial variation of community structure offers a new
 approach for the study of the biogeography of ecological networks. We see the
@@
 quantitative tools to estimate the confidence intervals around inferred
-interaction probabilities, as well as estimators? of the frequency of false
+interaction probabilities, as well as estimators of the frequency of false
 absences. Bayesian methods are promising to that end because we could use
@@
 \textbf{3. From interaction probabilities to a distribution of network
-properties}. Metrics are available to analyze the structure of probabilistic
+properties}. Metrics are available to analyse the structure of probabilistic
 networks \citep{Poisot2015c}. These metrics are useful as first approximation,
@@
 variation of ecological networks} supported by the Canadian Institute for
-Ecology and Evolution), and the \emph{ Next Generation Data, Models, and
+Ecology and Evolution), and the \emph{Next Generation Data, Models, and
 Theory Working Group}, supported by the Santa Fe Institute, the Betsy and
 Jesse Fink Foundation, the ASU-SFI Center for Biosocial Complex Systems, and
-NSF Grant PHY-1240192. DG also acknowledge financial support from NSERC-
+NSF Grant PHY-1240192. DG also acknowledges financial support from NSERC-
 Discovery grant program and Canada Research Chair program.
@@
 \centering
-\caption{Summary of model comparison for the interaction across all pairs of salix, gallers and parasitoids.}
+\caption{Summary of model comparison for the interaction across all pairs of \textit{Salix}, gallers and parasitoids.}
 \begin{tabular}{lllllll}
@@
 	Interaction & \# & Metaweb model & Co-occurrence model & LL & npars & AIC \\ \hline
-	Salix-Galler & 1 & $P(L_{ijy})$ & $P(X_{iy},X_{jy}|E_y)$ & -6022.1 & 7548 & 27140.3 \\
+	\textit{Salix}-Galler & 1 & $P(L_{ijy})$ & $P(X_{iy},X_{jy}|E_y)$ & -6022.1 & 7548 & 27140.3 \\
 	 & 2 & $P(L_{ijy}|X_{iy},X_{jy})$ & $P(X_{iy},X_{jy}|E_y)$ & -5547.9 & 7548 & 26191.8 \\
@@
 	 & 4 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy})$ & -5998.4 & 8806 & 30287.2 \\
-	 & 5 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})(X_{jy})$ & -6636.1 & 7548 & 27092.7 \\
+	 & 5 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})P(X_{jy})$ & -6636.1 & 7548 & 27092.7 \\
 	 & 6 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}|E_y)P(X_{jy}|E_y)$ & -6002.9 & 18870 & 49745.7 \\ \hline
@@
 as a sampling process of the regional pool of potential interactions. Species
-(indicated by colored nodes) are sampled first, and among the species found in
+(indicated by coloured nodes) are sampled first, and among the species found in
 the local network, only some interactions (indicated by blue links) occur.
@@
 proposed in this paper. As a concrete illustration of metaweb sampling, we
-here show a local interaction network among Salix (left/green), gallers
+here show a local interaction network among \textit{Salix} (left/green), gallers
 (center/red), and parasitoids (red/blue). The metaweb was constructed by
@@
 growth rate $r$ is positive \citep{Holt2009a}. The horizontal axis represents
-an environmental gradient impacting the growth of the focal species (in red).
-The location of each species along this gradient represents their optimum, and
-the vertical dotted lines represent the limits of the Grinnellian niche of the
-focal species. In food web ecology, the Eltonian niche represents the location
-of a species in the food web, as determined by its niche position ($n$) and
-its niche optimum ($c$). The vertical axis represents a niche gradient,
-for example a trait such as body size. The location of each species along this
-gradient represents their niche position. The focal species will feed only on prey
-species occupying niche locations within a given interval around the optimum,
-represented by the horizontal lines. The integrated Grinnellian and Eltonian
-niche corresponds to the square in the middle where an interaction is possible
-owing to a match of traits and spatial distribution. According to our
-probabilistic framework, the central square represents the area where the
-joint probability of observing co-occurrence and interactions is positive.
+an environmental gradient impacting the growth of a focal species (red point).
+The location of each species (grey points) along this gradient represents their
+optimum, and the vertical dotted lines represent the limits of the Grinnellian
+niche of the focal species. In food web ecology, the Eltonian niche represents
+the location of a species in the food web, as determined by its niche position
+($n$) and its niche optimum ($c$). The vertical axis represents a niche
+gradient, for example a trait such as body size. The location of each species
+along this gradient represents their niche position. The focal species will
+feed only on prey species occupying niche locations within a given interval
+around the optimum, represented by the horizontal lines. The integrated
+Grinnellian and Eltonian niche corresponds to the square in the middle where
+an interaction is possible owing to a match of traits and spatial
+distribution. The central square represents the area where the joint
+probability of observing co-occurrence and interactions is positive.
 
@@
 (\textit{Chrysocharis elongata}) across gradients of annual average
-temperature and annual precipitation}. The representation is based on
-predictions from Model 3 (see Table 1). In the left panel, open circles
-represent the absence of both species, whereas closed circles represent co-
-occurrence and plus signs the occurrence of only one of the two species. In
-the other two panels, open circles represent co-occurrence but an absence of
-interaction and closed circles the occurrence of an interaction.
+temperature and annual precipitation}. The colour gradient represents the
+probability of observing the event, from 0 (white) to 1 (black). The
+representation is based on predictions from Model 3 (see Table 1). In the left
+panel, open circles represent the absence of both species, whereas closed
+circles represent co- occurrence and plus signs the occurrence of only one of
+the two species. In the other two panels, open circles represent co-occurrence
+but an absence of interaction and closed circles the occurrence of an
+interaction.
 
@@
 leaf folder (\textit{Phyllocolpa prussica}) and a parasitoid
-(\textit{Chrysocharis elongata}) across Europe}. The maps are generated from 
-probabilities predicted by the model illustrated inFig. 3.
+(\textit{Chrysocharis elongata}) across Europe}. Climate data are extracted
+from WorldClim over a 1km x 1km grid and predictions made according to the
+model illustrated at Fig. 3. Colour gradient ranges from low values (dark
+blue) to high values (yellow).
+
+% %------------------------
+% \subsection*{Figure 5}
+
+% \textbf{Representation of the \textit{Salix}-galler and galler-parasitoid metawebs}.
+% Black cells indicate species pairs for which at least one interaction was
+% recorded, white cells indicate absence of recorded interactions and grey
+% cells show pairs of species never detected at the same site (and hence species
+% pairs for which we have no information on whether they would interact should
+% they co-occur).
 
@@
 
-\textbf{Representation of the Salix-galler and galler-parasitoid metawebs}.
-Black cells indicate species pairs for which at least one interaction was
-recorded, white cells indicate absence of recorded interactions and grey
-cells show pairs of species never detected at the same site (and hence species
-pairs for which we have no information on whether they would interact should
-they co-occur).
-
-%------------------------
-\subsection*{Figure 6}
-
 \textbf{Mapping the distribution of species richness, the number of links and
 connectance across Europe}. The representation is based on predictions from
-Model 3 (see Table 2). Species richness is obtained by summation of individual 
-occurrence probabilities, and link density by summation of interaction probabilities.
+Model 3 (see Table 2) using climate data extracted from WorldClim over a 1km x 1km grid. Species richness is obtained by summation of individual
+occurrence probabilities, and link density by summation of interaction
+probabilities. Colour gradient ranges from low values (dark blue) to high
+values (yellow).
 
@@
 
+% %------------------------
+% \subsection*{Figure 5}
+
+% \begin{figure}[ht!]
+% \centering\includegraphics[width=0.8\textwidth]{figures/mw_holes}
+% \end{figure}
+
+% \newpage
+
 %------------------------
 \subsection*{Figure 5}
-
-\begin{figure}[ht!]
-\centering\includegraphics[width=0.8\textwidth]{figures/mw_holes}
-\end{figure}
-
-\newpage
-
-%------------------------
-\subsection*{Figure 6}
 

### 2018-03-20 analysis/scripts/functions/get_LL.r

@@ -1,32 +1,0 @@
-# Compute the likelihood for a set of observations, given the model
-get_LL = function(model_list, data) {
-
-	modelC = model_list$modelC
-	modelL = model_list$modelL
-
-	if(is.null(modelC)) {
-		sumLL = 0
-		npars = 0
-	}
-
-	else {
-		# NUMBER OF PARAMETERS
-		if(is.null(modelC$ij)) nparsXij = length(modelC$i$coefficients)*2	
-		else nparsXij = length(modelC$ij$coefficients)
-		nparsLij = length(modelL$coefficients)	
-		npars = (nparsXij+nparsLij)
-
-		# COMPUTATION OF THE PROBABILITIES
-		probs = get_probs(model_list, newE = data$E)
-		PLijXij = probs$PLij*probs$PXij 
-
-		# COMPUTATION OF THE LIKELIHOOD
-		LL = numeric(length(data$Xij))
-		LL[data$Lij == 1] = log(PLijXij[data$Lij==1])
-		LL[data$Lij == 0] = log(1 - PLijXij[data$Lij==0])	
-		sumLL = sum(LL)
-	}
-
-	return(c(sumLL, npars))
-
-}

### 2018-03-20 analysis/scripts/functions/interactions_models.R

@@ -1,41 +1,0 @@
-# Returns the probability of observing the interaction ij 
-# independently of co-occurrence and of the environment
-# Havens type of interaction
-# We have to trick the glm function so that it returns a probability 
-# of 1 if the species do interact at least once, and 0 if they never
-# interact
-L0 <- function(data, selection) {
-   with(as.list(data),{
-
-        if(sum(Lij)>0) Lij_trick = numeric(length(Lij))+1
-          Lij_trick = numeric(length(Lij))
-        model <- glm(Lij_trick ~ 1, family = "binomial")
-
-        if(selection) {return(step(model,trace=0))}
-        else {return(model)}
-   })
-}
-
-# Returns the probability of observing the interaction ij when i 
-# and j are present independently of the environment
-L1 <- function(data, selection) {
-   with(as.list(data),{
-        model <- glm(Lij[Xij==1] ~ 1, family = "binomial")
-        if(selection) {return(step(model,trace=0))}
-        else {return(model)}
-   })
-}
-
-# Returns the probability of observing the interaction ij when i 
-# and j are present for each level of the environment
-L2 <- function(data, selection) {
-   with(as.list(data),{
-    subLij = Lij[Xij==1] 
-    subE = E[Xij==1,]  
-    Enames = expression("T","T2","PP","PP2")
-    fmla <- as.formula(paste("subLij ~ ", paste(Enames, collapse= "+")))     
-    model <- glm(fmla, family = "binomial",data=subE)
-    if(selection) {return(step(model,trace=0,direction = "forward"))}
-    else {return(model)}
-   })
-}

### 2018-03-20 analysis/scripts/functions/species_models.r

@@ -1,53 +1,0 @@
-# Returns the probability of observing the species i independently 
-# of the environment
-C0 <- function(data,selection) {
-   with(as.list(data),{
-        model = list()
-        model$i <- glm(Xi ~ 1, family = "binomial")
-        model$j <- glm(Xj ~ 1, family = "binomial")
-        if(selection) {return(list(i=step(model$i,trace=0),j=step(model$j,trace=0)))}
-        else {return(model)}
-   })
-}
-
-# Returns the probability of observing the pair ij independently 
-# of the environment
-C1 <- function(data, selection) {
-   with(as.list(data),{
-        model = list()    
-        model$ij <- glm(Xij ~ 1, family = "binomial")
-        if(selection) {return(list(ij = step(model$ij,trace=0)))}
-        else {return(list(ij = model$ij))}
-   })
-}
-
-# Returns the probability of observing the pair ij as a function 
-# of the environment
-C2 <- function(data, selection) {
-   with(as.list(data),{
-      Enames = expression("T","T2","PP","PP2")
-      fmla <- as.formula(paste("Xij ~ ", paste(Enames, collapse= "+")))     
-      model = list()    
-      model$ij <- glm(fmla, family = "binomial", data = E)
-      if(selection) {return(list(ij = step(model$ij,trace=0)))}
-      else {return(list(ij = model$ij))}
-   })
-}
-
-# Returns the probability of observing the species i as a function 
-# of the environment
-C3 <- function(data, selection) {
-   with(as.list(data),{
- #     Ei = E[match(unique(data$sites[data$IDi == i]),data$sites[data$IDi == i]),]
- #     Ej = E[match(unique(data$sites[data$IDj == j]),data$sites[data$IDj == j]),]
-      Enames = expression("T","T2","PP","PP2")
-      fmlai <- as.formula(paste("Xi ~ ", paste(Enames, collapse= "+")))  
-      fmlaj <- as.formula(paste("Xj ~ ", paste(Enames, collapse= "+"))) 
-      model = list()
-      model$i <- glm(fmlai, family = "binomial", data=E)
-      model$j <- glm(fmlaj, family = "binomial", data=E)
-      if(selection) {return(list(i = step(model$i,trace = 0), j= step(model$j,trace=0)))}
-      else {return(model)}
-   })
-}
-

### 2018-03-20 analysis/scripts/results/1_metaweb_sampling.r

@@ -1,139 +1,0 @@
-##################################################################
-# Script for Figure 1
-# Illustrating the sampling of the metaweb of interactions among salix,
-# gall insects and parasitoids across Europe
-# Dominique Gravel
-##################################################################
-
-rm(list = ls())
-
-# Load & prepare the data
-load("./data/expand_data.Rdata")
-load("./data/DF_split.Rdata")
-load("./data/pairs.Rdata")
-
-IDi = as.character(data$pairs.from)
-IDj = as.character(data$pairs.to)
-Si = length(unique(IDi))
-Sj = length(unique(IDj))
-unique_IDi = unique(IDi)
-unique_IDj = unique(IDj)
-IDcomm = IDj[match(unique_IDi,unique_IDj,nomatch=0)]
-unique_ID_all = unique(c(IDi,IDj))
-Sall = length(unique_ID_all)
-DF = data.frame(sites = data$pairs.sites_ID, IDi = IDi, IDj = IDj, Xi=data$Xi, Xj=data$Xj, Xij = data$Xij, Lij = data$Lij)
-
-#########################################################
-# Adjacency matrix for the metaweb
-#########################################################
-
-mw = data.frame(matrix(0, nr = Sall, nc = Sall))
-names(mw) = unique_ID_all
-row.names(mw) = unique_ID_all
-
-for(n in 1:nrow(pairs)) {
-
-	# Compute the number of links
-	nL = sum(DF_split[[n]]$Lij)
-
-	if(nL!=0) {
-
-		# Get the victim
-		i = which(unique_ID_all == DF_split[[n]]$IDi[1])
-
-		# Get the ennemy index
-		j = which(unique_ID_all == DF_split[[n]]$IDj[1])
-
-		# Put the record in the mw
-		mw[i,j] = 1
-		mw[j,i] = 1		
-	}
-}
-
-#########################################
-# Adjacency matrix for one site
-#########################################
-
-lw = data.frame(matrix(0, nr = Sall, nc = Sall))
-names(lw) = unique_ID_all
-row.names(lw) = unique_ID_all
-DF_split_sites = split(DF,DF$sites)
-site_index = 369 # Pick one that has a decent number of links
-
-for(n in 1:nrow(pairs)) {
-	# Compute the number of links
[…]

### 2018-03-20 analysis/scripts/results/2_example_pair.R

@@ -1,135 +1,0 @@
-##################################################################
-# Script for Figure 3
-# Illustrating the computation of interaction probabilities for a 
-# pair of species
-# Dominique Gravel
-##################################################################
-
-rm(list = ls())
-
-# Load some functions
-source("./scripts/functions/species_models.R")
-source("./scripts/functions/interactions_models.R")
-source("./scripts/functions/get_LL.R")
-source("./scripts/functions/get_probs.r")
-source("./scripts/functions/fit_models.r")
-
-# Load the data
-load("./data/DF_split.Rdata")
-load("./data/expand_data.Rdata")
-
-#########################################################
-# Fit the different models
-#########################################################
-
-# Find the nb of links per pair
-nL  = numeric(length(DF_split))
-nXi = numeric(length(DF_split))
-nXj = numeric(length(DF_split))
-nXij = numeric(length(DF_split))
-for(x in 1:length(DF_split)) {
-	nL[x] = sum(DF_split[[x]]$Lij)
-	nXi[x] = sum(DF_split[[x]]$Xi)
-	nXj[x] = sum(DF_split[[x]]$Xj)
-	nXij[x] = sum(DF_split[[x]]$Xij)
-}
-
-cbind(nL,nXi,nXj,nXij,nL,nL/nXij)[nL/nXij<0.7 & nL > 10,]
-
-# Subset the data
-pair_index = which(nL == 21 & nXij == 38) 
-data = DF_split[[pair_index]]
-data$E = data.frame(T = data$E$T/12, PP = data$E$PP/1000, T2 = data$E$T2/12^2, PP2 = data$E$PP2/1000^2)
-sum(data$Lij)
-sum(data$Xij)
-
-# Pick the model
-models_C2_L0 = fit_models(data, selection = FALSE, funC = C2, funL = L0)
-models_C2_L1 = fit_models(data, selection = FALSE, funC = C2, funL = L1)
-models_C2_L2 = fit_models(data, selection = FALSE, funC = C2, funL = L2)
[…]

### 2018-03-20 analysis/scripts/results/3_map_pair.R

@@ -1,113 +1,0 @@
-##################################################################
-# Script for Figure 4
-# Mapping across Europe the interaction probability between pairs of species
-# Dominique Gravel
-##################################################################
-
-rm(list=ls())
-
-library(raster)
-library(sp)
-library(rgdal)
-
-# Load & prepare the data
-load("./data/DF_split.Rdata")
-load("./data/expand_data.Rdata")
-
-IDi = data$pairs.IDi
-IDj = data$pairs.IDj
-Si = length(unique(IDi))
-Sj = length(unique(IDj))
-
-# Load the stuff to make the raster object
-wrld <- readOGR("data/map", layer="level1")
-europe <- wrld[1,]
-exteur <- extent(europe)
-xmin(exteur) = 0
-xmax(exteur) = 25
-ymin(exteur) = 40
-ymax(exteur) = 70
-
-# Extract the climatic variables
-clim = crop(getData("worldclim", var="bio", res=10), exteur)
-T = getValues(clim$bio1)
-PP = getValues(clim$bio12)
-
-############################################################
-# Extract the local networks over Europe
-############################################################
-
-ncell = length(T)
-map_E = data.frame(T = T, PP = PP, T2 = T^2, PP2 = PP^2)
-pair = 6128
-
-data = DF_split[[pair]]
-Xi = data$Xi
-Xj = data$Xj
-Xij = data$Xij
-Lij = data$Lij
-E = data$E	
-
-i = as.numeric(as.vector(data$IDi[1]))
-j = as.numeric(as.vector(data$IDj[1]))
-
-# Compute the models
-lm_i = glm(Xi ~ T+PP+T2+PP2, family = "binomial", data = E)
-lm_j = glm(Xj ~ T+PP+T2+PP2, family = "binomial", data = E)
-subE = subset(E,Xij == 1)
-subLij = subset(Lij, Xij == 1)
-lm_L = glm(subLij ~ T+PP+T2+PP2, family = "binomial", data = subE)
-
-# Compute expected probabilities over the gradient
-PXi_E = predict(lm_i, type="response", newdata=map_E)
-PXj_E = predict(lm_j, type="response", newdata=map_E)
[…]

### 2018-03-20 analysis/scripts/results/4_metaweb_holes.r

@@ -1,116 +1,0 @@
-##################################################################
-# Script for Figure 5
-# Illustrating the computation of interaction probabilities for a 
-# pair of species
-# Dominique Gravel
-##################################################################
-
-rm(list = ls())
-
-# Load & prepare the data
-load("./data/DF_split.Rdata")
-load("./data/pairs.Rdata")
-
-ID_S = unique(as.character(pairs$pairs.from[pairs$pairs.type=="SH"]))
-ID_H = unique(as.character(pairs$pairs.to[pairs$pairs.type=="SH"]))
-ID_P = unique(as.character(pairs$pairs.to[pairs$pairs.type=="HP"]))
-
-S_S = length(ID_S)
-S_H = length(ID_H)
-S_P = length(ID_P)
-
-#########################################################
-# Compile the metaweb
-#########################################################
-
-L_SH = matrix(0, nr = S_S, nc = S_H)
-X_SH = matrix(0,nr = S_S, nc = S_H)
-
-L_HP = matrix(0, nr = S_H, nc = S_P)
-X_HP = matrix(0,nr = S_H, nc = S_P)
-
-for(n in 1:length(DF_split)) {
-
-	# Compute the number of links
-	nL = sum(DF_split[[n]]$Lij)
-
-	# Compute the number of co-occurrences
-	nX = sum(DF_split[[n]]$Xij)
-
-	if(nX!=0) {
-
-		# Indices for the different species
-		if(pairs$pairs.type[n]=="SH") {
-			i = which(ID_S == pairs$pairs.from[n])
-			j = which(ID_H == pairs$pairs.to[n])			
-			L_SH[i,j] = nL/nX
-			X_SH[i,j] = nX
-		}
-
-		else {
-			i = which(ID_H == pairs$pairs.from[n])
-			j = which(ID_P == pairs$pairs.to[n])
-			L_HP[i,j] = nL/nX
-			X_HP[i,j] = nX			
-		}
-	}
-	cat(n,'\n')
-}
-
-# Sort the matrices by degree
-d_S = apply(L_SH,1,sum,na.rm=TRUE)
-d_Hi = apply(L_SH,2,sum,na.rm=TRUE)
-d_Hj = apply(L_HP,1,sum,na.rm=TRUE)
[…]

### 2018-03-20 analysis/scripts/results/table_all_models.R

@@ -7,11 +7,11 @@
 rm(list = ls())
 
 # Source the functions
-source("./scripts/functions/species_models.R")
-source("./scripts/functions/interactions_models.R")
-source("./scripts/functions/get_probs.R")
-source("./scripts/functions/get_LL.R")
-source("./scripts/functions/fit_models.R")
+source("./scripts/functions/species_models.r")
+source("./scripts/functions/interactions_models.r")
+source("./scripts/functions/get_probs.r")
+source("./scripts/functions/get_LL.r")
+source("./scripts/functions/fit_models.r")
 
 # Load & prepare the data
 load("./data/expand_data.Rdata")

### 2018-03-20 analysis/scripts/results/table_all_models.r

@@ -1,111 +1,0 @@
-##################################################################
-# Compute the likelihood for each model and each species pair
-# Record the results in a summary table
-# Dominique Gravel
-##################################################################
-
-rm(list = ls())
-
-# Source the functions
-source("./scripts/functions/species_models.r")
-source("./scripts/functions/interactions_models.r")
-source("./scripts/functions/get_probs.r")
-source("./scripts/functions/get_LL.r")
-source("./scripts/functions/fit_models.r")
-
-# Load & prepare the data
-load("./data/expand_data.Rdata")
-load("./data/DF_split.Rdata")
-load("./data/pairs.Rdata")
-
-IDi = data$pairs.IDi
-IDj = data$pairs.IDj
-Si = length(unique(IDi))
-Sj = length(unique(IDj))
-unique_IDi = unique(IDi)
-unique_IDj = unique(IDj)
-np = length(DF_split)
-type = numeric(np)
-
-# Lists to store the models 
-C2_L0 = matrix(nr = np, nc = 2)
-C2_L1 = matrix(nr = np, nc = 2)
-C2_L2 = matrix(nr = np, nc = 2)
-C0_L2 = matrix(nr = np, nc = 2)
-C1_L2 = matrix(nr = np, nc = 2)
-C3_L2 = matrix(nr = np, nc = 2)
-
-# Loop around all pairs of species
-count = 1
-for(x in 1:np) {
-
-	sub_data = DF_split[[x]]
-
-	IDs = as.matrix(sub_data[1,1:2])
-	test = which(pairs[,2] == as.character(IDs[1]) & pairs[,3]==as.character(IDs[2]) | pairs[,2]==as.character(IDs[2]) & pairs[,3]==as.character(IDs[1]))
-	if(length(test)!=0)	type[x] = unique(as.character(pairs[test,4]))
-	
-	# Compute the models
-	models_C2_L0 = fit_models(sub_data, selection = FALSE, funC = C2, funL = L0)
-	models_C2_L1 = fit_models(sub_data, selection = FALSE, funC = C2, funL = L1)
[…]

### 2018-03-20 analysis/source_all.R

@@ -1,17 +1,0 @@
-# Make sure to have all the required packages
-install.packages(c("igraph", "rgdal", "raster", "sp", "viridis","dismo"))
-
-# init parallel option
-parallel = TRUE
-
-# Process the data
-source("./scripts/data_processing/reformat_salix.r") # Note this one will take a lot of time (few hours)
-source("./scripts/data_processing/split_data.r")
-
-# Get the results
-source("./scripts/results/1_metaweb_sampling.r")
-source("./scripts/results/2_example_pair.r")
-source("./scripts/results/3_map_pair.r")
-source("./scripts/results/4_metaweb_holes.r")
-source("./scripts/results/5_map_all.r")
-source("./scripts/results/table_all_models.r")

### 2018-04-04 ms/ms_probaweb.tex
typos on the ms

@@
 \usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
 \usepackage{amsmath}
@@
 interactions in space and time -- \emph{i.e.} a novel approach to interaction
-distribution modelling. We apply this framework to host–parasite interactions
+distribution modeling. We apply this framework to host–parasite interactions
 across Europe and find that two aspects of the environment (temperature and
@@
 large spatial scales opens new perspectives at the interface of species
-distribution modelling and community ecology.
+distribution modeling and community ecology.
 
@@
 usually neglects variation in the way species interact with each other,
-despite accumulating empirical evidence that this is a major source of
+despite accumulating empirical evidence that is a major source of
 diversity \citep{Poisot2015a}. Given this omission, it is perhaps not
@@
 neglects a large part of the complexity of empirical communities, and will
-most likely deliver underwhelming results \citep{Poisot2015c}. Recent attempts
+most likely deliver biased metrics \citep{Poisot2015c}. Recent attempts
 at accounting for interactions in species distribution models
@@
 Species are represented as nodes, so that networks already encompass all the
-information used by current approaches of species distribution modelling; in
+information used by current approaches of species distribution modeling; in
 addition, interactions are represented by links, so that networks provide
@@
 Bascompte2007, Ings2009, Kefi2012}. There is, however, ample evidence that
-interaction networks vary in space and, time \citep{Laliberte2010, Poisot2012,
+interaction networks vary in space and time \citep{Laliberte2010, Poisot2012,
 Schleuning2012, Albouy2014, Poisot2016, Trojelsgaard2015}, even though there
@@
 theory provides explanations for variation in the distribution of the nodes
-\citep{Gravel2011c, Pillai2011,Cazelles2015}, but there is no such explanation
+\citep{Gravel2011c, Pillai2011,Cazelles2015}, but there are no such explanation
 to the variation of node and link occurrences. Consequently, we need theory to
@@
 Given the historically different approaches to modelling the distributions of
-species vs. interactions, there is need to bring the two together. Here, we
+species vs. interactions, there is a need to bring the two together. Here, we
 offer an integrated approach to do so, adopting the view that community
@@
 quantitative method to predict it. The problem could be formalized
-sequentially by understanding first why only a fraction of the species co-
-occur locally and second why these species do or do not interact.
+sequentially by understanding first why only a fraction of the species co-occur locally and second why these species do or do not interact.
 
@@
 Vellend2014}. Interaction themselves may impact co-distribution, as
-hypothesized long ago by Diamond \citet{Diamond1975}. Analyses of community
+hypothesized long ago by \citet{Diamond1975}. Analyses of community
 turnover are usually performed with data represented in a table with rows
@@
 partition it into dissimilarity due to changes in species richness and
-dissimilarity due to actual species turnover \citep{Baselga2010}. T Even
+dissimilarity due to actual species turnover \citep{Baselga2010}. Even
 though all of these methods compare whole lists of species among sites or
@@
 
-Similarly, we are now getting a better understanding of interaction turnover. As
+We are now getting a better understanding of interaction turnover. As
 mentioned above, in the network approach to community structure, species and
@@
 distributions and community assembly, from the local to the global scale.
-Following \citealt{Hutchinson1957}, the niche is viewed as the set of
+Following \citet{Hutchinson1957}, the niche is viewed as the set of
 environmental conditions allowing a population to establish and persist (see
 also \citealt{Holt2009a}). In other words, the niche is the location in that
-multidimensional space that allow a species to have a positive growth rate
+multidimensional space allowing a species to have a positive growth rate
 when rare \citep{Godsoe2017}.  Community turnover arises as a result of
@@
 ecologists have not moved far beyond the "n-dimensional hypervolume" defined
-by Hutchinson. Despite its intuitive interpretation and easy translation into
-species distribution models \citep{Boulangeat2012, Blonder2014}, the concept
-has been frequently criticized \citep{Hardin1960, Peters1991, Silvertown2004},
-and several attempts have been made to expand and improve it
-\citep{Pulliam2000, Chase2003, Soberon2007, Holt2009a, McInerny2012b}.
+by \citet{Hutchinson1957}. Despite its intuitive interpretation and easy
+translation into species distribution models \citep{Boulangeat2012,
+Blonder2014}, the concept has been frequently criticized \citep{Hardin1960,
+Peters1991, Silvertown2004}, and several attempts have been made to expand and
+improve it \citep{Pulliam2000, Chase2003, Soberon2007, Holt2009a,
+McInerny2012b}.
 
@@
 Their representation merges zero-net-growth isoclines delimiting the
-Grinnellian niche ("when does the population persists?") with impact vectors
+Grinnellian niche ("when does the population persist?") with impact vectors
 delimiting the Eltonian niche ("what is the per-capita impact?"). While this
@@
 representation of both components (Fig. 2). The underlying rationale is that,
-in addition to the environmental constraints on demographic performance (Fig.2
+in addition to the environmental constraints on demographic performance (Fig. 2,
 top panel), any organism requires resources to meet its metabolic demands and
-to sustain reproduction (Fig. 2 nodes in network of bottom panel). Abiotic
+to sustain reproduction (Fig. 2, nodes in network of bottom panel). Abiotic
 environmental axes are any non-consumable factors affecting the demographic
@@
 representation make operational the theoretical interpretation of the niche
-and species ranges by Godsoe et al. \citealt{Godsoe2017}. Accordingly, each
+and species ranges by \citet{Godsoe2017}. Accordingly, each
 species can be characterized by an optimal position along both the
@@
 they are co-occurring. This predicate can be refined using information on
-trait distribution and trait matching rules (\citep{Bartomeus2016}).
+trait distribution and trait matching rules \citep{Bartomeus2016}.
 Above, we referred to this entity as the "metaweb" and it corresponds to
@@
 $P(X_{iy},X_{jy}|E_y)$. In this situation, there are no underlying assumptions
-about the ecological processes responsible for co-occurrence. It could arise
-because interactions constrain distribution, where in such case the co-
-occurrence would be conditional on $L$, or, alternatively, because of
+about the ecological processes responsible for co-occurrence. Spatial associations between species could arise
+because interactions constrain distribution, where in such case the co-occurrence would be conditional on $L$, or, alternatively, because of
 environmental requirements shared between $i$ and $j$ \citep{Pollock2014,
@@
 Connor1979, Gotelli2000}). Second- and higher-order interactions (e.g. trophic
-cascades) could also affect co-occurrence \citep{Harris2017,
+cascades) could also affect co-occurrence \citep{Harris2016,
 Staniczenko2017}. Co-occurrence of multiple species embedded in ecological
@@
 (e.g. plant species sharing an herbivore, or herbivores sharing parasitoids,
-could repel each other in space \citealt{Holt1993}). The impact of direct
+could repel each other in space \citep{Holt1993}). The impact of direct
 interactions and first-order indirect interactions on co-occurrence tends to
@@
 revealed interactions to be sensitive to the environment. For instance,
-\citep{Mckinnon2010} showed that predation risks of shorebirds vary at the
+\citet{Mckinnon2010} showed that predation risks of shorebirds vary at the
 continental scale, decreasing from the south to the north. It is also common
@@
 objective here is to illustrate potential applications of the approach
-outlined above, rather than a specific attempt at describing the biogeography
+outlined above, rather than to specifically describe the biogeography
 of this particular community. The focal system consists of local food webs of
 willows (genus \textit{Salix}), their galling insects, and the natural enemies
-(parasitoids and inquilines) of these gallers. We ask:
+(parasitoids and inquilines) of gallers. We ask:
 i) how much does network structure vary across the gradient, and ii) what is
@@
 community of herbivorous insects, with one of the main herbivore groups being
-gall- inducing sawflies (Hymenoptera: Tenthredinidae: Nematinae: Euurina
-\citep{Kopelke1999}). Gall formation is induced by sawfly females during
+gall-inducing sawflies (Hymenoptera: Tenthredinidae: Nematinae: Euurina
+\citep{Kopelke1999}. Gall formation is induced by sawfly females during
 oviposition, and includes marked manipulation of host-plant chemistry by the
@@
 The current study represents the first analysis of the full data set
-from a spatial perspective. Full details about the data collection and species
+from a spatial perspective. Full details about data collection and species
 identification are provided in \citep{Kopelke2017}. Annual mean temperature
@@
 covariates could have also been considered to represent the high
-dimensionality of the niceh, these two variables are likely representative of
-the most important axes of the European climate, and are also more easily
+dimensionality of the niche, these two variables are likely representative of
+the most important axes of European climate, and are also more easily
 interpretable than reduced variables obtained, for example, by principal
@@
 directly represents the co-occurrence probability conditional on the local
-environment, $P(X_{iy},X_{jy}|E_y)$ (models are listed at Table 1 and 2).
+environment, $P(X_{iy},X_{jy}|E_y)$ (models are listed in Tables 1 and 2).
 Hence, this model makes no assumption about the mechanisms driving co-
@@
 divided by the number of times that they co-occurred. The third model is an
-extreme case performed only to test the hypothesis that if two species are
-found to interact at least once, then they should interact whenever they co-
-occur, $P(L_{ijy}|X_{iy},X_{jy})=1$. While not necessarily realistic, this
+extreme case evaluated only to test the hypothesis that if two species are
+found to interact at least once, then they should interact whenever they co-occur, $P(L_{ijy}|X_{iy},X_{jy})=1$. While not necessarily realistic, this
 model tests an assumption commonly invoked in the representation of local
@@
 interaction was observed, and as $\mathcal{L}(\theta_{ijy}|D_{ijy}) =
-1-P(L_{ijy}, X_{iy}, X_{jy})$ if no interaction was observed. The log-
-likelihood was summed over the entire dataset to compare the different models
+1-P(L_{ijy}, X_{iy}, X_{jy})$ if no interaction was observed. The log-likelihood was summed over the entire dataset to compare the different models
 by AIC. We therefore evaluate the likelihood of all local networks, given the
@@
 were consequently removed from the analysis. The log-likelihood reported
-across the entire dataset was summed over all pairs of species observed to co-
-occur at least once. Interactions between the first (\textit{Salix}) and
+across the entire dataset was therefore summed over all pairs of species observed to co-occur at least once. Interactions between the first (\textit{Salix}) and
 second (gallers) trophic layers and those between the second and third
@@
 expected network for each location in a 1 X 1 km grid and computed the
-probabilistic connectance following \citep{Poisot2015c}.
+probabilistic connectance following \citet{Poisot2015c}.
 
 All of the data are openly available in the database \emph{mangal}
-\citep{Poisot2015b} and all R scripts for running the analysis, are provided
+\citep{Poisot2015b} and all R scripts for running the analyses, are provided
 in the github repository 
@@
 
-Despite the extensive sampling, many pairs of species were observed to co-
-occur only a few times. This made it difficult to evaluate interaction
-probabilities with any reasonable confidence interval. Thus, we start with an
-example of a single pair of species selected because of its high number of co-
-occurrences ($N_{ij}=38$): the leaf folder \textit{Phyllocolpa prussica} and
+Despite the extensive sampling, many pairs of species were observed to co-occur only a few times. This made it difficult to evaluate interaction
+probabilities with any reasonable confidence. Thus, we start with an
+example of a single pair of species selected because of its high number of co-occurrences ($N_{ij}=38$): the leaf folder \textit{Phyllocolpa prussica} and
 the parasidoid \textit{Chrysocharis elongata}. These two fairly abundant
@@
 Alternatively, climatic variables significantly impacted co-occurrence (Model
-3 vs Model 4). The neutral model performed worse than the non-random co-
-occurrence model (Model 3 vs Model 6). The full model revealed that the
+3 vs Model 4). The neutral model performed worse than the non-random co-occurrence model (Model 3 vs Model 6). The full model revealed that the
 greatest interaction probability occurred at intermediate temperature and
@@
 the large-scale drivers of network turnover. The results were highly
-consistent among trophic layers (\textit{Salix}–gallers and
-gallers–parasitoids; Table 2), despite very significant variability in the fit
+consistent among trophic levels (\textit{Salix}–gallers and
+gallers–parasitoids; Table 2), despite large variability in the fit
 of the models to the different pairs of species. This variability was
-particularly important for the models of interactions, given co-occurrence.
+particularly important for the models of interactions given co-occurrence.
 Across all pairs of species, the conditional representation of interactions
@@
 network for each location. Using this approach, we mapped the expected
-distribution of network properties across Europe (Fig. 6). For simplicity, we
+distribution of network properties across Europe (Fig. 5). For simplicity, we
 chose to consider connectance as our descriptor of network configuration, as
@@
 rate different from species numbers. Connectance likewise peaked in Northern
-Europe (Fig. 6).
+Europe (Fig. 5).
 
@@
 \citealt{Roininen2005, Nyman2010, Leppanen2014}), but as a net outcome of
-different latitudinal trends across trophic levels, the distribution of co-
-occurrence and therefore of potential interactions differed between the first
+different latitudinal trends across trophic levels, the distribution of co-occurrence and therefore of potential interactions differed between the first
 and second layers of feeding links. The correlation between expected
-\textit{Salix} and gallers richness was 0.73, while it was 0.58 between
+\textit{Salix} and galler richness was 0.73, while it was 0.58 between
 gallers and their parasitoids. Therefore, the ratio of herbivores to
@@
 latitudes. Consequently, overall connectance peaks in Northern Europe (Fig.
-6).
+5).
 
@@
 environment, whereas the probability of observing an interaction between the
-two was, given co-occurrence, not detectably so. The interactions were  highly
+two was, given co-occurrence, not significantly so. The interactions were  highly
 uncertain, as only few pairs of species were systematically interacting when
 co-occurring but most not. This applies to the example species
-\textit{Phyllocolpa prussica} and \textit{Chrysocharis elongata} (Figs 2 and
-3), but also to all species pairs more generally. For the example species
+\textit{Phyllocolpa prussica} and \textit{Chrysocharis elongata} (Figs. 3 and
+4), but also to all species pairs more generally. For the example species
 pair, the full model revealed that the joint probability event (interaction
@@
 assumption in most documented metawebs to date (e.g. \citealt{Havens1992,
-Wood2015}). Rather, an interaction is better represented as aa stochastic
+Wood2015}). Rather, an interaction is better represented as a stochastic
 process whose probability is also influenced by the probability with which
@@
 splits into different sources of uncertainty – i.e., the extent to which a
-species at the higher trophic level runs into a species at the lower level co-
-occurring at the site, the extent to which this interaction is detected by an
+species at the higher trophic level runs into a species at the lower level co-occurring at the site, the extent to which this interaction is detected by an
 observer collecting a finite sample, or simply the uncertainty arising from
@@
 annual temperature and the precipitation gradient. The lack of detectable
-signal may be due to our choice of covariates. Indeed, a previous study on a
-similar system identified habitat characteristics as the primary drivers of
+signal may be due to our choice of covariates. Indeed, a previous study focusing on a subset of the system studied here identified habitat characteristics as the primary drivers of
 interactions \citep{Nyman2015}. New investigations with other systems will
@@
 parasitoid species that requires a host to develop. On the other hand,
-\citealt{Cazelles2016b} found that the strength of this association is often
-rather weak if not neutral (for instance, with the example pair analysed at
+\citet{Cazelles2016b} found that the strength of this association is often
+rather weak if not neutral (for instance, with the example pair presented in
 Table 1). The lack of an association could simply arise when the parasitoid is
-generalist enough that it is not obligated to track the distribution of any
+generalist enough that it is not constrained to track the distribution of any
 single/given host \citep{Cazelles2015}.
@@
 At present, there is only indirect support for the hypothesis that interacting
-species are conditionally distributed but this possibility should be the
+species are conditionally distributed, but this possibility should be the
 topic of theoretical investigation with dynamical metacommunity models \citep{Cazelles2015} and empirical hypothesis testing. The impact of ecological
 interactions on the distribution of co-occurrence has been the topic of many
-publications since \citealt{Diamond1975} seminal study on competition and
+publications since \citet{Diamond1975} seminal study on competition and
 "checkerboard" distribution, but pairwise approaches have only recently
@@
 of species co-occurence. Thus, to gain confidence that the probability of an
-interaction is low, extensive sampling (that is, several records of co-
-occurence) is needed. Generally, our confidence that the interaction is indeed
+interaction is low, extensive sampling (that is, several records of co-occurence) is needed. Generally, our confidence that the interaction is indeed
 impossible will increase with the number of observations of the species pair.
@@
 intentionally omitted the feedback of ecological interactions on co-occurrence
-in this framework. As abundance can impact the occurrence of interactions, and
+in this framework. As abundance can impact the occurrence of interactions, and,
 conversely since interactions impact abundance \citep{Canard2014}, we could
@@
 as a sampling process of the regional pool of potential interactions. Species
-(indicated by coloured nodes) are sampled first, and among the species found in
+(indicated by colored nodes) are sampled first, and among the species found in
 the local network, only some interactions (indicated by blue links) occur.
@@
 proposed in this paper. As a concrete illustration of metaweb sampling, we
-here show a local interaction network among \textit{Salix} (left/green), gallers
-(center/red), and parasitoids (red/blue). The metaweb was constructed by
+here show a local interaction network among \textit{Salix} (bottom/green), gallers
+(center/blue), and parasitoids (top/red). The metaweb was constructed by
 aggregating interactions observed across 370 local networks.
@@
 along this gradient represents their niche position. The focal species will
-feed only on prey species occupying niche locations within a given interval
+feed only on host/prey species occupying niche locations within a given interval
 around the optimum, represented by the horizontal lines. The integrated

### 2018-04-04 ms/ms_probaweb.tex
final edits and compilation

@@
 surprising that biogeographers are still struggling to establish whether
-interactions actually impact the distribution of species at large spatial
+interactions actually impacts the distribution of species at large spatial
 scales \citep{Kissling2012}. An interaction is conceived as the direct effect
@@
 scales up and impact the (co-)distribution of species remains matter of debate
-at the moment \citep{Wisz2012, GonzalezSalazar2013, Cazelles2016b,
+at the moment \citep{Wisz2012, GonzalezSalasar2013, Cazelles2016b,
 Harris2016, Godsoe2017}. Treating interactions as fixed events nonetheless
@@
 interactions are merely treated as fixed covariates affecting distribution.
-Second, they failed to provide a conceptual step forward, both in their
+Second, they fail to provide a conceptual step forward, both in their
 treatment of interactions and in the quality of the predictions they make.
@@
 network turnover. As an illustrative example, we apply this novel framework to
-a large data set on host–parasite interactions across Europe and find that two
+a large data set on host-parasite interactions across Europe and find that two
 aspects of the environment (temperature and precipitation) exert a strong
@@
 The problem of community assembly is often formulated as \textit{how are
-species sampled from a regional pool to constitute a local community
-\citep{Gotzenberger2012}?} This question could be rewritten to address the
+species sampled from a regional pool to constitute a local community}
+\citep{Gotzenberger2012}? This question could be rewritten to address the
 problem of network assembly, as \textit{how do samples from a regional pool of
@@
 successfully explained the complexity of a variety of networks, from food webs
-to plant–pollinator systems \citep{Allesina2008, Williams2010, Eklof2013}.
+to plant-pollinator systems \citep{Allesina2008, Williams2010, Eklof2013}.
 This conceptual framework is, however, limited to local communities, and does
@@
 We now turn to an illustration of our theory with the analysis of an empirical
-dataset of host–parasite networks sampled throughout the south–north
+dataset of host-parasite networks sampled throughout the south-north
 environmental gradient in continental Europe \citep{Kopelke2017}. Our
@@
 
-Local realizations of the willow–galler–parasitoid network were reconstructed
+Local realizations of the willow-galler-parasitoid network were reconstructed
 from community samples collected between 1982 and 2010. During this period,
@@
 co-occur (Fig. 3). The probabilities of co-occurrence and interaction can be
-represented in space, where we found that the highest interaction probability
+represented in space, where we find that the highest interaction probability
 occurred in Central Europe (Fig. 4).
@@
 the large-scale drivers of network turnover. The results were highly
-consistent among trophic levels (\textit{Salix}–gallers and
-gallers–parasitoids; Table 2), despite large variability in the fit
+consistent among trophic levels (\textit{Salix}-gallers and
+gallers-parasitoids; Table 2), despite large variability in the fit
 of the models to the different pairs of species. This variability was
@@
 interactions (Model 2 vs Model 3). Not surprisingly, for both types of
-interactions (\textit{Salix}–galler and galler–parasitoid), the log-likelihood
+interactions (\textit{Salix}-galler and galler-parasitoid), the log-likelihood
 increased when the environment was considered. However, the extra number of
@@
 basis of log-likelihood only, co-occurrence was non-neutral for both
-\textit{Salix}–galler and galler–parasitoid interactions. Thus, according to
+\textit{Salix}-galler and galler-parasitoid interactions. Thus, according to
 AIC, the best model was the one of non-random co-occurrence (Model 3 vs Model
@@
 
-Applying the framework to our large data set on host–parasite interactions
+Applying the framework to our large data set on host-parasite interactions
 across Europe revealed key features in the interaction between \textit{Salix}
@@
 occurrence probabilities, and link density by summation of interaction
-probabilities. Colour gradient ranges from low values (dark blue) to high
+probabilities. Colowr gradient ranges from low values (dark blue) to high
 values (yellow).
@@
 \begin{figure}[ht!]
-\centering\includegraphics[width=0.4\textwidth]{figures/mw_sampling}
+\centering\includegraphics[width=1\textwidth]{figures/mw_sampling}
 \end{figure}

### 2018-06-01 ms/ms_probaweb.tex
Secound round revisions Ecography

@@
 
-\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Benjamin Baiser$^{3}$, Jennifer
-A. Dunne$^{4}$, Jens-Peter Kopelke$^{5}$, Neo D. Martinez$^{6}$, Tommi
-Nyman$^{7}$, Timothée Poisot$^{2,8}$, Daniel B.
-Stouffer$^{9}$, Jason M. Tylianakis$^{9,10}$, Spencer A. Wood$^{11}$, Tomas Roslin$^{12}$ \\
-
-\textbf{1}: Canada Research Chair in Integrative Ecology. Département de
-biologie, Université de Sherbrooke, 2500 Boulevard l'Université,
-Sherbrooke (Québec). J1K 2R1\\
-\textbf{2}: Québec Centre for Biodiversity Science\\
-\textbf{3}: University of Florida, Department of Wildlife Ecology and Conservation, 110 Newins-Ziegler Hall, PO Box 110430, Gainesville, Fl. 32611-0430 \\
-\textbf{4}: Santa Fe Institute, 1399 Hyde Park Road, Santa Fe, NM 87501, USA.\\
-\textbf{5}: Senckenberg Research Institute and Natural History Museum, Senckenberganlage 25, D-60325 Frankfurt am Main, Germany\\
-\textbf{6}: Ecology and Evolutionary Biology Department, University of Arizona, P.O. Box 210088, Tucson, AZ 85721, USA\\
-\textbf{7}: University of Eastern Finland, Department of Environmental and Biological Sciences, P.O. Box 111, FI-80101 Joensuu, Finland\\
-\textbf{8}: Université de Montréal, Département des Sciences Biologiques, 90 Avenue Vincent d’Indy, Montréal, QC H2V3S9, Canada.\\
-\textbf{9}: Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch, New Zealand\\
-\textbf{10}: Department of Life Sciences, Imperial College London, Silwood Park Campus, 
-Buckhurst Road, Ascot, Berkshire SL5 7PY, United Kingdom\\
-\textbf{11}: University of Washington, School of Environmental and Forest Sciences,
-Box 352100, Seattle, WA 98195, USA\\
-\textbf{12}: Department of Ecology, Swedish University of Agricultural Sciences, Box 7044, 750 07 Uppsala, Sweden\\
-
-\textbf{Keywords:} networks, spatial ecology, co-occurrence, probability of interaction\\
+%\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Benjamin Baiser$^{3}$, Jennifer
+%A. Dunne$^{4}$, Jens-Peter Kopelke$^{5}$, Neo D. Martinez$^{6}$, Tommi
+%Nyman$^{7}$, Timothée Poisot$^{2,8}$, Daniel B.
+%Stouffer$^{9}$, Jason M. Tylianakis$^{9,10}$, Spencer A. Wood$^{11}$, Tomas Roslin$^{12}$ \\
+
+%\textbf{1}: Canada Research Chair in Integrative Ecology. Département de
+%biologie, Université de Sherbrooke, 2500 Boulevard l'Université,
+%Sherbrooke (Québec). J1K 2R1\\
+%\textbf{2}: Québec Centre for Biodiversity Science\\
+%\textbf{3}: University of Florida, Department of Wildlife Ecology and Conservation, 110 Newins-Ziegler Hall, PO Box 110430, Gainesville, Fl. 32611-0430 \\
+%\textbf{4}: Santa Fe Institute, 1399 Hyde Park Road, Santa Fe, NM 87501, USA.\\
+%\textbf{5}: Senckenberg Research Institute and Natural History Museum, Senckenberganlage 25, D-60325 Frankfurt am Main, Germany\\
+%\textbf{6}: Ecology and Evolutionary Biology Department, University of Arizona, P.O. Box 210088, Tucson, AZ 85721, USA\\
+%\textbf{7}: University of Eastern Finland, Department of Environmental and Biological Sciences, P.O. Box 111, FI-80101 Joensuu, Finland\\
+%\textbf{8}: Université de Montréal, Département des Sciences Biologiques, 90 Avenue Vincent d’Indy, Montréal, QC H2V3S9, Canada.\\
+%\textbf{9}: Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch, New Zealand\\
+%\textbf{10}: Department of Life Sciences, Imperial College London, Silwood Park Campus, 
+%Buckhurst Road, Ascot, Berkshire SL5 7PY, United Kingdom\\
+%\textbf{11}: University of Washington, School of Environmental and Forest Sciences,
+%Box 352100, Seattle, WA 98195, USA\\
+%\textbf{12}: Department of Ecology, Swedish University of Agricultural Sciences, Box 7044, 750 07 Uppsala, Sweden\\
+
 %\textbf{Words in the abstract: 226} \\ 
@@
 
-Authorship: DG, BB, JAD, NDM, TP, SAW, DBS and JMT contributed to the
-concepts; JPK, TN and TR contributed the data; DG developped the probabilistic
-approach and performed the analysis; DG, TP and TR wroted the first draft and
-all of the authors edited the manuscript.
-
-\newpage
+%Authorship: DG, BB, JAD, NDM, TP, SAW, DBS and JMT contributed to the
+%concepts; JPK, TN and TR contributed the data; DG developped the probabilistic
+%approach and performed the analysis; DG, TP and TR wroted the first draft and
+%all of the authors edited the manuscript.
+
+%\newpage
 \doublespacing
@@
 abundance of species. Both are driven by the way species interact with one
-another, but also by the way these interactions vary across time and space.
+another, but only recently community ecologists realized these interactions 
+vary across time and space and need to be documented.
 Here, we call for an integrated approach, adopting the view that community
@@
 distribution modeling and community ecology.
+
+\textbf{Keywords:} networks, spatial ecology, co-occurrence, probability of interaction\\
 
@@
 Vellend2014}. Interaction themselves may impact co-distribution, as
-hypothesized long ago by \citet{Diamond1975}. Analyses of community
-turnover are usually performed with data represented in a table with rows
-corresponding to sites (or measurements) and columns to species. Metrics of
-beta diversity quantify the variance of this community data
-\citep{Legendre2005}. Traditional approaches rely on measures of dissimilarity
-among communities, such as the Jaccard or Bray–Curtis indices. More recent
-approaches decompose total variation of the community data into species and
-site contributions to beta diversity \citep{Legendre2013}, and further
-partition it into dissimilarity due to changes in species richness and
-dissimilarity due to actual species turnover \citep{Baselga2010}. Even
-though all of these methods compare whole lists of species among sites or
-measurements, they remain fundamentally "species-based", since they report
-variation within columns. None of them explicitly considers variation of
-associations (i.e., of pairs or higher-order motifs – \citealt{Stouffer2007}).
-The only exceptions are the Joint Species Distribution Models
-\citep{Warton2015, Ovaskainen2017}, which further account for the covariance
-among species after representing their response to the environment.
+hypothesized long ago by \citet{Diamond1975}. Analyses of community turnover
+are usually performed with data represented in a table with rows corresponding
+to sites (or measurements) and columns to species. Metrics of beta diversity
+quantify the variance of this community data \citep{Legendre2005}. Traditional
+approaches rely on measures of dissimilarity among communities, such as the
+Jaccard or Bray–Curtis indices. More recent approaches decompose total
+variation of the community data into species and site contributions to beta
+diversity \citep{Legendre2013}, and further partition it into dissimilarity
+due to changes in species richness and dissimilarity due to actual species
+turnover \citep{Baselga2010}. Even though all of these methods compare whole
+lists of species among sites or measurements, they remain fundamentally
+"species-based", since they report variation within columns. None of them
+explicitly considers variation of associations (i.e., of pairs or higher-order
+motifs – \citealt{Stouffer2007}). Some previous studies have considered how
+species distribution could be influenced by the joint effects of the abiotic
+and biotic environment \citep{Stephens2009, GonzalezSalasar2013, Cazelles2015,
+Ovaskainen2017}, here we inverse the problem and describe how the distribution
+of biotic interactions is influenced by species distribution and the
+environment.
 
@@
 
-The first term on the right-hand side of the equation is the probability
-of observing the two species co-occurring at location $y$. It corresponds
-to the Grinnellian dimension of the niche. The second term represents the
-probability that an interaction occurs between species $i$ and $j$, given that
-they are co-occurring. This predicate can be refined using information on
-trait distribution and trait matching rules \citep{Bartomeus2016}.
-Above, we referred to this entity as the "metaweb" and it corresponds to
-the Eltonian dimension of the niche. Below, we will see how this formalism
-can be directly fit to empirical data. But before turning to an application,
-we will discuss the interpretation of different variants of these two terms.
+The first term on the right-hand side of the equation is the probability of
+observing the two species co-occurring at location $y$. It corresponds to the
+Grinnellian dimension of the niche. The second term represents the probability
+that an interaction occurs between species $i$ and $j$, given that they are
+co-occurring. This predicate can be refined using information on trait
+distribution and trait matching rules \citep{Bartomeus2016}. In short, here we
+avoid specific references to traits and considered that interactions are
+provided in the data. But one could develop the model further to integrated
+them, inspired by the framework in \citealt{Gravel2016}. They proposed to
+represent the occurence of an interaction between species as a joint
+probability event $P(L_{ij}, \mathbf{T}_i, \mathbf{T}_j|E)$, where
+$\mathbf{T}_i$ and $\mathbf{T}_j$ are trait vectors for species $i$ and $j$
+respectively. Then after, one may also consider how these traits are related
+to the environment and co-occur in order to develop a trait-based
+representation of the spatial variation of interactions. Above, we referred to
+this entity as the "metaweb" and it corresponds to the Eltonian dimension of
+the niche. Below, we will see how this formalism can be directly fit to
+empirical data, restricting ourselves to occurrences only and refering to the
+above citations for trait-matching and trait-environment relationships. But
+before turning to an application, we will discuss the interpretation of
+different variants of these two terms
 
@@
 local abundance and the local environment. In other words,
-$P(L_{ijy}|X_{ijy}=1) = 1$ and $P(L_{ijy}|X_{ijy}=0) = 0$. This approach might
-be a reasonable approximation if the spatial or temporal scale of sampling and
-inference is so large that the probability of observing at least one
-interaction converges to unity. In this scenario, network variation arises
-solely from species distributions.
+$P(L_{ijy}|X_{iy}=1,X_{jy}=1) = 1$. This approach might be a reasonable
+approximation if the spatial or temporal scale of sampling and inference is so
+large that the probability of observing at least one interaction converges to
+unity. In this scenario, network variation arises solely from species
+distributions.
 
@@
 predicted probabilities. The joint probability $P(L_{ijy},X_{iy},X_{jy})$ was
-then computed from Eq. 2, and the likelihood of each observation $D_{ijy}$ was computed
-as $\mathcal{L}(\theta_{ijy}|D_{ijy})=P(L_{ij},X_{iy},X_{jy})$ if an
-interaction was observed, and as $\mathcal{L}(\theta_{ijy}|D_{ijy}) =
+then computed from Eq. 2, and the likelihood of each observation $D_{ijy}$ given the model $\theta$ was computed
+as $\mathcal{L}(D_{ijy}|\theta)=P(L_{ij},X_{iy},X_{jy})$ if an
+interaction was observed, and as $\mathcal{L}(D_{ijy}|\theta) =
 1-P(L_{ijy}, X_{iy}, X_{jy})$ if no interaction was observed. The log-likelihood was summed over the entire dataset to compare the different models
@@
 
-Despite the extensive sampling, many pairs of species were observed to co-occur only a few times. This made it difficult to evaluate interaction
-probabilities with any reasonable confidence. Thus, we start with an
-example of a single pair of species selected because of its high number of co-occurrences ($N_{ij}=38$): the leaf folder \textit{Phyllocolpa prussica} and
+Despite the extensive sampling, many pairs of species were observed to co-
+occur only a few times. This made it difficult to evaluate interaction
+probabilities with any reasonable confidence. Thus, we start with an example
+of a single pair of species selected because of its high number of co-
+occurrences ($N_{ij}=38$): the leaf folder \textit{Phyllocolpa prussica} and
 the parasidoid \textit{Chrysocharis elongata}. These two fairly abundant
@@
 $P(L_{ij})=0.55$, which means they interacted at 21 different locations. Here,
-a comparison of model fit (Table 1) reveals that conditioning the interaction
+a comparison of model fit (Table 2) reveals that conditioning the interaction
 probability on local environmental conditions adds no explanatory power beyond
-a model assuming the same probability of interaction anywhere in space (Model 1
-vs Model 2). Moreover, when the two species co-occur, the occurrence of the
+a model assuming the same probability of interaction anywhere in space (Model
+2 vs Model 3). Moreover, when the two species co-occur, the occurrence of the
 interaction was insensitive to the environment (Model 2 vs Model 3).
 Alternatively, climatic variables significantly impacted co-occurrence (Model
-3 vs Model 4). The neutral model performed worse than the non-random co-occurrence model (Model 3 vs Model 6). The full model revealed that the
+3 vs Model 4). The independent model performed worse than the non-random co-
+occurrence model (Model 3 vs Model 6). The full model revealed that the
 greatest interaction probability occurred at intermediate temperature and
@@
 consistent among trophic levels (\textit{Salix}-gallers and
-gallers-parasitoids; Table 2), despite large variability in the fit
+gallers-parasitoids; Table 3), despite large variability in the fit
 of the models to the different pairs of species. This variability was
@@
 Across all pairs of species, the conditional representation of interactions
-performed better than the marginal one (Model 1 vs Model 2); that is,
+performed (Model 2) better than the marginal one (Model 1); that is,
 interactions did not occur systematically whenever the two species were found
@@
 the most parsimonious model excluded the effect of the environment. On the
-basis of log-likelihood only, co-occurrence was non-neutral for both
+basis of log-likelihood only, co-occurrence was non-independent for both
 \textit{Salix}-galler and galler-parasitoid interactions. Thus, according to
@@
 (e.g. \citealt{Tylianakis2007}), over environmental gradients
-\citep{Lurgi2012} and in time \citep{Trojelsgaard2015} is accumulating
+\citep{Lurgi2012} and in time \citep{Simanonok2014} is accumulating
 rapidly. It is not clear, however, to what extent the turnover of network
@@
 species-specific responses to the environment, impacting species richness, and
-that co-occurrence was mostly neutral. Further, the occurrence of interactions
+that co-occurrence was mostly independent. Further, the occurrence of interactions
 among host and parasite is highly stochastic even when both are present, and
@@
 
+The framework we provide complements methods to compute network beta-
+diversity presented by \citealt{Poisot2012} and \citealt{Poisot2018}. The total
+network turnover is partitionned in interaction turnover and species
+turnover, which in our approach would correspond to the three terms of Eq. 2,
+respectively. One could easily derive the different $\beta$ of
+\citealt{Poisot2012} using the fitted probabilities. For instance, for a pair
+of species $i$ and $j$ and sites $x$ and $y$, the expectation for the
+fraction $a$ for the interactions would be
+$P(L_{ijx}|X_{ix},X_{ijx})P(L_{ijx}|X_{ix},X_{ijx})$. The same could be
+computed for factions $b$ and $c$, and therefore the expected beta-diversity
+for an entire network could easily be recomputed this way. The interesting
+feature of the approach we proposed is that the different partitions for
+network turnover could be investigated according to different hypotheses (as
+performed here), in order to evaluate for instance the role of environmental
+heterogneity or species co-distribution on network turnover.
+
 We restricted our analysis to the effect of co-occurrence on ecological
@@
 )$, could be considered as a species distribution model taking into account
-the interaction between these species. This derivation would however
-critically depend on a strong \emph{a priori} expectation of the conditional
-probability of observing a species given the distribution of the other
-species. This assumption seems reasonable for some situations, such as a
-parasitoid species that requires a host to develop. On the other hand,
-\citet{Cazelles2016b} found that the strength of this association is often
-rather weak if not neutral (for instance, with the example pair presented in
-Table 1). The lack of an association could simply arise when the parasitoid is
-generalist enough that it is not constrained to track the distribution of any
-single/given host \citep{Cazelles2015}.
+the interaction between these species (in the same spirit as done by
+\citealt{GonzalezSalasar2013}). This derivation would however critically
+depend on a strong \emph{a priori} expectation of the conditional probability
+of observing a species given the distribution of the other species. This
+assumption seems reasonable for some situations, such as a parasitoid species
+that requires a host to develop. On the other hand, \citet{Cazelles2016b}
+found that the strength of this association is often rather weak if not
+inexistant (for instance, with the example pair presented in Table 1). The lack
+of an association could simply arise when the parasitoid is generalist enough
+that it is not constrained to track the distribution of any single/given host
+\citep{Cazelles2015}.
+
+The approach we presented could easily be expanded to account for traits, in
+order to have a complete and more mechanistic representation of the niche.
+Both the Eltonian and Grinelian dimensions of the niche could be represented
+as well. As mentioned earlier, \citealt{Gravel2016} proposed to represent the
+occurrence of interactions based on some trait-matching rules (given by a
+function of the type $P(L_{ij})|\mathbf{T}_i, \mathbf{T}_j, E)$) and the co-
+distribution of traits (corresponding to $P(\mathbf{T}_i, \mathbf{T}_j|E)$).
+The key  insight from this formalism proposed by \citealt{Gravel2016} is that
+trait co-distribution will impact the variation in network structure. As a
+result, it was found that network properties often co-vary with functional
+structure and functional diversity \citealp{Laigle2018}. The next step in the
+development of this framework will be to develop the models for the trait co-
+distribution, for instance following \citealt{Ovaskainen2017}. This may
+facilitate the accessibility and the applicability of the framework since the
+basic unit of analysis is no more the species, but rather a combination of
+traits, thereby facilitating the statistical analysis by sharing information
+among species.
 
@@
 species are conditionally distributed, but this possibility should be the
-topic of theoretical investigation with dynamical metacommunity models \citep{Cazelles2015} and empirical hypothesis testing. The impact of ecological
-interactions on the distribution of co-occurrence has been the topic of many
-publications since \citet{Diamond1975} seminal study on competition and
-"checkerboard" distribution, but pairwise approaches have only recently
-received attention \citep{Veech2013}. Whether two interacting species are more
-closely associated in space remains unclear, since most approaches based on
-null models consider community-level metrics (e.g. \citealt{Gotelli2000}),
-such as the C-score, thereby making it hard to evaluate if specific
-interactions do indeed affect co-occurrence. The expansion of the framework we
-describe to account for the difference between the realized and the
-fundamental niche will therefore require further investigation of the impact
-of interactions on co-occurrence.
+topic of theoretical investigation with dynamical metacommunity models
+\citep{Cazelles2015} and empirical hypothesis testing. The impact of
+ecological interactions on the distribution of co-occurrence has been the
+topic of many publications since \citet{Diamond1975} seminal study on
+competition and "checkerboard" distribution, but pairwise approaches have only
+recently received attention \citep{Veech2013}. Whether two interacting species
+are more closely associated in space remains unclear, since most approaches
+based on null models consider community-level metrics (e.g.
+\citealt{Gotelli2000}), such as the C-score, thereby making it hard to
+evaluate if specific interactions do indeed affect co-occurrence. The
+expansion of the framework we describe to account for the difference between
+the realized and the fundamental niche will therefore require further
+investigation of the impact of interactions on co-occurrence.
 
@@
 of species co-occurence. Thus, to gain confidence that the probability of an
-interaction is low, extensive sampling (that is, several records of co-occurence) is needed. Generally, our confidence that the interaction is indeed
+interaction is low, extensive sampling (that is, several records of co-
+occurence) is needed. Generally, our confidence that the interaction is indeed
 impossible will increase with the number of observations of the species pair.
@@
 can be set as a threshold above which a species pair has finally been observed
-"often enough". This will allow us to deal with both confirmed absences of
-interactions and mere absence of evidence.
+"often enough". For instance, if two species are observed together at $k=10$
+locations but they are never found interacting ($n=0$), this means that the
+maximum likelihood estimate for the probability of this binomial distribution
+is $p=0$. Using the Clopper-Pearson method to compute the 95\% confidence
+interval, we find that the real value of the probability of the interaction
+occuring is somewhere between 0 and 0.31. This interval is rather large,
+indicating that a significant amount of sampling is required to have credible
+interaction networks. Fortunately, there are bayesian methods could be used to
+complement available information and reduce this uncertainty
+\citep{Cirtwill2018}.
 
@@
 
+%\begin{landscape}
+\begin{table}[]
+\centering
+
+\caption{Example of data used to perform the analysis.
+Traditional species distribution models represent the occurrence of single species as a function of the environment, with models such as $X_i­~Temp$ performed one species after the other.
+Some also tried to represent both the abiotic and biotic niche, with models such as $X_i­~Temp + X_j$ (e.g.
+\citealt{GonzalezSalasar2013}), while the new joint species distribution models \citep{Ovaskainen2017} consider the entire community at once ($\mathbf{X}~Temp$) and aims at representing co-distribution ($X_{ij}$).
+Here the focus is on the occurrence of interactions, $L_{ij}$.
+The full model (see model 3, Tables 1 and 2) considers the result of two submodels, one representing the occurrence of interactions given co-occurrence, $L_{ij}~Temp$ (evaluated only on the subset of data where $X_{ij}=1$), and the other representing the co-occurrence, $X_{ij}~Temp$.}
+
+\begin{tabular}{llllllll}
+\hline
+	Location & $Sp_i$ & $Sp_j$ & $X_i$ & $X_j$ & $X_{ij}$ & $L_{ij}$ & Temp \\ \hline
+	1 & A & B & 0 & 0 & 0 & 0 & 20 \\ 
+	2 & A & B & 1 & 1 & 1 & 0 & 21 \\ 
+	3 & A & B & 1 & 0 & 0 & 0 & 22 \\ 
+	4 & A & B & 0 & 0 & 0 & 0 & 23 \\ 
+	5 & A & B & 1 & 1 & 1 & 1 & 24 \\ 
+	1 & A & C & 0 & 1 & 0 & 0 & 20 \\ 
+	2 & A & C & 1 & 0 & 0 & 0 & 21 \\ 
+	3 & A & C & 1 & 1 & 1 & 1 & 22 \\ 
+	4 & A & C & 0 & 0 & 0 & 0 & 23 \\ 
+	5 & A & C & 1 & 0 & 0 & 0 & 24 \\ 
+\hline
+\end{tabular}
+\end{table}
+%\end{landscape}
+
+\newpage
+%========================================================%
 \begin{landscape}
@@
 folder \textit{Phyllocolpa prussica}) and the parasitoid \textit{Chrysocharis
-elongata}}
+elongata}}. Note that $E$ is a short notation including both temperature and precipitation.
 \begin{tabular}{llllll}
@@
 	6 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}|E_y)P(X_{jy}|E_y)$ 	& -68.8 & 15 	& 167.6 \\
+\hline
 \end{tabular}
@@
 (center/blue), and parasitoids (top/red). The metaweb was constructed by
-aggregating interactions observed across 370 local networks.
+aggregating interactions observed across 370 local networks. Nodes were distributed 
+to minimize crossing of interactions.
 
@@
 connectance across Europe}. The representation is based on predictions from
-Model 3 (see Table 2) using climate data extracted from WorldClim over a 1km x 1km grid. Species richness is obtained by summation of individual
-occurrence probabilities, and link density by summation of interaction
-probabilities. Colowr gradient ranges from low values (dark blue) to high
-values (yellow).
+Model 3 (see Table 2) using climate data extracted from WorldClim over a 1km x
+1km grid. Species richness is obtained by summation of individual occurrence
+probabilities, and link density by summation of interaction probabilities.
+Color gradient ranges from low values (dark blue) to high values (yellow).
 

### 2018-07-31 ms/ms_probaweb.tex
add extension in path; change for png instead of pdf
attempt to convert to ms word

@@
 
-%\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Benjamin Baiser$^{3}$, Jennifer
-%A. Dunne$^{4}$, Jens-Peter Kopelke$^{5}$, Neo D. Martinez$^{6}$, Tommi
-%Nyman$^{7}$, Timothée Poisot$^{2,8}$, Daniel B.
-%Stouffer$^{9}$, Jason M. Tylianakis$^{9,10}$, Spencer A. Wood$^{11}$, Tomas Roslin$^{12}$ \\
-
-%\textbf{1}: Canada Research Chair in Integrative Ecology. Département de
-%biologie, Université de Sherbrooke, 2500 Boulevard l'Université,
-%Sherbrooke (Québec). J1K 2R1\\
-%\textbf{2}: Québec Centre for Biodiversity Science\\
-%\textbf{3}: University of Florida, Department of Wildlife Ecology and Conservation, 110 Newins-Ziegler Hall, PO Box 110430, Gainesville, Fl. 32611-0430 \\
-%\textbf{4}: Santa Fe Institute, 1399 Hyde Park Road, Santa Fe, NM 87501, USA.\\
-%\textbf{5}: Senckenberg Research Institute and Natural History Museum, Senckenberganlage 25, D-60325 Frankfurt am Main, Germany\\
-%\textbf{6}: Ecology and Evolutionary Biology Department, University of Arizona, P.O. Box 210088, Tucson, AZ 85721, USA\\
-%\textbf{7}: University of Eastern Finland, Department of Environmental and Biological Sciences, P.O. Box 111, FI-80101 Joensuu, Finland\\
-%\textbf{8}: Université de Montréal, Département des Sciences Biologiques, 90 Avenue Vincent d’Indy, Montréal, QC H2V3S9, Canada.\\
-%\textbf{9}: Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch, New Zealand\\
-%\textbf{10}: Department of Life Sciences, Imperial College London, Silwood Park Campus, 
-%Buckhurst Road, Ascot, Berkshire SL5 7PY, United Kingdom\\
-%\textbf{11}: University of Washington, School of Environmental and Forest Sciences,
-%Box 352100, Seattle, WA 98195, USA\\
-%\textbf{12}: Department of Ecology, Swedish University of Agricultural Sciences, Box 7044, 750 07 Uppsala, Sweden\\
+\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Benjamin Baiser$^{3}$, Jennifer
+A. Dunne$^{4}$, Jens-Peter Kopelke$^{5}$, Neo D. Martinez$^{6}$, Tommi
+Nyman$^{7}$, Timothée Poisot$^{2,8}$, Daniel B.
+Stouffer$^{9}$, Jason M. Tylianakis$^{9,10}$, Spencer A. Wood$^{11}$, Tomas Roslin$^{12}$ \\
+
+\textbf{1}: Canada Research Chair in Integrative Ecology. Département de
+biologie, Université de Sherbrooke, 2500 Boulevard l'Université,
+Sherbrooke (Québec). J1K 2R1\\
+\textbf{2}: Québec Centre for Biodiversity Science\\
+\textbf{3}: University of Florida, Department of Wildlife Ecology and Conservation, 110 Newins-Ziegler Hall, PO Box 110430, Gainesville, Fl. 32611-0430 \\
+\textbf{4}: Santa Fe Institute, 1399 Hyde Park Road, Santa Fe, NM 87501, USA.\\
+\textbf{5}: Senckenberg Research Institute and Natural History Museum, Senckenberganlage 25, D-60325 Frankfurt am Main, Germany\\
+\textbf{6}: Ecology and Evolutionary Biology Department, University of Arizona, P.O. Box 210088, Tucson, AZ 85721, USA\\
+\textbf{7}: University of Eastern Finland, Department of Environmental and Biological Sciences, P.O. Box 111, FI-80101 Joensuu, Finland\\
+\textbf{8}: Université de Montréal, Département des Sciences Biologiques, 90 Avenue Vincent d’Indy, Montréal, QC H2V3S9, Canada.\\
+\textbf{9}: Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch, New Zealand\\
+\textbf{10}: Department of Life Sciences, Imperial College London, Silwood Park Campus, 
+Buckhurst Road, Ascot, Berkshire SL5 7PY, United Kingdom\\
+\textbf{11}: University of Washington, School of Environmental and Forest Sciences,
+Box 352100, Seattle, WA 98195, USA\\
+\textbf{12}: Department of Ecology, Swedish University of Agricultural Sciences, Box 7044, 750 07 Uppsala, Sweden\\
 
@@
 
-%Authorship: DG, BB, JAD, NDM, TP, SAW, DBS and JMT contributed to the
-%concepts; JPK, TN and TR contributed the data; DG developped the probabilistic
-%approach and performed the analysis; DG, TP and TR wroted the first draft and
-%all of the authors edited the manuscript.
-
-%\newpage
+Authorship: DG, BB, JAD, NDM, TP, SAW, DBS and JMT contributed to the
+concepts; JPK, TN and TR contributed the data; DG developped the probabilistic
+approach and performed the analysis; DG, TP and TR wroted the first draft and
+all of the authors edited the manuscript.
+
+\newpage
 \doublespacing
@@
 abundance of species. Both are driven by the way species interact with one
-another, but only recently community ecologists realized these interactions 
-vary across time and space and need to be documented.
-Here, we call for an integrated approach, adopting the view that community
-structure is best represented as a network of ecological interactions, and
-show how it translates to biogeography questions. We propose that the
-ecological niche should encompass the effect of the environment
-on species distribution (the Grinnellian dimension of the niche) and on the
-ecological interactions among them (the Eltonian dimension). Starting from
-this concept, we develop a quantitative theory to explain turnover of
-interactions in space and time -- \emph{i.e.} a novel approach to interaction
-distribution modeling. We apply this framework to host–parasite interactions
-across Europe and find that two aspects of the environment (temperature and
-precipitation) exert a strong imprint on species co-occurrence, but not on
-species interactions. Even where species co-occur, interaction proves to be
-stochastic rather than deterministic, adding to variation in realized network
-structure. We also find that a large majority of host-parasite pairs are never
-found together, thus precluding any inferences regarding their probability to
-interact. This first attempt to explain variation of network structure at
-large spatial scales opens new perspectives at the interface of species
-distribution modeling and community ecology.
+another, but only recently community ecologists realized the need to document
+their spatial and temporal variation. Here, we call for an integrated
+approach, adopting the view that community structure is best represented as a
+network of ecological interactions, and show how it translates to biogeography
+questions. We propose that the ecological niche should encompass the effect of
+the environment on species distribution (the Grinnellian dimension of the
+niche) and on the ecological interactions among them (the Eltonian dimension).
+Starting from this concept, we develop a quantitative theory to explain
+turnover of interactions in space and time -- \emph{i.e.} a novel approach to
+interaction distribution modeling. We apply this framework to host–parasite
+interactions across Europe and find that two aspects of the environment
+(temperature and precipitation) exert a strong imprint on species co-
+occurrence, but not on species interactions. Even where species co-occur,
+interaction proves to be stochastic rather than deterministic, adding to
+variation in realized network structure. We also find that a large majority of
+host-parasite pairs are never found together, thus precluding any inferences
+regarding their probability to interact. This first attempt to explain
+variation of network structure at large spatial scales opens new perspectives
+at the interface of species distribution modeling and community ecology.
 
@@
 species distribution could be influenced by the joint effects of the abiotic
-and biotic environment \citep{Stephens2009, GonzalezSalasar2013, Cazelles2015,
+and biotic environment \citep{Stephens2009, GonzalezSalazar2013, Cazelles2015,
 Ovaskainen2017}, here we inverse the problem and describe how the distribution
@@
 co-occurring. This predicate can be refined using information on trait
-distribution and trait matching rules \citep{Bartomeus2016}. In short, here we
-avoid specific references to traits and considered that interactions are
-provided in the data. But one could develop the model further to integrated
-them, inspired by the framework in \citealt{Gravel2016}. They proposed to
-represent the occurence of an interaction between species as a joint
-probability event $P(L_{ij}, \mathbf{T}_i, \mathbf{T}_j|E)$, where
+distribution and trait matching rules . For brevity, we have here avoided
+specific references to traits and considered that the interactions are
+provided in the data. But one could develop the model further to integrate
+such traits, inspired by the framework developed by Gravel et al. 2016. They
+proposed to represent the occurence of an interaction between species as a
+joint probability event $P(L_{ij}, \mathbf{T}_i, \mathbf{T}_j|E)$, where
 $\mathbf{T}_i$ and $\mathbf{T}_j$ are trait vectors for species $i$ and $j$
-respectively. Then after, one may also consider how these traits are related
-to the environment and co-occur in order to develop a trait-based
-representation of the spatial variation of interactions. Above, we referred to
-this entity as the "metaweb" and it corresponds to the Eltonian dimension of
-the niche. Below, we will see how this formalism can be directly fit to
+respectively. In order to develop a trait-based representation of the spatial
+variation of interactions, one may thereafter consider how these traits are
+related to the environment and how they co-occur. Above, we referred to this
+entity as the "metaweb" and note that it corresponds to the Eltonian dimension
+of the niche. Below, we will see how this formalism can be directly fit to
 empirical data, restricting ourselves to occurrences only and refering to the
@@
 before turning to an application, we will discuss the interpretation of
-different variants of these two terms
+different variants of these two terms.
 
@@
 of the pairs of species may have been observed co-occurring only a few times,
-or never.
-As a consequence, despite the extent of the sampling, there is significant uncertainty in the quantification of some of the links.
-The above described methodology explicitly aims at describing this uncertainty, and research should be done to develop methods to reduce it (see Conclusion).
+or never. As a consequence, despite the extent of the sampling, there is
+significant uncertainty in the quantification of some of the links. The above
+described methodology explicitly aims at describing this uncertainty, and
+research should be done to develop methods to reduce it (see Conclusion).
 
@@
 
-The framework we provide complements methods to compute network beta-
-diversity presented by \citealt{Poisot2012} and \citealt{Poisot2018}. The total
-network turnover is partitionned in interaction turnover and species
-turnover, which in our approach would correspond to the three terms of Eq. 2,
-respectively. One could easily derive the different $\beta$ of
+The framework we provide complements methods to compute network beta-diversity
+presented by \citealt{Poisot2012} and \citealt{Poisot2018}. The total network
+turnover is partitioned into interaction turnover and species turnover – which
+in our approach would correspond to the three terms of Eq. 2, respectively.
+Importantly, one could easily derive the different $\beta$ of
 \citealt{Poisot2012} using the fitted probabilities. For instance, for a pair
-of species $i$ and $j$ and sites $x$ and $y$, the expectation for the
-fraction $a$ for the interactions would be
+of species $i$ and $j$ and sites $x$ and $y$, the expectation for the fraction
+$a$ for the interactions would be
 $P(L_{ijx}|X_{ix},X_{ijx})P(L_{ijx}|X_{ix},X_{ijx})$. The same could be
-computed for factions $b$ and $c$, and therefore the expected beta-diversity
-for an entire network could easily be recomputed this way. The interesting
-feature of the approach we proposed is that the different partitions for
-network turnover could be investigated according to different hypotheses (as
-performed here), in order to evaluate for instance the role of environmental
-heterogneity or species co-distribution on network turnover.
+computed for fractions $b$, and therefore the expected beta-diversity for an
+entire network could be recomputed this way. The novel feature of the approach
+presented here is then that the different contributions to network turnover
+can be attributed to different hypotheses (as performed here), in order to
+evaluate for instance the role of environmental heterogeneity or species co-
+distribution on network turnover.
 
@@
 )$, could be considered as a species distribution model taking into account
-the interaction between these species (in the same spirit as done by
-\citealt{GonzalezSalasar2013}). This derivation would however critically
-depend on a strong \emph{a priori} expectation of the conditional probability
-of observing a species given the distribution of the other species. This
-assumption seems reasonable for some situations, such as a parasitoid species
-that requires a host to develop. On the other hand, \citet{Cazelles2016b}
-found that the strength of this association is often rather weak if not
-inexistant (for instance, with the example pair presented in Table 1). The lack
-of an association could simply arise when the parasitoid is generalist enough
-that it is not constrained to track the distribution of any single/given host
+the interaction between these species (in the same spirit as done by Gonzalez-
+Salazar et al. 2013). This derivation would however critically depend on a
+strong \emph{a priori} expectation of the conditional probability of observing
+a species given the distribution of the other species. This assumption seems
+reasonable for some situations, such as a parasitoid species that requires a
+host to develop. On the other hand, \citet{Cazelles2016b} found that the
+strength of this association is often rather weak if not inexistant (for
+instance, with the example pair presented in Table 1). The lack of an
+association could simply arise when the parasitoid is generalist enough that
+it is not constrained to track the distribution of any single/given host
 \citep{Cazelles2015}.
@@
 The approach we presented could easily be expanded to account for traits, in
-order to have a complete and more mechanistic representation of the niche.
-Both the Eltonian and Grinelian dimensions of the niche could be represented
-as well. As mentioned earlier, \citealt{Gravel2016} proposed to represent the
-occurrence of interactions based on some trait-matching rules (given by a
-function of the type $P(L_{ij})|\mathbf{T}_i, \mathbf{T}_j, E)$) and the co-
-distribution of traits (corresponding to $P(\mathbf{T}_i, \mathbf{T}_j|E)$).
-The key  insight from this formalism proposed by \citealt{Gravel2016} is that
-trait co-distribution will impact the variation in network structure. As a
-result, it was found that network properties often co-vary with functional
-structure and functional diversity \citealp{Laigle2018}. The next step in the
-development of this framework will be to develop the models for the trait co-
-distribution, for instance following \citealt{Ovaskainen2017}. This may
-facilitate the accessibility and the applicability of the framework since the
-basic unit of analysis is no more the species, but rather a combination of
-traits, thereby facilitating the statistical analysis by sharing information
-among species.
+order to derive a complete and more mechanistic representation of the niche.
+In this context, both the Eltonian and Grinnellian dimensions of the niche
+could be represented. As mentioned earlier, \citealt{Gravel2016} proposed to
+represent the occurrence of interactions based on some trait-matching rules
+(given by a function of the type $P(L_{ij})|\mathbf{T}_i, \mathbf{T}_j, E)$)
+and the co-distribution of traits (corresponding to $P(\mathbf{T}_i,
+\mathbf{T}_j|E)$). The key  insight from the formalism proposed by
+\citealt{Gravel2016} is that the co-distribution of traits will impact
+variation in network structure. As a result, it was found that network
+properties often co-vary with functional structure and functional diversity
+\citealp{Laigle2018}. The next step in the development of this framework will
+be to develop the models for the co-distribution of traits, for instance
+following Ovaskainen et al. 2017. This may facilitate the accessibility and
+the applicability of the framework, since the basic unit of analysis is no
+longer the species, but rather a combination of traits, thereby facilitating
+the statistical analysis by sharing information among species.
 
@@
 "often enough". For instance, if two species are observed together at $k=10$
-locations but they are never found interacting ($n=0$), this means that the
-maximum likelihood estimate for the probability of this binomial distribution
-is $p=0$. Using the Clopper-Pearson method to compute the 95\% confidence
+locations but are never found interacting ($n=0$), this means that the maximum
+likelihood estimate for the probability of this binomial distribution is
+$p=0$. Using the Clopper-Pearson method to compute the 95\% confidence
 interval, we find that the real value of the probability of the interaction
@@
 indicating that a significant amount of sampling is required to have credible
-interaction networks. Fortunately, there are bayesian methods could be used to
-complement available information and reduce this uncertainty
+interaction networks. Fortunately, there are Bayesian methods which could be
+used to complement available information and reduce this uncertainty
 \citep{Cirtwill2018}.
@@
 \hline
-	Location & $Sp_i$ & $Sp_j$ & $X_i$ & $X_j$ & $X_{ij}$ & $L_{ij}$ & Temp \\ \hline
-	1 & A & B & 0 & 0 & 0 & 0 & 20 \\ 
-	2 & A & B & 1 & 1 & 1 & 0 & 21 \\ 
-	3 & A & B & 1 & 0 & 0 & 0 & 22 \\ 
-	4 & A & B & 0 & 0 & 0 & 0 & 23 \\ 
-	5 & A & B & 1 & 1 & 1 & 1 & 24 \\ 
-	1 & A & C & 0 & 1 & 0 & 0 & 20 \\ 
-	2 & A & C & 1 & 0 & 0 & 0 & 21 \\ 
-	3 & A & C & 1 & 1 & 1 & 1 & 22 \\ 
-	4 & A & C & 0 & 0 & 0 & 0 & 23 \\ 
-	5 & A & C & 1 & 0 & 0 & 0 & 24 \\ 
+Location & $Sp_i$ & $Sp_j$ & $X_i$ & $X_j$ & $X_{ij}$ & $L_{ij}$ & Av. temp \\ \hline
+Kühkopf 		& Phyllocolpa prussica  & Chrysocharis elongata & 1 & 1 & 1 & 1 &  8.25 \\
+Kühkopf 		& Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 1 & 0 & 0 &  8.25 \\
+Ötztal 			& Phyllocolpa prussica  & Chrysocharis elongata & 0 & 0 & 0 & 0 & -1.50 \\
+Ötztal 			& Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 0 & 0 & 0 & -1.50 \\
+Kilpisjärvi		& Phyllocolpa prussica  & Chrysocharis elongata & 0 & 1 & 0 & 0 & -1.92 \\
+Kilpisjärvi		& Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 1 & 0 & 0 & -1.92 \\
+Wüstensachsen	& Phyllocolpa prussica  & Chrysocharis elongata & 1 & 1 & 1 & 0 &  5.58 \\
+Wüstensachsen	& Phyllocolpa leucapsis & Chrysocharis elongata & 1 & 1 & 1 & 1 &  5.58 \\
+Steinamoen      & Phyllocolpa prussica  & Chrysocharis elongata & 0 & 1 & 0 & 0 &  3.17 \\
+Steinamoen      & Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 1 & 0 & 0 &  3.17 \\ 
 \hline

### 2018-08-30 ms/ms_probaweb.tex

@@
 species distribution could be influenced by the joint effects of the abiotic
-and biotic environment \citep{Stephens2009, GonzalezSalazar2013, Cazelles2015,
+and biotic environment \citep{Stephens2009, GonzalezSalasar2013, Cazelles2015,
 Ovaskainen2017}, here we inverse the problem and describe how the distribution
@@
 \begin{equation}
-	\text{P}(X_{iy},X_{jy},L_{ijy}|E_y)
+	\text{P}(X_{iy},X_{jy},L_{ijy}\lvert E_y)
 \end{equation}
@@
 \begin{equation}
-	P(X_{iy},X_{jy},L_{ijy}|E_y)=P(X_{iy},X_{jy}|E_y)P(L_{ijy}|X_{iy},X_{jy},E_y)
+	P(X_{iy},X_{jy},L_{ijy}\lvert E_y)=P(X_{iy},X_{jy}\lvert E_y)P(L_{ijy}\lvert X_{iy},X_{jy},E_y)
 \end{equation}
@@
 proposed to represent the occurence of an interaction between species as a
-joint probability event $P(L_{ij}, \mathbf{T}_i, \mathbf{T}_j|E)$, where
+joint probability event $P(L_{ij}, \mathbf{T}_i, \mathbf{T}_j\lvert E)$, where
 $\mathbf{T}_i$ and $\mathbf{T}_j$ are trait vectors for species $i$ and $j$
@@
 probability of co-occurrence directly to the environment,
-$P(X_{iy},X_{jy}|E_y)$. In this situation, there are no underlying assumptions
+$P(X_{iy},X_{jy}\lvert E_y)$. In this situation, there are no underlying assumptions
 about the ecological processes responsible for co-occurrence. Spatial associations between species could arise
@@
 and the conditional occurrence must be accounted for explicitly,
-$P(X_{iy},X_{jy} |E_y)=P(X_{iy}|E_y,X_{jy})P(X_{jy}|E_y)$. In the latter case,
+$P(X_{iy},X_{jy} \lvert E_y)=P(X_{iy}\lvert E_y,X_{jy})P(X_{jy}\lvert E_y)$. In the latter case,
 species are independent, and only the marginal occurrence must be accounted
-for, $P( X_{ijy}|E_y)=P(X_{iy} |E_y)P(X_{jy} |E_y)$.
+for, $P( X_{ijy}\lvert E_y)=P(X_{iy} \lvert E_y)P(X_{jy} \lvert E_y)$.
 
@@
 local abundance and the local environment. In other words,
-$P(L_{ijy}|X_{iy}=1,X_{jy}=1) = 1$. This approach might be a reasonable
+$P(L_{ijy}\lvert X_{iy}=1,X_{jy}=1) = 1$. This approach might be a reasonable
 approximation if the spatial or temporal scale of sampling and inference is so
@@
 Second, ecological interactions could also vary with the environment, so that
-$P(L_{ijy}|E_y)$. Although it is rare to see a conditional representation of
+$P(L_{ijy}\lvert E_y)$. Although it is rare to see a conditional representation of
 pairwise ecological interactions, experimental studies have frequently
@@
 directly represents the co-occurrence probability conditional on the local
-environment, $P(X_{iy},X_{jy}|E_y)$ (models are listed in Tables 1 and 2).
+environment, $P(X_{iy},X_{jy}\lvert E_y)$ (models are listed in Tables 1 and 2).
 Hence, this model makes no assumption about the mechanisms driving co-
@@
 independent occurrence of species. In this case, we independently fit
-$P(X_{iy} |E_y)$ and $P(X_{jy} |E_y)$, and we then take their product to
+$P(X_{iy} \lvert E_y)$ and $P(X_{jy} \lvert E_y)$, and we then take their product to
 derive the probability of co-occurrence. This model should be viewed as a null
@@
 probability. The first model conditions the interaction probability on the
-local environmental variables, $P(L_{ijy}|X_{iy},X_{jy},E_y)$. Consequently,
+local environmental variables, $P(L_{ijy}\lvert X_{iy},X_{jy},E_y)$. Consequently,
 the model was fit to the subset of the data where the two species co-occur.
 The second model fits the interaction probability independently of the local
-environmental variables, $P(L_{ijy}|X_{iy},X_{jy})$. It corresponds to the
+environmental variables, $P(L_{ijy}\lvert X_{iy},X_{jy})$. It corresponds to the
 number of times the two species were observed to interact when co-occurring,
@@
 extreme case evaluated only to test the hypothesis that if two species are
-found to interact at least once, then they should interact whenever they co-occur, $P(L_{ijy}|X_{iy},X_{jy})=1$. While not necessarily realistic, this
+found to interact at least once, then they should interact whenever they co-occur, $P(L_{ijy}\lvert X_{iy},X_{jy})=1$. While not necessarily realistic, this
 model tests an assumption commonly invoked in the representation of local
@@
 then computed from Eq. 2, and the likelihood of each observation $D_{ijy}$ given the model $\theta$ was computed
-as $\mathcal{L}(D_{ijy}|\theta)=P(L_{ij},X_{iy},X_{jy})$ if an
-interaction was observed, and as $\mathcal{L}(D_{ijy}|\theta) =
+as $\mathcal{L}(D_{ijy}\lvert \theta)=P(L_{ij},X_{iy},X_{jy})$ if an
+interaction was observed, and as $\mathcal{L}(D_{ijy}\lvert \theta) =
 1-P(L_{ijy}, X_{iy}, X_{jy})$ if no interaction was observed. The log-likelihood was summed over the entire dataset to compare the different models
@@
 $a$ for the interactions would be
-$P(L_{ijx}|X_{ix},X_{ijx})P(L_{ijx}|X_{ix},X_{ijx})$. The same could be
+$P(L_{ijx}\lvert X_{ix},X_{ijx})P(L_{ijx}\lvert X_{ix},X_{ijx})$. The same could be
 computed for fractions $b$, and therefore the expected beta-diversity for an
@@
 realized niche, and how this applies to our framework. For example, we have
-considered above simply the co-occurrence probability, $P(X_{iy},X_{jy}|E_y)$,
-which could be expanded as $P(X_{iy}|X_{jy},E_y) P(X_{jy}| E_y )$. After some
-re-arrangement of Eq. 2, the marginal occurrence probability, $P(X_{jy}|E_y
+considered above simply the co-occurrence probability, $P(X_{iy},X_{jy}\lvert E_y)$,
+which could be expanded as $P(X_{iy}\lvert X_{jy},E_y) P(X_{jy}\lvert  E_y )$. After some
+re-arrangement of Eq. 2, the marginal occurrence probability, $P(X_{jy}\lvert E_y
 )$, could be considered as a species distribution model taking into account
@@
 represent the occurrence of interactions based on some trait-matching rules
-(given by a function of the type $P(L_{ij})|\mathbf{T}_i, \mathbf{T}_j, E)$)
+(given by a function of the type $P(L_{ij})\lvert \mathbf{T}_i, \mathbf{T}_j, E)$)
 and the co-distribution of traits (corresponding to $P(\mathbf{T}_i,
-\mathbf{T}_j|E)$). The key  insight from the formalism proposed by
+\mathbf{T}_j\lvert E)$). The key  insight from the formalism proposed by
 \citealt{Gravel2016} is that the co-distribution of traits will impact
@@
 \hline
+
 Location & $Sp_i$ & $Sp_j$ & $X_i$ & $X_j$ & $X_{ij}$ & $L_{ij}$ & Av. temp \\ \hline
@@
 Steinamoen      & Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 1 & 0 & 0 &  3.17 \\
+
 \hline
@@
 	\# & Metaweb model 						& Co-occurrence model 			& LL 	& npars & AIC \\ \hline
-	1 & $P(L_{ijy})$ 						& $P(X_{iy},X_{jy}|E_y)$ 		& -71.1 & 6 	& 154.2 \\
-	2 & $P(L_{ijy} | X_{iy}, X_{jy})$ 		& $P(X_{iy},X_{jy}|E_y)$ 		& -65.7 & 6 	& 143.4 \\
-	3 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy}|E_y)$ 		& -65.6 & 10 	& 151.3 \\ \hline
-	4 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy})$ 			& -84.5 & 6 	& 183 \\
-	5 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})P(X_{jy})$ 			& -80.7 & 7 	& 173.4 \\
-	6 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}|E_y)P(X_{jy}|E_y)$ 	& -68.8 & 15 	& 167.6 \\
+	1 & $P(L_{ijy})$ 						& $P(X_{iy},X_{jy}\lvert E_y)$ 		& -71.1 & 6 	& 154.2 \\
+	2 & $P(L_{ijy} \lvert  X_{iy}, X_{jy})$ 		& $P(X_{iy},X_{jy}\lvert E_y)$ 		& -65.7 & 6 	& 143.4 \\
+	3 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy}\lvert E_y)$ 		& -65.6 & 10 	& 151.3 \\ \hline
+	4 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy})$ 			& -84.5 & 6 	& 183 \\
+	5 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})P(X_{jy})$ 			& -80.7 & 7 	& 173.4 \\
+	6 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}\lvert E_y)P(X_{jy}\lvert E_y)$ 	& -68.8 & 15 	& 167.6 \\
 \hline
@@
 	Interaction & \# & Metaweb model & Co-occurrence model & LL & npars & AIC \\ \hline
-	\textit{Salix}-Galler & 1 & $P(L_{ijy})$ & $P(X_{iy},X_{jy}|E_y)$ & -6022.1 & 7548 & 27140.3 \\
-	 & 2 & $P(L_{ijy}|X_{iy},X_{jy})$ & $P(X_{iy},X_{jy}|E_y)$ & -5547.9 & 7548 & 26191.8 \\
-	 & 3 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy}|E_y)$ & -5364.0 & 12580 & 35888.0 \\
-	 & 4 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy})$ & -5998.4 & 8806 & 30287.2 \\
-	 & 5 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})P(X_{jy})$ & -6636.1 & 7548 & 27092.7 \\
-	 & 6 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}|E_y)P(X_{jy}|E_y)$ & -6002.9 & 18870 & 49745.7 \\ \hline
-	Galler-Parasitoid & 1 & $P(L_{ijy})$ & $P(X_{iy},X_{jy}|E_y)$ & -22068.1 & 19206 & 82548.2 \\
-	 & 2 & $P(L_{ijy} | X_{iy}, X_{jy})$ & $P(X_{iy},X_{jy}|E_y)$ & -19504.8 & 19206 & 77421.6 \\
-	 & 3 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy}|E_y)$ & -20217.0 & 32010 & 104454.1 \\
-	 & 4 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy})$ & -19591.3 & 22407 & 77594.5 \\
-	 & 5 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})P(X_{jy})$ & -22491.5 & 19206 & 89796.9 \\
-	 & 6 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}|E_y)P(X_{jy}|E_y)$ & -18936.9 & 48015 & 133903.7 \\
+	\textit{Salix}-Galler & 1 & $P(L_{ijy})$ & $P(X_{iy},X_{jy}\lvert E_y)$ & -6022.1 & 7548 & 27140.3 \\
+	 & 2 & $P(L_{ijy}\lvert X_{iy},X_{jy})$ & $P(X_{iy},X_{jy}\lvert E_y)$ & -5547.9 & 7548 & 26191.8 \\
+	 & 3 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy}\lvert E_y)$ & -5364.0 & 12580 & 35888.0 \\
+	 & 4 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy})$ & -5998.4 & 8806 & 30287.2 \\
+	 & 5 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})P(X_{jy})$ & -6636.1 & 7548 & 27092.7 \\
+	 & 6 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}\lvert E_y)P(X_{jy}\lvert E_y)$ & -6002.9 & 18870 & 49745.7 \\ \hline
+	Galler-Parasitoid & 1 & $P(L_{ijy})$ & $P(X_{iy},X_{jy}\lvert E_y)$ & -22068.1 & 19206 & 82548.2 \\
+	 & 2 & $P(L_{ijy} \lvert  X_{iy}, X_{jy})$ & $P(X_{iy},X_{jy}\lvert E_y)$ & -19504.8 & 19206 & 77421.6 \\
+	 & 3 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy}\lvert E_y)$ & -20217.0 & 32010 & 104454.1 \\
+	 & 4 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy})$ & -19591.3 & 22407 & 77594.5 \\
+	 & 5 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})P(X_{jy})$ & -22491.5 & 19206 & 89796.9 \\
+	 & 6 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}\lvert E_y)P(X_{jy}\lvert E_y)$ & -18936.9 & 48015 & 133903.7 \\
 \hline
@@
 \begin{figure}[ht!]
-\centering\includegraphics[width=1\textwidth]{figures/mw_sampling}
+\centering\includegraphics[width=1\textwidth]{figures/mw_sampling.png}
 \end{figure}
@@
 \begin{figure}[ht!]
-\centering\includegraphics[width=0.6\textwidth]{figures/integrated_niche}
+\centering\includegraphics[width=0.6\textwidth]{figures/integrated_niche.png}
 \end{figure}
@@
 \begin{figure}[ht!]
-\centering\includegraphics[width=0.8\textwidth]{figures/example_pair}
+\centering\includegraphics[width=0.8\textwidth]{figures/example_pair.png}
 \end{figure}
@@
 \begin{figure}[ht!]
-\centering\includegraphics[width=0.8\textwidth]{figures/map_pair}
+\centering\includegraphics[width=0.8\textwidth]{figures/map_pair.png}
 \end{figure}
@@
 \begin{figure}[ht!]
-\centering\includegraphics[width=0.8\textwidth]{figures/map_connectance}
+\centering\includegraphics[width=0.8\textwidth]{figures/map_connectance.png}
 \end{figure}

### 2018-08-30 ms/ms_probaweb_for_conversion.tex

--- 2018-08-30 ms/ms_probaweb.tex
@@
 
-\textbf{Authors:} Dominique Gravel$^{1,2,*}$, Benjamin Baiser$^{3}$, Jennifer
-A. Dunne$^{4}$, Jens-Peter Kopelke$^{5}$, Neo D. Martinez$^{6}$, Tommi
-Nyman$^{7}$, Timothée Poisot$^{2,8}$, Daniel B.
-Stouffer$^{9}$, Jason M. Tylianakis$^{9,10}$, Spencer A. Wood$^{11}$, Tomas Roslin$^{12}$ \\
+\textbf{Authors:} Dominique Gravel (1,2,*), Benjamin Baiser (3), Jennifer
+A. Dunne (4), Jens-Peter Kopelke (5), Neo D. Martinez (6), Tommi
+Nyman (7), Timothée Poisot (2,8), Daniel B.
+Stouffer (9), Jason M. Tylianakis (9,10), Spencer A. Wood (11), Tomas Roslin (12) \\
 
@@
 \begin{equation}
-	\text{P}(X_{iy},X_{jy},L_{ijy}\lvert E_y)
+	\text{P}(X_{iy},X_{jy},L_{ijy}\mid E_y)
 \end{equation}
@@
 \begin{equation}
-	P(X_{iy},X_{jy},L_{ijy}\lvert E_y)=P(X_{iy},X_{jy}\lvert E_y)P(L_{ijy}\lvert X_{iy},X_{jy},E_y)
+	P(X_{iy},X_{jy},L_{ijy}\mid E_y)=P(X_{iy},X_{jy}\mid E_y)P(L_{ijy}\mid X_{iy},X_{jy},E_y)
 \end{equation}
@@
 proposed to represent the occurence of an interaction between species as a
-joint probability event $P(L_{ij}, \mathbf{T}_i, \mathbf{T}_j\lvert E)$, where
+joint probability event $P(L_{ij}, \mathbf{T}_i, \mathbf{T}_j\mid E)$, where
 $\mathbf{T}_i$ and $\mathbf{T}_j$ are trait vectors for species $i$ and $j$
@@
 probability of co-occurrence directly to the environment,
-$P(X_{iy},X_{jy}\lvert E_y)$. In this situation, there are no underlying assumptions
+$P(X_{iy},X_{jy}\mid E_y)$. In this situation, there are no underlying assumptions
 about the ecological processes responsible for co-occurrence. Spatial associations between species could arise
@@
 and the conditional occurrence must be accounted for explicitly,
-$P(X_{iy},X_{jy} \lvert E_y)=P(X_{iy}\lvert E_y,X_{jy})P(X_{jy}\lvert E_y)$. In the latter case,
+$P(X_{iy},X_{jy} \mid E_y)=P(X_{iy}\mid E_y,X_{jy})P(X_{jy}\mid E_y)$. In the latter case,
 species are independent, and only the marginal occurrence must be accounted
-for, $P( X_{ijy}\lvert E_y)=P(X_{iy} \lvert E_y)P(X_{jy} \lvert E_y)$.
+for, $P( X_{ijy}\mid E_y)=P(X_{iy} \mid E_y)P(X_{jy} \mid E_y)$.
 
@@
 local abundance and the local environment. In other words,
-$P(L_{ijy}\lvert X_{iy}=1,X_{jy}=1) = 1$. This approach might be a reasonable
+$P(L_{ijy}\mid X_{iy}=1,X_{jy}=1) = 1$. This approach might be a reasonable
 approximation if the spatial or temporal scale of sampling and inference is so
@@
 Second, ecological interactions could also vary with the environment, so that
-$P(L_{ijy}\lvert E_y)$. Although it is rare to see a conditional representation of
+$P(L_{ijy}\mid E_y)$. Although it is rare to see a conditional representation of
 pairwise ecological interactions, experimental studies have frequently
@@
 directly represents the co-occurrence probability conditional on the local
-environment, $P(X_{iy},X_{jy}\lvert E_y)$ (models are listed in Tables 1 and 2).
+environment, $P(X_{iy},X_{jy}\mid E_y)$ (models are listed in Tables 1 and 2).
 Hence, this model makes no assumption about the mechanisms driving co-
@@
 independent occurrence of species. In this case, we independently fit
-$P(X_{iy} \lvert E_y)$ and $P(X_{jy} \lvert E_y)$, and we then take their product to
+$P(X_{iy} \mid E_y)$ and $P(X_{jy} \mid E_y)$, and we then take their product to
 derive the probability of co-occurrence. This model should be viewed as a null
@@
 Whenever the environment was included as a covariate in the GLM, we considered
-a second-order polynomial term for both temperature and precipitation in
-order to account for optima in environmental conditions. There are
-consequently five parameters for the first model when fitting a given pair of
-species, 10 parameters for the second, and only one for the third model.
+a second-order polynomial term for both temperature and precipitation in order
+to account for optima in environmental conditions. There are consequently five
+parameters for the first model when fitting a given pair of species, 10
+parameters for the second, and only one for the third model.
 
@@
 probability. The first model conditions the interaction probability on the
-local environmental variables, $P(L_{ijy}\lvert X_{iy},X_{jy},E_y)$. Consequently,
+local environmental variables, $P(L_{ijy}\mid X_{iy},X_{jy},E_y)$. Consequently,
 the model was fit to the subset of the data where the two species co-occur.
 The second model fits the interaction probability independently of the local
-environmental variables, $P(L_{ijy}\lvert X_{iy},X_{jy})$. It corresponds to the
+environmental variables, $P(L_{ijy}\mid X_{iy},X_{jy})$. It corresponds to the
 number of times the two species were observed to interact when co-occurring,
@@
 extreme case evaluated only to test the hypothesis that if two species are
-found to interact at least once, then they should interact whenever they co-occur, $P(L_{ijy}\lvert X_{iy},X_{jy})=1$. While not necessarily realistic, this
+found to interact at least once, then they should interact whenever they co-
+occur, $P(L_{ijy}\mid X_{iy},X_{jy})=1$. While not necessarily realistic, this
 model tests an assumption commonly invoked in the representation of local
@@
 predicted probabilities. The joint probability $P(L_{ijy},X_{iy},X_{jy})$ was
-then computed from Eq. 2, and the likelihood of each observation $D_{ijy}$ given the model $\theta$ was computed
-as $\mathcal{L}(D_{ijy}\lvert \theta)=P(L_{ij},X_{iy},X_{jy})$ if an
-interaction was observed, and as $\mathcal{L}(D_{ijy}\lvert \theta) =
-1-P(L_{ijy}, X_{iy}, X_{jy})$ if no interaction was observed. The log-likelihood was summed over the entire dataset to compare the different models
-by AIC. We therefore evaluate the likelihood of all local networks, given the
-model. Not surprisingly, there was a very large number of species pairs for
-which this model could not be computed, as they simply never co-occurred. For
-these pairs, we have no information of the interaction probability, and they
-were consequently removed from the analysis. The log-likelihood reported
-across the entire dataset was therefore summed over all pairs of species observed to co-occur at least once. Interactions between the first (\textit{Salix}) and
-second (gallers) trophic layers and those between the second and third
-(parasitoids) were considered separately. Finally, we used the full model (in
-which both co-occurrence and the interaction are conditional on the
-environment) to interpolate species distributions and interaction
-probabilities across the entire European continent. We reconstructed the
-expected network for each location in a 1 X 1 km grid and computed the
-probabilistic connectance following \citet{Poisot2015c}.
+then computed from Eq. 2, and the likelihood of each observation $D_{ijy}$
+given the model $\theta$ was computed as
+$\mathcal{L}(D_{ijy}\mid \theta)=P(L_{ij},X_{iy},X_{jy})$ if an interaction was
+observed, and as $\mathcal{L}(D_{ijy}\mid \theta) = 1-P(L_{ijy}, X_{iy}, X_{jy})$
+if no interaction was observed. The log-likelihood was summed over the entire
+dataset to compare the different models by AIC. We therefore evaluate the
+likelihood of all local networks, given the model. Not surprisingly, there was
+a very large number of species pairs for which this model could not be
+computed, as they simply never co-occurred. For these pairs, we have no
+information of the interaction probability, and they were consequently removed
+from the analysis. The log-likelihood reported across the entire dataset was
+therefore summed over all pairs of species observed to co-occur at least once.
+Interactions between the first (\textit{Salix}) and second (gallers) trophic
+layers and those between the second and third (parasitoids) were considered
+separately. Finally, we used the full model (in which both co-occurrence and
+the interaction are conditional on the environment) to interpolate species
+distributions and interaction probabilities across the entire European
+continent. We reconstructed the expected network for each location in a 1 X 1
+km grid and computed the probabilistic connectance following
+\citet{Poisot2015c}.
 
@@
 the large-scale drivers of network turnover. The results were highly
-consistent among trophic levels (\textit{Salix}-gallers and
-gallers-parasitoids; Table 3), despite large variability in the fit
-of the models to the different pairs of species. This variability was
-particularly important for the models of interactions given co-occurrence.
-Across all pairs of species, the conditional representation of interactions
-performed (Model 2) better than the marginal one (Model 1); that is,
-interactions did not occur systematically whenever the two species were found
-co-occurring. Hence, in addition to species turnover, the stochastic nature of
-interactions contributes to network variability. In total, we recorded 1,173
-pairs of interactions, only 290 of which occurred more than five times. Out of
-these 290 interactions, 143 were systematically detected whenever the two
-species co-occurred. In the instances when species co-occurred, the two
-environmental variables considered proved relatively poor predictors of their
-interactions (Model 2 vs Model 3). Not surprisingly, for both types of
-interactions (\textit{Salix}-galler and galler-parasitoid), the log-likelihood
-increased when the environment was considered. However, the extra number of
-parameters exceeded the gain in log-likelihood and inflated AIC. Therefore,
-the most parsimonious model excluded the effect of the environment. On the
-basis of log-likelihood only, co-occurrence was non-independent for both
+consistent among trophic levels (\textit{Salix}-gallers and gallers-
+parasitoids; Table 3), despite large variability in the fit of the models to
+the different pairs of species. This variability was particularly important
+for the models of interactions given co-occurrence. Across all pairs of
+species, the conditional representation of interactions performed (Model 2)
+better than the marginal one (Model 1); that is, interactions did not occur
+systematically whenever the two species were found co-occurring. Hence, in
+addition to species turnover, the stochastic nature of interactions
+contributes to network variability. In total, we recorded 1,173 pairs of
+interactions, only 290 of which occurred more than five times. Out of these
+290 interactions, 143 were systematically detected whenever the two species
+co-occurred. In the instances when species co-occurred, the two environmental
+variables considered proved relatively poor predictors of their interactions
+(Model 2 vs Model 3). Not surprisingly, for both types of interactions
+(\textit{Salix}-galler and galler-parasitoid), the log-likelihood increased
+when the environment was considered. However, the extra number of parameters
+exceeded the gain in log-likelihood and inflated AIC. Therefore, the most
+parsimonious model excluded the effect of the environment. On the basis of
+log-likelihood only, co-occurrence was non-independent for both
 \textit{Salix}-galler and galler-parasitoid interactions. Thus, according to
@@
 \citealt{Roininen2005, Nyman2010, Leppanen2014}), but as a net outcome of
-different latitudinal trends across trophic levels, the distribution of co-occurrence and therefore of potential interactions differed between the first
+different latitudinal trends across trophic levels, the distribution of co-
+occurrence and therefore of potential interactions differed between the first
 and second layers of feeding links. The correlation between expected
-\textit{Salix} and galler richness was 0.73, while it was 0.58 between
-gallers and their parasitoids. Therefore, the ratio of herbivores to
-\textit{Salix} species is essentially constant across Europe, whereas each
-herbivore species is potentially attacked by a richer enemy community higher
-latitudes. Consequently, overall connectance peaks in Northern Europe (Fig.
-5).
+\textit{Salix} and galler richness was 0.73, while it was 0.58 between gallers
+and their parasitoids. Therefore, the ratio of herbivores to \textit{Salix}
+species is essentially constant across Europe, whereas each herbivore species
+is potentially attacked by a richer enemy community higher latitudes.
+Consequently, overall connectance peaks in Northern Europe (Fig. 5).
 
@@
 environment, whereas the probability of observing an interaction between the
-two was, given co-occurrence, not significantly so. The interactions were  highly
-uncertain, as only few pairs of species were systematically interacting when
-co-occurring but most not. This applies to the example species
+two was, given co-occurrence, not significantly so. The interactions were
+highly uncertain, as only few pairs of species were systematically interacting
+when co-occurring but most not. This applies to the example species
 \textit{Phyllocolpa prussica} and \textit{Chrysocharis elongata} (Figs. 3 and
@@
 splits into different sources of uncertainty – i.e., the extent to which a
-species at the higher trophic level runs into a species at the lower level co-occurring at the site, the extent to which this interaction is detected by an
+species at the higher trophic level runs into a species at the lower level co-
+occurring at the site, the extent to which this interaction is detected by an
 observer collecting a finite sample, or simply the uncertainty arising from
@@
 (e.g. \citealt{Tylianakis2007}), over environmental gradients
-\citep{Lurgi2012} and in time \citep{Simanonok2014} is accumulating
-rapidly. It is not clear, however, to what extent the turnover of network
-structure is driven by a systematic change in species composition or of
-pairwise interactions \citep{Poisot2012, Poisot2015a}. Our model comparison of
-host-parasite interactions revealed that most of the turnover is driven by
-species-specific responses to the environment, impacting species richness, and
-that co-occurrence was mostly independent. Further, the occurrence of interactions
+\citep{Lurgi2012} and in time \citep{Simanonok2014} is accumulating rapidly.
+It is not clear, however, to what extent the turnover of network structure is
+driven by a systematic change in species composition or of pairwise
+interactions \citep{Poisot2012, Poisot2015a}. Our model comparison of host-
+parasite interactions revealed that most of the turnover is driven by species-
+specific responses to the environment, impacting species richness, and that
+co-occurrence was mostly independent. Further, the occurrence of interactions
 among host and parasite is highly stochastic even when both are present, and
@@
 annual temperature and the precipitation gradient. The lack of detectable
-signal may be due to our choice of covariates. Indeed, a previous study focusing on a subset of the system studied here identified habitat characteristics as the primary drivers of
-interactions \citep{Nyman2015}. New investigations with other systems will
-thus be required to challenge this result. Under all circumstances,
-documenting the relationship between the environment and the occurrence of
-interactions at continental scales is critical for understanding how large-
-scale variation of trophic regulation influences community dynamics and
-ecosystem functioning \citep{Harfoot2014}.
+signal may be due to our choice of covariates. Indeed, a previous study
+focusing on a subset of the system studied here identified habitat
+characteristics as the primary drivers of interactions \citep{Nyman2015}. New
+investigations with other systems will thus be required to challenge this
+result. Under all circumstances, documenting the relationship between the
+environment and the occurrence of interactions at continental scales is
+critical for understanding how large- scale variation of trophic regulation
+influences community dynamics and ecosystem functioning \citep{Harfoot2014}.
 
@@
 $a$ for the interactions would be
-$P(L_{ijx}\lvert X_{ix},X_{ijx})P(L_{ijx}\lvert X_{ix},X_{ijx})$. The same could be
+$P(L_{ijx}\mid X_{ix},X_{ijx})P(L_{ijx}\mid X_{ix},X_{ijx})$. The same could be
 computed for fractions $b$, and therefore the expected beta-diversity for an
@@
 realized niche, and how this applies to our framework. For example, we have
-considered above simply the co-occurrence probability, $P(X_{iy},X_{jy}\lvert E_y)$,
-which could be expanded as $P(X_{iy}\lvert X_{jy},E_y) P(X_{jy}\lvert  E_y )$. After some
-re-arrangement of Eq. 2, the marginal occurrence probability, $P(X_{jy}\lvert E_y
+considered above simply the co-occurrence probability, $P(X_{iy},X_{jy}\mid E_y)$,
+which could be expanded as $P(X_{iy}\mid X_{jy},E_y) P(X_{jy}\mid  E_y )$. After some
+re-arrangement of Eq. 2, the marginal occurrence probability, $P(X_{jy}\mid E_y
 )$, could be considered as a species distribution model taking into account
@@
 represent the occurrence of interactions based on some trait-matching rules
-(given by a function of the type $P(L_{ij})\lvert \mathbf{T}_i, \mathbf{T}_j, E)$)
+(given by a function of the type $P(L_{ij})\mid \mathbf{T}_i, \mathbf{T}_j, E)$)
 and the co-distribution of traits (corresponding to $P(\mathbf{T}_i,
-\mathbf{T}_j\lvert E)$). The key  insight from the formalism proposed by
+\mathbf{T}_j\mid E)$). The key  insight from the formalism proposed by
 \citealt{Gravel2016} is that the co-distribution of traits will impact
@@
 
-%\begin{landscape}
-\begin{table}[]
-\centering
-
-\caption{Example of data used to perform the analysis.
+% %\begin{landscape}
+% \begin{table}[]
+% \centering
+
+% \caption{Example of data used to perform the analysis.
 Traditional species distribution models represent the occurrence of single species as a function of the environment, with models such as $X_i­~Temp$ performed one species after the other.
@@
 
-\begin{tabular}{llllllll}
-\hline
-
-Location & $Sp_i$ & $Sp_j$ & $X_i$ & $X_j$ & $X_{ij}$ & $L_{ij}$ & Av. temp \\ \hline
-Kühkopf 		& Phyllocolpa prussica  & Chrysocharis elongata & 1 & 1 & 1 & 1 &  8.25 \\
-Kühkopf 		& Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 1 & 0 & 0 &  8.25 \\
-Ötztal 			& Phyllocolpa prussica  & Chrysocharis elongata & 0 & 0 & 0 & 0 & -1.50 \\
-Ötztal 			& Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 0 & 0 & 0 & -1.50 \\
-Kilpisjärvi		& Phyllocolpa prussica  & Chrysocharis elongata & 0 & 1 & 0 & 0 & -1.92 \\
-Kilpisjärvi		& Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 1 & 0 & 0 & -1.92 \\
-Wüstensachsen	& Phyllocolpa prussica  & Chrysocharis elongata & 1 & 1 & 1 & 0 &  5.58 \\
-Wüstensachsen	& Phyllocolpa leucapsis & Chrysocharis elongata & 1 & 1 & 1 & 1 &  5.58 \\
-Steinamoen      & Phyllocolpa prussica  & Chrysocharis elongata & 0 & 1 & 0 & 0 &  3.17 \\
-Steinamoen      & Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 1 & 0 & 0 &  3.17 \\
-
-\hline
-\end{tabular}
-\end{table}
-%\end{landscape}
-
-\newpage
-%========================================================%
-\begin{landscape}
-\begin{table}[]
-\centering
-\caption{Summary of model comparison for the interaction between the leaf
-folder \textit{Phyllocolpa prussica}) and the parasitoid \textit{Chrysocharis
-elongata}}. Note that $E$ is a short notation including both temperature and precipitation.
-\begin{tabular}{llllll}
-\hline
-	\# & Metaweb model 						& Co-occurrence model 			& LL 	& npars & AIC \\ \hline
-	1 & $P(L_{ijy})$ 						& $P(X_{iy},X_{jy}\lvert E_y)$ 		& -71.1 & 6 	& 154.2 \\
-	2 & $P(L_{ijy} \lvert  X_{iy}, X_{jy})$ 		& $P(X_{iy},X_{jy}\lvert E_y)$ 		& -65.7 & 6 	& 143.4 \\
-	3 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy}\lvert E_y)$ 		& -65.6 & 10 	& 151.3 \\ \hline
-	4 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy})$ 			& -84.5 & 6 	& 183 \\
-	5 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})P(X_{jy})$ 			& -80.7 & 7 	& 173.4 \\
-	6 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}\lvert E_y)P(X_{jy}\lvert E_y)$ 	& -68.8 & 15 	& 167.6 \\
-\hline
-\end{tabular}
-\end{table}
-\end{landscape}
-
-\newpage
-%========================================================%
-
-\begin{landscape}
-\begin{table}[]
-\centering
-\caption{Summary of model comparison for the interaction across all pairs of \textit{Salix}, gallers and parasitoids.}
-\begin{tabular}{lllllll}
-\hline
-	Interaction & \# & Metaweb model & Co-occurrence model & LL & npars & AIC \\ \hline
-	\textit{Salix}-Galler & 1 & $P(L_{ijy})$ & $P(X_{iy},X_{jy}\lvert E_y)$ & -6022.1 & 7548 & 27140.3 \\
-	 & 2 & $P(L_{ijy}\lvert X_{iy},X_{jy})$ & $P(X_{iy},X_{jy}\lvert E_y)$ & -5547.9 & 7548 & 26191.8 \\
-	 & 3 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy}\lvert E_y)$ & -5364.0 & 12580 & 35888.0 \\
-	 & 4 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy})$ & -5998.4 & 8806 & 30287.2 \\
-	 & 5 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})P(X_{jy})$ & -6636.1 & 7548 & 27092.7 \\
-	 & 6 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}\lvert E_y)P(X_{jy}\lvert E_y)$ & -6002.9 & 18870 & 49745.7 \\ \hline
-	Galler-Parasitoid & 1 & $P(L_{ijy})$ & $P(X_{iy},X_{jy}\lvert E_y)$ & -22068.1 & 19206 & 82548.2 \\
-	 & 2 & $P(L_{ijy} \lvert  X_{iy}, X_{jy})$ & $P(X_{iy},X_{jy}\lvert E_y)$ & -19504.8 & 19206 & 77421.6 \\
-	 & 3 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy}\lvert E_y)$ & -20217.0 & 32010 & 104454.1 \\
-	 & 4 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy})$ & -19591.3 & 22407 & 77594.5 \\
-	 & 5 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})P(X_{jy})$ & -22491.5 & 19206 & 89796.9 \\
-	 & 6 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}\lvert E_y)P(X_{jy}\lvert E_y)$ & -18936.9 & 48015 & 133903.7 \\
-\hline
-\end{tabular}
-\end{table}
-\end{landscape}
+% \begin{tabular}{llllllll}
+% \hline
+
+% Location & $Sp_i$ & $Sp_j$ & $X_i$ & $X_j$ & $X_{ij}$ & $L_{ij}$ & Av. temp \\ \hline
+% Kühkopf 		& Phyllocolpa prussica  & Chrysocharis elongata & 1 & 1 & 1 & 1 &  8.25 \\
+% Kühkopf 		& Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 1 & 0 & 0 &  8.25 \\
+% Ötztal 			& Phyllocolpa prussica  & Chrysocharis elongata & 0 & 0 & 0 & 0 & -1.50 \\
+% Ötztal 			& Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 0 & 0 & 0 & -1.50 \\
+% Kilpisjärvi		& Phyllocolpa prussica  & Chrysocharis elongata & 0 & 1 & 0 & 0 & -1.92 \\
+% Kilpisjärvi		& Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 1 & 0 & 0 & -1.92 \\
+% Wüstensachsen	& Phyllocolpa prussica  & Chrysocharis elongata & 1 & 1 & 1 & 0 &  5.58 \\
+% Wüstensachsen	& Phyllocolpa leucapsis & Chrysocharis elongata & 1 & 1 & 1 & 1 &  5.58 \\
+% Steinamoen      & Phyllocolpa prussica  & Chrysocharis elongata & 0 & 1 & 0 & 0 &  3.17 \\
+% Steinamoen      & Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 1 & 0 & 0 &  3.17 \\
+
+% \hline
+% \end{tabular}
+% \end{table}
+% %\end{landscape}
+
+% \newpage
+% %========================================================%
+% \begin{landscape}
+% \begin{table}[]
+% \centering
+% \caption{Summary of model comparison for the interaction between the leaf
+% folder \textit{Phyllocolpa prussica}) and the parasitoid \textit{Chrysocharis
+% elongata}}. Note that $E$ is a short notation including both temperature and precipitation.
+% \begin{tabular}{llllll}
+% \hline
+% 	\# & Metaweb model 						& Co-occurrence model 			& LL 	& npars & AIC \\ \hline
+% 	1 & $P(L_{ijy})$ 						& $P(X_{iy},X_{jy}\mid E_y)$ 		& -71.1 & 6 	& 154.2 \\
+% 	2 & $P(L_{ijy} \mid  X_{iy}, X_{jy})$ 		& $P(X_{iy},X_{jy}\mid E_y)$ 		& -65.7 & 6 	& 143.4 \\
+% 	3 & $P(L_{ijy} \mid  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy}\mid E_y)$ 		& -65.6 & 10 	& 151.3 \\ \hline
+% 	4 & $P(L_{ijy} \mid  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy})$ 			& -84.5 & 6 	& 183 \\
+% 	5 & $P(L_{ijy} \mid  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})P(X_{jy})$ 			& -80.7 & 7 	& 173.4 \\
+% 	6 & $P(L_{ijy} \mid  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}\mid E_y)P(X_{jy}\mid E_y)$ 	& -68.8 & 15 	& 167.6 \\
+% \hline
+% \end{tabular}
+% \end{table}
+% \end{landscape}
+
+% \newpage
+% %========================================================%
+
+% \begin{landscape}
+% \begin{table}[]
+% \centering
+% \caption{Summary of model comparison for the interaction across all pairs of \textit{Salix}, gallers and parasitoids.}
+% \begin{tabular}{lllllll}
+% \hline
+% 	Interaction & \# & Metaweb model & Co-occurrence model & LL & npars & AIC \\ \hline
+% 	\textit{Salix}-Galler & 1 & $P(L_{ijy})$ & $P(X_{iy},X_{jy}\mid E_y)$ & -6022.1 & 7548 & 27140.3 \\
+% 	 & 2 & $P(L_{ijy}\mid X_{iy},X_{jy})$ & $P(X_{iy},X_{jy}\mid E_y)$ & -5547.9 & 7548 & 26191.8 \\
+% 	 & 3 & $P(L_{ijy} \mid  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy}\mid E_y)$ & -5364.0 & 12580 & 35888.0 \\
+% 	 & 4 & $P(L_{ijy} \mid  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy})$ & -5998.4 & 8806 & 30287.2 \\
+% 	 & 5 & $P(L_{ijy} \mid  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})P(X_{jy})$ & -6636.1 & 7548 & 27092.7 \\
+% 	 & 6 & $P(L_{ijy} \mid  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}\mid E_y)P(X_{jy}\mid E_y)$ & -6002.9 & 18870 & 49745.7 \\ \hline
+% 	Galler-Parasitoid & 1 & $P(L_{ijy})$ & $P(X_{iy},X_{jy}\mid E_y)$ & -22068.1 & 19206 & 82548.2 \\
+% 	 & 2 & $P(L_{ijy} \mid  X_{iy}, X_{jy})$ & $P(X_{iy},X_{jy}\mid E_y)$ & -19504.8 & 19206 & 77421.6 \\
+% 	 & 3 & $P(L_{ijy} \mid  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy}\mid E_y)$ & -20217.0 & 32010 & 104454.1 \\
+% 	 & 4 & $P(L_{ijy} \mid  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy})$ & -19591.3 & 22407 & 77594.5 \\
+% 	 & 5 & $P(L_{ijy} \mid  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})P(X_{jy})$ & -22491.5 & 19206 & 89796.9 \\
+% 	 & 6 & $P(L_{ijy} \mid  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}\mid E_y)P(X_{jy}\mid E_y)$ & -18936.9 & 48015 & 133903.7 \\
+% \hline
+% \end{tabular}
+% \end{table}
+% \end{landscape}
 
@@
 %------------------------
-\subsection*{Figure 1}
-
-\begin{figure}[ht!]
-\centering\includegraphics[width=1\textwidth]{figures/mw_sampling.png}
-\end{figure}
-
-\newpage
-
-%------------------------
-\subsection*{Figure 2}
-
-\begin{figure}[ht!]
-\centering\includegraphics[width=0.6\textwidth]{figures/integrated_niche.png}
-\end{figure}
-
-\newpage
-
-%------------------------
-\subsection*{Figure 3}
-
-\begin{figure}[ht!]
-\centering\includegraphics[width=0.8\textwidth]{figures/example_pair.png}
-\end{figure}
-
-\newpage
-
-%------------------------
-\subsection*{Figure 4}
-
-\begin{figure}[ht!]
-\centering\includegraphics[width=0.8\textwidth]{figures/map_pair.png}
-\end{figure}
-
-\newpage
+% \subsection*{Figure 1}
+
+% \begin{figure}[ht!]
+% \centering\includegraphics[width=1\textwidth]{figures/mw_sampling.png}
+% \end{figure}
+
+% \newpage
+
+% %------------------------
+% \subsection*{Figure 2}
+
+% \begin{figure}[ht!]
+% \centering\includegraphics[width=0.6\textwidth]{figures/integrated_niche.png}
+% \end{figure}
+
+% \newpage
+
+% %------------------------
+% \subsection*{Figure 3}
+
+% \begin{figure}[ht!]
+% \centering\includegraphics[width=0.8\textwidth]{figures/example_pair.png}
+% \end{figure}
+
+% \newpage
+
+% %------------------------
+% \subsection*{Figure 4}
+
+% \begin{figure}[ht!]
+% \centering\includegraphics[width=0.8\textwidth]{figures/map_pair.png}
+% \end{figure}
+
+% \newpage
+
+% % %------------------------
+% % \subsection*{Figure 5}
+
+% % \begin{figure}[ht!]
+% % \centering\includegraphics[width=0.8\textwidth]{figures/mw_holes}
+% % \end{figure}
+
+% % \newpage
 
@@
 % \begin{figure}[ht!]
-% \centering\includegraphics[width=0.8\textwidth]{figures/mw_holes}
+% \centering\includegraphics[width=0.8\textwidth]{figures/map_connectance.png}
 % \end{figure}
@@
 % \newpage
-
-%------------------------
-\subsection*{Figure 5}
-
-\begin{figure}[ht!]
-\centering\includegraphics[width=0.8\textwidth]{figures/map_connectance.png}
-\end{figure}
-
-\newpage
 
